---
title: "PRIMED Workflow for Group-Based Review"
author: "Mikkel H. Vembye"
subtitle: ""
date: "`r Sys.Date()`"
format:
  html: 
    keep-md: true
    self-contained: true
    grid: 
      margin-width: 350px
    code-fold: true
    code-summary: "Show the code"
    toc: true
    toc-location: left
pdf-engine: pdflatex
execute: 
  echo: true
  warning: false
  message: false
knitr:
  opts_chunk: 
    fig.pos: "H"
    fig.retina: 2
    cache: FALSE
    R.options:
      knitr.graphics.auto_pdf: true
      width: 100
      knitr.kable.NA: "-"
      dplyr.summarise.inform: FALSE
      pillar.print_max: 50
reference-location: margin
citation-location: margin
bibliography: bibliography.bib  
---

```{css, echo=FALSE}

.panel-tabset .nav-tabs {
  border-bottom: none;
}

.panel-tabset .nav-tabs .nav-link {
  border: 1px solid #555;
  border-radius: 5px 5px 0 0;
  margin-right: 5px;
  padding: 6px 12px;
  border-bottom: none; 
}

/* Style for the active tab */
.panel-tabset .nav-tabs .nav-link.active {
  background-color: #F5F5F5; 
  border-bottom: 1px solid white; 
}
```

# Introduction 

This document contains the preliminary data analysis for the meta-analyses with dependent effects (PRIMED) in [@Dalgaard2025]. As we conduct separate analyses for reintegration (primary analysis) and mental health (secondary analysis) outcomes, we have divided the tabulation and visualization according to the two types of effect size estimates. In most cases, the main presentation of reintegration outcome data appears in the center column of the document, while the presentation of the mental health outcome data is shown in the right column. Where larger tables or visualizations are required, we have used tabsets to distinguish between reintegration and mental health analyses. To view the mental health presentation, select the 'Mental health' tab. To find the mental helath presentation, press on the 'Mental health' tab. In a few instances, reintegration and mental health outcomes are tabulated and visualized together to provide an overall view of the relationships between these two types of estimates. All packages that we have used to create this document, can be found in the next section. 


## R packages
Below, we present the R package we use in this document. For exact R package versions, see the [Session Information](#session-info) at the bottom of this document. 

```{r set-up}
#| cache: false
#| code-fold: false

# Load packages -----------------------------------------------------------
library(knitr)
library(kableExtra)
library(skimr)
library(janitor)
library(tidyverse)
library(tidyr)
library(metafor)
library(clubSandwich)
library(fastDummies)  
library(ggrepel)
library(ggExtra)
library(ggridges)
library(MetBrewer)
library(GGally)
library(igraph)
library(fastDummies)
library(patchwork)
library(ggh4x)
```

# Data manipulation - prepare data sets

In the following section, we create all the variables that are used in the main analyses of the review. Unfold the below code to see this exact manipulations. 

## Loading data
```{r load-data}
# Loading the needed data for analysis
group_based_dat <- readRDS("Group-based interventions data.RDS") |> 
  # The post-measurement of Empowerment Scale seems flawed for the study by 
  # Barbic et al. 2009 we therefore we exclude it from the analysis
  filter(!(authors == "Barbic et al." & test_name == "The Empowerment Scale")) |> 
  mutate(
    author_year = paste(authors, year),
    study = paste(authors, year),
    study = stringi::stri_trans_general(study, "Latin-ASCII"),
    study = fct_relevel(study, sort)
  ) |> 
 # Remove unused outcomes
 filter(!str_detect(analysis_plan, "Unused"))

```

## Main variable manipulation
Unfold the below code, to find the primary data manipulation for the overall data, including both all reintegrational as well as mental health outcomes. 

```{r primary-data-manipultion}

gb_dat <- 
  group_based_dat |> 
  # Exclude the two binary outcomes
  filter(variable_type != "Binary") |>
  mutate(
    es_id = 1:n(),
    esid = es_id,
    
     # Main covariate adjusted effect cluster adjusted 
    gt_pop = if_else(!is.na(gt_post), gt_post, NA_real_),
    gt_pop = if_else(!is.na(gt_DD), gt_DD, gt_pop),
    gt_pop = if_else(!is.na(gt_adj), gt_adj, gt_pop),
    gt_pop = if_else(!is.na(gt_reg), gt_reg, gt_pop),
    gt_pop = if_else(!is.na(gt_DD_pop), gt_DD_pop, gt_pop),
    gt_pop = if_else(!is.na(gt_adj_pop), gt_adj_pop, gt_pop),
    
    vgt_pop = if_else(!is.na(vgt_post), vgt_post, NA_real_),
    vgt_pop = if_else(!is.na(vgt_DD), vgt_DD, vgt_pop),
    vgt_pop = if_else(!is.na(vgt_adj), vgt_adj, vgt_pop),
    vgt_pop = if_else(!is.na(vgt_reg), vgt_reg, vgt_pop),
    vgt_pop = if_else(!is.na(vgt_DD_pop), vgt_DD_pop, vgt_pop),
    vgt_pop = if_else(!is.na(vgt_adj_pop), vgt_adj_pop, vgt_pop),
    
    Wgt_pop = if_else(!is.na(Wgt_post), Wgt_post, NA_real_),
    Wgt_pop = if_else(!is.na(Wgt_DD), Wgt_DD, Wgt_pop),
    Wgt_pop = if_else(!is.na(Wgt_adj), Wgt_adj, Wgt_pop),
    Wgt_pop = if_else(!is.na(Wgt_reg), Wgt_reg, Wgt_pop),
    Wgt_pop = if_else(!is.na(Wgt_DD_pop), Wgt_DD_pop, Wgt_pop),
    Wgt_pop = if_else(!is.na(Wgt_adj_pop), Wgt_adj_pop, Wgt_pop),
    
    # Main covariate adjusted effect cluster adjusted 
    gt = if_else(!is.na(gt_post), gt_post, NA_real_),
    gt = if_else(!is.na(gt_DD), gt_DD, gt),
    gt = if_else(!is.na(gt_adj), gt_adj, gt),
    gt = if_else(!is.na(gt_reg), gt_reg, gt),
    
    vgt = if_else(!is.na(vgt_post), vgt_post, NA_real_),
    vgt = if_else(!is.na(vgt_DD), vgt_DD, vgt),
    vgt = if_else(!is.na(vgt_adj), vgt_adj, vgt),
    vgt = if_else(!is.na(vgt_reg), vgt_reg, vgt),
    
    Wgt = if_else(!is.na(Wgt_post), Wgt_post, NA_real_),
    Wgt = if_else(!is.na(Wgt_DD), Wgt_DD, Wgt),
    Wgt = if_else(!is.na(Wgt_adj), Wgt_adj, Wgt),
    Wgt = if_else(!is.na(Wgt_reg), Wgt_reg, Wgt),
    
    # Hedges g posttest only, adjusted for clustering
    # Imputing covariate-adjusted estimate when posttest calculation was not possible
    gt_post = if_else(is.na(gt_post) & !is.na(gt_reg), gt_reg, gt_post),
    gt_post = if_else(is.na(gt_post) & !is.na(gt_adj), gt_adj, gt_post),
    gt_post = if_else(is.na(gt_post) & !is.na(gt_DD), gt_DD, gt_post),
    
    vgt_post = if_else(is.na(vgt_post) & !is.na(vgt_reg), vgt_reg, vgt_post),
    vgt_post = if_else(is.na(vgt_post) & !is.na(vgt_adj), vgt_adj, vgt_post),
    vgt_post = if_else(is.na(vgt_post) & !is.na(vgt_DD), vgt_DD, vgt_post),
    
    Wgt_post = if_else(is.na(Wgt_post) & !is.na(Wgt_reg), Wgt_reg, Wgt_post),
    Wgt_post = if_else(is.na(Wgt_post) & !is.na(Wgt_adj), Wgt_adj, Wgt_post),
    Wgt_post = if_else(is.na(Wgt_post) & !is.na(Wgt_DD), Wgt_DD, Wgt_post),
    
    # Hedges' g posttest only, not-adjusted for clustering
    # Imputing covariate-adjusted estimate when posttest calculation was not possible
    g_post = if_else(is.na(g_post) & !is.na(g_reg), g_reg, g_post),
    g_post = if_else(is.na(g_post) & !is.na(g_adj), g_adj, g_post),
    g_post = if_else(is.na(g_post) & !is.na(g_DD), g_DD, g_post),
    
    vg_post = if_else(is.na(vg_post) & !is.na(vg_reg), vg_reg, vg_post),
    vg_post = if_else(is.na(vg_post) & !is.na(vg_adj), vg_adj, vg_post),
    vg_post = if_else(is.na(vg_post) & !is.na(vg_DD), vg_DD, vg_post),
    
    Wg_post = if_else(is.na(Wg_post) & !is.na(Wg_reg), Wg_reg, Wg_post),
    Wg_post = if_else(is.na(Wg_post) & !is.na(Wg_adj), Wg_adj, Wg_post),
    Wg_post = if_else(is.na(Wg_post) & !is.na(Wg_DD), Wg_DD, Wg_post),
    
    # Cohen's d posttest only, not-adjusted for clustering
    # Imputing covariate-adjusted estimate when posttest calculation was not possible
    d_post = if_else(is.na(d_post) & !is.na(d_reg), d_reg, d_post),
    d_post = if_else(is.na(d_post) & !is.na(d_adj), d_adj, d_post),
    d_post = if_else(is.na(d_post) & !is.na(d_DD), d_DD, d_post),
    
    vd_post = if_else(is.na(vd_post) & !is.na(vd_reg), vd_reg, vd_post),
    vd_post = if_else(is.na(vd_post) & !is.na(vd_adj), vd_adj, vd_post),
    vd_post = if_else(is.na(vd_post) & !is.na(vd_DD), vd_DD, vd_post),
    
    Wd_post = if_else(is.na(Wd_post) & !is.na(Wd_reg), Wd_reg, Wd_post),
    Wd_post = if_else(is.na(Wd_post) & !is.na(Wd_adj), Wd_adj, Wd_post),
    Wd_post = if_else(is.na(Wd_post) & !is.na(Wd_DD), Wd_DD, Wd_post),
    
    
    # Covariate adjusted Hedges' g, not cluster adjusted 
    g = if_else(!is.na(g_post), g_post, NA_real_),
    g = if_else(!is.na(g_DD), g_DD, g),
    g = if_else(!is.na(g_adj), g_adj, g),
    g = if_else(!is.na(g_reg), g_reg, g),
    
    vg = if_else(!is.na(vg_post), vg_post, NA_real_),
    vg = if_else(!is.na(vg_DD), vg_DD, vg),
    vg = if_else(!is.na(vg_adj), vg_adj, vg),
    vg = if_else(!is.na(vg_reg), vg_reg, vg),
    
    Wg = if_else(!is.na(Wg_post), Wg_post, NA_real_),
    Wg = if_else(!is.na(Wg_DD), Wg_DD, Wg),
    Wg = if_else(!is.na(Wg_adj), Wg_adj, Wg),
    Wg = if_else(!is.na(Wg_reg), Wg_reg, Wg),
    
    # Covariate-adjusted version of Cohen's d, neither cluster nor small sample adjusted
    d = if_else(!is.na(d_post), d_post, NA_real_),
    d = if_else(!is.na(d_DD), d_DD, d),
    d = if_else(!is.na(d_adj), d_adj, d),
    d = if_else(!is.na(d_reg), d_reg, d),
    
    vd = if_else(!is.na(vd_post), vd_post, NA_real_),
    vd = if_else(!is.na(vd_DD), vd_DD, vd),
    vd = if_else(!is.na(vd_adj), vd_adj, vd),
    vd = if_else(!is.na(vd_reg), vd_reg, vd),
    
    Wd = if_else(!is.na(Wd_post), Wd_post, NA_real_),
    Wd = if_else(!is.na(Wd_DD), Wd_DD, Wd),
    Wd = if_else(!is.na(Wd_adj), Wd_adj, Wd),
    Wd = if_else(!is.na(Wd_reg), Wd_reg, Wd),
    
    inv_sample_size = (1/N_t + 1/N_c),
    
    # ESS = round(4/vgt), # Using cluster bias corrected sampling variance
    
    studyid = if_else(authors == "Gonzalez & Prihoda", 500, studyid), 
    
    trt_id = if_else(str_detect(study, "Schaf") & trt_name == "Relapse Prevention Training", 2, trt_id),
    
    cnt = if_else(cnt == "USA", "US", cnt),
    
    design = if_else(design  == "QES-pretest", "QES", design),
    
    # MHV: Jeg synes ikke det er en god ide at ændre CRCT til RCT. Jeg vil gerne kunne se forskel.  
    # design = ifelse(design  == "CRCT", "RCT", design), 
    
    assessment = if_else(assessment == "Self  assesment", "Self assesment", assessment),
    
    randomization = if_else(randomization == "Simple Block Randomization", "Block randomized",
                           randomization),
    randomization = if_else(randomization == "Simple with permuted blocks, stratified by site",
                           "Stratified randomization", randomization),
   
    randomization = if_else(randomization == "Stratified?",
                           "Stratified randomization", randomization),
   
    randomization = if_else(is.na(randomization) & studyid == 102, 
                            "Stratified randomization", randomization),
   
    randomization = if_else(randomization == "Ratio and block randomized",
                           "Block randomized", randomization),
   
    randomization = if_else(randomization == "Block randomized stratified by site",
                           "Block randomized", randomization),
    
    randomization = if_else(randomization == "Resticted and adapted randomization (i.e. minimization)",
                           "Stratified randomization", randomization),
   
    randomization = if_else(randomization == "Unequal simple randomization",
                           "Block randomized", randomization),
   
    randomization = if_else(randomization == "Within-site basis and unequal allocation ratio",
                           "Stratified randomization", randomization),
    
    trt_type = if_else(trt_type == "Group-based  Cognitive Behavioral Therapy", 
                      "Group based Cognitive Behavioural Therapy", trt_type),
    trt_type = if_else(trt_type == "Group-based Cognitive Behavioral Therapy", 
                      "Group based Cognitive Behavioural Therapy", trt_type),
    trt_type = if_else(trt_type =="Group psychoeducation & Social skill training", 
                      "Group psychoeducation & Social Skill Training", trt_type),
    trt_type = if_else(trt_type =="Group psychoeducation", 
                      "Group Psychoeducation", trt_type),
    trt_type = if_else(trt_type =="Group psychoeducation & Social Skill Training", 
                      "Group Psychoeducation & Social Skill Training", trt_type),
    trt_type = if_else(trt_type =="Education and Illness Management", 
                      "Group Psychoeducation & Social Skill Training", trt_type),
    trt_type = if_else(trt_type =="Illness management", 
                      "Illness Management", trt_type),
    
    sample_factors = if_else(sample_factors =="Older with depression and anxiety", 
                            "Mixed", sample_factors), 
    sample_factors = if_else(sample_factors =="All suffered from severe mental illness", 
                            "Shared Social problem(s)/challenge(s)", sample_factors),
    sample_factors = if_else(sample_factors =="Shared origin and psychological distress", 
                            "Mixed", sample_factors),
    sample_factors = if_else(sample_factors =="persons with major psychiatric problems", 
                            "Shared Social problem(s)/challenge(s)", sample_factors),
    
    analysis_plan = if_else(analysis_plan == "Unused", "Unused outcomes", analysis_plan), 
    analysis_plan = case_match(
      analysis_plan,
      "Hope, Empowerment & Self-efficacy" ~ "Hope, empowerment & self-efficacy",
      "Wellbeing and Quality of Life" ~ "Wellbeing and quality of life",
      "All mental health outcomes" ~ "General mental health",
      "All mental health outcomes/Anxiety" ~ "Anxiety",
      "All mental health outcomes/Depression" ~ "Depression",
      "All mental health outcomes/Symptoms of psychosis" ~ "Symptoms of psychosis",
      "All mental health outcomes/Negative symptoms" ~ "Symptoms of psychosis",
      .default = analysis_plan
    ),
    
    test_type = if_else(test_type == "Clinical administered", "Clinician-rated measure", test_type),
    test_type = if_else(test_type == "Clinical interviews", "Clinician-rated measure", test_type),
    test_type = if_else(test_type == "Self report", "Self-reported", test_type),
    test_type = if_else(test_type == "Self report through clinical interview", "Self-reported", test_type),
    test_type = if_else(test_type == "Self-reported via diagnostic interview", "Self-reported", test_type), 
    
    measure_type = if_else(measure_type == "Pre-post with controls", "Post-intervention", measure_type),
   
    cluster_treatment = if_else(cluster_treatment == "Hierarchical mixed models", "Mixed-model", cluster_treatment),
   
    cluster_treatment = if_else(cluster_treatment == "Multilevel analysis and clustered standard errors", 
                        "Multilevel analysis", cluster_treatment),
   
    rob_tool = if_else(rob_tool == "Rob2", "RoB2", rob_tool),
    rob_tool = if_else(rob_tool == "Rob2 CRCT", "RoB2", rob_tool),
   
    analysis_strategy = if_else(str_detect(study, "Michalak"), "ITT", analysis_strategy),
   
    conventional = if_else(protocol != "Yes", 1, 0),
    prereg_chr = if_else(conventional == 0, "Preregistered", "Not preregistered"),
   
   # For publication/selection/small study bias testing
    Wse = sqrt(Wgt),
    t_i = gt/sqrt(Wgt),
   
   outcome_construct = case_match(
     analysis_plan,
     # Mental health outcomes
     c("General mental health", "Anxiety",
       "Depression", "Symptoms of psychosis") ~ "Mental health outcome",
     .default = "Reintegrational outcome"
   ),
   
   # Changing to numeric vectors
   across(c(age_mean_sample:male_pct_t, sessions_per_week), ~as.numeric(.x)),
   
   # Make weighted mean weighted by the group sample size 
   age_mean = if_else(
     is.na(age_mean_sample), 
     (age_mean_t*N_t + age_mean_c*N_c)/(N_t + N_c), 
     age_mean_sample
    ),
   
   male_pct = if_else(
     is.na(male_pct_sample),
     (male_pct_t*N_t + male_pct_c*N_c)/(N_t + N_c),
     male_pct_sample
   ),
   
   # duration_weeks has extract errors
   duration_in_weeks = time_from_baseline_weeks - time_after_end_intervention_weeks,
   total_number_of_sessions = round(sessions_per_week * duration_in_weeks),
   
   CBT_int = if_else(trt_group == "group-based CBT", "CBT", "Other"), 
   
   QES_design = if_else(design == "QES", "QES", "RCT"),
   
   overall_rob = case_match(
     Overall, 
     c("Serious", "High") ~ "Serious/High",
     c("Some concerns", "Moderate") ~ "Some concerns/Moderate",
     .default = "Low"
    ),
   
   overall_rob = factor(overall_rob, levels = c("Low", "Some concerns/Moderate", "Serious/High")),
   
   across(schizophrenia_or_primary_psychotic_disorder:dissociative_identity_disorder, ~ replace_na(.x, 0))
   
 ) |> 
  rowwise() |> 
  mutate(
    diagnosis = {
      col_ones <- names(
        across(.cols = schizophrenia_or_primary_psychotic_disorder:dissociative_identity_disorder)
        )[unlist(
          c_across(schizophrenia_or_primary_psychotic_disorder:dissociative_identity_disorder)
          ) == 1]
      n_ones <- length(col_ones)
      if (n_ones == 1) col_ones
      else if (n_ones > 1) "mixed"
    }
  ) |> 
  ungroup() |> 
  mutate(
    schizophrenia = if_else(str_detect(diagnosis, "schizophrenia"), "Schizophrenia", "Other")
  ) |> 
  mutate(
    # Used to remove ITT outcomes from Cano-Vindel et al. 2021 and Craigie & Nathan 2009 
    n_analysis_strategies = n_distinct(analysis_strategy),
    .by = study
  ) |> 
  # Removing ITT analyses from Cano-Vindel et al. 2021 and Craigie & Nathan 2009 
  filter(!c(str_detect(study, "Cano|Craigie|Woj") & analysis_strategy == "ITT")) 
```

```{r time-variable-vcalc}
#| eval: false

time_vcalc <- c(
  # Acarturk
  1,2,1,2,1,2,
  # Barbic
  1,1,1,
  # Bond
  1,1, 
  # Baekkelund, 
  1,1,2,2,
  # Cano-Vindel
  rep(c(1:4), each = 10),
  # Craigie & Nathan
  1,1,1,
  # Crawford (multi-treatment)
  rep(c(1,2), each = 2, 4),
  # Druss 2010
  1,1,
  #Druss 2018
  1,1,1,2,2,2,
  # Dyck
  1, 
  # Gestel-Timmermans
  rep(c(1,2), 5),
  # Gatz
  rep(1,5),
  # Gonzalaez
  rep(1,2),
  # Gordon 
  rep(1,4),
  # Gutman
  rep(1,2),
  # Hagen
  rep(1,4),
  # Haslem
  rep(1,3),
  # Hilden
  rep(1,7),
  # Himle
  rep(c(1,2), each = 6),
  #Jacob
  rep(c(1,2), each = 5),
  #James
  rep(1,5),
  # Kanie
  rep(1,4),
  # Lim
  rep(1,6),
  # Llyod-Evans
  rep(1,4),
  # Madigan
  rep(c(1,2), each = 6),
  # McCay 2006
  rep(1,4),
  # McCay 2007
  rep(1,3),
  # Michalak (multi-treatment)
  rep(1,14),
  # Morley 
  rep(1,4),
  # Morton
  rep(1,5),
  # Patterson
  rep(c(1,2), each = 5),
  # Popolo
  rep(1,2),
  # Rabenstein
  rep(1,3),
  # Rosenblum 
  rep(1,4),
  # Russinova 
  rep(c(1,2), each = 5),
  # Rusch
  rep(c(1,2), each = 6),
  # Sacks
  rep(1,5),
  # Sajatovic
  rep(c(1:3), each = 3),
  # Saloheimo
  1, 
  # Schrank
  rep(1,6),
  # Schafer (multi-treatment)
  rep(c(2,3,1), each = 2, 6),
  # Somers
  rep(1,5),
  # Tjaden
  rep(c(1,2), each = 4),
  # Valiente 
  rep(1,16),
  # Volpe
  rep(1,4),
  # Wojtalik 
  rep(1,2),
  #Wuthrich
  rep(1,4),
  # Smith 
  rep(1,3)
) 

gb_dat$time <- time_vcalc

```


## Creating primary and secondary data

Below, we separate the data by reintegrational (primary analysis) and mental health outcomes (secondary analyses)

::: {.panel-tabset}
## Reintegration data

A general overview of the main data, we use for analyses of reintegrational outcomes can be found in the scroll box below.

```{r reint-data}
#| tbl-cap: "Data with reintegration outcomes."
#| tbl-cap-location: top
#| label: tbl-reint-dat

reintegration_dat <- 
  gb_dat |> 
  filter(outcome_construct == "Reintegrational outcome") 

saveRDS(reintegration_dat, file = "reintegration_dat.rds")

reint_overview <- 
  reintegration_dat |> 
  select(
    study, eppi_id, esid, N_t, N_c, N_total, inv_sample_size, gt_pop, vgt_pop, Wgt_pop, gt, vgt, Wgt, Wse, 
    prereg_chr, conventional, analysis_plan, Overall, D5, D7, timing
  )

reint_overview |> 
  mutate(
    p_val = 2 * ( 1 - pnorm( abs(gt_pop) / sqrt(vgt_pop) ) )
  ) |> 
  select(
    `Authors (year)` = study, N_t, N_c,
    `Outcome construct` = analysis_plan, gt_pop, vgt_pop, Wgt, Wse, p_val, 
    `No protocol` = conventional, `Overall RoB` = Overall
  ) |> 
  kable(digits=3)  |> 
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    font_size = 10
  ) |> 
  scroll_box(width = "100%", height = "600px", fixed_thead = TRUE)
```

## Mental health data

A general overview of the main data, we use for analyses of mental health outcomes can be found the scroll box  below.

```{r mental-data}
#| tbl-cap: "Data with mental health outcomes."
#| tbl-cap-location: top
#| label: tbl-mental-dat


mental_health_dat <- 
  gb_dat |> 
  filter(outcome_construct == "Mental health outcome") 

saveRDS(mental_health_dat, file = "mental_health_dat.rds")

mental_overview_dat <- 
  mental_health_dat |> 
  select(
    study, eppi_id, esid, N_t, N_c, N_total, inv_sample_size, gt_pop, vgt_pop, Wgt_pop, gt, vgt, Wgt, Wse, 
    prereg_chr, conventional, analysis_plan, Overall, D5, D7, timing
  )

mental_overview_dat |> 
  mutate(
    p_val = 2 * ( 1 - pnorm( abs(gt_pop) / sqrt(vgt_pop) ) )
  ) |> 
  select(
    `Authors (year)` = study, N_t, N_c,
    `Outcome construct` = analysis_plan, gt_pop, vgt_pop, Wgt, Wse, p_val, 
    `No protocol` = conventional, `Overall RoB` = Overall
  ) |> 
  kable(digits=3)  |> 
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    font_size = 10
  ) |> 
  scroll_box(width = "100%", height = "300px", fixed_thead = TRUE)
```


:::

# Risk of bias

In this section, we present the main risk og bias (RoB) visualizations. 

::: {.callout-note}
Note that in plots where the number of studies appears on the x-axis, some bars differ in length. This occurs because a single study contribute multiple effect size estimates that received different RoB assessments.
:::

## RoB2
```{r rob2-dat}
rho <- 0.8

V_mat <- metafor::vcalc(vi = vgt_pop, cluster = study, obs = esid, data = reintegration_dat, rho = rho) 

rma_res <- 
  metafor::rma.mv(
    gt_pop, 
    V = V_mat,
    random = ~ 1 | study / esid,
    data = reintegration_dat
  )

tau2 <- rma_res$sigma2[1]
omega2<- rma_res$sigma2[2]

reint_rob2_dat <- 
  reintegration_dat |> 
  mutate(
    kj = n(),
    sigma2j = mean(vgt_pop),
    weight = 1 / (kj*tau2 + omega2 + (kj-1)*rho*sigma2j + sigma2j),
    .by = study
  ) |> 
  filter(rob_tool == "RoB2") |> 
  select(
    prereg = prereg_chr, study, D1:D5, Overall, weight
  ) 


rob_sum <-  
  reint_rob2_dat |> 
  pivot_longer(D1:Overall, names_to = "Category", values_to = "Rating") |> 
  mutate(
    Category = factor(
      Category, levels = c(paste0("D", 1:5), "Overall"), 
      labels = c(
        "Bias arising from the randomization process",
        "Bias due to deviations from intended interventions",
        "Bias due to missing outcome data",
        "Bias in measurement of the outcome",
        "Bias in selection of the reported result",
        "Overall risk of bias"
        )
      ),
    
    Rating = case_when(str_detect(Rating, "Some") ~ "Some concerns", .default = Rating),
    
    Rating = factor(Rating, levels = c("Low", "Some concerns", "High"))
    
  ) |> 
  group_by(prereg, Category, Rating, study) |> 
  summarize(
    effects = n(),
    weight = sum(weight),
    .groups = "drop_last"
  ) |> 
  summarise(
    studies = length(unique(study)),
    effects = sum(effects),
    weight = sum(weight),
    .groups = "drop_last"
  ) |> 
  mutate(
    effects_pct = 100 * effects / sum(effects),
    studies_pct = 100 * studies / sum(studies),
    effects_pct_w = weight/sum(weight) * 100,
    studies_w = studies * weight,
    studies_pct_w = studies_w / sum(studies_w) * 100
  ) |> 
  ungroup() 

# Mental health
V_mat_mental <- metafor::vcalc(vi = vgt_pop, cluster = study, obs = esid, data = mental_health_dat, rho = rho) 

rma_res_mental <- 
  metafor::rma.mv(
    gt_pop, 
    V = V_mat_mental,
    random = ~ 1 | study / esid,
    data = mental_health_dat
  )

tau2_mental <- rma_res_mental$sigma2[1]
omega2_mental <- rma_res_mental$sigma2[2]

mental_rob2_dat <- 
  mental_health_dat |> 
  mutate(
    kj = n(),
    sigma2j = mean(vgt_pop),
    weight = 1 / (kj*tau2_mental + omega2_mental + (kj-1)*rho*sigma2j + sigma2j),
    .by = study
  ) |> 
  filter(rob_tool == "RoB2") |> 
  select(
    prereg = prereg_chr, study, D1:D5, Overall, weight
  ) 


rob_sum_mental <-  
  mental_rob2_dat |> 
  pivot_longer(D1:Overall, names_to = "Category", values_to = "Rating") |> 
  mutate(
    Category = factor(
      Category, levels = c(paste0("D", 1:5), "Overall"), 
      labels = c(
        "Bias arising from the randomization process",
        "Bias due to deviations from intended interventions",
        "Bias due to missing outcome data",
        "Bias in measurement of the outcome",
        "Bias in selection of the reported result",
        "Overall risk of bias"
        )
      ),
    
    Rating = case_when(str_detect(Rating, "Some") ~ "Some concerns", .default = Rating),
    
    Rating = factor(Rating, levels = c("Low", "Some concerns", "High"))
    
  ) |> 
  group_by(prereg, Category, Rating, study) |> 
  summarize(
    effects = n(),
    weight = sum(weight),
    .groups = "drop_last"
  ) |> 
  summarise(
    studies = length(unique(study)),
    effects = sum(effects),
    weight = sum(weight),
    .groups = "drop_last"
  ) |> 
  mutate(
    effects_pct = 100 * effects / sum(effects),
    studies_pct = 100 * studies / sum(studies),
    effects_pct_w = weight/sum(weight) * 100,
    studies_w = studies * weight,
    studies_pct_w = studies_w / sum(studies_w) * 100
  ) |> 
  ungroup() 


```
### Overall (Not preregistered vs. preregistered)
::: {.column width="130%"}

::: {.panel-tabset}
### Reintegration

::: {.panel-tabset}
#### Number of studies/effects
```{r rob2-fig-number-reint}
#| label: fig-rob2-reint-raw-number
#| fig-cap: "RoB2 plot for reintegration studies and outcomes across type of registration (raw numbers)"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false
 
rob_pct_studies <- 
  rob_sum |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Study-level"
    ) |> 
  ggplot(aes(x = studies, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(level ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    x = "Number of studies",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "none"
  )  + 
  facetted_pos_scales(
    x = list(
      prereg == "Not preregistered" ~ scale_x_continuous(breaks = seq(0, 16, 2)
      )
    )
  )

rob_pct_effects <- 
  rob_sum |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Outcome-level"
    ) |> 
  ggplot(aes(x = effects, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(level ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    x = "Number of effects",
    y = "",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom",
    strip.text.x = element_blank()
  ) + 
  facetted_pos_scales(
    x = list(
      prereg == "Preregistered" ~ scale_x_continuous(breaks = seq(0, 150, 25)
      )
    )
  )


rob_pct_studies / rob_pct_effects

```


#### Weighted percentage
```{r rob2-weighted}
#| label: fig-rob2-reint-weigthed
#| fig-cap: "RoB2 plot for reintegration studies and outcomes across type of registration (weighted percentage)"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false
 
rob_pct_studies_weight <- 
  rob_sum |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = studies_pct_w, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(level ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "none",
    axis.title.x=element_blank()
  ) 

rob_pct_effects_weight <- 
  rob_sum |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Effects"
    ) |> 
  ggplot(aes(x = effects_pct_w, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(level ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    x = "Weighted percentage",
    y = "",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom",
    strip.text.x = element_blank()
  ) 


rob_pct_studies_weight / rob_pct_effects_weight

```


#### Raw percentage
```{r rob2-unweighted}
#| label: fig-rob2-reint-unweigthed
#| fig-cap: "RoB2 plot for reintegration studies and outcomes across type of registration (unweighted percentage)"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false
 
rob_pct_studies_unweight <- 
  rob_sum |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = studies_pct, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(level ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "none",
    axis.title.x=element_blank()
  ) 

rob_pct_effects_unweight <- 
  rob_sum |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Effects"
    ) |> 
  ggplot(aes(x = effects_pct, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(level ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    x = "Percentage",
    y = "",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom",
    strip.text.x = element_blank()
  ) 


rob_pct_studies_unweight / rob_pct_effects_unweight

```

:::

### Mental health
::: {.panel-tabset}
#### Number of studies/effects
```{r rob2-fig-number-mental}
#| label: fig-rob2-mental-raw-number
#| fig-cap: "RoB2 plot for mental health studies and outcomes across type of registration (raw numbers)"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false
 
rob_pct_studies_mental <- 
  rob_sum_mental |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Study-level"
    ) |> 
  ggplot(aes(x = studies, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(level ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    x = "Number of studies",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "none"
  )  + 
  facetted_pos_scales(
    x = list(
      prereg == "Not preregistered" ~ scale_x_continuous(breaks = seq(0, 16, 2)
      )
    )
  )

rob_pct_effects_mental <- 
  rob_sum_mental |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Outcome-level"
    ) |> 
  ggplot(aes(x = effects, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(level ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    x = "Number of effects",
    y = "",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom",
    strip.text.x = element_blank()
  ) 


rob_pct_studies_mental / rob_pct_effects_mental

```


#### Weighted percentage
```{r rob2-weighted-mental}
#| label: fig-rob2-mental-weigthed
#| fig-cap: "RoB2 plot for mental health studies and outcomes across type of registration (weighted percentage)"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false
 
rob_pct_studies_weight_mental <- 
  rob_sum_mental |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = studies_pct_w, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(level ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "none",
    axis.title.x=element_blank()
  ) 

rob_pct_effects_weight_mental <- 
  rob_sum_mental |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Effects"
    ) |> 
  ggplot(aes(x = effects_pct_w, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(level ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    x = "Weighted percentage",
    y = "",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom",
    strip.text.x = element_blank()
  ) 


rob_pct_studies_weight_mental / rob_pct_effects_weight_mental

```


#### Raw percentage
```{r rob2-unweighted-mental}
#| label: fig-rob2-mental-unweigthed
#| fig-cap: "RoB2 plot for mental health studies and outcomes across type of registration (unweighted percentage)"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false
 
rob_pct_studies_unweight_mental <- 
  rob_sum_mental |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = studies_pct, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(level ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "none",
    axis.title.x=element_blank()
  ) 

rob_pct_effects_unweight <- 
  rob_sum_mental |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Effects"
    ) |> 
  ggplot(aes(x = effects_pct, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(level ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    x = "Percentage",
    y = "",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom",
    strip.text.x = element_blank()
  ) 


rob_pct_studies_unweight / rob_pct_effects_unweight



```


:::

:::

:::


### Subgrouped risk of bias plots 
```{r rob2-dat-subgroup}

reint_rob2_subgrp_dat <- 
  reintegration_dat |> 
  mutate(
    kj = n(),
    sigma2j = mean(vgt_pop),
    weight = 1 / (kj*tau2 + omega2 + (kj-1)*rho*sigma2j + sigma2j),
    .by = study
  ) |> 
  filter(rob_tool == "RoB2" & str_detect(analysis_plan, "Alco|Well|Hope|Social")) |> 
  select(
    outcome = analysis_plan, prereg = prereg_chr, study, D1:D5, Overall, weight
  ) |> 
  mutate(
    outcome = case_match(
      outcome,
      "Alcohol and drug abuse/misuse" ~ "Alcohol/drugs",
      "Hope, empowerment & self-efficacy" ~ "Hope/empower",
      "Social functioning (degree of impairment)" ~ "Social function",
      "Wellbeing and quality of life" ~ "Wellbeing/QoL"
    )
  )


rob_sum_subgrp <-  
  reint_rob2_subgrp_dat |> 
  pivot_longer(D1:Overall, names_to = "Category", values_to = "Rating") |> 
  mutate(
    Category = factor(
      Category, levels = c(paste0("D", 1:5), "Overall"), 
      labels = c(
        "Bias arising from the randomization process",
        "Bias due to deviations from intended interventions",
        "Bias due to missing outcome data",
        "Bias in measurement of the outcome",
        "Bias in selection of the reported result",
        "Overall risk of bias"
        )
      ),
    
    Rating = case_when(str_detect(Rating, "Some") ~ "Some concerns", .default = Rating),
    
    Rating = factor(Rating, levels = c("Low", "Some concerns", "High"))
    
  ) |> 
  group_by(prereg, outcome, Category, Rating, study) |> 
  summarize(
    effects = n(),
    weight = sum(weight),
    .groups = "drop_last"
  ) |> 
  summarise(
    studies = length(unique(study)),
    effects = sum(effects),
    weight = sum(weight),
    .groups = "drop_last"
  ) |> 
  mutate(
    effects_pct = 100 * effects / sum(effects),
    studies_pct = 100 * studies / sum(studies),
    effects_pct_w = weight/sum(weight) * 100,
    studies_w = studies * weight,
    studies_pct_w = studies_w / sum(studies_w) * 100
  ) |> 
  ungroup() 

# Mental health
mental_rob2_subgrp_dat <- 
  mental_health_dat |> 
  mutate(
    kj = n(),
    sigma2j = mean(vgt_pop),
    weight = 1 / (kj*tau2 + omega2 + (kj-1)*rho*sigma2j + sigma2j),
    .by = study
  ) |> 
  filter(rob_tool == "RoB2") |> 
  select(
    outcome = analysis_plan, prereg = prereg_chr, study, D1:D5, Overall, weight
  ) |> 
  mutate(
    outcome = factor(
      outcome, 
      levels = c("Anxiety", "Depression", "General mental health", "Symptoms of psychosis")
    )
  )


rob_sum_subgrp_mental <-  
  mental_rob2_subgrp_dat |> 
  pivot_longer(D1:Overall, names_to = "Category", values_to = "Rating") |> 
  mutate(
    Category = factor(
      Category, levels = c(paste0("D", 1:5), "Overall"), 
      labels = c(
        "Bias arising from the randomization process",
        "Bias due to deviations from intended interventions",
        "Bias due to missing outcome data",
        "Bias in measurement of the outcome",
        "Bias in selection of the reported result",
        "Overall risk of bias"
        )
      ),
    
    Rating = case_when(str_detect(Rating, "Some") ~ "Some concerns", .default = Rating),
    
    Rating = factor(Rating, levels = c("Low", "Some concerns", "High"))
    
  ) |> 
  group_by(prereg, outcome, Category, Rating, study) |> 
  summarize(
    effects = n(),
    weight = sum(weight),
    .groups = "drop_last"
  ) |> 
  summarise(
    studies = length(unique(study)),
    effects = sum(effects),
    weight = sum(weight),
    .groups = "drop_last"
  ) |> 
  mutate(
    effects_pct = 100 * effects / sum(effects),
    studies_pct = 100 * studies / sum(studies),
    effects_pct_w = weight/sum(weight) * 100,
    studies_w = studies * weight,
    studies_pct_w = studies_w / sum(studies_w) * 100
  ) |> 
  ungroup() 


```

::: {.columns}

::: {.column width="130%"}

::: {.panel-tabset}
### Reintegration

::: {.panel-tabset}
#### Study-level

::: {.panel-tabset}
#### Number of studies
```{r rob2-subgroup-n-studies}
#| label: fig-rob2-reint-n-studies-subgroup
#| fig-cap: "RoB2 plot for reintegration studies and outcomes by type of registration and outcome (number of studies)"
#| fig.width: 9
#| fig.height: 10
#| fig.retina: 2
#| message: false
 
rob_studies_subgrp <- 
  rob_sum_subgrp |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = studies, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_nested_wrap(outcome ~ prereg, scales = "free_x", ncol = 2) + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    x = "Number of studies",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  )  + 
  facetted_pos_scales(
    x = list(
      prereg == "Not preregistered" & outcome == "Alcohol/drugs" ~ scale_x_continuous(breaks = seq(0, 2, 1)),
      prereg == "Preregistered" & outcome == "Wellbeing/QoL" ~ scale_x_continuous(breaks = seq(0, 14, 2)),
      prereg == "Preregistered" & outcome == "Social function" ~ scale_x_continuous(breaks = seq(0, 10, 2))
    )
  )

rob_studies_subgrp

```
#### Weighted percentage of studies
```{r rob2-subgroup-studies-weighted}
#| label: fig-rob2-reint-weigthed-subgroup
#| fig-cap: "RoB2 plot for reintegration studies and outcomes by type of registration and outcome (weighted percentage of studies)"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false
 
# Weigthed percent
rob_weight_pct_studies_subgrp <- 
  rob_sum_subgrp |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = studies_pct_w, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid2(outcome ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    x = "Weighted percentage of studies",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  ) 

rob_weight_pct_studies_subgrp

```

#### Unweighted percentage of studies
```{r rob2-subgroup-studies-unweight}
#| label: fig-rob2-reint-unweigthed-subgroup
#| fig-cap: "RoB2 plot for reintegration studies and outcomes by type of registration and outcome (unweighted percentage of studies)"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false

# unweigthed percent
rob_unweight_pct_studies_subgrp <- 
  rob_sum_subgrp |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = studies_pct, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid2(outcome ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    x = "Percentage of studies",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  ) 

rob_unweight_pct_studies_subgrp
```
:::

#### Outcome-level
::: {.panel-tabset}
#### Number of effects
```{r rob2-subgroup-n-effects}
#| label: fig-rob2-reint-n-effects-subgroup
#| fig-cap: "RoB2 plot for reintegration studies and outcomes by type of registration and outcome (number of effects)"
#| fig.width: 9
#| fig.height: 10
#| fig.retina: 2
#| message: false
 
rob_effects_subgrp <- 
  rob_sum_subgrp |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Effects"
    ) |> 
  ggplot(aes(x = effects, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_nested_wrap(outcome ~ prereg, scales = "free_x", ncol = 2) + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    x = "Number of effects",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  )  + 
  facetted_pos_scales(
    x = list(
      prereg == "Not preregistered" & outcome == "Hope/empower" ~ scale_x_continuous(breaks = seq(0, 12, 2)),
      prereg == "Preregistered" & outcome == "Hope/empower" ~ scale_x_continuous(breaks = seq(0, 20, 5)),
      prereg == "Not preregistered" & outcome == "Social function" ~ scale_x_continuous(breaks = seq(0, 10, 2)),
      prereg == "Preregistered" & outcome == "Social function" ~ scale_x_continuous(breaks = seq(0, 40, 10)),
      prereg == "Not preregistered" & outcome == "Wellbeing/QoL" ~ scale_x_continuous(breaks = seq(0, 10, 2))
    )
  )

rob_effects_subgrp

```
#### Weighted percentage of effects
```{r rob2-subgroup-effects-weighted}
#| label: fig-rob2-reint-weigthed-effects-subgroup
#| fig-cap: "RoB2 plot for reintegration studies and outcomes by type of registration and outcome (weighted percentage of effects)"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false
 
# Weigthed percent
rob_weight_pct_effects_subgrp <- 
  rob_sum_subgrp |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Effects"
    ) |> 
  ggplot(aes(x = effects_pct_w, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid2(outcome ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    x = "Weighted percentage of effects",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  ) 

rob_weight_pct_effects_subgrp

```

#### Unweighted percentage of effects
```{r rob2-subgroup-effects-unweight}
#| label: fig-rob2-reint-unweigthed-effects-subgroup
#| fig-cap: "RoB2 plot for reintegration studies and outcomes by type of registration and outcome (unweighted percentage of effects)"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false

# unweigthed percent
rob_unweight_pct_effects_subgrp <- 
  rob_sum_subgrp |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = effects_pct, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid2(outcome ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    x = "Percentage of effects",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  ) 

rob_unweight_pct_effects_subgrp
```
:::

:::

### Mental health

::: {.panel-tabset}
#### Study-level

::: {.panel-tabset}
#### Number of studies
```{r rob2-subgroup-n-studies-mental}
#| label: fig-rob2-mental-n-studies-subgroup
#| fig-cap: "RoB2 plot for mental studies and outcomes by type of registration and outcome (number of studies)"
#| fig.width: 9
#| fig.height: 10
#| fig.retina: 2
#| message: false
 
rob_studies_subgrp_mental <- 
  rob_sum_subgrp_mental |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = studies, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_nested_wrap(outcome ~ prereg, scales = "free_x", ncol = 2) + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    x = "Number of studies",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  )  + 
  facetted_pos_scales(
    x = list(
      prereg == "Not preregistered" & outcome == "Anxiety" ~ scale_x_continuous(breaks = seq(0, 2, 1)),
      prereg == "Preregistered" & outcome == "Depression" ~ scale_x_continuous(breaks = seq(0, 10, 2)),
      prereg == "Not preregistered" & outcome == "General mental health" ~ scale_x_continuous(breaks = seq(0, 10, 2)),
      prereg == "Preregistered" & outcome == "Symptoms of psychosis" ~ scale_x_continuous(breaks = seq(0, 2, 1))
    )
  )

rob_studies_subgrp_mental

```
#### Weighted percentage of studies
```{r rob2-subgroup-studies-weighted-mental}
#| label: fig-rob2-mental-weigthed-subgroup
#| fig-cap: "RoB2 plot for mental health studies and outcomes by type of registration and outcome (weighted percentage of studies)"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false
 
# Weigthed percent
rob_weight_pct_studies_subgrp_mental <- 
  rob_sum_subgrp_mental |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = studies_pct_w, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid2(outcome ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    x = "Weighted percentage of studies",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  ) 

rob_weight_pct_studies_subgrp_mental

```

#### Unweighted percentage of studies
```{r rob2-subgroup-studies-unweight-mental}
#| label: fig-rob2-mental-unweigthed-subgroup
#| fig-cap: "RoB2 plot for mental health studies and outcomes by type of registration and outcome (unweighted percentage of studies)"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false

# unweigthed percent
rob_unweight_pct_studies_subgrp_mental <- 
  rob_sum_subgrp_mental |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = studies_pct, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid2(outcome ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    x = "Percentage of studies",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  ) 

rob_unweight_pct_studies_subgrp_mental
```
:::

#### Outcome-level
::: {.panel-tabset}
#### Number of effects
```{r rob2-subgroup-n-effects-mental}
#| label: fig-rob2-mental-n-effects-subgroup
#| fig-cap: "RoB2 plot for mental studies and outcomes by type of registration and outcome (number of effects)"
#| fig.width: 9
#| fig.height: 10
#| fig.retina: 2
#| message: false
 
rob_effects_subgrp_mental <- 
  rob_sum_subgrp_mental |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Effects"
    ) |> 
  ggplot(aes(x = effects, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_nested_wrap(outcome ~ prereg, scales = "free_x", ncol = 2) + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    x = "Number of effects",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  )  + 
  facetted_pos_scales(
    x = list(
      prereg == "Not preregistered" & outcome == "Anxiety" ~ scale_x_continuous(breaks = seq(0, 2, 1)),
      prereg == "Preregistered" & outcome == "Anxiety" ~ scale_x_continuous(breaks = seq(0, 10, 2)),
      prereg == "Not preregistered" & outcome == "Depression" ~ scale_x_continuous(breaks = seq(0, 10, 2)),
      prereg == "Not preregistered" & outcome == "Symptoms of psychosis" ~ scale_x_continuous(breaks = seq(0, 10, 2))
    )
  )

rob_effects_subgrp_mental

```
#### Weighted percentage of effects
```{r rob2-subgroup-effects-weighted-mental}
#| label: fig-rob2-mental-weigthed-effects-subgroup
#| fig-cap: "RoB2 plot for mental health studies and outcomes by type of registration and outcome (weighted percentage of effects)"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false
 
# Weigthed percent
rob_weight_pct_effects_subgrp_mental <- 
  rob_sum_subgrp_mental |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Effects"
    ) |> 
  ggplot(aes(x = effects_pct_w, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid2(outcome ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    x = "Weighted percentage of effects",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  ) 

rob_weight_pct_effects_subgrp_mental

```

#### Unweighted percentage of effects
```{r rob2-subgroup-effects-unweight-mental}
#| label: fig-rob2-mental-unweigthed-effects-subgroup
#| fig-cap: "RoB2 plot for mental health studies and outcomes by type of registration and outcome (unweighted percentage of effects)"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false

# unweigthed percent
rob_unweight_pct_effects_subgrp_mental <- 
  rob_sum_subgrp_mental |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = effects_pct, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid2(outcome ~ prereg, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Some concerns" = "lightgoldenrodyellow", "High" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of the outcome",
      "Bias due to missing outcome data",
      "Bias due to deviations from intended interventions",
      "Bias arising from the randomization process"
    )
  ) +
  labs(
    y = "",
    x = "Percentage of effects",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  ) 

rob_unweight_pct_effects_subgrp_mental
```
:::

:::

:::

:::

:::

## ROBINS-I

```{r ROBINS-I-dat}

reint_robinsi_dat <- 
  reintegration_dat |> 
  mutate(
    kj = n(),
    sigma2j = mean(vgt_pop),
    weight = 1 / (kj*tau2 + omega2 + (kj-1)*rho*sigma2j + sigma2j),
    .by = study
  ) |> 
  filter(rob_tool == "ROBINS-I") |> 
  select(
    prereg = prereg_chr, study, D1:Overall, weight
  ) 


robinsi_sum <-  
  reint_robinsi_dat |> 
  pivot_longer(D1:Overall, names_to = "Category", values_to = "Rating") |> 
  mutate(
    Category = factor(
      Category, levels = c(paste0("D", 1:7), "Overall"), 
      labels = c(
        "Bias due to confounding",
        "Bias due to selection of participants",
        "Bias in classification of interventions",
        "Bias due to deviations from intended interventions",
        "Bias due to missing data",
        "Bias in measurement of outcomes",
        "Bias in selection of the reported result",
        "Overall risk of bias"
        )
      ),
    
    Rating = factor(Rating, levels = c("Low", "Moderate", "Serious"))
    
  ) |> 
  group_by(Category, Rating, study) |> 
  summarize(
    effects = n(),
    weight = sum(weight),
    .groups = "drop_last"
  ) |> 
  summarise(
    studies = length(unique(study)),
    effects = sum(effects),
    weight = sum(weight),
    .groups = "drop_last"
  ) |> 
  mutate(
    effects_pct = 100 * effects / sum(effects),
    studies_pct = 100 * studies / sum(studies),
    effects_pct_w = weight/sum(weight) * 100,
    studies_w = studies * weight,
    studies_pct_w = studies_w / sum(studies_w) * 100
  ) |> 
  ungroup() 

# Mental health
mental_robinsi_dat <- 
  mental_health_dat |> 
  mutate(
    kj = n(),
    sigma2j = mean(vgt_pop),
    weight = 1 / (kj*tau2 + omega2 + (kj-1)*rho*sigma2j + sigma2j),
    .by = study
  ) |> 
  filter(rob_tool == "ROBINS-I") |> 
  select(
    prereg = prereg_chr, study, D1:Overall, weight
  ) 


robinsi_sum_mental <-  
  mental_robinsi_dat |> 
  pivot_longer(D1:Overall, names_to = "Category", values_to = "Rating") |> 
  mutate(
    Category = factor(
      Category, levels = c(paste0("D", 1:7), "Overall"), 
      labels = c(
        "Bias due to confounding",
        "Bias due to selection of participants",
        "Bias in classification of interventions",
        "Bias due to deviations from intended interventions",
        "Bias due to missing data",
        "Bias in measurement of outcomes",
        "Bias in selection of the reported result",
        "Overall risk of bias"
        )
      ),
    
    Rating = factor(Rating, levels = c("Low", "Moderate", "Serious"))
    
  ) |> 
  group_by(Category, Rating, study) |> 
  summarize(
    effects = n(),
    weight = sum(weight),
    .groups = "drop_last"
  ) |> 
  summarise(
    studies = length(unique(study)),
    effects = sum(effects),
    weight = sum(weight),
    .groups = "drop_last"
  ) |> 
  mutate(
    effects_pct = 100 * effects / sum(effects),
    studies_pct = 100 * studies / sum(studies),
    effects_pct_w = weight/sum(weight) * 100,
    studies_w = studies * weight,
    studies_pct_w = studies_w / sum(studies_w) * 100
  ) |> 
  ungroup() 

```

::: {.column width="130%"}

::: {.panel-tabset}
### Reintegration

::: {.panel-tabset}
### Raw numbers
```{r robins-i-raw}
#| label: fig-rob2-robins-i-raw
#| fig-cap: "ROBINS-I plot for reintegration QES studies and outcomes (raw number)"
#| fig.width: 12
#| fig.height: 5
#| fig.retina: 2
#| message: false
 
robin_studies <- 
  robinsi_sum |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = studies, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(~ level, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Moderate" = "lightgoldenrodyellow", "Serious" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of outcomes",
      "Bias due to missing data",
      "Bias due to deviations from intended interventions",
      "Bias in classification of interventions",
      "Bias due to selection of participants",
      "Bias due to confounding"
    )
  ) +
  labs(
    y = "",
    x = "Raw number",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  ) 

robin_effects <- 
  robinsi_sum  |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Effects"
    ) |> 
  ggplot(aes(x = effects, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(~ level, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Moderate" = "lightgoldenrodyellow", "Serious" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of outcomes",
      "Bias due to missing data",
      "Bias due to deviations from intended interventions",
      "Bias in classification of interventions",
      "Bias due to selection of participants",
      "Bias due to confounding"
    )
  ) +
  labs(
    y = "",
    x = "Raw number",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom",
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) 


(robin_studies + robin_effects) +
  plot_layout(guides = "collect", axis_titles = "collect") & theme(legend.position = 'bottom') 

```
### Weighted percentage
```{r robins-i-weighted}
#| label: fig-rob2-robins-i-weigthed
#| fig-cap: "ROBINS-I plot for reintegration QES studies and outcomes (weighted percentage)"
#| fig.width: 12
#| fig.height: 5
#| fig.retina: 2
#| message: false
 
robin_pct_studies_weight <- 
  robinsi_sum |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = studies_pct_w, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(~ level, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Moderate" = "lightgoldenrodyellow", "Serious" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of outcomes",
      "Bias due to missing data",
      "Bias due to deviations from intended interventions",
      "Bias in classification of interventions",
      "Bias due to selection of participants",
      "Bias due to confounding"
    )
  ) +
  labs(
    y = "",
    x = "Weighted percentage",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  ) 

robin_pct_effects_weight <- 
  robinsi_sum  |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "% Effects"
    ) |> 
  ggplot(aes(x = effects_pct_w, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(~ level, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Moderate" = "lightgoldenrodyellow", "Serious" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of outcomes",
      "Bias due to missing data",
      "Bias due to deviations from intended interventions",
      "Bias in classification of interventions",
      "Bias due to selection of participants",
      "Bias due to confounding"
    )
  ) +
  labs(
    y = "",
    x = "Weighted percentage",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom",
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) 


(robin_pct_studies_weight + robin_pct_effects_weight) +
  plot_layout(guides = "collect", axis_titles = "collect") & theme(legend.position = 'bottom') 

```

### Unweighted percentage
```{r robins-i-unweighted}
#| label: fig-rob2-robins-i-unweigthed
#| fig-cap: "ROBINS-I plot for reintegration QES studies and outcomes (unweighted percentage)"
#| fig.width: 12
#| fig.height: 5
#| fig.retina: 2
#| message: false
 
robin_pct_studies_unweight <- 
  robinsi_sum |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = studies_pct, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(~ level, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Moderate" = "lightgoldenrodyellow", "Serious" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of outcomes",
      "Bias due to missing data",
      "Bias due to deviations from intended interventions",
      "Bias in classification of interventions",
      "Bias due to selection of participants",
      "Bias due to confounding"
    )
  ) +
  labs(
    y = "",
    x = "Percentage",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  ) 

robin_pct_effects_unweight <- 
  robinsi_sum  |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Effects"
    ) |> 
  ggplot(aes(x = effects_pct, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(~ level, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Moderate" = "lightgoldenrodyellow", "Serious" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of outcomes",
      "Bias due to missing data",
      "Bias due to deviations from intended interventions",
      "Bias in classification of interventions",
      "Bias due to selection of participants",
      "Bias due to confounding"
    )
  ) +
  labs(
    y = "",
    x = "Percentage",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom",
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) 




(robin_pct_studies_unweight + robin_pct_effects_unweight) +
  plot_layout(guides = "collect", axis_titles = "collect") & theme(legend.position = 'bottom') 


```
:::

### Mental health

::: {.panel-tabset}
### Raw numbers
```{r robins-i-raw-mental}
#| label: fig-rob2-robins-i-raw-mental
#| fig-cap: "ROBINS-I plot for mental health QES studies and outcomes (raw number)"
#| fig.width: 12
#| fig.height: 5
#| fig.retina: 2
#| message: false
 
robin_studies_mental <- 
  robinsi_sum_mental |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = studies, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(~ level, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Moderate" = "lightgoldenrodyellow", "Serious" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of outcomes",
      "Bias due to missing data",
      "Bias due to deviations from intended interventions",
      "Bias in classification of interventions",
      "Bias due to selection of participants",
      "Bias due to confounding"
    )
  ) +
  labs(
    y = "",
    x = "Raw number",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  ) 

robin_effects_mental <- 
  robinsi_sum_mental  |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Effects"
    ) |> 
  ggplot(aes(x = effects, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(~ level, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Moderate" = "lightgoldenrodyellow", "Serious" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of outcomes",
      "Bias due to missing data",
      "Bias due to deviations from intended interventions",
      "Bias in classification of interventions",
      "Bias due to selection of participants",
      "Bias due to confounding"
    )
  ) +
  labs(
    y = "",
    x = "Raw number",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom",
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) 


(robin_studies_mental + robin_effects_mental) +
  plot_layout(guides = "collect", axis_titles = "collect") & theme(legend.position = 'bottom') 

```

### Weighted percentage
```{r robins-i-weighted-mental}
#| label: fig-rob2-robins-i-weigthed-mental
#| fig-cap: "ROBINS-I plot for mental health QES studies and outcomes (weighted percentage)"
#| fig.width: 12
#| fig.height: 5
#| fig.retina: 2
#| message: false
 
robin_pct_studies_weight_mental <- 
  robinsi_sum_mental |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = studies_pct_w, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(~ level, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Moderate" = "lightgoldenrodyellow", "Serious" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of outcomes",
      "Bias due to missing data",
      "Bias due to deviations from intended interventions",
      "Bias in classification of interventions",
      "Bias due to selection of participants",
      "Bias due to confounding"
    )
  ) +
  labs(
    y = "",
    x = "Weighted percentage",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  ) 

robin_pct_effects_weight_mental <- 
  robinsi_sum_mental  |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Effects"
    ) |> 
  ggplot(aes(x = effects_pct_w, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(~ level, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Moderate" = "lightgoldenrodyellow", "Serious" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of outcomes",
      "Bias due to missing data",
      "Bias due to deviations from intended interventions",
      "Bias in classification of interventions",
      "Bias due to selection of participants",
      "Bias due to confounding"
    )
  ) +
  labs(
    y = "",
    x = "Weighted percentage",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom",
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) 


(robin_pct_studies_weight_mental + robin_pct_effects_weight_mental) +
  plot_layout(guides = "collect", axis_titles = "collect") & theme(legend.position = 'bottom') 

```

### Unweighted percentage
```{r robins-i-unweighted-mental}
#| label: fig-rob2-robins-i-unweigthed-mental
#| fig-cap: "ROBINS-I plot for mental health QES studies and outcomes (unweighted percentage)"
#| fig.width: 12
#| fig.height: 5
#| fig.retina: 2
#| message: false
 
robin_pct_studies_unweight_mental <- 
  robinsi_sum_mental |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Studies"
    ) |> 
  ggplot(aes(x = studies_pct, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(~ level, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Moderate" = "lightgoldenrodyellow", "Serious" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of outcomes",
      "Bias due to missing data",
      "Bias due to deviations from intended interventions",
      "Bias in classification of interventions",
      "Bias due to selection of participants",
      "Bias due to confounding"
    )
  ) +
  labs(
    y = "",
    x = "Percentage",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom"
  ) 

robin_pct_effects_unweight_mental <- 
  robinsi_sum_mental  |> 
  mutate(
    Rating = fct_rev(Rating),
    level = "Effects"
    ) |> 
  ggplot(aes(x = effects_pct, y = Category, fill = Rating)) + 
  geom_col(alpha = 0.9) +
  facet_grid(~ level, scales = "free_x") + 
  scale_fill_manual(
    values = c("Low" = "mediumaquamarine", "Moderate" = "lightgoldenrodyellow", "Serious" = "lightcoral")
  ) +
  scale_y_discrete(
    limits = rev,
    labels = c( 
      expression(bold("Overall risk of bias")),
      "Bias in selection of the reported result",
      "Bias in measurement of outcomes",
      "Bias due to missing data",
      "Bias due to deviations from intended interventions",
      "Bias in classification of interventions",
      "Bias due to selection of participants",
      "Bias due to confounding"
    )
  ) +
  labs(
    y = "",
    x = "Percentage",
    fill = "Risk of Bias"
  ) + 
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme_bw() + 
  theme(
    legend.position = "bottom",
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) 




(robin_pct_studies_unweight_mental + robin_pct_effects_unweight_mental) +
  plot_layout(guides = "collect", axis_titles = "collect") & theme(legend.position = 'bottom') 


```
:::

:::

:::

# Descriptives and Dependence Structures

## Timeline

```{r, time-plot}
#| label: fig-time-plot
#| fig-cap: "Number of studies included in meta-analysis by year."
#| fig-width: 12
#| fig-height: 8
#| message: false

# Figure 1: Number of included studies in the meta-analysis by year
G_timeplot <- 
  group_based_dat |> 
  mutate(
    prereg = if_else(
      str_detect(protocol, regex("yes", ignore_case = TRUE)), 
      "Preregistered", "Not preregistered"
    )
  ) |> 
  reframe(year = unique(year), prereg = unique(prereg), .by =  study)

# DONE
timeline_plot <-  ggplot(G_timeplot, aes(x = year, fill = prereg)) + 
  geom_bar(col = "black", alpha = 1, width = 1) +
  scale_x_continuous(breaks = seq(2000, 2022, 1)) + 
  scale_y_continuous(breaks = seq(0, 6.5, 1), limits = c(0, 7), expand = c(0,0)) + 
  theme_bw() + 
  scale_fill_brewer(palette="Paired")+
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    #panel.border = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    axis.line = element_line(colour = "black")
  ) +
  labs(
    x = "Year of publication",
    y = "Number of studies",
  )

timeline_plot

```


## Number effects across effect size metrics 

```{r}
# Number of studies reporting OR
group_based_dat |> 
  summarise(
    n = n(), 
    .by = c(study, effect_size)
  ) |> 
  summarise(
    N_studies = length(effect_size), 
    N_es = sum(n),
    .by = effect_size
  )
```


## Average pre-posttest correlation

::: {.columns}

::: {.column width="95%"}
### Reintegrational outcome
```{r pre-posttest-cor}
reintegration_dat |> 
  filter(
    str_detect(
      ppcor_method, regex("Cal", ignore_case = TRUE), 
    ) |
    str_detect(
      ppcor_method, regex("From study", ignore_case = TRUE), 
    ) 
  ) |> 
  select(contains("ppcor")) |> 
  pull(ppcor) |> 
  mean()
```
:::

::: {.column-margin}
### Mental health
```{r, pre-posttest-cor-mental}
mental_health_dat|> 
  filter(
    str_detect(
      ppcor_method, regex("Cal", ignore_case = TRUE), 
    ) |
    str_detect(
      ppcor_method, regex("From study", ignore_case = TRUE), 
    ) 
  ) |> 
  select(contains("ppcor")) |> 
  pull(ppcor) |> 
  mean()
```
:::

:::

## Number of effect size estimates per study

### Overall per study


```{r es-plot}
#| label: fig-es-hist-per-stud
#| fig-cap: "Distribution of number of effect size estimates per study"
#| fig.width: 6.5
#| fig.height: 7
#| message: false

es_plot_per_study <- 
  gb_dat |>
  arrange(desc(study)) |>
  mutate(study = factor(study, unique(study))) |> 
  ggplot(aes(x = study)) +
  geom_bar(aes(fill = outcome_construct)) +
  scale_y_continuous(breaks = seq(5, 40, by = 5)) + 
  theme_minimal() +
  theme(
    legend.position = "bottom"
  ) +
  coord_flip() +
  labs(
    x = paste0("Study (", n_distinct(gb_dat$study), " studies in total)"), 
    y = "Number of Effect Size Estimates",
    fill = "Outcome construct"
  ) +
  guides(fill = guide_legend(reverse=TRUE))

es_plot_per_study
```


### Across outcome subgroups per study

::: {.columns}

::: {.column width="95%"}

```{r es-plot-reint}
#| label: fig-es-hist-per-stud-reint
#| fig-cap: "Distribution of number of effects per study, by direction of the effects for reintegrational outcomes."
#| fig-width: 12
#| fig-height: 8
#| message: false

reintegration_dat |>
ggplot(aes(y = study, fill = gt_pop >= 0)) + 
geom_bar(data = subset(reintegration_dat, gt_pop >= 0), aes(x = after_stat(count)), stat = "count") + 
geom_bar(data = subset(reintegration_dat, gt_pop < 0), aes(x = -after_stat(count)), stat = "count") + 
theme_minimal() +
scale_x_continuous(labels = abs, breaks = scales::breaks_width(5), limits = c(-10, 30)) +
scale_y_discrete(limits=rev) +
scale_fill_manual(
  values = c(met.brewer("Navajo")[2], met.brewer("Navajo")[4]), 
  labels = c("Negative ES", "Non-negative ES"), 
  name = "Effect Size"
) +
labs(x = "Number of Effect Size Estimates", y = "", title = "Reintegration") +
theme(
    legend.position = "bottom",
    #legend.position.inside = c(0.95, 0.05),
    #legend.justification = c(1, 0),
    legend.background = element_blank(),
    plot.title = element_text(hjust = 0.5) 
  )
```
:::

::: {.column-margin}
```{r es-plot-mental}
#| label: fig-es-hist-per-stud-mental
#| fig-cap: "Distribution of number of effects per study, by direction of the effects for mental health outcomes."
#| fig-height: 8.5
#| message: false

mental_health_dat |>
ggplot(aes(y = study, fill = gt_pop >= 0)) + 
geom_bar(data = subset(mental_health_dat, gt_pop >= 0), aes(x = after_stat(count)), stat = "count") + 
geom_bar(data = subset(mental_health_dat, gt_pop < 0), aes(x = -after_stat(count)), stat = "count") + 
theme_minimal() +
scale_x_continuous(labels = abs, breaks = scales::breaks_width(5), limits = c(-5, 15)) +
scale_y_discrete(limits=rev) +
scale_fill_manual(
  values = c(met.brewer("Navajo")[2], met.brewer("Navajo")[4]), 
  labels = c("Negative ES", "Non-negative ES"), 
  name = "Effect Size"
) +
labs(x = "Number of Effect Size Estimates", y = "", title = "Mental Health") +
theme(
    legend.position = "bottom",
    #legend.position.inside = c(0.95, 0.2),
    #legend.justification = c(1, 0),
    legend.background = element_blank(),
    plot.title = element_text(hjust = 0.5) 
  )
```
:::

:::

### Overall across all studies and outcomes

```{r structure}
# Multi-arms studies
multi_arm_studies <- 
  gb_dat |> 
  filter(trt_id > 1) |> 
  reframe(study = unique(study))
  

# Multi-time-points studies
follow_up_studies <- 
  gb_dat |>
  summarise(
    time_points = length(unique(time_after_end_intervention_weeks)),
    .by = c(study, trt_id, ctr_id)
  ) |>
  filter(time_points > 1)

# Preregistered studies
prereg_studies <- 
  gb_dat |> 
  summarise(
    prereg_chr = unique(prereg_chr),
    n_es = n(),
    .by = study
  ) |> 
  summarise(
    N_studies = n_distinct(study),
    N_es = sum(n_es),
    .by = prereg_chr
  )

study_sample_sizes <- 
  gb_dat |>
  group_by(study, trt_id, ctr_id) |>
  summarise(
    effects = n(),
    participants = max(N_total)
  ) |>
  summarise(
    effects = sum(effects),
    participants = mean(participants),
    ctl_comparisons = n(),
    ctl_arms = paste(ctr_id, collapse = "; ")
  ) |>
  group_by(study, ctl_arms) |>
  summarise(
    effects = sum(effects),
    participants = mean(participants * (1 + ctl_comparisons * (n() - 1) / 2)),
    trt_comparisons = n(),
    trt_arms = paste(trt_id, collapse = "; "),
    ctl_comparisons = mean(ctl_comparisons)
  ) |>
  summarise(
    effects = sum(effects),
    participants = sum(participants),
    trt_comparisons = mean(trt_comparisons),
    ctl_comparisons = sum(ctl_comparisons)
  )

sample_size_summary <-
  study_sample_sizes |>
  summarise(
    studies = n(),
    studies_multiple_tx = sum(trt_comparisons > 1),
    studies_multiple_ctl = sum(ctl_comparisons > 1),
    n_effects = sum(effects),
    mean_effects = mean(effects),
    min_effects = min(effects),
    median_effects = median(effects),
    max_effects = max(effects),
    participants = round(sum(participants))
  ) |> 
  mutate(prereg = prereg_studies$N_studies[1])

n_studies <- sample_size_summary$studies
```

```{r structure-table}
#| tbl-cap: "Data structure for the all data."
#| tbl-cap-location: top
#| label: tbl-es-structure

kable(
  sample_size_summary,
  col.names = c(
    studies = "Studies",
    studies_multiple_tx = "Multi-treatment studies",
    studies_multiple_ctl = "Multi-control studies",
    n_effects = "Effects",
    mean_effects = "Mean",
    min_effects = "Minimum",
    median_effects = "Median",
    max_effects = "Maximum",
    participants = "Participants",
    prereg = "Preregistered studies"
  ),
  digits = 1
) |>
  kable_styling(bootstrap_options = c("striped", "condensed"),
                full_width = FALSE)
```


```{r, sum-es-per-study-plot}
#| label: fig-es-hist
#| fig-cap: "Distribution of number of effect size estimates per study"
#| fig.width: 9
#| fig.height: 7
#| message: false

gb_dat |> 
  summarise(
    es_count = n(),
    .by = study
  ) |>  
  arrange(es_count) |> 
  ggplot(aes(x = es_count)) +
  geom_histogram(binwidth = 0.5, fill = met.brewer("Navajo")[4]) +
  scale_x_continuous(breaks = seq(0, 40, by = 5)) +
  scale_y_continuous(breaks = seq(0, 10, 2)) +
  theme_minimal() +
  labs(x = "Effect Size Estimates per Study", y = "Number of Studies")

```

### Across outcome subgroups 

::: {.columns}

::: {.column width="95%"}

```{r structure-reint}
# Multi-arms studies
multi_arm_studies_reint <- 
  reintegration_dat |> 
  filter(trt_id > 1) |> 
  reframe(study = unique(study))
  

# Multi-time-points studies
follow_up_studies_reint <- 
  reintegration_dat |>
  summarise(
    time_points = length(unique(time_after_end_intervention_weeks)),
    .by = c(study, trt_id, ctr_id)
  ) |>
  filter(time_points > 1)

# Preregistered studies
prereg_studies_reint <- 
  reintegration_dat |> 
  summarise(
    prereg_chr = unique(prereg_chr),
    n_es = n(),
    .by = study
  ) |> 
  summarise(
    N_studies = n_distinct(study),
    N_es = sum(n_es),
    .by = prereg_chr
  )

study_sample_sizes_reint <- 
  reintegration_dat |>
  group_by(study, trt_id, ctr_id) |>
  summarise(
    effects = n(),
    participants = max(N_total)
  ) |>
  summarise(
    effects = sum(effects),
    participants = mean(participants),
    ctl_comparisons = n(),
    ctl_arms = paste(ctr_id, collapse = "; ")
  ) |>
  group_by(study, ctl_arms) |>
  summarise(
    effects = sum(effects),
    participants = mean(participants * (1 + ctl_comparisons * (n() - 1) / 2)),
    trt_comparisons = n(),
    trt_arms = paste(trt_id, collapse = "; "),
    ctl_comparisons = mean(ctl_comparisons)
  ) |>
  summarise(
    effects = sum(effects),
    participants = sum(participants),
    trt_comparisons = mean(trt_comparisons),
    ctl_comparisons = sum(ctl_comparisons)
  )

sample_size_summary_reint <-
  study_sample_sizes_reint |>
  summarise(
    studies = n(),
    studies_multiple_tx = sum(trt_comparisons > 1),
    studies_multiple_ctl = sum(ctl_comparisons > 1),
    n_effects = sum(effects),
    mean_effects = mean(effects),
    min_effects = min(effects),
    median_effects = median(effects),
    max_effects = max(effects),
    participants = round(sum(participants))
  ) |> 
  mutate(prereg = prereg_studies_reint$N_studies[1])

n_studies_reint <- sample_size_summary_reint$studies
```

```{r structure-table-reint}
#| tbl-cap: "Data structure for the reintegrational data."
#| tbl-cap-location: top
#| label: tbl-es-structure-reint

kable(
  sample_size_summary_reint,
  col.names = c(
    studies = "Studies",
    studies_multiple_tx = "Multi-treatment studies",
    studies_multiple_ctl = "Multi-control studies",
    n_effects = "Effects",
    mean_effects = "Mean",
    min_effects = "Minimum",
    median_effects = "Median",
    max_effects = "Maximum",
    participants = "Participants",
    prereg = "Preregistered studies"
  ),
  digits = 1
) |>
  kable_styling(bootstrap_options = c("striped", "condensed"),
                full_width = FALSE)
```
:::

::: {.column-margin}
```{r structure-mental}
# Multi-arms studies
multi_arm_studies_mental <- 
  mental_health_dat |> 
  filter(trt_id > 1) |> 
  reframe(study = unique(study))
  

# Multi-time-points studies
follow_up_studies_mental <- 
  mental_health_dat |>
  summarise(
    time_points = length(unique(time_after_end_intervention_weeks)),
    .by = c(study, trt_id, ctr_id)
  ) |>
  filter(time_points > 1)

# Preregistered studies
prereg_studies_mental <- 
  mental_health_dat |> 
  summarise(
    prereg_chr = unique(prereg_chr),
    n_es = n(),
    .by = study
  ) |> 
  summarise(
    N_studies = n_distinct(study),
    N_es = sum(n_es),
    .by = prereg_chr
  )

study_sample_sizes_mental <- 
  mental_health_dat |>
  group_by(study, trt_id, ctr_id) |>
  summarise(
    effects = n(),
    participants = max(N_total)
  ) |>
  summarise(
    effects = sum(effects),
    participants = mean(participants),
    ctl_comparisons = n(),
    ctl_arms = paste(ctr_id, collapse = "; ")
  ) |>
  group_by(study, ctl_arms) |>
  summarise(
    effects = sum(effects),
    participants = mean(participants * (1 + ctl_comparisons * (n() - 1) / 2)),
    trt_comparisons = n(),
    trt_arms = paste(trt_id, collapse = "; "),
    ctl_comparisons = mean(ctl_comparisons)
  ) |>
  summarise(
    effects = sum(effects),
    participants = sum(participants),
    trt_comparisons = mean(trt_comparisons),
    ctl_comparisons = sum(ctl_comparisons)
  )

sample_size_summary_mental <-
  study_sample_sizes_mental |>
  summarise(
    studies = n(),
    studies_multiple_tx = sum(trt_comparisons > 1),
    studies_multiple_ctl = sum(ctl_comparisons > 1),
    n_effects = sum(effects),
    mean_effects = mean(effects),
    min_effects = min(effects),
    median_effects = median(effects),
    max_effects = max(effects),
    participants = round(sum(participants))
  ) |> 
  mutate(prereg = prereg_studies_mental$N_studies[1])

n_studies_mental <- sample_size_summary_mental$studies
```

```{r structure-table-mental}
#| tbl-cap: "Data structure for the mental health data."
#| tbl-cap-location: top
#| label: tbl-es-structure-mental

kable(
  sample_size_summary_mental,
  col.names = c(
    studies = "Studies",
    studies_multiple_tx = "Multi-treatment studies",
    studies_multiple_ctl = "Multi-control studies",
    n_effects = "Effects",
    mean_effects = "Mean",
    min_effects = "Minimum",
    median_effects = "Median",
    max_effects = "Maximum",
    participants = "Participants",
    prereg = "Preregistered studies"
  ),
  digits = 1
) |>
  kable_styling(bootstrap_options = c("striped", "condensed"),
                full_width = FALSE)
```
:::

:::

::: {.columns}

::: {.column width="95%"}
```{r sum-es-plot-reint}
#| label: fig-es-hist-reint
#| fig-cap: "Distribution of number of effects per study for mental for reintegrational outcomes."
#| fig-width: 9
#| fig-height: 6
#| message: false

reintegration_dat |> 
  summarise(
    es_count = n(),
    .by = study
  ) |>  
  arrange(es_count) |> 
  ggplot(aes(x = es_count)) +
  geom_histogram(binwidth = 0.5, fill = "cornflowerblue") +
  scale_x_continuous(breaks = seq(0, 30, by = 5)) +
  scale_y_continuous(breaks = seq(0, 14, 2), limits = c(0, 14)) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Effect Size Estimates per Study", y = "Number of Studies", title = "Reintegration") +
  expand_limits(x = 30)
```
:::

::: {.column-margin}
```{r es-plot-mental}
#| label: fig-es-hist-mental
#| fig-cap: "Distribution of number of effects per study for mental health outcomes."
#| fig-height: 8
#| message: false

mental_health_dat |> 
  summarise(
    es_count = n(),
    .by = study
  ) |>  
  arrange(es_count) |> 
  ggplot(aes(x = es_count)) +
  geom_histogram(binwidth = 0.5, fill = "gray") +
  scale_x_continuous(breaks = seq(0, 20, by = 5)) +
  scale_y_continuous(breaks = seq(0, 10, 2), limits = c(0, 11)) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Effect Size Estimates per Study", y = "Number of Studies", title = "Mental Health") +
  expand_limits(x = 20)
```
:::

:::

## Data structure by outcome constructs

```{r labeled-cat-hist-ridge-function}
label_cat_hist_ridge <- function(data, n_es, variable, label_map, level_order) {
  require(dplyr)
  require(rlang)
  require(tidyr)
  require(ggplot2)
  require(forcats)
  
  n_es_exp <- enquo(n_es)
  var_exp <- enquo(variable)
  
  data <- data |> 
    mutate(
      !!var_exp := fct_recode(!!var_exp, !!!label_map),
      !!var_exp := fct_relevel(!!var_exp, !!!level_order),
      !!var_exp := fct_rev(!!var_exp)
    ) 
  
  ggplot(data, aes(
    x = !!n_es_exp,
    y = !!var_exp,
    fill = !!var_exp
  )) +
    geom_density_ridges(
      alpha = 1,
      stat = "binline",
      bins = 30,
      scale = 0.7,
      linewidth = 0.1,
      draw_baseline = FALSE
    ) +
    theme_minimal() +
    labs(y = "", x = "Effect Size Estimates per Study") +
    theme(legend.position = "none")
}

```

The following plot shows the effect size estimates distribution within each outcome construct.

::: {.columns}

::: {.column width="95%"}
```{r outcome-construct-ridge-hist}
#| label: fig-outcome-construct-ridge-hist
#| fig-cap: "Distribution of effect size estimates, by reintegrational outcome constructs."
#| fig.width: 9
#| fig.height: 6.5
#| fig.retina: 2
#| message: false

n_es_by_construct <- 
  gb_dat |> 
  filter(str_detect(outcome_construct, "Re")) |> 
  summarise(effects = n(), .by = c(study, analysis_plan)) |> 
  mutate(J = n(), .by = c(analysis_plan)) |> 
  arrange(desc(J)) 

# Used to construct out_label 
#label_dat <- 
#  n_es_by_construct |> 
#  summarise(J = n(), N_es = sum(effects), .by = analysis_plan)


out_label <- c(
  "Wellbeing and quality of life (J = 24, K = 67)" = "Wellbeing and quality of life",
  "Social functioning (degree of impairment) (J =16, K = 47)" = "Social functioning (degree of impairment)",
  "Hope, empowerment & self-efficacy (J = 12, K = 32)" = "Hope, empowerment & self-efficacy",
  "Alcohol and drug abuse/misuse (J = 7, K = 31)" = "Alcohol and drug abuse/misuse",
  "Self-esteem (J = 5, K = 14)" = "Self-esteem",
  "Loneliness (J = 4, K = 5)" = "Loneliness",
  "Physical health (J = 2, K = 3)" = "Physical health",
  "Psychiatric hospitalization (J = 1, K = 1)" = "Psychiatric hospitalization",
  "Employment (J = 1, K = 2)" = "Employment"
)

out_level <- c(
 "Wellbeing and quality of life (J = 24, K = 67)",
  "Social functioning (degree of impairment) (J =16, K = 47)",
  "Hope, empowerment & self-efficacy (J = 12, K = 32)",
  "Alcohol and drug abuse/misuse (J = 7, K = 31)",
  "Self-esteem (J = 5, K = 14)",
  "Loneliness (J = 4, K = 5)",
  "Physical health (J = 2, K = 3)",
  "Psychiatric hospitalization (J = 1, K = 1)",
  "Employment (J = 1, K = 2)"
)

label_cat_hist_ridge(
  data = n_es_by_construct, 
  n_es = effects, 
  variable = analysis_plan, 
  label_map = out_label, 
  level_order = out_level
) + 
  expand_limits(x = 20) + 
  labs(title = "Reintegrational outcomes") + 
  theme(plot.title = element_text(hjust = 0.5))

```
:::

::: {.column-margin}
```{r outcome-construct-ridge-hist-mental}
#| label: fig-outcome-construct-ridge-hist-mental
#| fig-cap: "Distribution of effect size estimates, by mental health outcome constructs."
#| fig.height: 8.5
#| fig.retina: 2
#| message: false

n_es_by_construct_mental <- 
  gb_dat |> 
  filter(str_detect(outcome_construct, "Men")) |> 
  summarise(effects = n(), .by = c(study, analysis_plan)) |> 
  mutate(J = n(), .by = c(analysis_plan)) |> 
  arrange(desc(J)) 

# Used to construct out_label_mental 
#label_dat_mental <- 
#  n_es_by_construct_mental |> 
#  summarise(J = n(), N_es = sum(effects), .by = analysis_plan)

out_label_mental <- c(
  "General mental health (J = 28, K = 70)" = "General mental health",
  "Depression (J = 19, K = 36)" = "Depression",
  "Anxiety (J = 9, K = 14)" = "Anxiety",
  "Symptoms of psychosis (J = 7, K = 21)" = "Symptoms of psychosis"
)

out_level_mental <- c(
  "General mental health (J = 28, K = 70)",
  "Depression (J = 19, K = 36)",
  "Anxiety (J = 9, K = 14)",
  "Symptoms of psychosis (J = 7, K = 21)"
)

label_cat_hist_ridge(
  data = n_es_by_construct_mental, 
  n_es = effects, 
  variable = analysis_plan, 
  label_map = out_label_mental, 
  level_order = out_level_mental
) + 
  expand_limits(x = 15) + 
  labs(title = "Mental heath outcomes") + 
  theme(plot.title = element_text(hjust = 0.5))

```
:::

:::

## Primary study sample size


### Total sample sizes

::: {.columns}

::: {.column width="95%"}
```{r sample-size-overall-reint}
#| tbl-cap: "Distribution of primary study sample sizes at post test for reintegrational outcomes"
#| tbl-cap-location: top
#| label: tbl-sample-size

# Used when describing the treatment group sample sizes
N_t_stud_trtid <- 
  reintegration_dat |> 
  reframe(N_treat = max(N_t), .by = c(study, trt_id)) 

N_t_total <- 
  N_t_stud_trtid |> 
  summarise(N_t_total = sum(N_treat), .by = study)

N_c_total <- 
  reintegration_dat |> 
  summarise(N_c_total = max(N_c), .by = study)

N_total_dat <- 
  left_join(N_t_total, N_c_total, by = join_by(study)) |> 
  mutate(N_total = N_t_total + N_c_total)


primary_sample_size_descriptive <- 
  N_total_dat$N_total |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

primary_sample_size_descriptive |>
  knitr::kable(
    digits = 2,
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

::: {.column-margin} 
```{r sample-size-overall-mental}
#| tbl-cap: "Distribution of primary study sample sizes at post test for mental health outcomes"
#| tbl-cap-location: top
#| label: tbl-sample-size-mental


# Used when describing the treatment group sample sizes
N_t_stud_trtid_mental <- 
  mental_health_dat |> 
  reframe(N_treat = max(N_t), .by = c(study, trt_id)) 

N_t_total_mental <- 
  N_t_stud_trtid_mental |> 
  summarise(N_t_total = sum(N_treat), .by = study)

N_c_total_mental <- 
  mental_health_dat |> 
  summarise(N_c_total = max(N_c), .by = study)

N_total_dat_mental <- 
  left_join(N_t_total_mental, N_c_total_mental, by = join_by(study)) |> 
  mutate(N_total = N_t_total + N_c_total)


primary_sample_size_descriptive_mental <- 
  N_total_dat_mental$N_total |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

primary_sample_size_descriptive_mental |>
  knitr::kable(
    digits = 2,
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

:::

The following plot displays the distribution of study sample sizes at post-test.

::: {.columns}

::: {.column width="95%"}
```{r sample-size-plot-reint}
#| label: fig-sample-size-reint
#| fig-cap: "Distribution of primary study sample sizes at post test for reintegrational outcomes."
#| fig.height: 2.5
#| fig.width: 8
#| fig.retina: 2
#| message: false
study_sizes_plot_reint <- 
  ggplot(N_total_dat, aes(N_total)) + 
  geom_density(fill = "cornflowerblue", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Sample Size", y = "")
study_sizes_plot_reint
```
:::

::: {.column-margin}
```{r sample-size-plot-mental}
#| label: fig-sample-size-mental
#| fig-cap: "Distribution of primary study sample sizes at post test for mental health outcomes."
#| fig.height: 4
#| fig.retina: 2
#| message: false
study_sizes_plot_mental <- 
  ggplot(N_total_dat_mental, aes(N_total)) + 
  geom_density(fill = "gray", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Sample Size", y = "")
study_sizes_plot_mental

```
:::

:::

### Treatment group

::: {.columns}

::: {.column width="95%"}
```{r sample-size-treatment-reint}
#| tbl-cap: "Distribution of treatment sample sizes at post test for reintegrational outcomes"
#| tbl-cap-location: top
#| label: tbl-sample-size-treatment


treatment_sample_size_descriptive <- 
  N_t_stud_trtid$N_treat |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

treatment_sample_size_descriptive |>
  knitr::kable(
    digits = 2,
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

::: {.column-margin} 
```{r sample-size-treatment-mental}
#| tbl-cap: "Distribution of treatment sample sizes at post test for mental health outcomes"
#| tbl-cap-location: top
#| label: tbl-sample-size-treatment-mental


treatment_sample_size_descriptive_mental <- 
  N_t_stud_trtid_mental$N_treat |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

treatment_sample_size_descriptive_mental |>
  knitr::kable(
    digits = 2,
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

:::

The following plot displays the distribution of treatment sample sizes at post-test.

::: {.columns}

::: {.column width="95%"}
```{r sample-size-treatment-plot-reint}
#| label: fig-sample-size-treatment-reint
#| fig-cap: "Distribution of treatment sample sizes at post test for reintegrational outcomes."
#| fig.height: 2.5
#| fig.width: 8
#| fig.retina: 2
#| message: false
treatment_sizes_plot_reint <- 
  ggplot(N_t_stud_trtid, aes(N_treat)) + 
  geom_density(fill = "cornflowerblue", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Treatment Sample Size", y = "")
treatment_sizes_plot_reint
```
:::

::: {.column-margin}
```{r sample-size-treatment-plot-mental}
#| label: fig-sample-size-treatment-mental
#| fig-cap: "Distribution of treatment sample sizes at post test for mental health outcomes."
#| fig.height: 4
#| fig.retina: 2
#| message: false
treatment_sizes_plot_mental <- 
  ggplot(N_t_stud_trtid_mental, aes(N_treat)) + 
  geom_density(fill = "gray", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Treatment Sample Size", y = "")
treatment_sizes_plot_mental

```
:::

:::

### Control group

::: {.columns}

::: {.column width="95%"}
```{r sample-size-control-reint}
#| tbl-cap: "Distribution of control group sample sizes at post test for reintegrational outcomes"
#| tbl-cap-location: top
#| label: tbl-sample-size-control


control_sample_size_descriptive <- 
  N_total_dat$N_c_total |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

control_sample_size_descriptive |>
  knitr::kable(
    digits = 2,
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

::: {.column-margin} 
```{r sample-size-control-mental}
#| tbl-cap: "Distribution of control group sample sizes at post test for mental health outcomes"
#| tbl-cap-location: top
#| label: tbl-sample-size-control-mental


control_sample_size_descriptive_mental <- 
  N_total_dat_mental$N_c_total |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

control_sample_size_descriptive_mental |>
  knitr::kable(
    digits = 2,
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

:::

The following plot displays the distribution of control sample sizes at post-test.

::: {.columns}

::: {.column width="95%"}
```{r sample-size-control-plot-reint}
#| label: fig-sample-size-control-reint
#| fig-cap: "Distribution of control group sample sizes at post test for reintegrational outcomes."
#| fig.height: 2.5
#| fig.width: 8
#| fig.retina: 2
#| message: false
control_sizes_plot_reint <- 
  ggplot(N_total_dat, aes(N_c_total)) + 
  geom_density(fill = "cornflowerblue", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Control Group Sample Size", y = "")
control_sizes_plot_reint
```
:::

::: {.column-margin}
```{r sample-size-control-plot-mental}
#| label: fig-sample-size-control-mental
#| fig-cap: "Distribution of control group sample sizes at post test for mental health outcomes."
#| fig.height: 4
#| fig.retina: 2
#| message: false
control_sizes_plot_mental <- 
  ggplot(N_total_dat_mental, aes(N_c_total)) + 
  geom_density(fill = "gray", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Control Group Sample Size", y = "")
control_sizes_plot_mental

```
:::

:::

## Study sample sizes versus number of effect size estimates per study

```{r bivariate-es-plot}
#| label: fig-es-distribution-bivariate
#| fig-cap: "Study sample sizes versus number of effect size estimates for reintegrational outcomes"
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

plot <- 
  reintegration_dat |> 
  summarise(effects = n(), .by = study) |> 
  left_join(N_total_dat, by = join_by(study)) |> 
  relocate(effects, .after = N_total) |> 
  ggplot(aes(x = N_total, y = effects)) +
  geom_point(alpha = 0.5) +
  scale_x_continuous(breaks = seq(0, 650, by = 50)) +
  guides(size = "none") + 
  theme_minimal() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.9, 0.05),
    legend.justification = c(1, 0),
    legend.background = element_blank()
  ) +
  labs(x = "Total sample size", y = "Number of effect size estimates per study", color = "") +
  expand_limits(y = 30)

ggMarginal(plot, type = "density")

```

# Moderators
```{r cross-tab-function}
cat_dat_cross <- function(variable, study_id, data) {
  
  require(dplyr)
  require(rlang)
  require(tidyr)
  
  var_exp <- enquo(variable)
  study_id_exp <- enquo(study_id)
  study_id_name <- as_name(study_id_exp)
  
  
    res_dat <- data %>%
      group_by(!!study_id_exp) %>%
      reframe(var_exp_mirror = unique(!!var_exp))  %>%
      full_join(data,
                by = c(study_id_name),
                relationship = "many-to-many") %>%
      group_by(!!var_exp, var_exp_mirror) %>%
      reframe(
        m = n_distinct(!!study_id_exp),
        k = n()
      ) %>%
      mutate(size = paste0(m, " (", k, ")")) %>%
      select(-m, -k) |>
      pivot_wider(names_from = var_exp_mirror, values_from = "size")
  
  names(res_dat)[1] <- "level" 
  
  res_dat <- 
    res_dat |> 
    mutate(
      level = factor(level, levels = unique(names(res_dat[-1])))
    ) |> 
    arrange(level)

  return(res_dat)
}
```

## Categorical moderators

### Outcome measure

```{r outcome-dependency-table-reint}
#| tbl-cap: "Dependency table for preregistration status (reintegration)"
#| tbl-cap-location: top
#| label: tbl-outcome

outcome_dat_cross <- cat_dat_cross(
  data = reintegration_dat,
  variable = analysis_plan,
  study_id = study
)


outcome_dat_cross |>
  knitr::kable(
    "html",
    col.names = c(
      "Outcome",
      colnames(outcome_dat_cross)[-1]
    )
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = "Values outside the parentheses are number of studies, with the number of samples and effect size estimates shown in the parentheses.",
    general_title = "Note: ",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```


::: {.columns}

::: {.column width="95%"}
```{r outcome-subgroup-dependency-table-reint}
#| tbl-cap: "Dependency table for outcome used for subgroup analysis (reintegration)"
#| tbl-cap-location: top
#| label: tbl-outcome-subgroup

outcome_subgroup_dat_cross <- cat_dat_cross(
  data = filter(reintegration_dat, str_detect(analysis_plan, "Alco|Hope|Social|Well")),
  variable = analysis_plan,
  study_id = study
)


outcome_subgroup_dat_cross |>
  knitr::kable(
    "html",
    col.names = c(
      "Outcome",
      colnames(outcome_subgroup_dat_cross)[-1]
    )
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = "Values outside the parentheses are number of studies, with the number of samples and effect size estimates shown in the parentheses.", 
    general_title = "Note: ",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

::: {.column-margin}
```{r outcome-subgroup-dependency-table-mental}
#| tbl-cap: "Dependency table for outcome used for subgroup analysis (mental health)"
#| tbl-cap-location: top
#| label: tbl-outcome-subgroup-mental

outcome_subgroup_dat_cross_mental <- cat_dat_cross(
  data = mental_health_dat,
  variable = analysis_plan,
  study_id = study
)


outcome_subgroup_dat_cross_mental |>
  knitr::kable(
    "html",
    col.names = c(
      "Outcome",
      colnames(outcome_subgroup_dat_cross_mental)[-1]
    )
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = "Values outside the parentheses are number of studies, with the number of samples and effect size estimates shown in the parentheses.", 
    general_title = "Note: ",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

:::


##### Ridge plot of effect size estimates

```{r cat-ridge-function}
cat_ridge <- function(data, es, v, variable) {
  require(dplyr)
  require(rlang)
  require(tidyr)
  require(ggplot2)
  
  es_exp <- enquo(es)
  var_exp <- enquo(variable)
  v_exp <- enquo(v)
  
  data |> 
    mutate(!!var_exp := fct_rev(!!var_exp)) |> 
  ggplot(aes(
    x = !!es_exp,
    y = !!var_exp,
    fill = !!var_exp
  )) +
    geom_density_ridges(
      aes(
        point_colour = !!var_exp,
        point_size = 1 / !!v_exp
      ),
      alpha = .2,
      point_alpha = 0.5,
      jittered_points = TRUE
    ) +
    theme_minimal() +
    labs(y = "", x = "Standardized Mean Difference (Hedges' g)") +
    theme(legend.position = "none")
}
```


::: {.columns}

::: {.column width="95%"}

::: {.panel-tabset}
###### Subgroup analyzed
```{r type-ridge-reint-analyzed}
#| label: fig-type-ridge-reint-analyzed
#| fig-cap: "Distribution of effect size estimates, by reintegrational outcomes"
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

analyzed_outcomes <- 
  reintegration_dat |> 
  filter(str_detect(analysis_plan, "Alco|Hope|Social|Well"))

cat_ridge(data = analyzed_outcomes, es = gt_pop, variable = analysis_plan, v = vgt_pop)
```

###### Not subgroup analyzed
```{r type-ridge-reint-not-analyzed}
#| label: fig-type-ridge-reint-not-analyzed
#| fig-cap: "Distribution of effect size estimates, by reintegrational outcomes."
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

not_analyzed_outcomes <- 
  reintegration_dat |> 
  filter(!str_detect(analysis_plan, "Alco|Hope|Social|Well"))

cat_ridge(data = not_analyzed_outcomes, es = gt_pop, variable = analysis_plan, v = vgt_pop)
```
:::

:::

::: {.column-margin}
```{r type-ridge-mental-analyzed}
#| label: fig-type-ridge-mental-analyzed
#| fig-cap: "Distribution of effect size estimates, by mental health outcomes."
#| fig.height: 7
#| fig.retina: 2
#| message: false

cat_ridge(data = mental_health_dat, es = gt_pop, variable = analysis_plan, v = vgt_pop)
```
:::

:::

##### Network plot for outcome construct
The following plot shows the network structure of outcomes constructs. Each node represent an outcome construct, the edge between a pair of nodes indicates that there is at least one study that examined the contracts between that pair of constructs The width of the edges indicates the number of studies that compare that pair of constructs. The size of the node corresponds to the number of studies measure that construct.  


```{r network-plot}
#| label: fig-network
#| fig-cap: "Network structure of contrasts between primary and secondary outcome constructs"
#| fig.width: 7
#| fig.height: 6
#| fig.retina: 2
#| message: false

gb_dat_reduced <- gb_dat |> select(study, analysis_plan)

res_dat <- gb_dat_reduced |> 
  group_by(study) |>
  reframe(var_exp_mirror = unique(analysis_plan))  |>
  full_join(gb_dat_reduced ,
            by = join_by(study),
            relationship = "many-to-many") |>
  group_by(analysis_plan, var_exp_mirror) |>
  reframe(
    m = n_distinct(study),
    k = n()
  ) |>
  mutate(size = m) |> 
  select(-m, -k) |>
  arrange(var_exp_mirror) |> 
  pivot_wider(names_from = var_exp_mirror, values_from = "size") |> 
  arrange(analysis_plan) |> 
  as.data.frame()


names(res_dat)[1] <- "level"


edges <- res_dat  |>
  rename(from = "level") |> 
  pivot_longer(-from, names_to = "to", values_to = "weight") |>
  filter(from != to, !is.na(weight)) |> 
  mutate(
    from_chr = as.character(from),
    to_chr = as.character(to),
    grp_str = paste0(pmin(from_chr, to_chr, na.rm = TRUE), "_", pmax(from_chr, to_chr, na.rm = TRUE))
  ) |> 
  distinct(grp_str, .keep_all = TRUE) |>
  select(from, to, weight)

g <- graph_from_data_frame(edges, directed = FALSE)
layout <- layout_in_circle(g)

# Adjust label position outward
label_coords <- layout
label_coords[, 1] <- c(
  label_coords[1, 1] * 1.35, #1.5,
  label_coords[2:6, 1] * 1.5, #1.63,
  label_coords[7, 1] * 1.35, #1.68,
  label_coords[8:13, 1] * 1.4 #1.63
)

label_coords[, 2] <- c(
  label_coords[c(1:3), 2],
  label_coords[4, 2] * 1.13,
  label_coords[5, 2] * 1.3,
  label_coords[6, 2] * 1.13,
  label_coords[c(7:9), 2] * 1.13,
  label_coords[10, 2] * 1.3,
  label_coords[11, 2] * 1.3,
  label_coords[12, 2] * 1.3,
  label_coords[13, 2] * 1.13
)

node_sizes <- diag(as.matrix(res_dat[, -1]))

plot(
  g,
  layout = layout,
  edge.width = E(g)$weight,
  edge.color = met.brewer("Navajo")[5],
  vertex.size = node_sizes[c(1:8, 10:13, 9)],
  vertex.label = NA,
  vertex.color = met.brewer("Navajo")[4],
  vertex.frame.width = 0
)

text(
  x = label_coords[, 1],
  y = label_coords[, 2],
  labels = paste0(str_wrap(names(res_dat[c(2:9, 11:14, 10)]), width = 15), "\n(J = ", node_sizes, ")"),
  cex = 0.6,
  col = "black",
  xpd = NA
)


```

### Diagnosis (schizophrenia vs. rest of the effects)

::: {.columns}

::: {.column width="95%"}
```{r diagnosis-dependency-table-reint}
#| tbl-cap: "Dependency table for diagnosis (reintegration)"
#| tbl-cap-location: top
#| label: tbl-diagnosis-subgroup-reint


diagnosis_subgroup_dat_cross <- cat_dat_cross(
  data = reintegration_dat,
  variable = schizophrenia,
  study_id = study
)

diagnosis_subgroup_dat_cross |>
  knitr::kable(
    "html",
    col.names = c(
      "Diagnosis",
      colnames(diagnosis_subgroup_dat_cross)[-1]
    )
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = "Values outside the parentheses are number of studies, with the number of samples and effect size estimates shown in the parentheses.", 
    general_title = "Note: ",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

::: {.column-margin}
```{r diagnosis-dependency-table-mental}
#| tbl-cap: "Dependency table for diagnosis (mental health)"
#| tbl-cap-location: top
#| label: tbl-diagnosis-subgroup-mental

diagnosis_subgroup_dat_cross_mental <- cat_dat_cross(
  data = mental_health_dat,
  variable = schizophrenia,
  study_id = study
)

diagnosis_subgroup_dat_cross_mental |>
  knitr::kable(
    "html",
    col.names = c(
      "Diagnosis",
      colnames(diagnosis_subgroup_dat_cross_mental)[-1]
    )
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = "Values outside the parentheses are number of studies, with the number of samples and effect size estimates shown in the parentheses.", 
    general_title = "Note: ",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

:::


::: {.columns}

::: {.column width="95%"}
```{r diagnosis-ridge-reint}
#| label: fig-diagnosis-ridge-reint
#| fig-cap: "Distribution of effect size estimates, by diagnosis (reintegrational outcome)."
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

cat_ridge(data = reintegration_dat, es = gt_pop, variable = schizophrenia, v = vgt_pop)
```
:::

::: {.column-margin}
```{r type-ridge-mental}
#| label: fig-type-ridge-mental
#| fig-cap: "Distribution of effect size estimates, by diagnosis (mental health)."
#| fig.height: 6.5
#| fig.retina: 2
#| message: false

cat_ridge(data = mental_health_dat, es = gt_pop, variable = schizophrenia, v = vgt_pop)
```
:::

:::

### Type of intervention

::: {.columns}

::: {.column width="95%"}
```{r cbt-dependency-table-reint}
#| tbl-cap: "Dependency table for type of intervention (reintegration)"
#| tbl-cap-location: top
#| label: tbl-cbt-subgroup

cbt_subgroup_dat_cross <- cat_dat_cross(
  data = reintegration_dat,
  variable = CBT_int,
  study_id = study
)

cbt_subgroup_dat_cross |>
  knitr::kable(
    "html",
    col.names = c(
      "Intervention",
      colnames(cbt_subgroup_dat_cross)[-1]
    )
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = "Values outside the parentheses are number of studies, with the number of samples and effect size estimates shown in the parentheses.", 
    general_title = "Note: ",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

::: {.column-margin}
```{r cbt-dependency-table-mental}
#| tbl-cap: "Dependency table for type of intervention (mental health)"
#| tbl-cap-location: top
#| label: tbl-cbt-subgroup-mental

cbt_subgroup_dat_cross_mental <- cat_dat_cross(
  data = mental_health_dat,
  variable = CBT_int,
  study_id = study
)

cbt_subgroup_dat_cross_mental |>
  knitr::kable(
    "html",
    col.names = c(
      "Intervention",
      colnames(cbt_subgroup_dat_cross_mental)[-1]
    )
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = "Values outside the parentheses are number of studies, with the number of samples and effect size estimates shown in the parentheses.", 
    general_title = "Note: ",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

:::

::: {.columns}

::: {.column width="95%"}
```{r cbt-ridge-reint}
#| label: fig-cbt-ridge-reint
#| fig-cap: "Distribution of effect size estimates, by type of intervention (reintegrational outcome)."
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

cat_ridge(data = reintegration_dat, es = gt_pop, variable = CBT_int, v = vgt_pop)
```
:::

::: {.column-margin}
```{r cbt-ridge-mental}
#| label: fig-cbt-ridge-mental
#| fig-cap: "Distribution of effect size estimates, by type of intervention (mental health)."
#| fig.height: 6.5
#| fig.retina: 2
#| message: false

cat_ridge(data = mental_health_dat, es = gt_pop, variable = CBT_int, v = vgt_pop)
```
:::

:::

#### EGM-like plot

::: {.columns}

::: {.column width="160%"}

::: {.panel-tabset}
##### Reintegrational outcomes
```{r egm-reint}
#| label: fig-egm-reint
#| fig-cap: "EGM for reintegrational outcomes"
#| fig.width: 18
#| fig.height: 18
#| fig.retina: 2
#| message: false

egm_dat_reint <- 
  reintegration_dat |> 
  summarise(
    n = n(),
    n_studies = factor(n_distinct(study), levels = c(1:4)),
    .by = c(trt_group, analysis_plan, prereg_chr)
  ) |> 
  mutate(
    n_prereg = case_match(
      prereg_chr,
      "Preregistered" ~ 0.5,
      "Not preregistered" ~ 0
    ),
    
    constant = "Intervention",
    
    outcome = case_match(
      analysis_plan,
      "Alcohol and drug abuse/misuse" ~ "Alcohol/drugs",
      "Hope, empowerment & self-efficacy" ~ "Hope",
      "Psychiatric hospitalization" ~ "Psych hospital",
      "Social functioning (degree of impairment)" ~ "Social func",
      "Wellbeing and quality of life" ~ "Wellbeing/QoL",
      .default = analysis_plan
    ),
    
    intervention = case_match(
      trt_group,
      "group-based CBT" ~ "GrpCBT",
      "stress management" ~ "StressMan",
      "vocational training" ~ "JobTrain",
      "group psychotherapy"  ~ "GrpPsychT",
      "art therapy" ~ "ArtT",
      "illness management" ~ "IllMan",
      "group psychoeducation" ~ "GrpPsychEdu",
      "seeking safety" ~ "SeekSafe",
      "social cognition and interaction training" ~ "SCIT",
      "illness and addiction management" ~ "Ill&AddMan",
      "social network training" ~ "NetworkTrain",
      "cognitive-behavioral social skills training" ~ "CBSST",
      "residential treatment" ~ "ResidentTreat",
      "positive psychology group intervention" ~ "PosiPsychGrp",
      "addiction management" ~ "AddMan",
      "reading group intervention" ~ "ReadGrp"
    )
    
    
    #intervention_name = case_match(
    #  intervention,
    #  "Sanctions and economic incentives" ~ "Econ incentives",
    #  "Introduction programmes" ~ "Intro program",
    #  "Combination programmes" ~ "Combi program",
    #  "Language training" ~ "Lang train",
    #  "Labour market training" ~ "Lab market train",
    #  "Job search assistance" ~" Job search ass",
    #  "Subsidized public sector employment" ~ "Sub public emp"
    #),
    #
    #outcome = if_else(outcome == "Duration of social assistance spells", "Dur. social ass spells", outcome)
    
  ) 

egm_dat_reint |> 
  ggplot(aes(x = n_prereg, y =  constant, size = n, color = n_studies)) + 
  geom_point() +
  scale_size(range = c(6, 14)) +
  geom_text(aes(label = n), color = "black", size = 3.5) +
  scale_x_continuous(breaks = seq(0,0.5,0.5), limits = c(0, 1), labels = c("Conventional", "Preregistered")) +
  scale_y_discrete("Interventions") +
  facet_grid(intervention~outcome, scales = "free_y", space = "free_y") +
  theme_bw() + 
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1),
    #panel.grid.major = element_blank(),
    #panel.grid.minor = element_blank(),
    #panel.background = element_blank(),
    axis.text.y = element_blank(),   
    axis.ticks.y = element_blank(),  
    axis.title.y = element_blank(),
    plot.caption = element_text(hjust = 0, size = 14)
  ) +
  coord_cartesian(xlim = c(-0.25, 0.75), ylim = NULL) +
  guides(size = "none") + 
  xlab("Type of registration") +
  labs(
    color = "Number of studies",
    caption = paste0(
      "Note: GrpCBT = Group-based CBT, StressMan = Stress mangement, JobTrain = Vocational training, ",
      "GrpPsychT = Group psychotherapy, ArtT = Art Therapy, IllMan = Ill management,\n",
      "GrpPsychEdu = Group Psychoeducation, SeekSafe = Seeking safety, ",
      "SCIT = cognitive-behavioral social skills training, ResidentTreat = Residential treatment,\n",
      "PosiPsychGrp = Positive Psychology group therapy, AddMan = Addiction mangement, ",
      "ReadGrp = Reading group."
    )
  )


```

##### Mental health outcomes
```{r egm-mental}
#| label: fig-egm-mental
#| fig-cap: "EGM for mental health outcomes"
#| fig.width: 18
#| fig.height: 18
#| fig.retina: 2
#| message: false

egm_dat_mental <- 
  mental_health_dat |> 
  summarise(
    n = n(),
    n_studies = factor(n_distinct(study), levels = c(1:4)),
    .by = c(trt_group, analysis_plan, prereg_chr)
  ) |> 
  mutate(
    n_prereg = case_match(
      prereg_chr,
      "Preregistered" ~ 0.5,
      "Not preregistered" ~ 0
    ),
    
    constant = "Intervention",
    
    outcome = analysis_plan,
    
    intervention = case_match(
      trt_group,
      "group-based CBT" ~ "GrpCBT",
      "stress management" ~ "StressMan",
      "vocational training" ~ "JobTrain",
      "group psychotherapy"  ~ "GrpPsychT",
      "art therapy" ~ "ArtT",
      "illness management" ~ "IllMan",
      "group psychoeducation" ~ "GrpPsychEdu",
      "seeking safety" ~ "SeekSafe",
      "social cognition and interaction training" ~ "SCIT",
      "illness and addiction management" ~ "Ill&AddMan",
      "social network training" ~ "NetworkTrain",
      "cognitive-behavioral social skills training" ~ "CBSST",
      "residential treatment" ~ "ResidentTreat",
      "positive psychology group intervention" ~ "PosiPsychGrp",
      "addiction management" ~ "AddMan",
      "reading group intervention" ~ "ReadGrp",
      "group psychoeducation & social skill training" ~ "GrpPsyEdu&SS"
    )
    
    
    #intervention_name = case_match(
    #  intervention,
    #  "Sanctions and economic incentives" ~ "Econ incentives",
    #  "Introduction programmes" ~ "Intro program",
    #  "Combination programmes" ~ "Combi program",
    #  "Language training" ~ "Lang train",
    #  "Labour market training" ~ "Lab market train",
    #  "Job search assistance" ~" Job search ass",
    #  "Subsidized public sector employment" ~ "Sub public emp"
    #),
    #
    #outcome = if_else(outcome == "Duration of social assistance spells", "Dur. social ass spells", outcome)
    
  ) 

egm_dat_mental |> 
  ggplot(aes(x = n_prereg, y =  constant, size = n, color = n_studies)) + 
  geom_point() +
  scale_size(range = c(6, 14)) +
  geom_text(aes(label = n), color = "black", size = 3.5) +
  scale_x_continuous(breaks = seq(0,0.5,0.5), limits = c(0, 1), labels = c("Conventional", "Preregistered")) +
  scale_y_discrete("Interventions") +
  facet_grid(intervention~outcome, scales = "free_y", space = "free_y") +
  theme_bw() + 
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 45, hjust = 1),
    #panel.grid.major = element_blank(),
    #panel.grid.minor = element_blank(),
    #panel.background = element_blank(),
    axis.text.y = element_blank(),   
    axis.ticks.y = element_blank(),  
    axis.title.y = element_blank(),
    plot.caption = element_text(hjust = 0, size = 12)
  ) +
  coord_cartesian(xlim = c(-0.25, 0.75), ylim = NULL) +
  guides(size = "none") + 
  xlab("Type of registration") +
  labs(
    color = "Number of studies",
    caption = paste0(
      "Note: GrpCBT = Group-based CBT, StressMan = Stress mangement, JobTrain = Vocational training,",
      "GrpPsychT = Group psychotherapy, ArtT = Art Therapy,\nIllMan = Ill management,",
      "GrpPsychEdu = Group Psychoeducation, SeekSafe = Seeking safety,",
      "SCIT = cognitive-behavioral social skills training,\nResidentTreat = Residential treatment,",
      "PosiPsychGrp = Positive Psychology group therapy, AddMan = Addiction mangement, ",
      "ReadGrp = Reading group,\nGrpPsyEdu&SS = Group psychoeducation & social skill training."
    )
  )


```

:::

:::

:::


### Type of test

::: {.columns}

::: {.column width="95%"}
```{r test-type-dependency-table-reint}
#| tbl-cap: "Dependency table for type of test (reintegration)"
#| tbl-cap-location: top
#| label: tbl-test-type-subgroup

test_type_dat <- 
  reintegration_dat |> 
  filter(test_type != "Raw events")

test_type_dat_cross <- cat_dat_cross(
  data = test_type_dat,
  variable = test_type,
  study_id = study
)

test_type_dat_cross |>
  knitr::kable(
    "html",
    col.names = c(
      "Type of test",
      colnames(test_type_dat_cross)[-1]
    )
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = "Values outside the parentheses are number of studies, with the number of samples and effect size estimates shown in the parentheses.", 
    general_title = "Note: ",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

::: {.column-margin}
```{r test-type-dependency-table-mental}
#| tbl-cap: "Dependency table for type of test (mental health)"
#| tbl-cap-location: top
#| label: tbl-test-type-subgroup-mental

test_type_dat_mental <- 
  mental_health_dat |> 
  filter(test_type != "Raw events")


test_type_dat_cross_mental <- cat_dat_cross(
  data = test_type_dat_mental,
  variable = test_type,
  study_id = study
)

test_type_dat_cross_mental |>
  knitr::kable(
    "html",
    col.names = c(
      "Type of test",
      colnames(test_type_dat_cross_mental)[-1]
    )
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = "Values outside the parentheses are number of studies, with the number of samples and effect size estimates shown in the parentheses.", 
    general_title = "Note: ",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

:::

::: {.columns}

::: {.column width="95%"}
```{r test-type-ridge-reint}
#| label: fig-test-type-ridge-reint
#| fig-cap: "Distribution of effect size estimates, by type of test (reintegrational outcome)."
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

cat_ridge(data = test_type_dat, es = gt_pop, variable = test_type, v = vgt_pop)
```
:::

::: {.column-margin}
```{r test-type-ridge-mental}
#| label: fig-test-type-ridge-mental
#| fig-cap: "Distribution of effect size estimates, by type of test (mental health)."
#| fig.height: 6.2
#| fig.retina: 2
#| message: false

cat_ridge(data = test_type_dat_mental, es = gt_pop, variable = test_type, v = vgt_pop)
```
:::

:::

::: {.columns}

::: {.column width="130%"}
```{r es-pval-plot-reint}
#| label: fig-es-pval-reint
#| fig-cap: "Distributions of effect size by p values and outcome measure type."
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false

test_type_dat_all <- 
  gb_dat |> 
  filter(test_type != "Raw events") |> 
  mutate(
    p_val = 2 * ( 1 - pnorm( abs(gt_pop) / sqrt(vgt_pop) ) ),
  )


ggplot(test_type_dat_all, aes(y = gt_pop, x = p_val, color = test_type)) +
geom_point() + 
geom_hline(yintercept = 0) + 
geom_vline(xintercept = .05, color = "gray") +
facet_grid(outcome_construct~test_type) +
theme_bw() +
theme(legend.position="none") +
labs(x = "p values", y = "Effect sizes (Hedges' g)")

```
:::

:::

### ITT vs. TOT
::: {.columns}

::: {.column width="95%"}
```{r strategy-dependency-table-reint}
#| tbl-cap: "Dependency table for estimation strategy (reintegration)"
#| tbl-cap-location: top
#| label: tbl-strategy-subgroup

strategy_subgroup_dat_cross <- cat_dat_cross(
  data = reintegration_dat,
  variable = analysis_strategy,
  study_id = study
)

strategy_subgroup_dat_cross |>
  knitr::kable(
    "html",
    col.names = c(
      "Strategy",
      colnames(strategy_subgroup_dat_cross)[-1]
    )
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = paste0("Values outside the parentheses are number of studies,", "
                     with the number of samples and effect size estimates shown in the parentheses. ",
                     "TOT = treatment on the treated, ITT = Intention to treat."
                     ), 
    general_title = "Note: ",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

::: {.column-margin}
```{r strategy-dependency-table-mental}
#| tbl-cap: "Dependency table for estimation strategy (mental health)"
#| tbl-cap-location: top
#| label: tbl-strategy-subgroup-mental

strategy_subgroup_dat_cross_mental <- cat_dat_cross(
  data = mental_health_dat,
  variable = analysis_strategy,
  study_id = study
)

strategy_subgroup_dat_cross_mental |>
  knitr::kable(
    "html",
    col.names = c(
      "Strategy",
      colnames(strategy_subgroup_dat_cross_mental)[-1]
    ) 
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = paste0("Values outside the parentheses are number of studies,", "
                     with the number of samples and effect size estimates shown in the parentheses. ",
                     "TOT = treatment on the treated, ITT = Intention to treat."
                     ), 
    general_title = "Note: ",
    footnote_as_chunk = T
  )  |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

:::

::: {.columns}

::: {.column width="95%"}
```{r strategy-ridge-reint}
#| label: fig-strategy-ridge-reint
#| fig-cap: "Distribution of effect size estimates, by estiamtion strategy (reintegrational outcome)."
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

cat_ridge(data = reintegration_dat, es = gt_pop, variable = analysis_strategy, v = vgt_pop)
```
:::

::: {.column-margin}
```{r strategy-ridge-mental}
#| label: fig-strategy-ridge-mental
#| fig-cap: "Distribution of effect size estimates, by estiamtion strategy (mental health)."
#| fig.height: 6.5
#| fig.retina: 2
#| message: false

cat_ridge(data = mental_health_dat, es = gt_pop, variable = analysis_strategy, v = vgt_pop)
```
:::

:::

### RCT vs. QES
::: {.columns}

::: {.column width="95%"}
```{r design-dependency-table-reint}
#| tbl-cap: "Dependency table for type of research design (reintegration)"
#| tbl-cap-location: top
#| label: tbl-design-subgroup

design_subgroup_dat_cross <- cat_dat_cross(
  data = reintegration_dat,
  variable = QES_design,
  study_id = study
)

design_subgroup_dat_cross |>
  knitr::kable(
    "html",
    col.names = c(
      "Design",
      colnames(design_subgroup_dat_cross)[-1]
    )
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = paste0("Values outside the parentheses are number of studies,", "
                     with the number of samples and effect size estimates shown in the parentheses."
                     ), 
    general_title = "Note: ",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

::: {.column-margin}
```{r design-dependency-table-mental}
#| tbl-cap: "Dependency table for type of research design (mental health)"
#| tbl-cap-location: top
#| label: tbl-design-subgroup-mental

design_subgroup_dat_cross_mental <- cat_dat_cross(
  data = mental_health_dat,
  variable = QES_design,
  study_id = study
)

design_subgroup_dat_cross_mental |>
  knitr::kable(
    "html",
    col.names = c(
      "Design",
      colnames(design_subgroup_dat_cross_mental)[-1]
    )
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = paste0("Values outside the parentheses are number of studies,", "
                     with the number of samples and effect size estimates shown in the parentheses."
                     ), 
    general_title = "Note: ",
    footnote_as_chunk = T
  )  |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

:::

::: {.columns}

::: {.column width="95%"}
```{r design-ridge-reint}
#| label: fig-design-ridge-reint
#| fig-cap: "Distribution of effect size estimates, by research design (reintegrational outcome)."
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

cat_ridge(data = reintegration_dat, es = gt_pop, variable = QES_design, v = vgt_pop)
```
:::

::: {.column-margin}
```{r design-ridge-mental}
#| label: fig-design-ridge-mental
#| fig-cap: "Distribution of effect size estimates, by research design (mental health)."
#| fig.height: 6.5
#| fig.retina: 2
#| message: false

cat_ridge(data = mental_health_dat, es = gt_pop, variable = QES_design, v = vgt_pop)
```
:::

:::

### Type of control
::: {.columns}

::: {.column width="95%"}
```{r control-dependency-table-reint}
#| tbl-cap: "Dependency table for type of control group (reintegration)"
#| tbl-cap-location: top
#| label: tbl-control-subgroup

control_subgroup_dat_cross <- cat_dat_cross(
  data = reintegration_dat,
  variable = control,
  study_id = study
)

control_subgroup_dat_cross |>
  knitr::kable(
    "html",
    col.names = c(
      "Control",
      colnames(control_subgroup_dat_cross)[-1]
    ) 
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    paste0(
      "Values outside the parentheses are number of studies,", "
       with the number of samples and effect size estimates shown in the parentheses."
    ), 
    general_title = "Note: ",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

::: {.column-margin}
```{r control-dependency-table-mental}
#| tbl-cap: "Dependency table for type of control group (mental health)"
#| tbl-cap-location: top
#| label: tbl-control-subgroup-mental

control_subgroup_dat_cross_mental <- cat_dat_cross(
  data = mental_health_dat,
  variable = control,
  study_id = study
)

control_subgroup_dat_cross_mental |>
  knitr::kable(
    "html",
    col.names = c(
      "Control",
      colnames(control_subgroup_dat_cross_mental)[-1]
    )
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = "See note in the reintegration table to the left.", 
    general_title = "Note: ",
    footnote_as_chunk = T
  )  |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

:::

::: {.columns}

::: {.column width="95%"}
```{r control-ridge-reint}
#| label: fig-control-ridge-reint
#| fig-cap: "Distribution of effect size estimates, by type of control group (reintegrational outcome)."
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

cat_ridge(data = reintegration_dat, es = gt_pop, variable = control, v = vgt_pop)
```
:::

::: {.column-margin}
```{r control-ridge-mental}
#| label: fig-control-ridge-mental
#| fig-cap: "Distribution of effect size estimates, by type of control group (mental health)."
#| fig.height: 6.5
#| fig.retina: 2
#| message: false

cat_ridge(data = mental_health_dat, es = gt_pop, variable = control, v = vgt_pop)
```
:::

:::


### Risk of bias (RoB)
::: {.columns}

::: {.column width="95%"}
```{r rob-dependency-table-reint}
#| tbl-cap: "Dependency table across overall risk of bias assessments (reintegration)"
#| tbl-cap-location: top
#| label: tbl-rob-subgroup

rob_subgroup_dat_cross <- cat_dat_cross(
  data = reintegration_dat,
  variable = overall_rob,
  study_id = study
)

rob_subgroup_dat_cross |>
  knitr::kable(
    "html",
    col.names = c(
      "Risk of bias judgment",
      colnames(rob_subgroup_dat_cross)[-1]
    ) 
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = paste0("Values outside the parentheses are number of studies,", "
                     with the number of samples and effect size estimates shown in the parentheses."
                     ), 
    general_title = "Note: ",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

::: {.column-margin}
```{r rob-dependency-table-mental}
#| tbl-cap: "Dependency table across overall risk of bias assessments (mental health)"
#| tbl-cap-location: top
#| label: tbl-rob-subgroup-mental

rob_subgroup_dat_cross_mental <- cat_dat_cross(
  data = mental_health_dat,
  variable = overall_rob,
  study_id = study
)

rob_subgroup_dat_cross_mental |>
  knitr::kable(
    "html",
    col.names = c(
      "Risk of bias judgment",
      colnames(rob_subgroup_dat_cross_mental)[-1]
    ) 
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = paste0("Values outside the parentheses are number of studies,", "
                     with the number of samples and effect size estimates shown in the parentheses."
                     ), 
    general_title = "Note: ",
    footnote_as_chunk = T
  )  |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

:::

::: {.columns}

::: {.column width="95%"}
```{r rob-ridge-reint}
#| label: fig-rob-ridge-reint
#| fig-cap: "Distribution of effect size estimates, by overall risk of bias assessment (reintegrational outcome)."
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

cat_ridge(data = reintegration_dat, es = gt_pop, variable = overall_rob, v = vgt_pop)
```
:::

::: {.column-margin}
```{r rob-ridge-mental}
#| label: fig-rob-ridge-mental
#| fig-cap: "Distribution of effect size estimates, by overall risk of bias assessment (mental health)."
#| fig.height: 6.5
#| fig.retina: 2
#| message: false

cat_ridge(data = gb_dat, es = gt_pop, variable = overall_rob, v = vgt_pop) 
```
:::

:::

### Preregistered vs. not preregistered studies {.tabset}
::: {.columns}

::: {.column width="95%"}
```{r prereg-dependency-table-reint}
#| tbl-cap: "Dependency table by type of registration (reintegration)"
#| tbl-cap-location: top
#| label: tbl-prereg-subgroup

prereg_subgroup_dat_cross <- cat_dat_cross(
  data = reintegration_dat,
  variable = prereg_chr,
  study_id = study
)

prereg_subgroup_dat_cross |>
  knitr::kable(
    "html",
    col.names = c(
      "Registration",
      colnames(prereg_subgroup_dat_cross)[-1]
    )
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = paste0("Values outside the parentheses are number of studies,", "
                     with the number of samples and effect size estimates shown in the parentheses."
                     ), 
    general_title = "Note: ",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

::: {.column-margin}
```{r prereg-dependency-table-mental}
#| tbl-cap: "Dependency table by type of registration (mental health)"
#| tbl-cap-location: top
#| label: tbl-prereg-subgroup-mental

prereg_subgroup_dat_cross_mental <- cat_dat_cross(
  data = mental_health_dat,
  variable = prereg_chr,
  study_id = study
)

prereg_subgroup_dat_cross_mental |>
  knitr::kable(
    "html",
    col.names = c(
      "Risk of bias judgment",
      colnames(prereg_subgroup_dat_cross_mental)[-1]
    ) 
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = paste0("Values outside the parentheses are number of studies,", "
                     with the number of samples and effect size estimates shown in the parentheses."
                     ), 
    general_title = "Note: ",
    footnote_as_chunk = T
  )  |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```
:::

:::

::: {.columns}

::: {.column width="95%"}
```{r prereg-ridge-reint}
#| label: fig-prereg-ridge-reint
#| fig-cap: "Distribution of effect size estimates, by type of registration (reintegrational outcome)."
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

cat_ridge(data = reintegration_dat, es = gt_pop, variable = prereg_chr, v = vgt_pop)
```
:::

::: {.column-margin}
```{r prereg-ridge-mental}
#| label: fig-prereg-ridge-mental
#| fig-cap: "Distribution of effect size estimates, by type of registration (mental health)."
#| fig.height: 6.5
#| fig.retina: 2
#| message: false

cat_ridge(data = gb_dat, es = gt_pop, variable = prereg_chr, v = vgt_pop) 
```
:::

:::

::: {.columns}

::: {.column width="130%"}
```{r prereg-rob-ridge-mental}
#| label: fig-prereg-rob-ridge-mental
#| fig-cap: "Distribution of effect size estimates, by risk of bias assessemnt across outcomes and registration (mental health)."
#| fig.height: 6
#| fig.width: 9
#| fig.retina: 2
#| message: false

cat_ridge(data = gb_dat, es = gt_pop, variable = overall_rob, v = vgt_pop) + 
  facet_grid(outcome_construct~prereg_chr) + 
  theme(
    strip.background = element_rect(color = "black", fill = "gray92")
  )
```
:::

:::
## Continuous moderators

::: {.columns}

::: {.column width="95%"}
```{r, continuous-mod-reint}
#| tbl-cap: "Distribution of continuous moderators (reintegration)"
#| tbl-cap-location: top
#| label: tbl-continuous-characteristics-reint

var_labels <- c(
  "Mean age" = "age",
  "Percent Male" = "male_pct",
  "Total Number of Sessions" = "sessions",
  "Sessions per Week" = "intensity",
  "Length of Intervention (in Weeks)" = "duration",
  "Weeks After End of Intervention" = "timing",
  "Weeks from Baseline" = "weeks_from_baseline"
)

continuous_descriptives <- 
 reintegration_dat |> 
  summarise(
    age = mean(age_mean),
    male_pct = mean(male_pct),
    sessions = mean(total_number_of_sessions),
    intensity = mean(sessions_per_week),
    duration = mean(duration_in_weeks),
    timing = mean(time_after_end_intervention_weeks),
    weeks_from_baseline = mean(time_from_baseline_weeks),
    .by = study
  ) 

continuous_descriptives_tab <- 
  continuous_descriptives |> 
  #pivot_longer(
  #  cols = age:male_pct,
  #  names_to = "var",
  #  values_to = "val"
  #) |> 
  #arrange(var)
  gather(var, val, age, male_pct, sessions, intensity, duration, timing, weeks_from_baseline) |>
  summarise(
    `% Missing` = 100 * mean(is.na(val)),
    Mean = mean(val, na.rm = TRUE),
    SD = sd(val, na.rm = TRUE),
    Min = min(val, na.rm = TRUE),
    LQ = quantile(val, na.rm = TRUE)[2],
    Median = median(val, na.rm = TRUE),
    UQ = quantile(val, na.rm = TRUE)[4],
    Max = max(val, na.rm = TRUE),
    .by = var
  ) |> 
  mutate(
    var = factor(var, levels = var_labels, labels = names(var_labels))
  )

knitr::kable(
  continuous_descriptives_tab, 
  col.names = c("Variable", colnames(continuous_descriptives_tab)[-1]),
  digits = 1,
  booktabs = TRUE
) |>
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) |>
  collapse_rows(1, valign = "top")

```
:::

::: {.column-margin}
```{r, continuous-mod-mental}
#| tbl-cap: "Distribution of continuous moderators (mental health)"
#| tbl-cap-location: top
#| label: tbl-continuous-characteristics-mental

var_labels_mental <- c(
  "Mean age" = "age",
  "Percent Male" = "male_pct",
  "N Sessions" = "sessions",
  "Sessions Week" = "intensity",
  "Length" = "duration",
  "Weeks After Intervention" = "timing",
  "Weeks Baseline" = "weeks_from_baseline"
)

continuous_descriptives_mental <- 
 mental_health_dat |> 
  summarise(
    age = mean(age_mean),
    male_pct = mean(male_pct),
    sessions = mean(total_number_of_sessions),
    intensity = mean(sessions_per_week),
    duration = mean(duration_in_weeks),
    timing = mean(time_after_end_intervention_weeks),
    weeks_from_baseline = mean(time_from_baseline_weeks),
    .by = study
  ) 

continuous_descriptives_tab_mental <- 
  continuous_descriptives_mental |> 
  #pivot_longer(
  #  cols = age:male_pct,
  #  names_to = "var",
  #  values_to = "val"
  #) |> 
  #arrange(var)
  gather(var, val, age, male_pct, sessions, intensity, duration, timing, weeks_from_baseline) |>
  summarise(
    `% Missing` = 100 * mean(is.na(val)),
    Mean = mean(val, na.rm = TRUE),
    SD = sd(val, na.rm = TRUE),
    Min = min(val, na.rm = TRUE),
    LQ = quantile(val, na.rm = TRUE)[2],
    Median = median(val, na.rm = TRUE),
    UQ = quantile(val, na.rm = TRUE)[4],
    Max = max(val, na.rm = TRUE),
    .by = var
  ) |> 
  mutate(
    var = factor(var, levels = var_labels_mental, labels = names(var_labels_mental))
  )

knitr::kable(
  continuous_descriptives_tab_mental, 
  col.names = c("Variable", colnames(continuous_descriptives_tab)[-1]),
  digits = 1,
  booktabs = TRUE
) |>
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) |>
  collapse_rows(1, valign = "top")

```
:::

:::

### Age distribution across studies
```{r density-plot-function}
density_plot <- function(variable, x_title, data, color = "cornflowerblue") {
  require(dplyr)
  require(tidyr)
  require(ggplot2)
  require(rlang)
  require(MetBrewer)
  
  var_exp <- enquo(variable)
  var_str <- as_label(var_exp)
  
  data |>
    ggplot(aes(x = !!var_exp)) +
    geom_density(fill = color, alpha = 0.8) +
    geom_rug(alpha = 0.7, length = unit(0.04, "npc")) +
    scale_y_continuous(labels = scales::label_number(accuracy = 10^(-3))) +
    theme_minimal() +
    labs(x = x_title, y = "")
}
```

::: {.columns}

::: {.column width="95%"}
```{r age-density-reint}
#| label: fig-age-density-reint
#| fig-cap: "Distribution of average age in a study (reintegrational)."
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

age_density <- density_plot(age, "Mean Age", continuous_descriptives)

age_density + expand_limits(x = 70)
```
:::

::: {.column-margin}
```{r age-density-mental}
#| label: fig-age-density-mental
#| fig-cap: "Distribution of average age in a study (mental health)."
#| fig.height: 6.5
#| fig.retina: 2
#| message: false

age_density_mental <- density_plot(age, "Mean Age", continuous_descriptives_mental, color = "gray")

age_density_mental + expand_limits(x = 70)
```
:::

:::

### Percent males in sample distribution across studies
::: {.columns}

::: {.column width="95%"}
```{r males-density-reint}
#| label: fig-males-density-reint
#| fig-cap: "Distribution proportion of males in each study (reintegration)."
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

male_density <- suppressWarnings(density_plot(male_pct, "Proportion Male", continuous_descriptives))
male_density 
```
:::

::: {.column-margin}
```{r males-density-mental}
#| label: fig-males-density-mental
#| fig-cap: "Distribution proportion of males in each study (mental health)."
#| fig.height: 6.5
#| fig.retina: 2
#| message: false

male_density_mental <- suppressWarnings(density_plot(male_pct, "Proportion Male", continuous_descriptives_mental, color = "gray"))
male_density_mental 
```
:::

:::

### Total number of sessions


```{r hist-plot-function}
hist_plot <- function(variable, x_title, data, color = "cornflowerblue") {
  require(dplyr)
  require(tidyr)
  require(ggplot2)
  require(rlang)
  require(MetBrewer)
  
  var_exp <- enquo(variable)
  var_str <- as_label(var_exp)
  
  x_vals <- data[[var_str]]
  min_val <- floor(min(x_vals, na.rm = TRUE))
  max_val <- ceiling(max(x_vals, na.rm = TRUE))
  
  data |>
    ggplot(aes(x = !!var_exp)) +
    geom_histogram(binwidth = 1, boundary = 0, fill = color, alpha = 0.8) +
    scale_x_continuous(breaks = pretty(seq(min_val, max_val, by = 1), n = 5)) +
    scale_y_continuous(breaks = seq(0, 10, 2)) +
    theme_minimal() +
    labs(x = x_title, y = "")
}
```


::: {.columns}

::: {.column width="95%"}
```{r sessions-hist-reint}
#| label: fig-sessions-hist-reint
#| fig-cap: "Distribution of study sessions (reintegration)."
#| fig.width: 7
#| fig.height: 4
#| fig.retina: 2
#| message: false

sessions_hist <- hist_plot(sessions, "Total Number of Sessions in Intervention", continuous_descriptives)
sessions_hist + labs(title = "Reintegration") + theme(plot.title = element_text(hjust = 0.5))
```
:::

::: {.column-margin}
```{r sessions-hist-mental}
#| label: fig-sessions-hist-mental
#| fig-cap: "Distribution of study sessions (mental health)."
#| fig.height: 6.5
#| fig.retina: 2
#| message: false

sessions_hist_mental <- hist_plot(sessions, "Total Number of Sessions in Intervention", continuous_descriptives_mental, color = "gray")
sessions_hist_mental + labs(title = "Mental Health") + theme(plot.title = element_text(hjust = 0.5))
```
:::

:::

### Duration and intensity (number of sessions per week)
::: {.columns}

::: {.column width="95%"}
```{r duration-plot-reint}
#| label: fig-duration-reint
#| fig-cap: "Length of intervention in weeks (reintegration)"
#| fig.width: 6.8
#| fig.height: 7
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

reintegration_dat |>
  select(study, duration_in_weeks, sessions_per_week, N_total) |> 
  filter(!is.na(sessions_per_week)) |>  
  arrange(desc(duration_in_weeks)) |> 
  mutate(
    study = factor(study, levels = unique(study)),
    sessions = case_when(
      sessions_per_week < 1 ~ "1<",
      sessions_per_week == 1 ~ "1",
      sessions_per_week == 1.5 ~ "1.5",
      sessions_per_week == 2 ~ "2",
      sessions_per_week == 2.5 ~ "2.5",
      sessions_per_week > 2 ~ ">10"
    ),
    sessions = factor(sessions, levels = unique(sessions))
  ) |> 
  ggplot(aes(y = study, x = duration_in_weeks, color = study)) +
  geom_segment(aes(x = 0, xend = duration_in_weeks, y = study, yend = study)) +
  geom_vline(xintercept = c(13, 26, 52, 78), linetype = "dashed", alpha = 0.5) +
  geom_point(
    aes(size = N_total)
  ) +
  scale_x_continuous(breaks = seq(0, 80, 10)) +
  facet_grid(vars(sessions_per_week), scales = "free_y", space = "free_y", switch = "y") + 
  #scale_size(breaks = c(0.5, 1, 1.5, 2, 10.5), limits = c(0, 10.5)) +
  labs(
    x = "Lenght of intervention in weeks", 
    y = "", 
    caption = paste0(
      "The light gray facet grids indicate the average number of sessions per week.\n", 
      "The dashed lines indicate 3 months, 6 months, 1 year, and 1.5 years, respectively.\n",
      "The point sizes are weighted by the study sample sizes."
      )
  ) +
  theme_minimal() + 
  scale_colour_discrete(guide = "none") +
  theme(
    legend.position = "none", 
    strip.text = element_text(color = "black"),
    strip.background.y = element_rect(fill = "gray93", color = "white"),
    strip.text.y.left = element_text(angle = 0),
    plot.caption = element_text(hjust = 0)
  ) 
```
:::

::: {.column-margin}
```{r duration-plot-mental}
#| label: fig-duration-mental
#| fig-cap: "Length of intervention in weeks (mental health)"
#| fig.height: 11
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

mental_health_dat |>
  select(study, duration_in_weeks, sessions_per_week, N_total) |> 
  filter(!is.na(sessions_per_week)) |>  
  arrange(desc(duration_in_weeks)) |> 
  mutate(
    study = factor(study, levels = unique(study)),
    sessions = case_when(
      sessions_per_week < 1 ~ "Less than 1",
      sessions_per_week == 1 ~ "1 per week",
      sessions_per_week == 2 ~ "2 per week",
      sessions_per_week > 2 ~ ">10"
    ),
    sessions = factor(sessions, levels = unique(sessions))
  ) |> 
  ggplot(aes(y = study, x = duration_in_weeks, color = study)) +
  geom_segment(aes(x = 0, xend = duration_in_weeks, y = study, yend = study)) +
  geom_vline(xintercept = c(13, 26, 52, 78), linetype = "dashed", alpha = 0.5) +
  geom_point(
    aes(size = N_total)
  ) +
  scale_x_continuous(breaks = seq(0, 80, 10)) +
  facet_grid(vars(sessions_per_week), scales = "free_y", space = "free_y", switch = "y") + 
  #scale_size(breaks = c(0.5, 1, 1.5, 2, 10.5), limits = c(0, 10.5)) +
  labs(
    x = "Lenght of intervention in weeks", 
    y = "", 
    caption = 
      paste0(
      "The light gray facet grids indicate the average number of sessions per week.\n", 
      "The dashed lines indicate 3 months, 6 months, 1 year, and 1.5 years, respectively.\n",
      "The point sizes are weighted by the study sample sizes."
      )
  ) +
  theme_minimal() + 
  scale_colour_discrete(guide = "none") +
  theme(
    legend.position = "none", 
    strip.text = element_text(color = "black"),
    strip.background.y = element_rect(fill = "gray93", color = "white"),
    strip.text.y.left = element_text(angle = 0),
    plot.caption = element_text(hjust = 0)
  )  
```
::: 

:::

### Weeks after end of intervention

::: {.columns}

::: {.column width="95%"}
```{r follow-up-plot-connected-reint}
#| label: fig-follow-up-connected-reint
#| fig-cap: "Weeks after end of interventions for all studies (reintegration)"
#| fig.width: 6.5
#| fig.height: 7
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

reintegration_dat |>
  select(study, time_after_end_intervention_weeks, N_total) |> 
  arrange(desc(study)) |> 
  mutate(study = factor(study, levels = unique(study))) |> 
  ggplot(aes(y = study, x = time_after_end_intervention_weeks, color = study)) +
  geom_point(aes(size = N_total),
             alpha = 0.5) +
  geom_line() +
  labs(x = "Weeks after end of intervention all studies", y = "")+
  theme_minimal() + 
  theme(legend.position = "none")
```
:::

::: {.column-margin}
```{r follow-up-plot-connected-mental}
#| label: fig-follow-up-connected-mental
#| fig-cap: "Weeks after end of interventions for all studies (mental health)"
#| fig.height: 11
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

mental_health_dat |>
  select(study, time_after_end_intervention_weeks, N_total) |> 
  arrange(desc(study)) |> 
  mutate(study = factor(study, levels = unique(study))) |> 
  ggplot(aes(y = study, x = time_after_end_intervention_weeks, color = study)) +
  geom_point(aes(size = N_total),
             alpha = 0.5) +
  geom_line() +
  labs(x = "Weeks after end of intervention all studies", y = "")+
  theme_minimal() + 
  theme(legend.position = "none")
```
::: 

:::

#### Correlation between effect size estimates and measurement timing
::: {.columns}

::: {.column width="95%"}
```{r es-time-plot-reint}
#| label: fig-es-time-reint
#| fig-cap: "Length of intervention in weeks (reintegration)"
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

reintegration_dat |> 
  select(study, gt_pop, vgt_pop, time_after_end_intervention_weeks) |> 
  ggplot() +
  aes(x = time_after_end_intervention_weeks, y = gt_pop, color = study) +
  geom_vline(xintercept = 0) + 
  geom_hline(yintercept = 0) + 
  geom_point(aes(size = 1/vgt_pop), alpha = 0.30) + 
  geom_smooth(method = "lm", formula = y ~ x, color = "yellow") + 
  scale_x_continuous(breaks = seq(0, 55, 5)) +
  theme_minimal() + 
  theme(legend.position = "none") + 
  labs(x = "Follow-up duration (months)", y = "Hedges' g")

```
:::

::: {.column-margin}
```{r es-time-plot-mental}
#| label: fig-es-time-mental
#| fig-cap: "Length of intervention in weeks (mental health)"
#| fig.height: 6
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

mental_health_dat |> 
  select(study, gt_pop, vgt_pop, time_after_end_intervention_weeks) |> 
  ggplot() +
  aes(x = time_after_end_intervention_weeks, y = gt_pop, color = study) +
  geom_vline(xintercept = 0) + 
  geom_hline(yintercept = 0) + 
 geom_point(aes(size = 1/vgt_pop), alpha = 0.30) + 
  geom_smooth(method = "lm", formula = y ~ x, color = "yellow") + 
  scale_x_continuous(breaks = seq(0, 55, 5)) +
  theme_minimal() + 
  theme(legend.position = "none") + 
  labs(x = "Follow-up duration (months)", y = "Hedges' g")
```
:::

:::


## Multivariate structure

### Covariance plots

::: {.columns}

::: {.column width="160%"}

::: {.panel-tabset}
### Substantial categorical and continuous moderators

::: {.panel-tabset}
#### Reintegration (across subgroup analyzed outcomes)

```{r, multivaraite-plot-reint}
#| label: fig-multivariate-plot-reint
#| fig-cap: "Multivariate structure between substaintial/theoretical categorical and continuous (reintegration)"
#| fig.width: 24
#| fig.height: 24
#| fig.retina: 2
#| message: false
#| eval: true

multivariate_dat_reint <- 
  reintegration_dat |>
  filter(str_detect(analysis_plan, "Alco|Hope|Social|Well")) |> 
  select(
    `Outcome` = analysis_plan,
    `Sample diagnosis` = schizophrenia,
    `Intervention` = CBT_int,
    `Type of test` = test_type,
    `Mean age` = age_mean,
    `% male` = male_pct,
    `Duration` = duration_in_weeks,
    `Intensity` = sessions_per_week,
    `Follow-up` = time_after_end_intervention_weeks
  )

multivariate_pairs_reint <- ggpairs(multivariate_dat_reint) + theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 10, angle = 45, vjust = 1, hjust=1),  
    axis.text.y = element_text(size = 10) 
  ) 

multivariate_pairs_reint
```


#### Mental health
```{r, multivaraite-dat-mental}
#| label: fig-multivariate-plot-mental
#| fig-cap: "Multivariate structure between substaintial/theoretical categorical and continuous covariates (mental health)"
#| fig.width: 24
#| fig.height: 24
#| fig.retina: 2
#| message: false
#| eval: true

multivariate_dat_mental <- 
  mental_health_dat |> 
  select(
    `Outcome` = analysis_plan,
    `Sample diagnosis` = schizophrenia,
    `Intervention` = CBT_int,
    `Type of test` = test_type,
    `Mean age` = age_mean,
    `% male` = male_pct,
    `Duration` = duration_in_weeks,
    `Intensity` = sessions_per_week,
    `Follow-up` = time_after_end_intervention_weeks
  )

multivariate_pairs_mental <- ggpairs(multivariate_dat_mental) + theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 10, angle = 45, vjust = 1, hjust=1),  
    axis.text.y = element_text(size = 10) 
  )

multivariate_pairs_mental
```

:::


### Methodological categorical and continuous moderators

::: {.panel-tabset}
#### Reintegration (across subgroup analyzed outcomes)

```{r, multivaraite-dat-reint-method}
#| label: fig-multivariate-plot-reint-method
#| fig-cap: "Multivariate structure between methodological categorical and continuous covariates (reintegration)"
#| fig.width: 24
#| fig.height: 24
#| fig.retina: 2
#| message: false
#| eval: true

multivariate_dat_reint_method <- 
  reintegration_dat |>
  filter(str_detect(analysis_plan, "Alco|Hope|Social|Well")) |> 
  select(
    `Strategy` = analysis_strategy,
    `Design` = QES_design,
    `Control grp` = control,
    `RoB` = overall_rob,
    `Preregistration` = prereg_chr,
    `Mean age` = age_mean,
    `% male` = male_pct,
    `Duration` = duration_in_weeks,
    `Intensity` = sessions_per_week,
    `Follow-up` = time_after_end_intervention_weeks
  )

multivariate_pairs_reint_method <- ggpairs(multivariate_dat_reint_method) + theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 9, angle = 45, vjust = 1, hjust=1),  
    axis.text.y = element_text(size = 9) 
  ) 

multivariate_pairs_reint_method
```

#### Mental health
```{r, multivaraite-dat-mental-method}
#| label: fig-multivariate-plot-mental-method
#| fig-cap: "Multivariate structure between methodological categorical and continuous (mental health)"
#| fig.width: 24
#| fig.height: 24
#| fig.retina: 2
#| message: false
#| eval: true

multivariate_dat_mental_method <- 
  mental_health_dat |> 
  select(
    `Strategy` = analysis_strategy,
    `Design` = QES_design,
    `Control grp` = control,
    `RoB` = overall_rob,
    `Preregistration` = prereg_chr,
    `Mean age` = age_mean,
    `% male` = male_pct,
    `Duration` = duration_in_weeks,
    `Intensity` = sessions_per_week,
    `Follow-up` = time_after_end_intervention_weeks
  )

multivariate_pairs_mental_method <- ggpairs(multivariate_dat_mental_method) + theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 9, angle = 45, vjust = 1, hjust=1),  
    axis.text.y = element_text(size = 9) 
  )

multivariate_pairs_mental_method 
```

:::


### Substantial and methodological categorical moderators

::: {.panel-tabset}
#### Reintegration (across subgroup analyzed outcomes)

```{r, multivaraite-dat-reint-method-theoretical}
#| label: fig-multivariate-plot-reint-method-theoretical
#| fig-cap: "Multivariate structure between substantial and methodological categorical covariates (reintegration)"
#| fig.width: 24
#| fig.height: 24
#| fig.retina: 2
#| message: false
#| eval: true

multivariate_dat_reint_method_theo <- 
  reintegration_dat |>
  filter(str_detect(analysis_plan, "Alco|Hope|Social|Well")) |> 
  select(
    `Outcome` = analysis_plan,
    `Sample diagnosis` = schizophrenia,
    `Intervention` = CBT_int,
    `Type of test` = test_type,
    `Strategy` = analysis_strategy,
    `Design` = QES_design,
    `Control grp` = control,
    `RoB` = overall_rob,
    `Preregistration` = prereg_chr
  )

multivariate_pairs_reint_method_theo <- ggpairs(multivariate_dat_reint_method_theo) + theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 9, angle = 45, vjust = 1, hjust=1),  
    axis.text.y = element_text(size = 9) 
  ) 

multivariate_pairs_reint_method_theo
```

#### Mental health
```{r, multivaraite-dat-mental-method-theoretical}
#| label: fig-multivariate-plot-mental-method-theoretical
#| fig-cap: "Multivariate structure between substantial and methodological categorical covariates (mental health)"
#| fig.width: 24
#| fig.height: 24
#| fig.retina: 2
#| message: false
#| eval: true

multivariate_dat_mental_method_theo <- 
  mental_health_dat |> 
  select(
    `Outcome` = analysis_plan,
    `Sample diagnosis` = schizophrenia,
    `Intervention` = CBT_int,
    `Type of test` = test_type,
    `Strategy` = analysis_strategy,
    `Design` = QES_design,
    `Control grp` = control,
    `RoB` = overall_rob,
    `Preregistration` = prereg_chr,
    `Mean age` = age_mean,
    `% male` = male_pct,
    `Duration` = duration_in_weeks,
    `Intensity` = sessions_per_week,
    `Follow-up` = time_after_end_intervention_weeks
  )

multivariate_pairs_mental_method_theo <- ggpairs(multivariate_dat_mental_method_theo) + theme(
    text = element_text(size = 18),
    axis.text.x = element_text(size = 9, angle = 45, vjust = 1, hjust=1),  
    axis.text.y = element_text(size = 9) 
  )

multivariate_pairs_mental_method_theo
```

:::

:::

:::

:::

### Covariance matrices
::: {.columns}

::: {.column width="160%"}

::: {.panel-tabset}
### Reintegrational outcomes

::: {.panel-tabset}
#### Across all outcomes
```{r correlation-matrix-reint}
#| tbl-cap: "Correlation matrix across all reintegration outcomes."
#| tbl-cap-location: top
#| label: tbl-cor-matix-reint
#| message: false

cor_mat_dat_cat <- 
  reintegration_dat |> 
  filter(str_detect(analysis_plan, "Alco|Hope|Social|Well") & test_type != "Raw events") |> 
  select(
    plan = analysis_plan,
    samp = schizophrenia,
    treat = CBT_int,
    test = test_type,
    str = analysis_strategy,
    des = QES_design,
    ctr = control,
    rob = overall_rob,
    pre = prereg_chr
  )

cat_dummy_dat <- 
  fastDummies::dummy_cols(cor_mat_dat_cat) %>% 
  select(where(is.numeric))


cor_mat_dat_con <- 
  reintegration_dat |> 
  filter(str_detect(analysis_plan, "Alco|Hope|Social|Well") & test_type != "Raw events") |> 
  select(
    age = age_mean,
    male = male_pct,
    dur = duration_in_weeks,
    int = sessions_per_week,
    FU = time_after_end_intervention_weeks,
    sess = total_number_of_sessions
  )

cor_mat_dat <- 
  bind_cols(cat_dummy_dat, cor_mat_dat_con) |> 
  select(
    alcho = `plan_Alcohol and drug abuse/misuse`,
    hope = `plan_Hope, empowerment & self-efficacy`,
    sfunc = `plan_Social functioning (degree of impairment)`,
    wellb = `plan_Wellbeing and quality of life`,
    s_schizo = samp_Schizophrenia,
    s_oth = samp_Other,
    cbt_trt = treat_CBT, 
    oth_trt = treat_Other,
    test_clin = `test_Clinician-rated measure`,
    test_self = `test_Self-reported`,
    itt = str_ITT,
    tot = str_TOT,
    qes = des_QES,
    rct = des_RCT,
    tau = ctr_TAU,
    tau_wait = `ctr_TAU with Waiting-list`,
    wait = `ctr_Waiting-list only`,
    ind_trt = `ctr_Individual treatment` ,
    rob_low = rob_Low,
    rob_mod = `rob_Some concerns/Moderate`,
    rob_high = `rob_Serious/High`,
    prereg = pre_Preregistered, 
    conventional = `pre_Not preregistered`,
    everything()
  ) |> 
  na.omit()

cor_mat <- 
  cor(
  model.matrix(
    reformulate(names(cor_mat_dat[,1:ncol(cor_mat_dat)])), 
    data = cor_mat_dat
    )
  ) |>  
  as.data.frame() |> 
  select(-c(`(Intercept)`)) |>  
  na.omit() |> 
  mutate(
    
    across(.cols = everything(), ~ round(.x, 2))
  )

cor_mat_formatted <- 
  cor_mat |> 
  mutate(
    across(.cols = everything(), ~ cell_spec(.x, bold = ifelse(abs(.x) > 0.5, T, F)))
  )

kbl(
  cor_mat_formatted, 
  escape = F,
  col.names = c("Category", colnames(cor_mat))
  ) |> 
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    font_size = 10
  ) |> 
  scroll_box(width = "100%", height = "100%", fixed_thead = TRUE)

```

#### Alcohol and drug abuse/misuse
Excluded factors due to no variation: type of sample (schizophania vs. rest), low risk of bias.
```{r correlation-matrix-alcohol}
#| tbl-cap: "Correlation matrix based on alcohol outcome only."
#| tbl-cap-location: top
#| label: tbl-cor-matix-alcohol
#| message: false

cor_mat_dat_cat_alcohol <- 
  reintegration_dat |> 
  filter(str_detect(analysis_plan, "Alco") & test_type != "Raw events") |> 
  select(
    treat = CBT_int,
    test = test_type,
    str = analysis_strategy,
    des = QES_design,
    ctr = control,
    rob = overall_rob,
    pre = prereg_chr
  )

cat_dummy_dat_alcohol <- 
  fastDummies::dummy_cols(cor_mat_dat_cat_alcohol) %>% 
  select(where(is.numeric))


cor_mat_dat_con_alcohol <- 
  reintegration_dat |> 
  filter(str_detect(analysis_plan, "Alco") & test_type != "Raw events") |> 
  select(
    age = age_mean,
    male = male_pct,
    dur = duration_in_weeks,
    int = sessions_per_week,
    FU = time_after_end_intervention_weeks,
    sess = total_number_of_sessions
  )

cor_mat_dat_alcohol <- 
  bind_cols(cat_dummy_dat_alcohol, cor_mat_dat_con_alcohol) |> 
  select(
    cbt_trt = treat_CBT, 
    oth_trt = treat_Other,
    test_clin = `test_Clinician-rated measure`,
    test_self = `test_Self-reported`,
    itt = str_ITT,
    tot = str_TOT,
    qes = des_QES,
    rct = des_RCT,
    tau = ctr_TAU,
    tau_wait = `ctr_TAU with Waiting-list`,
    rob_mod = `rob_Some concerns/Moderate`,
    rob_high = `rob_Serious/High`,
    prereg = pre_Preregistered, 
    conventional = `pre_Not preregistered`,
    age:sess
  ) |> 
  na.omit()

cor_mat_alcohol <- 
  cor(
    model.matrix(
      reformulate(names(cor_mat_dat_alcohol[,1:ncol(cor_mat_dat_alcohol)])), 
      data = cor_mat_dat_alcohol
    )
  ) |> 
  as.data.frame() |> 
  select(-c(`(Intercept)`)) |>   
  na.omit() |> 
  mutate(
    
    across(.cols = everything(), ~ round(.x, 2))
  )

cor_mat_formatted_alcohol <- 
  cor_mat_alcohol |> 
  mutate(
    across(.cols = everything(), ~ cell_spec(.x, bold = ifelse(abs(.x) > 0.5, T, F)))
  )


kbl(
  cor_mat_formatted_alcohol, 
  escape = F,
  col.names = c("Category", colnames(cor_mat_alcohol))
  ) |> 
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    font_size = 10
  ) |> 
  scroll_box(width = "100%", height = "100%", fixed_thead = TRUE)

```


#### Hope, empowerment & self-efficacy
Excluded factors due to no variation: type of intervention (CBT vs. rest) and type of test.
```{r correlation-matrix-hope}
#| tbl-cap: "Correlation matrix based on hope, empowerment & self-efficacy outcomes only."
#| tbl-cap-location: top
#| label: tbl-cor-matix-hope
#| message: false

cor_mat_dat_cat_hope <- 
  reintegration_dat |> 
  filter(str_detect(analysis_plan, "Hope") & test_type != "Raw events") |> 
  select(
    samp = schizophrenia,
    treat = CBT_int,
    test = test_type,
    str = analysis_strategy,
    des = QES_design,
    ctr = control,
    rob = overall_rob,
    pre = prereg_chr
  )

cat_dummy_dat_hope <- 
  fastDummies::dummy_cols(cor_mat_dat_cat_hope) %>% 
  select(where(is.numeric))


cor_mat_dat_con_hope <- 
  reintegration_dat |> 
  filter(str_detect(analysis_plan, "Hope") & test_type != "Raw events") |> 
  select(
    age = age_mean,
    male = male_pct,
    dur = duration_in_weeks,
    int = sessions_per_week,
    FU = time_after_end_intervention_weeks,
    sess = total_number_of_sessions
  )

cor_mat_dat_hope <- 
  bind_cols(cat_dummy_dat_hope, cor_mat_dat_con_hope) |> 
  select(
    s_schizo = samp_Schizophrenia,
    s_oth = samp_Other,
    itt = str_ITT,
    tot = str_TOT,
    qes = des_QES,
    rct = des_RCT,
    tau = ctr_TAU,
    tau_wait = `ctr_TAU with Waiting-list`,
    wait = `ctr_Waiting-list only`,
    ind_trt = `ctr_Individual treatment` ,
    rob_low = rob_Low,
    rob_mod = `rob_Some concerns/Moderate`,
    rob_high = `rob_Serious/High`,
    prereg = pre_Preregistered, 
    conventional = `pre_Not preregistered`,
    age:sess
  ) |> 
  na.omit()

cor_mat_hope <- 
  cor(
    model.matrix(
      reformulate(names(cor_mat_dat_hope[,1:ncol(cor_mat_dat_hope)])), 
      data = cor_mat_dat_hope
    )
  ) |>  
  as.data.frame() |>  
  select(-c(`(Intercept)`)) |>  
  na.omit() |> 
  mutate(
    across(.cols = everything(), ~ round(.x, 2))
  )

cor_mat_formatted_hope <- 
  cor_mat_hope |> 
  mutate(
    across(.cols = everything(), ~ cell_spec(.x, bold = ifelse(abs(.x) > 0.5, T, F)))
  )

kbl(
  cor_mat_formatted_hope, 
  escape = F,
  col.names = c("Category", colnames(cor_mat_hope))
  ) |> 
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    font_size = 10
  ) |> 
  scroll_box(width = "100%", height = "100%", fixed_thead = TRUE)

```

#### Social functioning (degree of impairment)
Excluded factors due to no appearance: waitlist-only
```{r correlation-matrix-social}
#| tbl-cap: "Correlation matrix based on social functioning outcomes only."
#| tbl-cap-location: top
#| label: tbl-cor-matix-social
#| message: false

cor_mat_dat_cat_social <- 
  reintegration_dat |> 
  filter(str_detect(analysis_plan, "Social") & test_type != "Raw events") |> 
  select(
    samp = schizophrenia,
    treat = CBT_int,
    test = test_type,
    str = analysis_strategy,
    des = QES_design,
    ctr = control,
    rob = overall_rob,
    pre = prereg_chr
  )

cat_dummy_dat_social <- 
  fastDummies::dummy_cols(cor_mat_dat_cat_social) %>% 
  select(where(is.numeric))


cor_mat_dat_con_social <- 
  reintegration_dat |> 
  filter(str_detect(analysis_plan, "Social") & test_type != "Raw events") |> 
  select(
    age = age_mean,
    male = male_pct,
    dur = duration_in_weeks,
    int = sessions_per_week,
    FU = time_after_end_intervention_weeks,
    sess = total_number_of_sessions
  )

cor_mat_dat_social <- 
  bind_cols(cat_dummy_dat_social, cor_mat_dat_con_social) |> 
  select(
    s_schizo = samp_Schizophrenia,
    s_oth = samp_Other,
    cbt_trt = treat_CBT, 
    oth_trt = treat_Other,
    test_clin = `test_Clinician-rated measure`,
    test_self = `test_Self-reported`,
    itt = str_ITT,
    tot = str_TOT,
    qes = des_QES,
    rct = des_RCT,
    tau = ctr_TAU,
    tau_wait = `ctr_TAU with Waiting-list`,
    ind_trt = `ctr_Individual treatment` ,
    rob_low = rob_Low,
    rob_mod = `rob_Some concerns/Moderate`,
    rob_high = `rob_Serious/High`,
    prereg = pre_Preregistered, 
    conventional = `pre_Not preregistered`,
    everything()
  ) |> 
  na.omit()

cor_mat_social <- 
  cor(
    model.matrix(
      reformulate(names(cor_mat_dat_social[,1:ncol(cor_mat_dat_social)])), 
      data = cor_mat_dat_social
      )
  ) |> 
  as.data.frame() |>  
  select(-c(`(Intercept)`)) |> 
  na.omit() |> 
  mutate(
    across(.cols = everything(), ~ round(.x, 2))
  )

cor_mat_formatted_social <- 
  cor_mat_social |> 
  mutate(
    across(.cols = everything(), ~ cell_spec(.x, bold = ifelse(abs(.x) > 0.5, T, F)))
  )

kbl(
  cor_mat_formatted_social, 
  escape = F,
  col.names = c("Category", colnames(cor_mat_social))
  ) |> 
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    font_size = 10
  ) |> 
  scroll_box(width = "100%", height = "100%", fixed_thead = TRUE)

```

#### Wellbeing and quality of life
Excluded factors due to no appearance: waitlist-only
```{r correlation-matrix-wellbeing}
#| tbl-cap: "Correlation matrix based on wellbeing and quality of life outcomes only."
#| tbl-cap-location: top
#| label: tbl-cor-matix-wellbeing
#| message: false

cor_mat_dat_cat_well <- 
  reintegration_dat |> 
  filter(str_detect(analysis_plan, "Well") & test_type != "Raw events") |> 
  select(
    samp = schizophrenia,
    treat = CBT_int,
    test = test_type,
    str = analysis_strategy,
    des = QES_design,
    ctr = control,
    rob = overall_rob,
    pre = prereg_chr
  )

cat_dummy_dat_well <- 
  fastDummies::dummy_cols(cor_mat_dat_cat_well) %>% 
  select(where(is.numeric))


cor_mat_dat_con_well <- 
  reintegration_dat |> 
  filter(str_detect(analysis_plan, "Well") & test_type != "Raw events") |> 
  select(
    age = age_mean,
    male = male_pct,
    dur = duration_in_weeks,
    int = sessions_per_week,
    FU = time_after_end_intervention_weeks,
    sess = total_number_of_sessions
  )

cor_mat_dat_well <- 
  bind_cols(cat_dummy_dat_well, cor_mat_dat_con_well) |> 
  select(
    s_schizo = samp_Schizophrenia,
    s_oth = samp_Other,
    cbt_trt = treat_CBT, 
    oth_trt = treat_Other,
    test_clin = `test_Clinician-rated measure`,
    test_self = `test_Self-reported`,
    itt = str_ITT,
    tot = str_TOT,
    qes = des_QES,
    rct = des_RCT,
    tau = ctr_TAU,
    tau_wait = `ctr_TAU with Waiting-list`,
    wait = `ctr_Waiting-list only`,
    ind_trt = `ctr_Individual treatment` ,
    rob_low = rob_Low,
    rob_mod = `rob_Some concerns/Moderate`,
    rob_high = `rob_Serious/High`,
    prereg = pre_Preregistered, 
    conventional = `pre_Not preregistered`,
    everything()
  ) |> 
  na.omit()

cor_mat_well <- 
  cor(
    model.matrix(
      reformulate(names(cor_mat_dat_well[,1:ncol(cor_mat_dat_well)])), 
      data = cor_mat_dat_well
      )
  ) |> 
  as.data.frame() |>  
  select(-c(`(Intercept)`)) |> 
  na.omit() |> 
  mutate(
    across(.cols = everything(), ~ round(.x, 2))
  )

cor_mat_formatted_well <- 
  cor_mat_well |> 
  mutate(
    across(.cols = everything(), ~ cell_spec(.x, bold = ifelse(abs(.x) > 0.5, T, F)))
  )

kbl(
  cor_mat_formatted_well, 
  escape = F,
  col.names = c("Category", colnames(cor_mat_well))
  ) |> 
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    font_size = 10
  ) |> 
  scroll_box(width = "100%", height = "100%", fixed_thead = TRUE)

```

:::

### Mental health outcomes

```{r correlation-matrix-mental}
#| tbl-cap: "Correlation matrix across all mental health outcomes."
#| tbl-cap-location: top
#| label: tbl-cor-matix-mental
#| message: false

cor_mat_dat_cat_mental <- 
  mental_health_dat |> 
  filter(test_type != "Raw events") |> 
  select(
    plan = analysis_plan,
    samp = schizophrenia,
    treat = CBT_int,
    test = test_type,
    str = analysis_strategy,
    des = QES_design,
    ctr = control,
    rob = overall_rob,
    pre = prereg_chr
  )

cat_dummy_dat_mental <- 
  fastDummies::dummy_cols(cor_mat_dat_cat_mental) %>% 
  select(where(is.numeric))


cor_mat_dat_con_mental <- 
  mental_health_dat |>  
  filter(test_type != "Raw events") |> 
  select(
    age = age_mean,
    male = male_pct,
    dur = duration_in_weeks,
    int = sessions_per_week,
    FU = time_after_end_intervention_weeks,
    sess = total_number_of_sessions
  )

cor_mat_dat_mental <- 
  bind_cols(cat_dummy_dat_mental, cor_mat_dat_con_mental) |> 
  select(
    anxiety = plan_Anxiety,
    depress = plan_Depression,
    g_mental = `plan_General mental health`,
    symptoms = `plan_Symptoms of psychosis`,
    s_schizo = samp_Schizophrenia,
    s_oth = samp_Other,
    cbt_trt = treat_CBT, 
    oth_trt = treat_Other,
    test_clin = `test_Clinician-rated measure`,
    test_self = `test_Self-reported`,
    itt = str_ITT,
    tot = str_TOT,
    qes = des_QES,
    rct = des_RCT,
    tau = ctr_TAU,
    tau_wait = `ctr_TAU with Waiting-list`,
    wait = `ctr_Waiting-list only`,
    ind_trt = `ctr_Individual treatment` ,
    rob_low = rob_Low,
    rob_mod = `rob_Some concerns/Moderate`,
    rob_high = `rob_Serious/High`,
    prereg = pre_Preregistered, 
    conventional = `pre_Not preregistered`,
    everything()
  ) |> 
  na.omit()

cor_mat_mental <- 
  cor(
    model.matrix(
      reformulate(names(cor_mat_dat_mental[,1:ncol(cor_mat_dat_mental)])), 
      data = cor_mat_dat_mental
      )
  ) %>% 
  as.data.frame() %>% 
  select(-c(`(Intercept)`)) %>% 
  na.omit() |> 
  mutate(
    
    across(.cols = everything(), ~ round(.x, 2))
  )

cor_mat_formatted_mental <- 
  cor_mat_mental |> 
  mutate(
    across(.cols = everything(), ~ cell_spec(.x, bold = ifelse(abs(.x) > 0.5, T, F)))
  )


kbl(
  cor_mat_formatted_mental, 
  escape = F,
  col.names = c("Category", colnames(cor_mat_mental))
  ) |> 
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    font_size = 10
  ) |> 
  scroll_box(width = "100%", height = "100%", fixed_thead = TRUE)

```

:::

:::

:::

# Standard Errors and Other Auxiliary Data

## SE forest plot

This forest plot shows the within- and between study variation of standard error of effect size estimates for reintegrational outcomes.

::: {.columns}

::: {.column width="95%"}
```{r se-plot-reintegration}
#| label: fig-forset-plot-se
#| fig-cap: "Forest plot of standard error of reintegrational effect size estimates."
#| fig.width: 6.8
#| fig.height: 7
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

reintegration_dat |> 
  arrange(desc(study)) |>
  mutate(
    study = factor(study, unique(study)),
    segt_pop = sqrt(vgt_pop)
    ) |> 
  ggplot(aes(x = segt_pop, y = study, color = study)) +
  geom_point(aes(size = N_total), alpha = 0.5) +
  scale_y_discrete() +
  theme_minimal() +
  labs(y = "", x = "SE") +
  theme(legend.position = "none", axis.text.y = element_text(size = 10))

```
:::

::: {.column-margin}
```{r se-plot-mental}
#| label: fig-forset-plot-se-mental
#| fig-cap: "Forest plot of standard error of mental health effect size estimates."
#| fig.height: 11
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

mental_health_dat |> 
  arrange(desc(study)) |>
  mutate(
    study = factor(study, unique(study)),
    segt_pop = sqrt(vgt_pop)
    ) |> 
  ggplot(aes(x = segt_pop, y = study, color = study)) +
  geom_point(aes(size = N_total), alpha = 0.5) +
  scale_y_discrete() +
  theme_minimal() +
  labs(y = "", x = "SE") +
  theme(legend.position = "none", axis.text.y = element_text(size = 10))

```
:::

:::

## Modified SE forest plot
::: {.columns}

::: {.column width="95%"}
```{r se-plot-reintegration-modified}
#| label: fig-forset-plot-se-modified
#| fig-cap: "Forest plot of modified standard error of reintegrational effect size estimates."
#| fig.width: 6.8
#| fig.height: 7
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

reintegration_dat |> 
  arrange(desc(study)) |>
  mutate(
    study = factor(study, unique(study)),
    Wse_pop = sqrt(Wgt_pop)
    ) |> 
  ggplot(aes(x = Wse_pop, y = study, color = study)) +
  geom_point(aes(size = N_total), alpha = 0.5, position = position_jitter(height = 0.4)) +
  scale_y_discrete() +
  theme_minimal() +
  labs(y = "", x = "Modified SE") +
  theme(legend.position = "none", axis.text.y = element_text(size = 10))

```
:::

::: {.column-margin}
```{r se-plot-mental-modified}
#| label: fig-forset-plot-se-mental-modified
#| fig-cap: "Forest plot of modified standard error of mental health effect size estimates."
#| fig.height: 11
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

mental_health_dat |> 
  arrange(desc(study)) |>
  mutate(
    study = factor(study, unique(study)),
    Wse_pop = sqrt(Wgt_pop)
    ) |> 
  ggplot(aes(x = Wse_pop, y = study, color = study)) +
  geom_point(aes(size = N_total), alpha = 0.5, position = position_jitter(height = 0.4)) +
  scale_y_discrete() +
  theme_minimal() +
  labs(y = "", x = "Modified SE") +
  theme(legend.position = "none", axis.text.y = element_text(size = 10))

```
:::

:::

## Inverse sampling covariance weights plot
::: {.columns}

::: {.column width="95%"}
```{r ISCW-plot}
#| label: fig-iscw
#| fig-cap: "Plot of inverse sampling covariance (ISC) weights for each study (reintegrational outcomes)"
#| fig.width: 6.8
#| fig.height: 7
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

iscw <-
  function(k, rho, v) {
    iscw_weights <-  k / (((k - 1) * rho + 1) * v)
    return(iscw_weights)
  }

rho_val <- round(seq(0, 0.8, 0.2), 1)

ISCW_plot <- 
  reintegration_dat |> 
  expand_grid(rho = rho_val) |> 
  group_by(study, rho) |> 
  summarise(
    k = n(),
    v_bar = mean(vgt_pop)
  ) |> 
  ungroup() |> 
  mutate(iscw_w = iscw(k, rho, v_bar),
         depd = ifelse(k > 1, 1, 0)) |> 
  group_by(rho) |> 
  mutate(iscw_w_norm = iscw_w / sum(iscw_w)) |> 
  ungroup() |> 
  distinct(study, rho, iscw_w_norm, depd) |> 
  mutate(study = factor(study, levels = study[rho == 0.8][order(iscw_w_norm[rho == 0.8])])) |> 
  ggplot(aes(y = iscw_w_norm, x = study, group = factor(rho), colour = factor(rho))) +
  geom_point() +
  geom_line() + 
  theme_minimal() +
  coord_flip() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.8, 0.2)
  ) +
  labs(x = "", y = "Normalized Weight", colour = "Assumed Correlation") 

ISCW_plot

```
:::

::: {.column-margin}
```{r ISCW-plot-mental}
#| label: fig-iscw-mental
#| fig-cap: "Plot of inverse sampling covariance (ISC) weights for each study (mental healt outcomes)"
#| fig.height: 11
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

ISCW_plot_mental <- 
  mental_health_dat |> 
  expand_grid(rho = rho_val) |> 
  group_by(study, rho) |> 
  summarise(
    k = n(),
    v_bar = mean(vgt_pop)
  ) |> 
  ungroup() |> 
  mutate(iscw_w = iscw(k, rho, v_bar),
         depd = ifelse(k > 1, 1, 0)) |> 
  group_by(rho) |> 
  mutate(iscw_w_norm = iscw_w / sum(iscw_w)) |> 
  ungroup() |> 
  distinct(study, rho, iscw_w_norm, depd) |> 
  mutate(study = factor(study, levels = study[rho == 0.8][order(iscw_w_norm[rho == 0.8])])) |> 
  ggplot(aes(y = iscw_w_norm, x = study, group = factor(rho), colour = factor(rho))) +
  geom_point() +
  geom_line() + 
  theme_minimal() +
  coord_flip() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.85, 0.2)
  ) +
  labs(x = "", y = "Normalized Weight", colour = "Assumed Correlation") 

ISCW_plot_mental

```
:::

:::

## Study sample sizes versus standard error estimates

::: {.columns}

::: {.column width="95%"}
```{r sample-vs-se}
#| label: fig-sample-vs-se
#| fig-cap: "Study sample sizes versus reintegrational standard error estimates"
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

reintegration_dat |> 
  mutate(segt_pop = sqrt(vgt_pop)) |> 
  ggplot(aes(N_total, segt_pop)) + 
  geom_point() +
  geom_smooth() +
  theme_bw() +
  labs(x = "Total sample size", y = "Modified standard error")

```
:::

::: {.column-margin}
```{r sample-vs-se-mental}
#| label: fig-sample-vs-se-mental
#| fig-cap: "Study sample sizes versus mental health standard error estimates"
#| fig.height: 5.5
#| fig.retina: 2
#| message: false

mental_health_dat |> 
  mutate(segt_pop = sqrt(vgt_pop)) |> 
  ggplot(aes(N_total, segt_pop)) + 
  geom_point() +
  geom_smooth() +
  theme_bw() +
  labs(x = "Total sample size", y = "Modified standard error")

```
:::

:::

## Standard error vs. scaled standrad error
::: {.columns}

::: {.column width="95%"}
```{r se-vs-scaled}
#| label: fig-se-vs-scaled
#| fig-cap: "Standard error vs. modified standard errors (reintegration)"
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false


reintegration_dat |> 
  mutate(
    sample_above_100 = if_else(N_total >100, "Sample > 100", "Sample < 100"),
    sample_above_100 = factor(sample_above_100, levels = c( "Sample > 100", "Sample < 100")),
    segt_pop = sqrt(vgt_pop),
    diff_se = sqrt(Wgt_pop) - sqrt(vgt_pop)
  ) |> 
  ggplot(aes(gt_pop, diff_se, color = sample_above_100)) + 
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw() +
  theme(
    plot.caption=element_text(hjust = 0, size = 10),
    legend.position= "bottom",
    legend.title = element_blank(),
    panel.spacing.x = unit(5, "mm"), 
    panel.spacing.y = unit(5, "mm"),
    #panel.grid.major = element_blank(),
    #panel.grid.minor = element_blank()
  ) +
  scale_x_continuous(expand=c(0,0), breaks = seq(-1L, 1.5, 0.2)) + 
  scale_y_continuous(expand=c(0,0), breaks = seq(-0.1, 0.1, 0.01)) + 
  expand_limits(x = c(-0.6, 1.5), y = c(-0.041, 0.01)) +
  labs(y = "Modified SE - SE (used in main analysis)", x = "Effect size estimate")


```
:::

::: {.column-margin}
```{r se-vs-scaled-mental}
#| label: fig-se-vs-scaled-mental
#| fig-cap: "Standard error vs. modified standard errors (mental health outcomes)"
#| fig.height: 5.5
#| fig.retina: 2
#| message: false

mental_health_dat |> 
  mutate(
    sample_above_100 = if_else(N_total >100, "Sample > 100", "Sample < 100"),
    sample_above_100 = factor(sample_above_100, levels = c( "Sample > 100", "Sample < 100")),
    segt_pop = sqrt(vgt_pop),
    diff_se = sqrt(Wgt_pop) - sqrt(vgt_pop)
  ) |> 
  ggplot(aes(gt_pop, diff_se, color = sample_above_100)) + 
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw() +
  theme(
    plot.caption=element_text(hjust = 0, size = 10),
    legend.position= "bottom",
    legend.title = element_blank(),
    panel.spacing.x = unit(5, "mm"), 
    panel.spacing.y = unit(5, "mm"),
    #panel.grid.major = element_blank(),
    #panel.grid.minor = element_blank()
  ) +
  scale_x_continuous(expand=c(0,0), breaks = seq(-1L, 2, 0.2)) + 
  scale_y_continuous(expand=c(0,0), breaks = seq(-0.1, 0.1, 0.01)) + 
  expand_limits(x = c(-0.71, 2), y = c(-0.091, 0.01)) +
  labs(y = "Modified SE - SE (used in main analysis)", x = "Effect size estimate")



```

:::

:::

# Effect size estimates distributions and outliers

## Marginal distributions 
::: {.columns}

::: {.column width="95%"}
```{r es-distribution-table}
#| tbl-cap-location: top
#| label: tab-es-distribution
reintegration_dat$gt_pop |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) |>
  knitr::kable(
    digits = 2,
    caption = "Marginal distribution of effect size estimates",
    booktabs = TRUE
  )  |> 
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)
```
:::

::: {.column-margin} 
```{r es-distribution-table-mental}
#| tbl-cap-location: top
#| label: tab-es-distribution-mental
mental_health_dat$gt_pop |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) |>
  knitr::kable(
    digits = 2,
    caption = "Marginal distribution of effect size estimates",
    booktabs = TRUE
  )  |> 
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)
```
:::

:::

## Marginal distribution plots

::: {.columns}

::: {.column width="95%"}
```{r es-distribution-plot}
#| label: fig-es-distribution
#| fig-cap: "Empirical distribution of reintegrational effect size estimates. Solid vertical lines indicate lower and upper quartiles. Dashed lines indicate the 1st quartile minus 3 times the inter-quartile range and the 3rd quartile plus 3 times the interquartile range. Effect sizes outside of the range of dashed lines would be considered outliers according to Tukey's (1977) definition."
#| fig.width: 8
#| fig.height: 2.5
#| fig.retina: 2
#| message: false


qrtls <- quantile(reintegration_dat$gt_pop, c(.25, .75), na.rm = TRUE)
fences <-  qrtls + 3 * diff(qrtls) * c(-1, 1)
fence_dat <- data.frame(qrtl = qrtls, fence = fences)

es_dist_plot <- 
  ggplot(reintegration_dat, aes(gt_pop)) + 
  geom_density(fill = "cornflowerblue", alpha = 0.8) + 
  geom_vline(data = fence_dat, aes(xintercept = qrtl), linetype = "solid") + 
  geom_vline(data = fence_dat, aes(xintercept = fence), linetype = "dashed") + 
  geom_rug(alpha = 0.25) + 
  theme_minimal() + 
  theme(axis.title.y = element_blank()) +
  labs(x = "Effect size estimate")

es_dist_plot

```
:::

::: {.column-margin} 
```{r es-distribution-plot-mental}
#| label: fig-es-distribution-mental
#| fig-cap: "Empirical distribution of mental health effect size estimates. Solid vertical lines indicate lower and upper quartiles. Dashed lines indicate the 1st quartile minus 3 times the inter-quartile range and the 3rd quartile plus 3 times the interquartile range. Effect sizes outside of the range of dashed lines would be considered outliers according to Tukey's (1977) definition."
#| fig.height: 4
#| fig.retina: 2
#| message: false


qrtls_mental <- quantile(mental_health_dat$gt_pop, c(.25, .75), na.rm = TRUE)
fences_mental <-  qrtls_mental + 3 * diff(qrtls_mental) * c(-1, 1)
fence_dat_mental <- data.frame(qrtl = qrtls_mental, fence = fences_mental)

es_dist_plot_mental <- 
  ggplot(mental_health_dat, aes(gt_pop)) + 
  geom_density(fill = "gray", alpha = 0.8) + 
  geom_vline(data = fence_dat_mental, aes(xintercept = qrtl), linetype = "solid") + 
  geom_vline(data = fence_dat_mental, aes(xintercept = fence), linetype = "dashed") + 
  geom_rug(alpha = 0.25) + 
  theme_minimal() + 
  theme(axis.title.y = element_blank()) +
  labs(x = "Effect size estimate")

es_dist_plot_mental

```
:::

:::

## Effect size distribution across type of outcomes

::: {.panel-tabset}
## Reintegrational outcomes
```{r es-dist-subgroup-plot}
#| label: fig-es-distribution-reint-subgroup
#| fig-cap: "Empirical distribution of effect size estimates, by reintegrational constructs" 
#| fig.retina: 2
#| message: false

outcomes_reint_dat <- 
  reintegration_dat |> 
  filter(!str_detect(analysis_plan, "Psychiatric")) |> 
  group_by(analysis_plan) |> 
  reframe(
    qrtl = quantile(gt,  c(.25, .75)),
    fence = qrtl + 3 * diff(qrtl) * c(-1,1),
    .groups = "drop"
  )


reintegration_outcome_plot <- 
  reintegration_dat |> 
  #Has only one data point
  filter(!str_detect(analysis_plan, "Psychiatric")) |> 
  ggplot(aes(x = gt_pop, fill = analysis_plan)) + 
  geom_density(alpha = 0.7) +
  geom_vline(data = outcomes_reint_dat, aes(xintercept = qrtl), linetype = "solid")+
  geom_vline(data = outcomes_reint_dat, aes(xintercept = fence), linetype = "dashed")+
  geom_rug(alpha = 0.25) +
  facet_wrap(~analysis_plan, ncol = 2) +
  theme_minimal() +
  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank()) +
  labs(x = "Effect size estimate", ); reintegration_outcome_plot

```


## Mental health outcomes
```{r es-dist-subgroup-plot-mental}
#| label: fig-es-distribution-mental-subgroup
#| fig-cap: "Empirical distribution of effect size estimates, by mental health constructs" 
#| fig.retina: 2
#| message: false

outcome_mental_health_dat <- 
  mental_health_dat |> 
  group_by(analysis_plan) |> 
  reframe(
    qrtl = quantile(gt,  c(.25, .75)),
    fence = qrtl + 3 * diff(qrtl) * c(-1,1),
    
    .groups = "drop"
  )

mental_health_outcomes_plot <- 
  mental_health_dat |> 
  ggplot(aes(x = gt_pop, fill = analysis_plan)) + 
  geom_density(alpha = 0.7) +
  geom_vline(data = outcome_mental_health_dat, aes(xintercept = qrtl), linetype = "solid")+
  geom_vline(data = outcome_mental_health_dat, aes(xintercept = fence), linetype = "dashed")+
  geom_rug(alpha = 0.25) +
  facet_wrap(~analysis_plan, scales = "free") +
  theme_minimal() +
  theme(legend.position = "none", axis.title.y = element_blank(), axis.text = element_blank()) +
  labs(x = "Effect size estimate"); mental_health_outcomes_plot

```

:::



# Colophon

::: {.callout-note icon=false appearance="simple" title="Session Information" collapse=false #session-info}


```{r colophon}
#| code-fold: false
#| echo: false 
sessioninfo::session_info()
```

:::

