---
title: "PRIMED Workflow for Group-Based Review"
author: "Mikkel H. Vembye"
subtitle: ""
date: "`r Sys.Date()`"
format:
  html: 
    keep-md: true
    self-contained: true
    grid: 
      margin-width: 350px
    code-fold: true
    code-summary: "Show the code"
    toc: true
    toc-location: left
pdf-engine: pdflatex
execute: 
  echo: fenced
  warning: false
knitr:
  opts_chunk: 
    fig.pos: "H"
    fig.retina: 2
    cache: FALSE
    R.options:
      knitr.graphics.auto_pdf: true
      width: 100
      knitr.kable.NA: "-"
      dplyr.summarise.inform: FALSE
reference-location: margin
citation-location: margin
bibliography: bibliography.bib  
---

# Introduction 

This document contains all preliminary data analysis for the meta-analyses with dependent effects (PRIMED) in [@Dalgaard2025]. Below one can inspect the R packages we use for this analysis as well as the data set behind our analyses. 


## R packages
For exact R package versions, see the colophon by unfolding the [Session Information](#session-info) at the bottom of this document. 

```{r set-up}
#| cache: false
#| code-fold: false

# Load packages -----------------------------------------------------------
library(knitr)
library(kableExtra)
library(skimr)
library(janitor)
library(tidyverse)
library(metafor)
library(clubSandwich)
library(fastDummies)  
library(ggrepel)
library(ggExtra)
library(ggridges)
library(MetBrewer)
library(GGally)
```

# Data manipulation - prepare data sets

In the following section, we construct all the main variables that are used in the main analysis of the review. Unfold the below code to see this exact manipulations. 

```{r load-data}
# Loading the needed data for analysis
group_based_dat <- readRDS("Group-based interventions data.RDS") |> 
  # The post-measurement of Empowerment Scale seems flawed for the study by 
  # Barbic et al. 2009 we therefore we exclude it from the analysis
  filter(!(authors == "Barbic et al." & test_name == "The Empowerment Scale")) |> 
  mutate(
    author_year = paste(authors, year),
    study = paste(authors, year)
  ) |> 
 # Remove unused outcomes
 filter(!str_detect(analysis_plan, "Unused"))

```

Primary data manipulation for the overall data, including both all reintegrational as well as mental health outcomes

```{r primary-data-manipultion}

gb_dat <- 
  group_based_dat |> 
  # Exclude the two binary outcomes
  filter(variable_type != "Binary") |>
  mutate(
    es_id = 1:n(),
    esid = es_id,
    
     # Main covariate adjusted effect cluster adjusted 
    gt_pop = if_else(!is.na(gt_post), gt_post, NA_real_),
    gt_pop = if_else(!is.na(gt_DD), gt_DD, gt_pop),
    gt_pop = if_else(!is.na(gt_adj), gt_adj, gt_pop),
    gt_pop = if_else(!is.na(gt_reg), gt_reg, gt_pop),
    gt_pop = if_else(!is.na(gt_DD_pop), gt_DD_pop, gt_pop),
    gt_pop = if_else(!is.na(gt_adj_pop), gt_adj_pop, gt_pop),
    
    vgt_pop = if_else(!is.na(vgt_post), vgt_post, NA_real_),
    vgt_pop = if_else(!is.na(vgt_DD), vgt_DD, vgt_pop),
    vgt_pop = if_else(!is.na(vgt_adj), vgt_adj, vgt_pop),
    vgt_pop = if_else(!is.na(vgt_reg), vgt_reg, vgt_pop),
    vgt_pop = if_else(!is.na(vgt_DD_pop), vgt_DD_pop, vgt_pop),
    vgt_pop = if_else(!is.na(vgt_adj_pop), vgt_adj_pop, vgt_pop),
    
    # Main covariate adjusted effect cluster adjusted 
    gt = if_else(!is.na(gt_post), gt_post, NA_real_),
    gt = if_else(!is.na(gt_DD), gt_DD, gt),
    gt = if_else(!is.na(gt_adj), gt_adj, gt),
    gt = if_else(!is.na(gt_reg), gt_reg, gt),
    
    vgt = if_else(!is.na(vgt_post), vgt_post, NA_real_),
    vgt = if_else(!is.na(vgt_DD), vgt_DD, vgt),
    vgt = if_else(!is.na(vgt_adj), vgt_adj, vgt),
    vgt = if_else(!is.na(vgt_reg), vgt_reg, vgt),
    
    Wgt = if_else(!is.na(Wgt_post), Wgt_post, NA_real_),
    Wgt = if_else(!is.na(Wgt_DD), Wgt_DD, Wgt),
    Wgt = if_else(!is.na(Wgt_adj), Wgt_adj, Wgt),
    Wgt = if_else(!is.na(Wgt_reg), Wgt_reg, Wgt),
    
    # Hedges g posttest only, adjusted for clustering
    # Imputing covariate-adjusted estimate when posttest calculation was not possible
    gt_post = if_else(is.na(gt_post) & !is.na(gt_reg), gt_reg, gt_post),
    gt_post = if_else(is.na(gt_post) & !is.na(gt_adj), gt_adj, gt_post),
    gt_post = if_else(is.na(gt_post) & !is.na(gt_DD), gt_DD, gt_post),
    
    vgt_post = if_else(is.na(vgt_post) & !is.na(vgt_reg), vgt_reg, vgt_post),
    vgt_post = if_else(is.na(vgt_post) & !is.na(vgt_adj), vgt_adj, vgt_post),
    vgt_post = if_else(is.na(vgt_post) & !is.na(vgt_DD), vgt_DD, vgt_post),
    
    Wgt_post = if_else(is.na(Wgt_post) & !is.na(Wgt_reg), Wgt_reg, Wgt_post),
    Wgt_post = if_else(is.na(Wgt_post) & !is.na(Wgt_adj), Wgt_adj, Wgt_post),
    Wgt_post = if_else(is.na(Wgt_post) & !is.na(Wgt_DD), Wgt_DD, Wgt_post),
    
    # Hedges' g posttest only, not-adjusted for clustering
    # Imputing covariate-adjusted estimate when posttest calculation was not possible
    g_post = if_else(is.na(g_post) & !is.na(g_reg), g_reg, g_post),
    g_post = if_else(is.na(g_post) & !is.na(g_adj), g_adj, g_post),
    g_post = if_else(is.na(g_post) & !is.na(g_DD), g_DD, g_post),
    
    vg_post = if_else(is.na(vg_post) & !is.na(vg_reg), vg_reg, vg_post),
    vg_post = if_else(is.na(vg_post) & !is.na(vg_adj), vg_adj, vg_post),
    vg_post = if_else(is.na(vg_post) & !is.na(vg_DD), vg_DD, vg_post),
    
    Wg_post = if_else(is.na(Wg_post) & !is.na(Wg_reg), Wg_reg, Wg_post),
    Wg_post = if_else(is.na(Wg_post) & !is.na(Wg_adj), Wg_adj, Wg_post),
    Wg_post = if_else(is.na(Wg_post) & !is.na(Wg_DD), Wg_DD, Wg_post),
    
    # Cohen's d posttest only, not-adjusted for clustering
    # Imputing covariate-adjusted estimate when posttest calculation was not possible
    d_post = if_else(is.na(d_post) & !is.na(d_reg), d_reg, d_post),
    d_post = if_else(is.na(d_post) & !is.na(d_adj), d_adj, d_post),
    d_post = if_else(is.na(d_post) & !is.na(d_DD), d_DD, d_post),
    
    vd_post = if_else(is.na(vd_post) & !is.na(vd_reg), vd_reg, vd_post),
    vd_post = if_else(is.na(vd_post) & !is.na(vd_adj), vd_adj, vd_post),
    vd_post = if_else(is.na(vd_post) & !is.na(vd_DD), vd_DD, vd_post),
    
    Wd_post = if_else(is.na(Wd_post) & !is.na(Wd_reg), Wd_reg, Wd_post),
    Wd_post = if_else(is.na(Wd_post) & !is.na(Wd_adj), Wd_adj, Wd_post),
    Wd_post = if_else(is.na(Wd_post) & !is.na(Wd_DD), Wd_DD, Wd_post),
    
    
    # Covariate adjusted Hedges' g, not cluster adjusted 
    g = if_else(!is.na(g_post), g_post, NA_real_),
    g = if_else(!is.na(g_DD), g_DD, g),
    g = if_else(!is.na(g_adj), g_adj, g),
    g = if_else(!is.na(g_reg), g_reg, g),
    
    vg = if_else(!is.na(vg_post), vg_post, NA_real_),
    vg = if_else(!is.na(vg_DD), vg_DD, vg),
    vg = if_else(!is.na(vg_adj), vg_adj, vg),
    vg = if_else(!is.na(vg_reg), vg_reg, vg),
    
    Wg = if_else(!is.na(Wg_post), Wg_post, NA_real_),
    Wg = if_else(!is.na(Wg_DD), Wg_DD, Wg),
    Wg = if_else(!is.na(Wg_adj), Wg_adj, Wg),
    Wg = if_else(!is.na(Wg_reg), Wg_reg, Wg),
    
    # Covariate-adjusted version of Cohen's d, neither cluster nor small sample adjusted
    d = if_else(!is.na(d_post), d_post, NA_real_),
    d = if_else(!is.na(d_DD), d_DD, d),
    d = if_else(!is.na(d_adj), d_adj, d),
    d = if_else(!is.na(d_reg), d_reg, d),
    
    vd = if_else(!is.na(vd_post), vd_post, NA_real_),
    vd = if_else(!is.na(vd_DD), vd_DD, vd),
    vd = if_else(!is.na(vd_adj), vd_adj, vd),
    vd = if_else(!is.na(vd_reg), vd_reg, vd),
    
    Wd = if_else(!is.na(Wd_post), Wd_post, NA_real_),
    Wd = if_else(!is.na(Wd_DD), Wd_DD, Wd),
    Wd = if_else(!is.na(Wd_adj), Wd_adj, Wd),
    Wd = if_else(!is.na(Wd_reg), Wd_reg, Wd),
    
    inv_sample_size = (1/N_t + 1/N_c),
    
    # ESS = round(4/vgt), # Using cluster bias corrected sampling variance
    
    studyid = if_else(authors == "Gonzalez & Prihoda", 500, studyid), 
    
    cnt = if_else(cnt == "USA", "US", cnt),
    
    design = if_else(design  == "QES-pretest", "QES", design),
    
    # MHV: Jeg synes ikke det er en god ide at ændre CRCT til RCT. Jeg vil gerne kunne se forskel.  
    # design = ifelse(design  == "CRCT", "RCT", design), 
    
    assessment = if_else(assessment == "Self  assesment", "Self assesment", assessment),
    
    randomization = if_else(randomization == "Simple Block Randomization", "Block randomized",
                           randomization),
    randomization = if_else(randomization == "Simple with permuted blocks, stratified by site",
                           "Stratified randomization", randomization),
   
    randomization = if_else(randomization == "Stratified?",
                           "Stratified randomization", randomization),
   
    randomization = if_else(is.na(randomization) & studyid == 102, 
                            "Stratified randomization", randomization),
   
    randomization = if_else(randomization == "Ratio and block randomized",
                           "Block randomized", randomization),
   
    randomization = if_else(randomization == "Block randomized stratified by site",
                           "Block randomized", randomization),
    
    randomization = if_else(randomization == "Resticted and adapted randomization (i.e. minimization)",
                           "Stratified randomization", randomization),
   
    randomization = if_else(randomization == "Unequal simple randomization",
                           "Block randomized", randomization),
   
    randomization = if_else(randomization == "Within-site basis and unequal allocation ratio",
                           "Stratified randomization", randomization),
    
    trt_type = if_else(trt_type == "Group-based  Cognitive Behavioral Therapy", 
                      "Group based Cognitive Behavioural Therapy", trt_type),
    trt_type = if_else(trt_type == "Group-based Cognitive Behavioral Therapy", 
                      "Group based Cognitive Behavioural Therapy", trt_type),
    trt_type = if_else(trt_type =="Group psychoeducation & Social skill training", 
                      "Group psychoeducation & Social Skill Training", trt_type),
    trt_type = if_else(trt_type =="Group psychoeducation", 
                      "Group Psychoeducation", trt_type),
    trt_type = if_else(trt_type =="Group psychoeducation & Social Skill Training", 
                      "Group Psychoeducation & Social Skill Training", trt_type),
    trt_type = if_else(trt_type =="Education and Illness Management", 
                      "Group Psychoeducation & Social Skill Training", trt_type),
    trt_type = if_else(trt_type =="Illness management", 
                      "Illness Management", trt_type),
    
    sample_factors = if_else(sample_factors =="Older with depression and anxiety", 
                            "Mixed", sample_factors), 
    sample_factors = if_else(sample_factors =="All suffered from severe mental illness", 
                            "Shared Social problem(s)/challenge(s)", sample_factors),
    sample_factors = if_else(sample_factors =="Shared origin and psychological distress", 
                            "Mixed", sample_factors),
    sample_factors = if_else(sample_factors =="persons with major psychiatric problems", 
                            "Shared Social problem(s)/challenge(s)", sample_factors),
    
    analysis_plan = if_else(analysis_plan == "Unused", "Unused outcomes", analysis_plan), 
    analysis_plan = case_match(
      analysis_plan,
      "Hope, Empowerment & Self-efficacy" ~ "Hope, empowerment & self-efficacy",
      "Wellbeing and Quality of Life" ~ "Wellbeing and quality of life",
      "All mental health outcomes" ~ "General mental health",
      "All mental health outcomes/Anxiety" ~ "Anxiety",
      "All mental health outcomes/Depression" ~ "Depression",
      "All mental health outcomes/Symptoms of psychosis" ~ "Symptoms of psychosis",
      "All mental health outcomes/Negative symptoms" ~ "Symptoms of psychosis",
      .default = analysis_plan
    ),
    
    test_type = if_else(test_type == "Clinical administered", "Clinician-rated measure", test_type),
    test_type = if_else(test_type == "Clinical interviews", "Clinician-rated measure", test_type),
    test_type = if_else(test_type == "Self report", "Self-reported", test_type),
    test_type = if_else(test_type == "Self report through clinical interview", "Self-reported", test_type),
    test_type = if_else(test_type == "Self-reported via diagnostic interview", "Self-reported", test_type), 
    
    measure_type = if_else(measure_type == "Pre-post with controls", "Post-intervention", measure_type),
   
    cluster_treatment = if_else(cluster_treatment == "Hierarchical mixed models", "Mixed-model", cluster_treatment),
   
    cluster_treatment = if_else(cluster_treatment == "Multilevel analysis and clustered standard errors", 
                        "Multilevel analysis", cluster_treatment),
   
    rob_tool = if_else(rob_tool == "Rob2", "RoB2", rob_tool),
    rob_tool = if_else(rob_tool == "Rob2 CRCT", "RoB2", rob_tool),
   
    timing = if_else(study == "Acarturk et al. 2022" & timing == "Followup", "3m", timing),
    timing = if_else(Author == "Barbic et al. 2009", "post", timing), 
    timing = if_else(Author == "Bond et al. 2015", "post", timing),
    timing = if_else(Author == "Craigie & Nathan 2009", "post", timing),
    timing = if_else(Author == "Gatz et al. 2007", "post", timing),
    timing = if_else(Author == "Gordon et al. 2018", "post", timing), 
    timing = if_else(Author == "Gutman et al. 2019", "post", timing),
    timing = if_else(Author == "Bond et al. 2015", "post", timing), 
    timing = if_else(Author == "Hagen et al. 2005", "post", timing),
    timing = if_else(Author == "Haslam et al. 2019", "post", timing),
    timing = if_else(Author == "Hilden et al. 2021", "post", timing),
    timing = if_else(Author == "James et al. 2004", "post", timing),
    timing = if_else(Author == "Lim et al. 2020", "post", timing),
    timing = if_else(Author == "Lloyd-Evans et al. 2020", "post", timing),
    timing = if_else(Author == "McCay et al. 2006", "post", timing),
    timing = if_else(Author == "McCay et al. 2007", "post", timing),
    timing = if_else(Author == "Michalak et al. 2015", "post", timing),
    timing = if_else(Author == "Morley et al. 2024", "post", timing),
    timing = if_else(Author == "Morton et al. 2012", "post", timing),
    timing = if_else(Author == "Popolo et al. 2019", "post", timing),
    timing = if_else(Author == "Rabenstein et al. 2015", "post", timing),
    timing = if_else(Author == "Rosenblum et al. 2014", "3", timing),
    timing = if_else(Author == "Sacks et al. 2011", "post", timing), 
    timing = if_else(Author == "Schrank et al. 2016", "post", timing),
    timing = if_else(Author == "Somers et al. 2017", "post", timing),
    timing = if_else(Author == "Valiente et al. 2022", "post", timing),
    timing = if_else(Author == "Volpe et al. 2015", "post", timing),
    timing = if_else(Author == "Wojtalik et al. 2022", "post", timing),
    timing = if_else(Author == "Wuthrich et al. 2013/2021", "post", timing),
    timing = if_else(Author == "Druss et al. 2010", "post", timing),
    timing = if_else(Author == "Gonzales & Prihoda 2007", "post", timing),
    timing = if_else(Author == "Dyck et al. 2000", "post", timing),
   
    analysis_strategy = if_else(str_detect(study, "Michalak"), "ITT", analysis_strategy),
   
    conventional = if_else(protocol != "Yes", 1, 0),
    prereg_chr = if_else(conventional == 0, "Preregistered", "Not preregistered"),
   
   # For publication/selection/small study bias testing
    Wse = sqrt(Wgt),
    t_i = gt/sqrt(Wgt),
   
   outcome_construct = case_match(
     analysis_plan,
     # Mental health outcomes
     "General mental health" ~ "Mental health outcome",
     "Anxiety" ~ "Mental health outcome",
     "Depression" ~ "Mental health outcome",
     "Symptoms of psychosis" ~ "Mental health outcome",
     
     # Reintegrational health outcomes
     "Wellbeing and quality of life" ~ "Reintegational outcome", 
     "Hope, empowerment & self-efficacy" ~ "Reintegational outcome",
     "Psychiatric hospitalization" ~ "Reintegational outcome",
     "Social functioning (degree of impairment)" ~ "Reintegational outcome",
     "Loneliness" ~ "Reintegational outcome",
     "Alcohol and drug abuse/misuse" ~ "Reintegational outcome",
     "Physical health" ~ "Reintegational outcome",
     "Self-esteem" ~ "Reintegational outcome",
     "Employment" ~ "Reintegational outcome"
   ),
   
   # Changing to numeric vectors
   across(c(age_mean_sample:male_pct_t, sessions_per_week), ~as.numeric(.x)),
   
   # Make weighted mean weighted by the group sample size 
   age_mean = if_else(
     is.na(age_mean_sample), 
     (age_mean_t*N_t + age_mean_c*N_c)/(N_t + N_c), 
     age_mean_sample
    ),
   
   male_pct = if_else(
     is.na(male_pct_sample),
     (male_pct_t*N_t + male_pct_c*N_c)/(N_t + N_c),
     male_pct_sample
   )
   
 ) |> 
  mutate(
    # Used to remove ITT outcomes from Cano-Vindel et al. 2021 and Craigie & Nathan 2009 
    n_analysis_strategies = n_distinct(analysis_strategy),
    .by = study
  ) |> 
  # Removing ITT analyses from Cano-Vindel et al. 2021 and Craigie & Nathan 2009 
  filter(!c(str_detect(study, "Cano|Craigie|Woj") & analysis_strategy == "ITT")) 

```

Below, we separate the data by reintegrational (primary analysis) and mental health outcomes (secondary analyses)

::: {.panel-tabset}
## Reintegration data

A general overview of the main data, we use for analyses of reintegrational outcomes can be found below.

```{r load-reint-data}

reintergation_dat <- 
  gb_dat |> 
  filter(outcome_construct == "Reintegational outcome") 


reint_overview <- 
  reintergation_dat |> 
  select(
    study, eppi_id, esid, N_t, N_c, N_total, inv_sample_size, gt, vgt, Wgt, Wse, 
    prereg_chr, conventional, analysis_plan, Overall, D5, D7, timing
  )

reint_overview |> 
  mutate(
    p_val = 2 * ( 1 - pnorm( abs(gt) / sqrt(Wgt) ) )
  ) |> 
  select(
    `Authors (year)` = study, N_t, N_c,
    `Outcome construct` = analysis_plan, gt, vgt, Wgt, Wse, p_val, 
    `No protocol` = conventional, `Overall RoB` = Overall
  ) |> 
  kable(digits=3)  |> 
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    font_size = 10
  ) |> 
  scroll_box(width = "100%", height = "300px", fixed_thead = TRUE)
```

## Mental health data

A general overview of the main data, we use for analyses of mental health outcomes can be found below.

```{r}
mental_health_dat <- 
  gb_dat |> 
  filter(outcome_construct == "Mental health outcome") 

mental_overview_dat <- 
  mental_health_dat |> 
  select(
    study, eppi_id, esid, N_t, N_c, N_total, inv_sample_size, gt, vgt, Wgt, Wse, 
    prereg_chr, conventional, analysis_plan, Overall, D5, D7, timing
  )

mental_overview_dat |> 
  mutate(
    p_val = 2 * ( 1 - pnorm( abs(gt) / sqrt(Wgt) ) )
  ) |> 
  select(
    `Authors (year)` = study, N_t, N_c,
    `Outcome construct` = analysis_plan, gt, vgt, Wgt, Wse, p_val, 
    `No protocol` = conventional, `Overall RoB` = Overall
  ) |> 
  kable(digits=3)  |> 
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    font_size = 10
  ) |> 
  scroll_box(width = "100%", height = "300px", fixed_thead = TRUE)
```


:::

# Step 1 - Descriptives and Dependence Structures

## Timeline

```{r, time-plot}
#| label: fig-time-plot
#| fig-cap: "Number of studies included in meta-analysis by year."
#| fig-width: 12
#| fig-height: 8
#| message: false

# Figure 1: Number of included studies in the meta-analysis by year
G_timeplot <- 
  group_based_dat |> 
  mutate(
    prereg = if_else(
      str_detect(protocol, regex("yes", ignore_case = TRUE)), 
      "Preregistered", "Not preregistered"
    )
  ) |> 
  reframe(year = unique(year), prereg = unique(prereg), .by =  study)

# DONE
timeline_plot <-  ggplot(G_timeplot, aes(x = year, fill = prereg)) + 
  geom_bar(col = "black", alpha = 1, width = 1) +
  scale_x_continuous(breaks = seq(2000, 2022, 1)) + 
  scale_y_continuous(breaks = seq(0, 6.5, 1), limits = c(0, 7), expand = c(0,0)) + 
  theme_bw() + 
  scale_fill_brewer(palette="Paired")+
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    #panel.border = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    axis.line = element_line(colour = "black")
  ) +
  labs(
    x = "Year of publication",
    y = "Number of studies",
  )

timeline_plot

```

## Number of preregistered vs. not preregistered studies {.tabset}

```{r}

gb_dat |> 
  summarise(
    prereg_chr = unique(prereg_chr),
    n_es = n(),
    .by = study
  ) |> 
  summarise(
    N_studies = n_distinct(study),
    N_es = sum(n_es),
    .by = prereg_chr
  )


```

::: {.panel-tabset}
### Reintegration 
```{r}
reintergation_dat |> 
  summarise(
    prereg_chr = unique(prereg_chr),
    n_es = n(),
    .by = study
  ) |> 
  summarise(
    N_studies = n_distinct(study),
    N_es = sum(n_es),
    .by = prereg_chr
  )
```

### Mental health
```{r}
mental_health_dat |> 
  summarise(
    prereg_chr = unique(prereg_chr),
    n_es = n(),
    .by = study
  ) |> 
  summarise(
    N_studies = n_distinct(study),
    N_es = sum(n_es),
    .by = prereg_chr
  )
```

:::

## Number effects across effect size metrics 

```{r}
# Number of studies reporting OR
group_based_dat |> 
  summarise(
    n = n(), 
    .by = c(study, effect_size)
  ) |> 
  summarise(
    N_studies = length(effect_size), 
    N_es = sum(n),
    .by = effect_size
  )
```


## Number of effect size estimates per study

### Overall per study


```{r es-plot}
#| label: fig-es-hist-per-stud
#| fig-cap: "Distribution of number of effect size estimates per study"
#| fig.width: 9
#| fig.height: 10
#| message: false

es_plot_per_study <- 
  gb_dat |>
  arrange(desc(study)) |>
  mutate(study = factor(study, unique(study))) |> 
  ggplot(aes(x = study)) +
  geom_bar(aes(fill = outcome_construct)) +
  scale_y_continuous(breaks = seq(5, 40, by = 5)) + 
  theme_minimal() +
  theme(
    legend.position = "bottom"
  ) +
  coord_flip() +
  labs(
    x = paste0("Study (", n_distinct(gb_dat$study), " studies in total)"), 
    y = "Number of Effect Size Estimates",
    fill = "Outcome construct"
  ) +
  guides(fill = guide_legend(reverse=TRUE))

es_plot_per_study
```


### Across outcome subgroups per study

::: {.columns}

::: {.column width="95%"}
```{r es-plot-reint}
#| label: fig-es-hist-per-stud-reint
#| fig-cap: "Distribution of number of effects per study, by direction of the effects for reintegrational outcomes."
#| fig-width: 12
#| fig-height: 8
#| message: false

reintergation_dat |>
ggplot(aes(y = study, fill = gt_pop >= 0)) + 
geom_bar(data = subset(reintergation_dat, gt_pop >= 0), aes(x = after_stat(count)), stat = "count") + 
geom_bar(data = subset(reintergation_dat, gt_pop < 0), aes(x = -after_stat(count)), stat = "count") + 
theme_minimal() +
scale_x_continuous(labels = abs, breaks = scales::breaks_width(5), limits = c(-10, 30)) +
scale_y_discrete(limits=rev) +
scale_fill_manual(
  values = c(met.brewer("Navajo")[2], met.brewer("Navajo")[4]), 
  labels = c("Negative ES", "Non-negative ES"), 
  name = "Effect Size"
) +
labs(x = "Number of Effect Size Estimates", y = "", title = "Reintegration") +
theme(
    legend.position = "bottom",
    #legend.position.inside = c(0.95, 0.05),
    #legend.justification = c(1, 0),
    legend.background = element_blank(),
    plot.title = element_text(hjust = 0.5) 
  )
```
:::

::: {.column-margin}
```{r es-plot-mental}
#| label: fig-es-hist-per-stud-mental
#| fig-cap: "Distribution of number of effects per study, by direction of the effects for mental health outcomes."
#| fig-height: 8.5
#| message: false

mental_health_dat |>
ggplot(aes(y = study, fill = gt_pop >= 0)) + 
geom_bar(data = subset(mental_health_dat, gt_pop >= 0), aes(x = after_stat(count)), stat = "count") + 
geom_bar(data = subset(mental_health_dat, gt_pop < 0), aes(x = -after_stat(count)), stat = "count") + 
theme_minimal() +
scale_x_continuous(labels = abs, breaks = scales::breaks_width(5), limits = c(-5, 15)) +
scale_y_discrete(limits=rev) +
scale_fill_manual(
  values = c(met.brewer("Navajo")[2], met.brewer("Navajo")[4]), 
  labels = c("Negative ES", "Non-negative ES"), 
  name = "Effect Size"
) +
labs(x = "Number of Effect Size Estimates", y = "", title = "Mental Health") +
theme(
    legend.position = "bottom",
    #legend.position.inside = c(0.95, 0.2),
    #legend.justification = c(1, 0),
    legend.background = element_blank(),
    plot.title = element_text(hjust = 0.5) 
  )
```
:::

:::

### Overall across all studies 

```{r, sum-es-per-study-plot}
#| label: fig-es-hist
#| fig-cap: "Distribution of number of effect size estimates per study"
#| fig.width: 9
#| fig.height: 7
#| message: false

gb_dat |> 
  summarise(
    es_count = n(),
    .by = study
  ) |>  
  arrange(es_count) |> 
  ggplot(aes(x = es_count)) +
  geom_histogram(binwidth = 0.5, fill = met.brewer("Navajo")[4]) +
  scale_x_continuous(breaks = seq(0, 40, by = 5)) +
  scale_y_continuous(breaks = seq(0, 10, 2)) +
  theme_minimal() +
  labs(x = "Effect Size Estimates per Study", y = "Number of Studies")

```

### Across outcome subgroups 

::: {.columns}

::: {.column width="95%"}
```{r sum-es-plot-reint}
#| label: fig-es-hist-reint
#| fig-cap: "Distribution of number of effects per study for mental for reintegrational outcomes."
#| fig-width: 9
#| fig-height: 6
#| message: false

reintergation_dat |> 
  summarise(
    es_count = n(),
    .by = study
  ) |>  
  arrange(es_count) |> 
  ggplot(aes(x = es_count)) +
  geom_histogram(binwidth = 0.5, fill = "cornflowerblue") +
  scale_x_continuous(breaks = seq(0, 30, by = 5)) +
  scale_y_continuous(breaks = seq(0, 14, 2), limits = c(0, 14)) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Effect Size Estimates per Study", y = "Number of Studies", title = "Reintegration") +
  expand_limits(x = 30)
```
:::

::: {.column-margin}
```{r es-plot-mental}
#| label: fig-es-hist-mental
#| fig-cap: "Distribution of number of effects per study for mental health outcomes."
#| fig-height: 8.5
#| message: false

mental_health_dat |> 
  summarise(
    es_count = n(),
    .by = study
  ) |>  
  arrange(es_count) |> 
  ggplot(aes(x = es_count)) +
  geom_histogram(binwidth = 0.5, fill = "pink") +
  scale_x_continuous(breaks = seq(0, 20, by = 5)) +
  scale_y_continuous(breaks = seq(0, 10, 2), limits = c(0, 11)) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Effect Size Estimates per Study", y = "Number of Studies", title = "Mental Health") +
  expand_limits(x = 20)
```
:::

:::

## Data structure by outcome constructs

```{r labeled-cat-hist-ridge-function}
label_cat_hist_ridge <- function(data, n_es, variable, label_map, level_order) {
  require(dplyr)
  require(rlang)
  require(tidyr)
  require(ggplot2)
  require(forcats)
  
  n_es_exp <- enquo(n_es)
  var_exp <- enquo(variable)
  
  data <- data |> 
    mutate(
      !!var_exp := fct_recode(!!var_exp, !!!label_map),
      !!var_exp := fct_relevel(!!var_exp, !!!level_order),
      !!var_exp := fct_rev(!!var_exp)
    ) 
  
  ggplot(data, aes(
    x = !!n_es_exp,
    y = !!var_exp,
    fill = !!var_exp
  )) +
    geom_density_ridges(
      alpha = 1,
      stat = "binline",
      bins = 30,
      scale = 0.7,
      linewidth = 0.1,
      draw_baseline = FALSE
    ) +
    theme_minimal() +
    labs(y = "", x = "Effect Size Estimates per Study") +
    theme(legend.position = "none")
}

```

The following plot shows the effect size estimates distribution within each outcome construct.

::: {.columns}

::: {.column width="95%"}
```{r outcome-construct-ridge-hist}
#| label: fig-outcome-construct-ridge-hist
#| fig-cap: "Distribution of effect size estimates, by reintegrational outcome constructs."
#| fig.width: 9
#| fig.height: 6.5
#| fig.retina: 2
#| message: false

n_es_by_construct <- 
  gb_dat |> 
  filter(str_detect(outcome_construct, "Re")) |> 
  summarise(effects = n(), .by = c(study, analysis_plan)) |> 
  mutate(J = n(), .by = c(analysis_plan)) |> 
  arrange(desc(J)) 

# Used to construct out_label 
#label_dat <- 
#  n_es_by_construct |> 
#  summarise(J = n(), N_es = sum(effects), .by = analysis_plan)


out_label <- c(
  "Wellbeing and quality of life (J = 24, K = 67)" = "Wellbeing and quality of life",
  "Social functioning (degree of impairment) (J =16, K = 47)" = "Social functioning (degree of impairment)",
  "Hope, empowerment & self-efficacy (J = 12, K = 32)" = "Hope, empowerment & self-efficacy",
  "Alcohol and drug abuse/misuse (J = 7, K = 31)" = "Alcohol and drug abuse/misuse",
  "Self-esteem (J = 5, K = 14)" = "Self-esteem",
  "Loneliness (J = 4, K = 5)" = "Loneliness",
  "Physical health (J = 2, K = 3)" = "Physical health",
  "Psychiatric hospitalization (J = 1, K = 1)" = "Psychiatric hospitalization",
  "Employment (J = 1, K = 2)" = "Employment"
)

out_level <- c(
 "Wellbeing and quality of life (J = 24, K = 67)",
  "Social functioning (degree of impairment) (J =16, K = 47)",
  "Hope, empowerment & self-efficacy (J = 12, K = 32)",
  "Alcohol and drug abuse/misuse (J = 7, K = 31)",
  "Self-esteem (J = 5, K = 14)",
  "Loneliness (J = 4, K = 5)",
  "Physical health (J = 2, K = 3)",
  "Psychiatric hospitalization (J = 1, K = 1)",
  "Employment (J = 1, K = 2)"
)

label_cat_hist_ridge(
  data = n_es_by_construct, 
  n_es = effects, 
  variable = analysis_plan, 
  label_map = out_label, 
  level_order = out_level
) + 
  expand_limits(x = 20) + 
  labs(title = "Reintegrational outcomes") + 
  theme(plot.title = element_text(hjust = 0.5))

```
:::

::: {.column-margin}
```{r outcome-construct-ridge-hist-mental}
#| label: fig-outcome-construct-ridge-hist-mental
#| fig-cap: "Distribution of effect size estimates, by mental health outcome constructs."
#| fig.height: 8.5
#| fig.retina: 2
#| message: false

n_es_by_construct_mental <- 
  gb_dat |> 
  filter(str_detect(outcome_construct, "Men")) |> 
  summarise(effects = n(), .by = c(study, analysis_plan)) |> 
  mutate(J = n(), .by = c(analysis_plan)) |> 
  arrange(desc(J)) 

# Used to construct out_label_mental 
#label_dat_mental <- 
#  n_es_by_construct_mental |> 
#  summarise(J = n(), N_es = sum(effects), .by = analysis_plan)

out_label_mental <- c(
  "General mental health (J = 28, K = 70)" = "General mental health",
  "Depression (J = 19, K = 36)" = "Depression",
  "Anxiety (J = 9, K = 14)" = "Anxiety",
  "Symptoms of psychosis (J = 7, K = 21)" = "Symptoms of psychosis"
)

out_level_mental <- c(
  "General mental health (J = 28, K = 70)",
  "Depression (J = 19, K = 36)",
  "Anxiety (J = 9, K = 14)",
  "Symptoms of psychosis (J = 7, K = 21)"
)

label_cat_hist_ridge(
  data = n_es_by_construct_mental, 
  n_es = effects, 
  variable = analysis_plan, 
  label_map = out_label_mental, 
  level_order = out_level_mental
) + 
  expand_limits(x = 15) + 
  labs(title = "Mental heath outcomes") + 
  theme(plot.title = element_text(hjust = 0.5))

```
:::

:::

## Primary study sample size


### Total sample sizes

::: {.columns}

::: {.column width="95%"}
```{r sample-size-overall-reint}
#| tbl-cap-location: top
#| label: tab-sample-size

# Used when describing the treatment group sample sizes
N_t_stud_trtid <- 
  reintergation_dat |> 
  reframe(N_treat = max(N_t), .by = c(study, trt_id)) 

N_t_total <- 
  N_t_stud_trtid |> 
  summarise(N_t_total = sum(N_treat), .by = study)

N_c_total <- 
  reintergation_dat |> 
  summarise(N_c_total = max(N_c), .by = study)

N_total_dat <- 
  left_join(N_t_total, N_c_total, by = join_by(study)) |> 
  mutate(N_total = N_t_total + N_c_total)


primary_sample_size_descriptive <- 
  N_total_dat$N_total |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

primary_sample_size_descriptive |>
  knitr::kable(
    digits = 2,
    caption = "Distribution of primary study sample sizes at post test for reintegrational outcomes",
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

::: {.column-margin} 
```{r sample-size-overall-mental}
#| tbl-cap-location: top
#| label: tab-sample-size-mental


# Used when describing the treatment group sample sizes
N_t_stud_trtid_mental <- 
  mental_health_dat |> 
  reframe(N_treat = max(N_t), .by = c(study, trt_id)) 

N_t_total_mental <- 
  N_t_stud_trtid_mental |> 
  summarise(N_t_total = sum(N_treat), .by = study)

N_c_total_mental <- 
  mental_health_dat |> 
  summarise(N_c_total = max(N_c), .by = study)

N_total_dat_mental <- 
  left_join(N_t_total_mental, N_c_total_mental, by = join_by(study)) |> 
  mutate(N_total = N_t_total + N_c_total)


primary_sample_size_descriptive_mental <- 
  N_total_dat_mental$N_total |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

primary_sample_size_descriptive_mental |>
  knitr::kable(
    digits = 2,
    caption = "Distribution of primary study sample sizes at post test for mental health outcomes",
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

:::

The following plot displays the distribution of study sample sizes at post-test.

::: {.columns}

::: {.column width="95%"}
```{r sample-size-plot-reint}
#| label: fig-sample-size-reint
#| fig-cap: "Distribution of primary study sample sizes at post test for reintegrational outcomes."
#| fig.height: 2.5
#| fig.width: 8
#| fig.retina: 2
#| message: false
study_sizes_plot_reint <- 
  ggplot(N_total_dat, aes(N_total)) + 
  geom_density(fill = "cornflowerblue", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Sample Size", y = "")
study_sizes_plot_reint
```
:::

::: {.column-margin}
```{r sample-size-plot-mental}
#| label: fig-sample-size-mental
#| fig-cap: "Distribution of primary study sample sizes at post test for mental health outcomes."
#| fig.height: 4
#| fig.retina: 2
#| message: false
study_sizes_plot_mental <- 
  ggplot(N_total_dat_mental, aes(N_total)) + 
  geom_density(fill = "pink", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Sample Size", y = "")
study_sizes_plot_mental

```
:::

:::

### Treatment group

::: {.columns}

::: {.column width="95%"}
```{r sample-size-treatment-reint}
#| tbl-cap-location: top
#| label: tab-sample-size-treatment


treatment_sample_size_descriptive <- 
  N_t_stud_trtid$N_treat |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

treatment_sample_size_descriptive |>
  knitr::kable(
    digits = 2,
    caption = "Distribution of treatment sample sizes at post test for reintegrational outcomes",
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

::: {.column-margin} 
```{r sample-size-treatment-mental}
#| tbl-cap-location: top
#| label: tab-sample-size-treatment-mental


treatment_sample_size_descriptive_mental <- 
  N_t_stud_trtid_mental$N_treat |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

treatment_sample_size_descriptive_mental |>
  knitr::kable(
    digits = 2,
    caption = "Distribution of treatment sample sizes at post test for mental health outcomes",
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

:::

The following plot displays the distribution of treatment sample sizes at post-test.

::: {.columns}

::: {.column width="95%"}
```{r sample-size-treatment-plot-reint}
#| label: fig-sample-size-treatment-reint
#| fig-cap: "Distribution of treatment sample sizes at post test for reintegrational outcomes."
#| fig.height: 2.5
#| fig.width: 8
#| fig.retina: 2
#| message: false
treatment_sizes_plot_reint <- 
  ggplot(N_t_stud_trtid, aes(N_treat)) + 
  geom_density(fill = "cornflowerblue", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Treatment Sample Size", y = "")
treatment_sizes_plot_reint
```
:::

::: {.column-margin}
```{r sample-size-treatment-plot-mental}
#| label: fig-sample-size-treatment-mental
#| fig-cap: "Distribution of treatment sample sizes at post test for mental health outcomes."
#| fig.height: 4
#| fig.retina: 2
#| message: false
treatment_sizes_plot_mental <- 
  ggplot(N_t_stud_trtid_mental, aes(N_treat)) + 
  geom_density(fill = "pink", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Treatment Sample Size", y = "")
treatment_sizes_plot_mental

```
:::

:::

### Control group

::: {.columns}

::: {.column width="95%"}
```{r sample-size-control-reint}
#| tbl-cap-location: top
#| label: tab-sample-size-control


control_sample_size_descriptive <- 
  N_total_dat$N_c_total |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

control_sample_size_descriptive |>
  knitr::kable(
    digits = 2,
    caption = "Distribution of control group sample sizes at post test for reintegrational outcomes",
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

::: {.column-margin} 
```{r sample-size-control-mental}
#| tbl-cap-location: top
#| label: tab-sample-size-control-mental


control_sample_size_descriptive_mental <- 
  N_total_dat_mental$N_c_total |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

control_sample_size_descriptive_mental |>
  knitr::kable(
    digits = 2,
    caption = "Distribution of control group sample sizes at post test for mental health outcomes",
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

:::

The following plot displays the distribution of control sample sizes at post-test.

::: {.columns}

::: {.column width="95%"}
```{r sample-size-control-plot-reint}
#| label: fig-sample-size-control-reint
#| fig-cap: "Distribution of control group sample sizes at post test for reintegrational outcomes."
#| fig.height: 2.5
#| fig.width: 8
#| fig.retina: 2
#| message: false
control_sizes_plot_reint <- 
  ggplot(N_total_dat, aes(N_c_total)) + 
  geom_density(fill = "cornflowerblue", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Control Group Sample Size", y = "")
control_sizes_plot_reint
```
:::

::: {.column-margin}
```{r sample-size-control-plot-mental}
#| label: fig-sample-size-control-mental
#| fig-cap: "Distribution of control group sample sizes at post test for mental health outcomes."
#| fig.height: 4
#| fig.retina: 2
#| message: false
control_sizes_plot_mental <- 
  ggplot(N_total_dat_mental, aes(N_c_total)) + 
  geom_density(fill = "pink", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Control Group Sample Size", y = "")
control_sizes_plot_mental

```
:::

:::

## Studies with multiple treatments

```{r study-multi-treatment}
reintergation_dat |> 
  filter(trt_id > 1) |> 
  reframe(study = unique(study)) 
```

## Total number of participant

```{r number-of-participants}
sum(N_total_dat$N_total)
```

## Study sample sizes versus number of effect size estimates per study

```{r bivariate-es-plot}
#| label: fig-es-distribution-bivariate
#| fig-cap: "Study sample sizes versus number of effect size estimates for reintegrational outcomes"
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

plot <- 
  reintergation_dat |> 
  summarise(effects = n(), .by = study) |> 
  left_join(N_total_dat, by = join_by(study)) |> 
  relocate(effects, .after = N_total) |> 
  ggplot(aes(x = N_total, y = effects)) +
  geom_point(alpha = 0.5) +
  scale_x_continuous(breaks = seq(0, 650, by = 50)) +
  guides(size = "none") + 
  theme_minimal() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.9, 0.05),
    legend.justification = c(1, 0),
    legend.background = element_blank()
  ) +
  labs(x = "Total sample size", y = "Number of effect size estimates per study", color = "") +
  expand_limits(y = 30)

ggMarginal(plot, type = "density")

```




# Step 2 - Study Characteristics and Potential Moderators

# Step 3 - Standard Errors and Other Auxiliary Data

# Step 4 - Visualization of the Distribution of Effect Size Estimates

# Colophon

::: {.callout-note icon=false appearance="simple" title="Session Information" collapse=true #session-info}


```{r}
#| code-fold: false
#| echo: false 
sessioninfo::session_info()
```

:::

