---
title: "PRIMED Workflow for Group-Based Review"
author: "Mikkel H. Vembye"
subtitle: ""
date: "`r Sys.Date()`"
format:
  html: 
    keep-md: true
    self-contained: true
    grid: 
      margin-width: 350px
    code-fold: true
    code-summary: "Show the code"
    toc: true
    toc-location: left
pdf-engine: pdflatex
execute: 
  echo: fenced
  warning: false
knitr:
  opts_chunk: 
    fig.pos: "H"
    fig.retina: 2
    cache: FALSE
    R.options:
      knitr.graphics.auto_pdf: true
      width: 100
      knitr.kable.NA: "-"
      dplyr.summarise.inform: FALSE
reference-location: margin
citation-location: margin
bibliography: bibliography.bib  
---

# Introduction 

This document contains all preliminary data analysis for the meta-analyses with dependent effects (PRIMED) in [@Dalgaard2025]. Below one can inspect the R packages we use for this analysis as well as the data set behind our analyses. 


## R packages
For exact R package versions, see the colophon by unfolding the [Session Information](#session-info) at the bottom of this document. 

```{r set-up}
#| cache: false
#| code-fold: false

# Load packages -----------------------------------------------------------
library(knitr)
library(kableExtra)
library(skimr)
library(janitor)
library(tidyverse)
library(metafor)
library(clubSandwich)
library(fastDummies)  
library(ggrepel)
library(ggExtra)
library(ggridges)
library(MetBrewer)
library(GGally)
library(igraph)
```

# Data manipulation - prepare data sets

In the following section, we construct all the main variables that are used in the main analysis of the review. Unfold the below code to see this exact manipulations. 

```{r load-data}
# Loading the needed data for analysis
group_based_dat <- readRDS("Group-based interventions data.RDS") |> 
  # The post-measurement of Empowerment Scale seems flawed for the study by 
  # Barbic et al. 2009 we therefore we exclude it from the analysis
  filter(!(authors == "Barbic et al." & test_name == "The Empowerment Scale")) |> 
  mutate(
    author_year = paste(authors, year),
    study = paste(authors, year)
  ) |> 
 # Remove unused outcomes
 filter(!str_detect(analysis_plan, "Unused"))

```

Primary data manipulation for the overall data, including both all reintegrational as well as mental health outcomes

```{r primary-data-manipultion}

gb_dat <- 
  group_based_dat |> 
  # Exclude the two binary outcomes
  filter(variable_type != "Binary") |>
  mutate(
    es_id = 1:n(),
    esid = es_id,
    
     # Main covariate adjusted effect cluster adjusted 
    gt_pop = if_else(!is.na(gt_post), gt_post, NA_real_),
    gt_pop = if_else(!is.na(gt_DD), gt_DD, gt_pop),
    gt_pop = if_else(!is.na(gt_adj), gt_adj, gt_pop),
    gt_pop = if_else(!is.na(gt_reg), gt_reg, gt_pop),
    gt_pop = if_else(!is.na(gt_DD_pop), gt_DD_pop, gt_pop),
    gt_pop = if_else(!is.na(gt_adj_pop), gt_adj_pop, gt_pop),
    
    vgt_pop = if_else(!is.na(vgt_post), vgt_post, NA_real_),
    vgt_pop = if_else(!is.na(vgt_DD), vgt_DD, vgt_pop),
    vgt_pop = if_else(!is.na(vgt_adj), vgt_adj, vgt_pop),
    vgt_pop = if_else(!is.na(vgt_reg), vgt_reg, vgt_pop),
    vgt_pop = if_else(!is.na(vgt_DD_pop), vgt_DD_pop, vgt_pop),
    vgt_pop = if_else(!is.na(vgt_adj_pop), vgt_adj_pop, vgt_pop),
    
    # Main covariate adjusted effect cluster adjusted 
    gt = if_else(!is.na(gt_post), gt_post, NA_real_),
    gt = if_else(!is.na(gt_DD), gt_DD, gt),
    gt = if_else(!is.na(gt_adj), gt_adj, gt),
    gt = if_else(!is.na(gt_reg), gt_reg, gt),
    
    vgt = if_else(!is.na(vgt_post), vgt_post, NA_real_),
    vgt = if_else(!is.na(vgt_DD), vgt_DD, vgt),
    vgt = if_else(!is.na(vgt_adj), vgt_adj, vgt),
    vgt = if_else(!is.na(vgt_reg), vgt_reg, vgt),
    
    Wgt = if_else(!is.na(Wgt_post), Wgt_post, NA_real_),
    Wgt = if_else(!is.na(Wgt_DD), Wgt_DD, Wgt),
    Wgt = if_else(!is.na(Wgt_adj), Wgt_adj, Wgt),
    Wgt = if_else(!is.na(Wgt_reg), Wgt_reg, Wgt),
    
    # Hedges g posttest only, adjusted for clustering
    # Imputing covariate-adjusted estimate when posttest calculation was not possible
    gt_post = if_else(is.na(gt_post) & !is.na(gt_reg), gt_reg, gt_post),
    gt_post = if_else(is.na(gt_post) & !is.na(gt_adj), gt_adj, gt_post),
    gt_post = if_else(is.na(gt_post) & !is.na(gt_DD), gt_DD, gt_post),
    
    vgt_post = if_else(is.na(vgt_post) & !is.na(vgt_reg), vgt_reg, vgt_post),
    vgt_post = if_else(is.na(vgt_post) & !is.na(vgt_adj), vgt_adj, vgt_post),
    vgt_post = if_else(is.na(vgt_post) & !is.na(vgt_DD), vgt_DD, vgt_post),
    
    Wgt_post = if_else(is.na(Wgt_post) & !is.na(Wgt_reg), Wgt_reg, Wgt_post),
    Wgt_post = if_else(is.na(Wgt_post) & !is.na(Wgt_adj), Wgt_adj, Wgt_post),
    Wgt_post = if_else(is.na(Wgt_post) & !is.na(Wgt_DD), Wgt_DD, Wgt_post),
    
    # Hedges' g posttest only, not-adjusted for clustering
    # Imputing covariate-adjusted estimate when posttest calculation was not possible
    g_post = if_else(is.na(g_post) & !is.na(g_reg), g_reg, g_post),
    g_post = if_else(is.na(g_post) & !is.na(g_adj), g_adj, g_post),
    g_post = if_else(is.na(g_post) & !is.na(g_DD), g_DD, g_post),
    
    vg_post = if_else(is.na(vg_post) & !is.na(vg_reg), vg_reg, vg_post),
    vg_post = if_else(is.na(vg_post) & !is.na(vg_adj), vg_adj, vg_post),
    vg_post = if_else(is.na(vg_post) & !is.na(vg_DD), vg_DD, vg_post),
    
    Wg_post = if_else(is.na(Wg_post) & !is.na(Wg_reg), Wg_reg, Wg_post),
    Wg_post = if_else(is.na(Wg_post) & !is.na(Wg_adj), Wg_adj, Wg_post),
    Wg_post = if_else(is.na(Wg_post) & !is.na(Wg_DD), Wg_DD, Wg_post),
    
    # Cohen's d posttest only, not-adjusted for clustering
    # Imputing covariate-adjusted estimate when posttest calculation was not possible
    d_post = if_else(is.na(d_post) & !is.na(d_reg), d_reg, d_post),
    d_post = if_else(is.na(d_post) & !is.na(d_adj), d_adj, d_post),
    d_post = if_else(is.na(d_post) & !is.na(d_DD), d_DD, d_post),
    
    vd_post = if_else(is.na(vd_post) & !is.na(vd_reg), vd_reg, vd_post),
    vd_post = if_else(is.na(vd_post) & !is.na(vd_adj), vd_adj, vd_post),
    vd_post = if_else(is.na(vd_post) & !is.na(vd_DD), vd_DD, vd_post),
    
    Wd_post = if_else(is.na(Wd_post) & !is.na(Wd_reg), Wd_reg, Wd_post),
    Wd_post = if_else(is.na(Wd_post) & !is.na(Wd_adj), Wd_adj, Wd_post),
    Wd_post = if_else(is.na(Wd_post) & !is.na(Wd_DD), Wd_DD, Wd_post),
    
    
    # Covariate adjusted Hedges' g, not cluster adjusted 
    g = if_else(!is.na(g_post), g_post, NA_real_),
    g = if_else(!is.na(g_DD), g_DD, g),
    g = if_else(!is.na(g_adj), g_adj, g),
    g = if_else(!is.na(g_reg), g_reg, g),
    
    vg = if_else(!is.na(vg_post), vg_post, NA_real_),
    vg = if_else(!is.na(vg_DD), vg_DD, vg),
    vg = if_else(!is.na(vg_adj), vg_adj, vg),
    vg = if_else(!is.na(vg_reg), vg_reg, vg),
    
    Wg = if_else(!is.na(Wg_post), Wg_post, NA_real_),
    Wg = if_else(!is.na(Wg_DD), Wg_DD, Wg),
    Wg = if_else(!is.na(Wg_adj), Wg_adj, Wg),
    Wg = if_else(!is.na(Wg_reg), Wg_reg, Wg),
    
    # Covariate-adjusted version of Cohen's d, neither cluster nor small sample adjusted
    d = if_else(!is.na(d_post), d_post, NA_real_),
    d = if_else(!is.na(d_DD), d_DD, d),
    d = if_else(!is.na(d_adj), d_adj, d),
    d = if_else(!is.na(d_reg), d_reg, d),
    
    vd = if_else(!is.na(vd_post), vd_post, NA_real_),
    vd = if_else(!is.na(vd_DD), vd_DD, vd),
    vd = if_else(!is.na(vd_adj), vd_adj, vd),
    vd = if_else(!is.na(vd_reg), vd_reg, vd),
    
    Wd = if_else(!is.na(Wd_post), Wd_post, NA_real_),
    Wd = if_else(!is.na(Wd_DD), Wd_DD, Wd),
    Wd = if_else(!is.na(Wd_adj), Wd_adj, Wd),
    Wd = if_else(!is.na(Wd_reg), Wd_reg, Wd),
    
    inv_sample_size = (1/N_t + 1/N_c),
    
    # ESS = round(4/vgt), # Using cluster bias corrected sampling variance
    
    studyid = if_else(authors == "Gonzalez & Prihoda", 500, studyid), 
    
    cnt = if_else(cnt == "USA", "US", cnt),
    
    design = if_else(design  == "QES-pretest", "QES", design),
    
    # MHV: Jeg synes ikke det er en god ide at ændre CRCT til RCT. Jeg vil gerne kunne se forskel.  
    # design = ifelse(design  == "CRCT", "RCT", design), 
    
    assessment = if_else(assessment == "Self  assesment", "Self assesment", assessment),
    
    randomization = if_else(randomization == "Simple Block Randomization", "Block randomized",
                           randomization),
    randomization = if_else(randomization == "Simple with permuted blocks, stratified by site",
                           "Stratified randomization", randomization),
   
    randomization = if_else(randomization == "Stratified?",
                           "Stratified randomization", randomization),
   
    randomization = if_else(is.na(randomization) & studyid == 102, 
                            "Stratified randomization", randomization),
   
    randomization = if_else(randomization == "Ratio and block randomized",
                           "Block randomized", randomization),
   
    randomization = if_else(randomization == "Block randomized stratified by site",
                           "Block randomized", randomization),
    
    randomization = if_else(randomization == "Resticted and adapted randomization (i.e. minimization)",
                           "Stratified randomization", randomization),
   
    randomization = if_else(randomization == "Unequal simple randomization",
                           "Block randomized", randomization),
   
    randomization = if_else(randomization == "Within-site basis and unequal allocation ratio",
                           "Stratified randomization", randomization),
    
    trt_type = if_else(trt_type == "Group-based  Cognitive Behavioral Therapy", 
                      "Group based Cognitive Behavioural Therapy", trt_type),
    trt_type = if_else(trt_type == "Group-based Cognitive Behavioral Therapy", 
                      "Group based Cognitive Behavioural Therapy", trt_type),
    trt_type = if_else(trt_type =="Group psychoeducation & Social skill training", 
                      "Group psychoeducation & Social Skill Training", trt_type),
    trt_type = if_else(trt_type =="Group psychoeducation", 
                      "Group Psychoeducation", trt_type),
    trt_type = if_else(trt_type =="Group psychoeducation & Social Skill Training", 
                      "Group Psychoeducation & Social Skill Training", trt_type),
    trt_type = if_else(trt_type =="Education and Illness Management", 
                      "Group Psychoeducation & Social Skill Training", trt_type),
    trt_type = if_else(trt_type =="Illness management", 
                      "Illness Management", trt_type),
    
    sample_factors = if_else(sample_factors =="Older with depression and anxiety", 
                            "Mixed", sample_factors), 
    sample_factors = if_else(sample_factors =="All suffered from severe mental illness", 
                            "Shared Social problem(s)/challenge(s)", sample_factors),
    sample_factors = if_else(sample_factors =="Shared origin and psychological distress", 
                            "Mixed", sample_factors),
    sample_factors = if_else(sample_factors =="persons with major psychiatric problems", 
                            "Shared Social problem(s)/challenge(s)", sample_factors),
    
    analysis_plan = if_else(analysis_plan == "Unused", "Unused outcomes", analysis_plan), 
    analysis_plan = case_match(
      analysis_plan,
      "Hope, Empowerment & Self-efficacy" ~ "Hope, empowerment & self-efficacy",
      "Wellbeing and Quality of Life" ~ "Wellbeing and quality of life",
      "All mental health outcomes" ~ "General mental health",
      "All mental health outcomes/Anxiety" ~ "Anxiety",
      "All mental health outcomes/Depression" ~ "Depression",
      "All mental health outcomes/Symptoms of psychosis" ~ "Symptoms of psychosis",
      "All mental health outcomes/Negative symptoms" ~ "Symptoms of psychosis",
      .default = analysis_plan
    ),
    
    test_type = if_else(test_type == "Clinical administered", "Clinician-rated measure", test_type),
    test_type = if_else(test_type == "Clinical interviews", "Clinician-rated measure", test_type),
    test_type = if_else(test_type == "Self report", "Self-reported", test_type),
    test_type = if_else(test_type == "Self report through clinical interview", "Self-reported", test_type),
    test_type = if_else(test_type == "Self-reported via diagnostic interview", "Self-reported", test_type), 
    
    measure_type = if_else(measure_type == "Pre-post with controls", "Post-intervention", measure_type),
   
    cluster_treatment = if_else(cluster_treatment == "Hierarchical mixed models", "Mixed-model", cluster_treatment),
   
    cluster_treatment = if_else(cluster_treatment == "Multilevel analysis and clustered standard errors", 
                        "Multilevel analysis", cluster_treatment),
   
    rob_tool = if_else(rob_tool == "Rob2", "RoB2", rob_tool),
    rob_tool = if_else(rob_tool == "Rob2 CRCT", "RoB2", rob_tool),
   
    timing = if_else(study == "Acarturk et al. 2022" & timing == "Followup", "3m", timing),
    timing = if_else(Author == "Barbic et al. 2009", "post", timing), 
    timing = if_else(Author == "Bond et al. 2015", "post", timing),
    timing = if_else(Author == "Craigie & Nathan 2009", "post", timing),
    timing = if_else(Author == "Gatz et al. 2007", "post", timing),
    timing = if_else(Author == "Gordon et al. 2018", "post", timing), 
    timing = if_else(Author == "Gutman et al. 2019", "post", timing),
    timing = if_else(Author == "Bond et al. 2015", "post", timing), 
    timing = if_else(Author == "Hagen et al. 2005", "post", timing),
    timing = if_else(Author == "Haslam et al. 2019", "post", timing),
    timing = if_else(Author == "Hilden et al. 2021", "post", timing),
    timing = if_else(Author == "James et al. 2004", "post", timing),
    timing = if_else(Author == "Lim et al. 2020", "post", timing),
    timing = if_else(Author == "Lloyd-Evans et al. 2020", "post", timing),
    timing = if_else(Author == "McCay et al. 2006", "post", timing),
    timing = if_else(Author == "McCay et al. 2007", "post", timing),
    timing = if_else(Author == "Michalak et al. 2015", "post", timing),
    timing = if_else(Author == "Morley et al. 2024", "post", timing),
    timing = if_else(Author == "Morton et al. 2012", "post", timing),
    timing = if_else(Author == "Popolo et al. 2019", "post", timing),
    timing = if_else(Author == "Rabenstein et al. 2015", "post", timing),
    timing = if_else(Author == "Rosenblum et al. 2014", "3", timing),
    timing = if_else(Author == "Sacks et al. 2011", "post", timing), 
    timing = if_else(Author == "Schrank et al. 2016", "post", timing),
    timing = if_else(Author == "Somers et al. 2017", "post", timing),
    timing = if_else(Author == "Valiente et al. 2022", "post", timing),
    timing = if_else(Author == "Volpe et al. 2015", "post", timing),
    timing = if_else(Author == "Wojtalik et al. 2022", "post", timing),
    timing = if_else(Author == "Wuthrich et al. 2013/2021", "post", timing),
    timing = if_else(Author == "Druss et al. 2010", "post", timing),
    timing = if_else(Author == "Gonzales & Prihoda 2007", "post", timing),
    timing = if_else(Author == "Dyck et al. 2000", "post", timing),
   
    analysis_strategy = if_else(str_detect(study, "Michalak"), "ITT", analysis_strategy),
   
    conventional = if_else(protocol != "Yes", 1, 0),
    prereg_chr = if_else(conventional == 0, "Preregistered", "Not preregistered"),
   
   # For publication/selection/small study bias testing
    Wse = sqrt(Wgt),
    t_i = gt/sqrt(Wgt),
   
   outcome_construct = case_match(
     analysis_plan,
     # Mental health outcomes
     "General mental health" ~ "Mental health outcome",
     "Anxiety" ~ "Mental health outcome",
     "Depression" ~ "Mental health outcome",
     "Symptoms of psychosis" ~ "Mental health outcome",
     
     # Reintegrational health outcomes
     "Wellbeing and quality of life" ~ "Reintegational outcome", 
     "Hope, empowerment & self-efficacy" ~ "Reintegational outcome",
     "Psychiatric hospitalization" ~ "Reintegational outcome",
     "Social functioning (degree of impairment)" ~ "Reintegational outcome",
     "Loneliness" ~ "Reintegational outcome",
     "Alcohol and drug abuse/misuse" ~ "Reintegational outcome",
     "Physical health" ~ "Reintegational outcome",
     "Self-esteem" ~ "Reintegational outcome",
     "Employment" ~ "Reintegational outcome"
   ),
   
   # Changing to numeric vectors
   across(c(age_mean_sample:male_pct_t, sessions_per_week), ~as.numeric(.x)),
   
   # Make weighted mean weighted by the group sample size 
   age_mean = if_else(
     is.na(age_mean_sample), 
     (age_mean_t*N_t + age_mean_c*N_c)/(N_t + N_c), 
     age_mean_sample
    ),
   
   male_pct = if_else(
     is.na(male_pct_sample),
     (male_pct_t*N_t + male_pct_c*N_c)/(N_t + N_c),
     male_pct_sample
   ),
   
   # duration_weeks has extract errors
   duration_in_weeks = time_from_baseline_weeks - time_after_end_intervention_weeks,
   total_number_of_sessions = round(sessions_per_week * duration_in_weeks)
   
 ) |> 
  mutate(
    # Used to remove ITT outcomes from Cano-Vindel et al. 2021 and Craigie & Nathan 2009 
    n_analysis_strategies = n_distinct(analysis_strategy),
    .by = study
  ) |> 
  # Removing ITT analyses from Cano-Vindel et al. 2021 and Craigie & Nathan 2009 
  filter(!c(str_detect(study, "Cano|Craigie|Woj") & analysis_strategy == "ITT")) 

```

Below, we separate the data by reintegrational (primary analysis) and mental health outcomes (secondary analyses)

::: {.panel-tabset}
## Reintegration data

A general overview of the main data, we use for analyses of reintegrational outcomes can be found below.

DESCRIPTIVE DATA AS FOR SPIRTUAL STUDY

```{r load-reint-data}

reintergation_dat <- 
  gb_dat |> 
  filter(outcome_construct == "Reintegational outcome") 


reint_overview <- 
  reintergation_dat |> 
  select(
    study, eppi_id, esid, N_t, N_c, N_total, inv_sample_size, gt, vgt, Wgt, Wse, 
    prereg_chr, conventional, analysis_plan, Overall, D5, D7, timing
  )

reint_overview |> 
  mutate(
    p_val = 2 * ( 1 - pnorm( abs(gt) / sqrt(Wgt) ) )
  ) |> 
  select(
    `Authors (year)` = study, N_t, N_c,
    `Outcome construct` = analysis_plan, gt, vgt, Wgt, Wse, p_val, 
    `No protocol` = conventional, `Overall RoB` = Overall
  ) |> 
  kable(digits=3)  |> 
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    font_size = 10
  ) |> 
  scroll_box(width = "100%", height = "300px", fixed_thead = TRUE)
```

## Mental health data

A general overview of the main data, we use for analyses of mental health outcomes can be found below.

```{r}
mental_health_dat <- 
  gb_dat |> 
  filter(outcome_construct == "Mental health outcome") 

mental_overview_dat <- 
  mental_health_dat |> 
  select(
    study, eppi_id, esid, N_t, N_c, N_total, inv_sample_size, gt, vgt, Wgt, Wse, 
    prereg_chr, conventional, analysis_plan, Overall, D5, D7, timing
  )

mental_overview_dat |> 
  mutate(
    p_val = 2 * ( 1 - pnorm( abs(gt) / sqrt(Wgt) ) )
  ) |> 
  select(
    `Authors (year)` = study, N_t, N_c,
    `Outcome construct` = analysis_plan, gt, vgt, Wgt, Wse, p_val, 
    `No protocol` = conventional, `Overall RoB` = Overall
  ) |> 
  kable(digits=3)  |> 
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    font_size = 10
  ) |> 
  scroll_box(width = "100%", height = "300px", fixed_thead = TRUE)
```


:::

# Descriptives and Dependence Structures

## Timeline

```{r, time-plot}
#| label: fig-time-plot
#| fig-cap: "Number of studies included in meta-analysis by year."
#| fig-width: 12
#| fig-height: 8
#| message: false

# Figure 1: Number of included studies in the meta-analysis by year
G_timeplot <- 
  group_based_dat |> 
  mutate(
    prereg = if_else(
      str_detect(protocol, regex("yes", ignore_case = TRUE)), 
      "Preregistered", "Not preregistered"
    )
  ) |> 
  reframe(year = unique(year), prereg = unique(prereg), .by =  study)

# DONE
timeline_plot <-  ggplot(G_timeplot, aes(x = year, fill = prereg)) + 
  geom_bar(col = "black", alpha = 1, width = 1) +
  scale_x_continuous(breaks = seq(2000, 2022, 1)) + 
  scale_y_continuous(breaks = seq(0, 6.5, 1), limits = c(0, 7), expand = c(0,0)) + 
  theme_bw() + 
  scale_fill_brewer(palette="Paired")+
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    #panel.border = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    axis.line = element_line(colour = "black")
  ) +
  labs(
    x = "Year of publication",
    y = "Number of studies",
  )

timeline_plot

```


## Number effects across effect size metrics 

```{r}
# Number of studies reporting OR
group_based_dat |> 
  summarise(
    n = n(), 
    .by = c(study, effect_size)
  ) |> 
  summarise(
    N_studies = length(effect_size), 
    N_es = sum(n),
    .by = effect_size
  )
```


## Number of effect size estimates per study

### Overall per study


```{r es-plot}
#| label: fig-es-hist-per-stud
#| fig-cap: "Distribution of number of effect size estimates per study"
#| fig.width: 6.5
#| fig.height: 7
#| message: false

es_plot_per_study <- 
  gb_dat |>
  arrange(desc(study)) |>
  mutate(study = factor(study, unique(study))) |> 
  ggplot(aes(x = study)) +
  geom_bar(aes(fill = outcome_construct)) +
  scale_y_continuous(breaks = seq(5, 40, by = 5)) + 
  theme_minimal() +
  theme(
    legend.position = "bottom"
  ) +
  coord_flip() +
  labs(
    x = paste0("Study (", n_distinct(gb_dat$study), " studies in total)"), 
    y = "Number of Effect Size Estimates",
    fill = "Outcome construct"
  ) +
  guides(fill = guide_legend(reverse=TRUE))

es_plot_per_study
```


### Across outcome subgroups per study

::: {.columns}

::: {.column width="95%"}

```{r es-plot-reint}
#| label: fig-es-hist-per-stud-reint
#| fig-cap: "Distribution of number of effects per study, by direction of the effects for reintegrational outcomes."
#| fig-width: 12
#| fig-height: 8
#| message: false

reintergation_dat |>
ggplot(aes(y = study, fill = gt_pop >= 0)) + 
geom_bar(data = subset(reintergation_dat, gt_pop >= 0), aes(x = after_stat(count)), stat = "count") + 
geom_bar(data = subset(reintergation_dat, gt_pop < 0), aes(x = -after_stat(count)), stat = "count") + 
theme_minimal() +
scale_x_continuous(labels = abs, breaks = scales::breaks_width(5), limits = c(-10, 30)) +
scale_y_discrete(limits=rev) +
scale_fill_manual(
  values = c(met.brewer("Navajo")[2], met.brewer("Navajo")[4]), 
  labels = c("Negative ES", "Non-negative ES"), 
  name = "Effect Size"
) +
labs(x = "Number of Effect Size Estimates", y = "", title = "Reintegration") +
theme(
    legend.position = "bottom",
    #legend.position.inside = c(0.95, 0.05),
    #legend.justification = c(1, 0),
    legend.background = element_blank(),
    plot.title = element_text(hjust = 0.5) 
  )
```
:::

::: {.column-margin}
```{r es-plot-mental}
#| label: fig-es-hist-per-stud-mental
#| fig-cap: "Distribution of number of effects per study, by direction of the effects for mental health outcomes."
#| fig-height: 8.5
#| message: false

mental_health_dat |>
ggplot(aes(y = study, fill = gt_pop >= 0)) + 
geom_bar(data = subset(mental_health_dat, gt_pop >= 0), aes(x = after_stat(count)), stat = "count") + 
geom_bar(data = subset(mental_health_dat, gt_pop < 0), aes(x = -after_stat(count)), stat = "count") + 
theme_minimal() +
scale_x_continuous(labels = abs, breaks = scales::breaks_width(5), limits = c(-5, 15)) +
scale_y_discrete(limits=rev) +
scale_fill_manual(
  values = c(met.brewer("Navajo")[2], met.brewer("Navajo")[4]), 
  labels = c("Negative ES", "Non-negative ES"), 
  name = "Effect Size"
) +
labs(x = "Number of Effect Size Estimates", y = "", title = "Mental Health") +
theme(
    legend.position = "bottom",
    #legend.position.inside = c(0.95, 0.2),
    #legend.justification = c(1, 0),
    legend.background = element_blank(),
    plot.title = element_text(hjust = 0.5) 
  )
```
:::

:::

### Overall across all studies and outcomes

```{r structure}
# Multi-arms studies
multi_arm_studies <- 
  gb_dat |> 
  filter(trt_id > 1) |> 
  reframe(study = unique(study))
  

# Multi-time-points studies
follow_up_studies <- 
  gb_dat |>
  summarise(
    time_points = length(unique(time_after_end_intervention_weeks)),
    .by = c(study, trt_id, ctr_id)
  ) |>
  filter(time_points > 1)

# Preregistered studies
prereg_studies <- 
  gb_dat |> 
  summarise(
    prereg_chr = unique(prereg_chr),
    n_es = n(),
    .by = study
  ) |> 
  summarise(
    N_studies = n_distinct(study),
    N_es = sum(n_es),
    .by = prereg_chr
  )

study_sample_sizes <- 
  gb_dat |>
  group_by(study, trt_id, ctr_id) |>
  summarise(
    effects = n(),
    participants = max(N_total)
  ) |>
  summarise(
    effects = sum(effects),
    participants = mean(participants),
    ctl_comparisons = n(),
    ctl_arms = paste(ctr_id, collapse = "; ")
  ) |>
  group_by(study, ctl_arms) |>
  summarise(
    effects = sum(effects),
    participants = mean(participants * (1 + ctl_comparisons * (n() - 1) / 2)),
    trt_comparisons = n(),
    trt_arms = paste(trt_id, collapse = "; "),
    ctl_comparisons = mean(ctl_comparisons)
  ) |>
  summarise(
    effects = sum(effects),
    participants = sum(participants),
    trt_comparisons = mean(trt_comparisons),
    ctl_comparisons = sum(ctl_comparisons)
  )

sample_size_summary <-
  study_sample_sizes |>
  summarise(
    studies = n(),
    studies_multiple_tx = sum(trt_comparisons > 1),
    studies_multiple_ctl = sum(ctl_comparisons > 1),
    n_effects = sum(effects),
    mean_effects = mean(effects),
    min_effects = min(effects),
    median_effects = median(effects),
    max_effects = max(effects),
    participants = round(sum(participants))
  ) |> 
  mutate(prereg = prereg_studies$N_studies[1])

n_studies <- sample_size_summary$studies
```

```{r structure-table}
#| tbl-cap-location: top
#| label: tab-es-structure

kable(
  sample_size_summary,
  caption = "Data structure for the all data",
  col.names = c(
    studies = "Studies",
    studies_multiple_tx = "Multi-treatment studies",
    studies_multiple_ctl = "Multi-control studies",
    n_effects = "Effects",
    mean_effects = "Mean",
    min_effects = "Minimum",
    median_effects = "Median",
    max_effects = "Maximum",
    participants = "Participants",
    prereg = "Preregistered studies"
  ),
  digits = 1
) |>
  kable_styling(bootstrap_options = c("striped", "condensed"),
                full_width = FALSE)
```


```{r, sum-es-per-study-plot}
#| label: fig-es-hist
#| fig-cap: "Distribution of number of effect size estimates per study"
#| fig.width: 9
#| fig.height: 7
#| message: false

gb_dat |> 
  summarise(
    es_count = n(),
    .by = study
  ) |>  
  arrange(es_count) |> 
  ggplot(aes(x = es_count)) +
  geom_histogram(binwidth = 0.5, fill = met.brewer("Navajo")[4]) +
  scale_x_continuous(breaks = seq(0, 40, by = 5)) +
  scale_y_continuous(breaks = seq(0, 10, 2)) +
  theme_minimal() +
  labs(x = "Effect Size Estimates per Study", y = "Number of Studies")

```

### Across outcome subgroups 

::: {.columns}

::: {.column width="95%"}

```{r structure-reint}
# Multi-arms studies
multi_arm_studies_reint <- 
  reintergation_dat |> 
  filter(trt_id > 1) |> 
  reframe(study = unique(study))
  

# Multi-time-points studies
follow_up_studies_reint <- 
  reintergation_dat |>
  summarise(
    time_points = length(unique(time_after_end_intervention_weeks)),
    .by = c(study, trt_id, ctr_id)
  ) |>
  filter(time_points > 1)

# Preregistered studies
prereg_studies_reint <- 
  reintergation_dat |> 
  summarise(
    prereg_chr = unique(prereg_chr),
    n_es = n(),
    .by = study
  ) |> 
  summarise(
    N_studies = n_distinct(study),
    N_es = sum(n_es),
    .by = prereg_chr
  )

study_sample_sizes_reint <- 
  reintergation_dat |>
  group_by(study, trt_id, ctr_id) |>
  summarise(
    effects = n(),
    participants = max(N_total)
  ) |>
  summarise(
    effects = sum(effects),
    participants = mean(participants),
    ctl_comparisons = n(),
    ctl_arms = paste(ctr_id, collapse = "; ")
  ) |>
  group_by(study, ctl_arms) |>
  summarise(
    effects = sum(effects),
    participants = mean(participants * (1 + ctl_comparisons * (n() - 1) / 2)),
    trt_comparisons = n(),
    trt_arms = paste(trt_id, collapse = "; "),
    ctl_comparisons = mean(ctl_comparisons)
  ) |>
  summarise(
    effects = sum(effects),
    participants = sum(participants),
    trt_comparisons = mean(trt_comparisons),
    ctl_comparisons = sum(ctl_comparisons)
  )

sample_size_summary_reint <-
  study_sample_sizes_reint |>
  summarise(
    studies = n(),
    studies_multiple_tx = sum(trt_comparisons > 1),
    studies_multiple_ctl = sum(ctl_comparisons > 1),
    n_effects = sum(effects),
    mean_effects = mean(effects),
    min_effects = min(effects),
    median_effects = median(effects),
    max_effects = max(effects),
    participants = round(sum(participants))
  ) |> 
  mutate(prereg = prereg_studies_reint$N_studies[1])

n_studies_reint <- sample_size_summary_reint$studies
```

```{r structure-table-reint}
#| tbl-cap-location: top
#| label: tab-es-structure-reint

kable(
  sample_size_summary_reint,
  caption = "Data structure for the reintegrational data",
  col.names = c(
    studies = "Studies",
    studies_multiple_tx = "Multi-treatment studies",
    studies_multiple_ctl = "Multi-control studies",
    n_effects = "Effects",
    mean_effects = "Mean",
    min_effects = "Minimum",
    median_effects = "Median",
    max_effects = "Maximum",
    participants = "Participants",
    prereg = "Preregistered studies"
  ),
  digits = 1
) |>
  kable_styling(bootstrap_options = c("striped", "condensed"),
                full_width = FALSE)
```
:::

::: {.column-margin}
```{r structure-mental}
# Multi-arms studies
multi_arm_studies_mental <- 
  mental_health_dat |> 
  filter(trt_id > 1) |> 
  reframe(study = unique(study))
  

# Multi-time-points studies
follow_up_studies_mental <- 
  mental_health_dat |>
  summarise(
    time_points = length(unique(time_after_end_intervention_weeks)),
    .by = c(study, trt_id, ctr_id)
  ) |>
  filter(time_points > 1)

# Preregistered studies
prereg_studies_mental <- 
  mental_health_dat |> 
  summarise(
    prereg_chr = unique(prereg_chr),
    n_es = n(),
    .by = study
  ) |> 
  summarise(
    N_studies = n_distinct(study),
    N_es = sum(n_es),
    .by = prereg_chr
  )

study_sample_sizes_mental <- 
  mental_health_dat |>
  group_by(study, trt_id, ctr_id) |>
  summarise(
    effects = n(),
    participants = max(N_total)
  ) |>
  summarise(
    effects = sum(effects),
    participants = mean(participants),
    ctl_comparisons = n(),
    ctl_arms = paste(ctr_id, collapse = "; ")
  ) |>
  group_by(study, ctl_arms) |>
  summarise(
    effects = sum(effects),
    participants = mean(participants * (1 + ctl_comparisons * (n() - 1) / 2)),
    trt_comparisons = n(),
    trt_arms = paste(trt_id, collapse = "; "),
    ctl_comparisons = mean(ctl_comparisons)
  ) |>
  summarise(
    effects = sum(effects),
    participants = sum(participants),
    trt_comparisons = mean(trt_comparisons),
    ctl_comparisons = sum(ctl_comparisons)
  )

sample_size_summary_mental <-
  study_sample_sizes_mental |>
  summarise(
    studies = n(),
    studies_multiple_tx = sum(trt_comparisons > 1),
    studies_multiple_ctl = sum(ctl_comparisons > 1),
    n_effects = sum(effects),
    mean_effects = mean(effects),
    min_effects = min(effects),
    median_effects = median(effects),
    max_effects = max(effects),
    participants = round(sum(participants))
  ) |> 
  mutate(prereg = prereg_studies_mental$N_studies[1])

n_studies_mental <- sample_size_summary_mental$studies
```

```{r structure-table-mental}
#| tbl-cap-location: top
#| label: tab-es-structure-mental

kable(
  sample_size_summary_mental,
  caption = "Data structure for the mental health data",
  col.names = c(
    studies = "J",
    studies_multiple_tx = "M-t",
    studies_multiple_ctl = "M-c",
    n_effects = "ES",
    mean_effects = "Mean",
    min_effects = "Min",
    median_effects = "Median",
    max_effects = "Max",
    participants = "N",
    prereg = "Prereg"
  ),
  digits = 1
) |>
  kable_styling(bootstrap_options = c("striped", "condensed"),
                full_width = FALSE)
```
:::

:::

::: {.columns}

::: {.column width="95%"}
```{r sum-es-plot-reint}
#| label: fig-es-hist-reint
#| fig-cap: "Distribution of number of effects per study for mental for reintegrational outcomes."
#| fig-width: 9
#| fig-height: 6
#| message: false

reintergation_dat |> 
  summarise(
    es_count = n(),
    .by = study
  ) |>  
  arrange(es_count) |> 
  ggplot(aes(x = es_count)) +
  geom_histogram(binwidth = 0.5, fill = "cornflowerblue") +
  scale_x_continuous(breaks = seq(0, 30, by = 5)) +
  scale_y_continuous(breaks = seq(0, 14, 2), limits = c(0, 14)) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Effect Size Estimates per Study", y = "Number of Studies", title = "Reintegration") +
  expand_limits(x = 30)
```
:::

::: {.column-margin}
```{r es-plot-mental}
#| label: fig-es-hist-mental
#| fig-cap: "Distribution of number of effects per study for mental health outcomes."
#| fig-height: 8
#| message: false

mental_health_dat |> 
  summarise(
    es_count = n(),
    .by = study
  ) |>  
  arrange(es_count) |> 
  ggplot(aes(x = es_count)) +
  geom_histogram(binwidth = 0.5, fill = "gray") +
  scale_x_continuous(breaks = seq(0, 20, by = 5)) +
  scale_y_continuous(breaks = seq(0, 10, 2), limits = c(0, 11)) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Effect Size Estimates per Study", y = "Number of Studies", title = "Mental Health") +
  expand_limits(x = 20)
```
:::

:::

## Data structure by outcome constructs

```{r labeled-cat-hist-ridge-function}
label_cat_hist_ridge <- function(data, n_es, variable, label_map, level_order) {
  require(dplyr)
  require(rlang)
  require(tidyr)
  require(ggplot2)
  require(forcats)
  
  n_es_exp <- enquo(n_es)
  var_exp <- enquo(variable)
  
  data <- data |> 
    mutate(
      !!var_exp := fct_recode(!!var_exp, !!!label_map),
      !!var_exp := fct_relevel(!!var_exp, !!!level_order),
      !!var_exp := fct_rev(!!var_exp)
    ) 
  
  ggplot(data, aes(
    x = !!n_es_exp,
    y = !!var_exp,
    fill = !!var_exp
  )) +
    geom_density_ridges(
      alpha = 1,
      stat = "binline",
      bins = 30,
      scale = 0.7,
      linewidth = 0.1,
      draw_baseline = FALSE
    ) +
    theme_minimal() +
    labs(y = "", x = "Effect Size Estimates per Study") +
    theme(legend.position = "none")
}

```

The following plot shows the effect size estimates distribution within each outcome construct.

::: {.columns}

::: {.column width="95%"}
```{r outcome-construct-ridge-hist}
#| label: fig-outcome-construct-ridge-hist
#| fig-cap: "Distribution of effect size estimates, by reintegrational outcome constructs."
#| fig.width: 9
#| fig.height: 6.5
#| fig.retina: 2
#| message: false

n_es_by_construct <- 
  gb_dat |> 
  filter(str_detect(outcome_construct, "Re")) |> 
  summarise(effects = n(), .by = c(study, analysis_plan)) |> 
  mutate(J = n(), .by = c(analysis_plan)) |> 
  arrange(desc(J)) 

# Used to construct out_label 
#label_dat <- 
#  n_es_by_construct |> 
#  summarise(J = n(), N_es = sum(effects), .by = analysis_plan)


out_label <- c(
  "Wellbeing and quality of life (J = 24, K = 67)" = "Wellbeing and quality of life",
  "Social functioning (degree of impairment) (J =16, K = 47)" = "Social functioning (degree of impairment)",
  "Hope, empowerment & self-efficacy (J = 12, K = 32)" = "Hope, empowerment & self-efficacy",
  "Alcohol and drug abuse/misuse (J = 7, K = 31)" = "Alcohol and drug abuse/misuse",
  "Self-esteem (J = 5, K = 14)" = "Self-esteem",
  "Loneliness (J = 4, K = 5)" = "Loneliness",
  "Physical health (J = 2, K = 3)" = "Physical health",
  "Psychiatric hospitalization (J = 1, K = 1)" = "Psychiatric hospitalization",
  "Employment (J = 1, K = 2)" = "Employment"
)

out_level <- c(
 "Wellbeing and quality of life (J = 24, K = 67)",
  "Social functioning (degree of impairment) (J =16, K = 47)",
  "Hope, empowerment & self-efficacy (J = 12, K = 32)",
  "Alcohol and drug abuse/misuse (J = 7, K = 31)",
  "Self-esteem (J = 5, K = 14)",
  "Loneliness (J = 4, K = 5)",
  "Physical health (J = 2, K = 3)",
  "Psychiatric hospitalization (J = 1, K = 1)",
  "Employment (J = 1, K = 2)"
)

label_cat_hist_ridge(
  data = n_es_by_construct, 
  n_es = effects, 
  variable = analysis_plan, 
  label_map = out_label, 
  level_order = out_level
) + 
  expand_limits(x = 20) + 
  labs(title = "Reintegrational outcomes") + 
  theme(plot.title = element_text(hjust = 0.5))

```
:::

::: {.column-margin}
```{r outcome-construct-ridge-hist-mental}
#| label: fig-outcome-construct-ridge-hist-mental
#| fig-cap: "Distribution of effect size estimates, by mental health outcome constructs."
#| fig.height: 8.5
#| fig.retina: 2
#| message: false

n_es_by_construct_mental <- 
  gb_dat |> 
  filter(str_detect(outcome_construct, "Men")) |> 
  summarise(effects = n(), .by = c(study, analysis_plan)) |> 
  mutate(J = n(), .by = c(analysis_plan)) |> 
  arrange(desc(J)) 

# Used to construct out_label_mental 
#label_dat_mental <- 
#  n_es_by_construct_mental |> 
#  summarise(J = n(), N_es = sum(effects), .by = analysis_plan)

out_label_mental <- c(
  "General mental health (J = 28, K = 70)" = "General mental health",
  "Depression (J = 19, K = 36)" = "Depression",
  "Anxiety (J = 9, K = 14)" = "Anxiety",
  "Symptoms of psychosis (J = 7, K = 21)" = "Symptoms of psychosis"
)

out_level_mental <- c(
  "General mental health (J = 28, K = 70)",
  "Depression (J = 19, K = 36)",
  "Anxiety (J = 9, K = 14)",
  "Symptoms of psychosis (J = 7, K = 21)"
)

label_cat_hist_ridge(
  data = n_es_by_construct_mental, 
  n_es = effects, 
  variable = analysis_plan, 
  label_map = out_label_mental, 
  level_order = out_level_mental
) + 
  expand_limits(x = 15) + 
  labs(title = "Mental heath outcomes") + 
  theme(plot.title = element_text(hjust = 0.5))

```
:::

:::

## Primary study sample size


### Total sample sizes

::: {.columns}

::: {.column width="95%"}
```{r sample-size-overall-reint}
#| tbl-cap-location: top
#| label: tab-sample-size

# Used when describing the treatment group sample sizes
N_t_stud_trtid <- 
  reintergation_dat |> 
  reframe(N_treat = max(N_t), .by = c(study, trt_id)) 

N_t_total <- 
  N_t_stud_trtid |> 
  summarise(N_t_total = sum(N_treat), .by = study)

N_c_total <- 
  reintergation_dat |> 
  summarise(N_c_total = max(N_c), .by = study)

N_total_dat <- 
  left_join(N_t_total, N_c_total, by = join_by(study)) |> 
  mutate(N_total = N_t_total + N_c_total)


primary_sample_size_descriptive <- 
  N_total_dat$N_total |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

primary_sample_size_descriptive |>
  knitr::kable(
    digits = 2,
    caption = "Distribution of primary study sample sizes at post test for reintegrational outcomes",
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

::: {.column-margin} 
```{r sample-size-overall-mental}
#| tbl-cap-location: top
#| label: tab-sample-size-mental


# Used when describing the treatment group sample sizes
N_t_stud_trtid_mental <- 
  mental_health_dat |> 
  reframe(N_treat = max(N_t), .by = c(study, trt_id)) 

N_t_total_mental <- 
  N_t_stud_trtid_mental |> 
  summarise(N_t_total = sum(N_treat), .by = study)

N_c_total_mental <- 
  mental_health_dat |> 
  summarise(N_c_total = max(N_c), .by = study)

N_total_dat_mental <- 
  left_join(N_t_total_mental, N_c_total_mental, by = join_by(study)) |> 
  mutate(N_total = N_t_total + N_c_total)


primary_sample_size_descriptive_mental <- 
  N_total_dat_mental$N_total |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

primary_sample_size_descriptive_mental |>
  knitr::kable(
    digits = 2,
    caption = "Distribution of primary study sample sizes at post test for mental health outcomes",
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

:::

The following plot displays the distribution of study sample sizes at post-test.

::: {.columns}

::: {.column width="95%"}
```{r sample-size-plot-reint}
#| label: fig-sample-size-reint
#| fig-cap: "Distribution of primary study sample sizes at post test for reintegrational outcomes."
#| fig.height: 2.5
#| fig.width: 8
#| fig.retina: 2
#| message: false
study_sizes_plot_reint <- 
  ggplot(N_total_dat, aes(N_total)) + 
  geom_density(fill = "cornflowerblue", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Sample Size", y = "")
study_sizes_plot_reint
```
:::

::: {.column-margin}
```{r sample-size-plot-mental}
#| label: fig-sample-size-mental
#| fig-cap: "Distribution of primary study sample sizes at post test for mental health outcomes."
#| fig.height: 4
#| fig.retina: 2
#| message: false
study_sizes_plot_mental <- 
  ggplot(N_total_dat_mental, aes(N_total)) + 
  geom_density(fill = "gray", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Sample Size", y = "")
study_sizes_plot_mental

```
:::

:::

### Treatment group

::: {.columns}

::: {.column width="95%"}
```{r sample-size-treatment-reint}
#| tbl-cap-location: top
#| label: tab-sample-size-treatment


treatment_sample_size_descriptive <- 
  N_t_stud_trtid$N_treat |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

treatment_sample_size_descriptive |>
  knitr::kable(
    digits = 2,
    caption = "Distribution of treatment sample sizes at post test for reintegrational outcomes",
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

::: {.column-margin} 
```{r sample-size-treatment-mental}
#| tbl-cap-location: top
#| label: tab-sample-size-treatment-mental


treatment_sample_size_descriptive_mental <- 
  N_t_stud_trtid_mental$N_treat |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

treatment_sample_size_descriptive_mental |>
  knitr::kable(
    digits = 2,
    caption = "Distribution of treatment sample sizes at post test for mental health outcomes",
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

:::

The following plot displays the distribution of treatment sample sizes at post-test.

::: {.columns}

::: {.column width="95%"}
```{r sample-size-treatment-plot-reint}
#| label: fig-sample-size-treatment-reint
#| fig-cap: "Distribution of treatment sample sizes at post test for reintegrational outcomes."
#| fig.height: 2.5
#| fig.width: 8
#| fig.retina: 2
#| message: false
treatment_sizes_plot_reint <- 
  ggplot(N_t_stud_trtid, aes(N_treat)) + 
  geom_density(fill = "cornflowerblue", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Treatment Sample Size", y = "")
treatment_sizes_plot_reint
```
:::

::: {.column-margin}
```{r sample-size-treatment-plot-mental}
#| label: fig-sample-size-treatment-mental
#| fig-cap: "Distribution of treatment sample sizes at post test for mental health outcomes."
#| fig.height: 4
#| fig.retina: 2
#| message: false
treatment_sizes_plot_mental <- 
  ggplot(N_t_stud_trtid_mental, aes(N_treat)) + 
  geom_density(fill = "gray", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Treatment Sample Size", y = "")
treatment_sizes_plot_mental

```
:::

:::

### Control group

::: {.columns}

::: {.column width="95%"}
```{r sample-size-control-reint}
#| tbl-cap-location: top
#| label: tab-sample-size-control


control_sample_size_descriptive <- 
  N_total_dat$N_c_total |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

control_sample_size_descriptive |>
  knitr::kable(
    digits = 2,
    caption = "Distribution of control group sample sizes at post test for reintegrational outcomes",
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

::: {.column-margin} 
```{r sample-size-control-mental}
#| tbl-cap-location: top
#| label: tab-sample-size-control-mental


control_sample_size_descriptive_mental <- 
  N_total_dat_mental$N_c_total |> 
  skim() |>
  select(-skim_type, -skim_variable, -n_missing, -complete_rate, -numeric.hist) |>
  rename_at(vars(starts_with("numeric.")), ~ str_remove(., "numeric\\.")) 

control_sample_size_descriptive_mental |>
  knitr::kable(
    digits = 2,
    caption = "Distribution of control group sample sizes at post test for mental health outcomes",
    booktabs = TRUE
  ) |>
  kable_styling(bootstrap_options = c("striped","condensed"), full_width = FALSE)

```
:::

:::

The following plot displays the distribution of control sample sizes at post-test.

::: {.columns}

::: {.column width="95%"}
```{r sample-size-control-plot-reint}
#| label: fig-sample-size-control-reint
#| fig-cap: "Distribution of control group sample sizes at post test for reintegrational outcomes."
#| fig.height: 2.5
#| fig.width: 8
#| fig.retina: 2
#| message: false
control_sizes_plot_reint <- 
  ggplot(N_total_dat, aes(N_c_total)) + 
  geom_density(fill = "cornflowerblue", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Control Group Sample Size", y = "")
control_sizes_plot_reint
```
:::

::: {.column-margin}
```{r sample-size-control-plot-mental}
#| label: fig-sample-size-control-mental
#| fig-cap: "Distribution of control group sample sizes at post test for mental health outcomes."
#| fig.height: 4
#| fig.retina: 2
#| message: false
control_sizes_plot_mental <- 
  ggplot(N_total_dat_mental, aes(N_c_total)) + 
  geom_density(fill = "gray", alpha = 0.8) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug(alpha = 0.8) +
  scale_y_continuous(NULL, breaks = NULL) + 
  theme_minimal() + 
  labs(x = "Total Control Group Sample Size", y = "")
control_sizes_plot_mental

```
:::

:::

## Study sample sizes versus number of effect size estimates per study

```{r bivariate-es-plot}
#| label: fig-es-distribution-bivariate
#| fig-cap: "Study sample sizes versus number of effect size estimates for reintegrational outcomes"
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

plot <- 
  reintergation_dat |> 
  summarise(effects = n(), .by = study) |> 
  left_join(N_total_dat, by = join_by(study)) |> 
  relocate(effects, .after = N_total) |> 
  ggplot(aes(x = N_total, y = effects)) +
  geom_point(alpha = 0.5) +
  scale_x_continuous(breaks = seq(0, 650, by = 50)) +
  guides(size = "none") + 
  theme_minimal() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.9, 0.05),
    legend.justification = c(1, 0),
    legend.background = element_blank()
  ) +
  labs(x = "Total sample size", y = "Number of effect size estimates per study", color = "") +
  expand_limits(y = 30)

ggMarginal(plot, type = "density")

```


# Moderators
```{r cross-tab-function}
cat_dat_cross <- function(variable, study_id, data) {
  
  require(dplyr)
  require(rlang)
  require(tidyr)
  
  var_exp <- enquo(variable)
  study_id_exp <- enquo(study_id)
  study_id_name <- as_name(study_id_exp)
  
  
    res_dat <- data %>%
      group_by(!!study_id_exp) %>%
      reframe(var_exp_mirror = unique(!!var_exp))  %>%
      full_join(data,
                by = c(study_id_name),
                relationship = "many-to-many") %>%
      group_by(!!var_exp, var_exp_mirror) %>%
      reframe(
        m = n_distinct(!!study_id_exp),
        k = n()
      ) %>%
      mutate(size = paste0(m, " (", k, ")")) %>%
      select(-m, -k) |>
      pivot_wider(names_from = var_exp_mirror, values_from = "size")
  
  names(res_dat)[1] <- "level" 
  #res_dat <- res_dat[c("level", levels(res_dat$level)[res_dat$level])]

  return(res_dat)
}

```

## Categorical moderators

### Substantial 

#### Outcome measure

```{r outcome-dependency-table-reint}

outcome_dat_cross <- cat_dat_cross(
  data = reintergation_dat,
  variable = analysis_plan,
  study_id = study
)

#| tbl-cap-location: top
#| label: tab-outcome

outcome_dat_cross |>
  knitr::kable(
    "html",
    col.names = c(
      "Outcome",
      colnames(outcome_dat_cross)[-1]
    ),
    caption = "Dependency table for preregistration status (reintegration)"
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    "Values outside the parentheses are number of studies, with the number of samples and effect size estimates shown in the parentheses.",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```

```{r outcome-subgroup-dependency-table-reint}

outcome_subgroup_dat_cross <- cat_dat_cross(
  data = filter(reintergation_dat, str_detect(analysis_plan, "Alco|Hope|Social|Well")),
  variable = analysis_plan,
  study_id = study
)

#| tbl-cap-location: top
#| label: tab-outcome-subgroup

outcome_subgroup_dat_cross |>
  knitr::kable(
    "html",
    col.names = c(
      "Outcome",
      colnames(outcome_subgroup_dat_cross)[-1]
    ),
    caption = "Dependency table for outcome used for subgroup analysis (reintegration)"
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    general = "Values outside the parentheses are number of studies, with the number of samples and effect size estimates shown in the parentheses.", 
    general_title = "Note: ",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```

##### Ridge plot of effect size estimates

```{r cat-ridge-function}
cat_ridge <- function(data, es, v, variable) {
  require(dplyr)
  require(rlang)
  require(tidyr)
  require(ggplot2)
  
  es_exp <- enquo(es)
  var_exp <- enquo(variable)
  v_exp <- enquo(v)
  
  data |> 
    mutate(!!var_exp := fct_rev(!!var_exp)) |> 
  ggplot(aes(
    x = !!es_exp,
    y = !!var_exp,
    fill = !!var_exp
  )) +
    geom_density_ridges(
      aes(
        point_colour = !!var_exp,
        point_size = 1 / !!v_exp
      ),
      alpha = .2,
      point_alpha = 0.5,
      jittered_points = TRUE
    ) +
    theme_minimal() +
    labs(y = "", x = "Standardized Mean Difference (Hedges' g)") +
    theme(legend.position = "none")
}
```


::: {.columns}

::: {.column width="95%"}

::: {.panel-tabset}
###### Subgroup analyzed
```{r type-ridge-reint-analyzed}
#| label: fig-type-ridge-reint-analyzed
#| fig-cap: "Distribution of effect size estimates, by reintegrational outcomes"
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

analyzed_outcomes <- 
  reintergation_dat |> 
  filter(str_detect(analysis_plan, "Alco|Hope|Social|Well"))

cat_ridge(data = analyzed_outcomes, es = gt_pop, variable = analysis_plan, v = vgt_pop)
```

###### Not subgroup analyzed
```{r type-ridge-reint-not-analyzed}
#| label: fig-type-ridge-reint-not-analyzed
#| fig-cap: "Distribution of effect size estimates, by reintegrational outcomes."
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

not_analyzed_outcomes <- 
  reintergation_dat |> 
  filter(!str_detect(analysis_plan, "Alco|Hope|Social|Well"))

cat_ridge(data = not_analyzed_outcomes, es = gt_pop, variable = analysis_plan, v = vgt_pop)
```
:::

:::

::: {.column-margin}
```{r type-ridge-mental-analyzed}
#| label: fig-type-ridge-mental-analyzed
#| fig-cap: "Distribution of effect size estimates, by mental health outcomes."
#| fig.height: 7
#| fig.retina: 2
#| message: false

cat_ridge(data = mental_health_dat, es = gt_pop, variable = analysis_plan, v = vgt_pop)
```
:::

:::

##### Network plot for outcome construct
The following plot shows the network structure of outcomes constructs. Each node represent an outcome construct, the edge between a pair of nodes indicates that there is at least one study that examined the contracts between that pair of constructs The width of the edges indicates the number of studies that compare that pair of constructs. The size of the node corresponds to the number of studies measure that construct.  
```{r incidents}
incidents_matrix <- function(variable, study_id, data) {
  
  require(dplyr)
  require(rlang)
  require(tidyr)
  
  var_exp <- enquo(variable)
  study_id_exp <- enquo(study_id)
  study_id_name <- as_name(study_id_exp)
  
  
  res_dat <- data %>%
    group_by(!!study_id_exp) %>%
    reframe(var_exp_mirror = unique(!!var_exp))  %>%
    full_join(data,
              by = c(study_id_name),
              relationship = "many-to-many") %>%
    group_by(!!var_exp, var_exp_mirror) %>%
    reframe(
      m = n_distinct(!!study_id_exp),
      k = n()
    ) %>%
    mutate(size = m) %>%
    select(-m, -k) |>
    pivot_wider(names_from = var_exp_mirror, values_from = "size")
 
  
  names(res_dat)[1] <- "level" 
  
  return(res_dat)
}
```

```{r}

outcome_construct_incidents_matrix <- incidents_matrix(
  variable = analysis_plan,
  study_id = study,
  data = gb_dat
)  |> 
  as.data.frame() |> 
  relocate(Employment, .after = Depression) |> 
  relocate(Loneliness, .before = `Physical health`) |> 
  relocate(`Psychiatric hospitalization`, .after = `Physical health`) |> 
  relocate(`Self-esteem`, .after = `Psychiatric hospitalization`)

edges <- outcome_construct_incidents_matrix %>%
  rename(from = "level") |> 
  pivot_longer(-from, names_to = "to", values_to = "weight") %>%
  filter(from != to, !is.na(weight)) |> 
  mutate(
    from_chr = as.character(from),
    to_chr = as.character(to),
    tmp = paste0(pmin(from_chr, to_chr), "_", pmax(from_chr, to_chr))
  ) %>% 
  distinct(tmp, .keep_all = TRUE) %>%
  select(from, to, weight)

g <- graph_from_data_frame(edges, directed = FALSE)
```

```{r network-plot}
#| label: fig-network
#| fig-cap: "Network structure of contrasts between primary and secondary outcome constructs"
#| fig.width: 7
#| fig.height: 6
#| fig.retina: 2
#| message: false

network_plot <- 
  function(
    layout_g, incidents_matrix 
    ) {

  layout <- layout_in_circle(layout_g)

  # Adjust label position outward
  label_coords <- layout
  label_coords[, 1] <- c(
    label_coords[1, 1] * 1.35, #1.5,
    label_coords[2:6, 1] * 1.4, #1.63,
    label_coords[7, 1] * 1.35, #1.68,
    label_coords[8:13, 1] * 1.4 #1.63
  )

  label_coords[, 2] <- c(
    label_coords[c(1:3), 2],
    label_coords[4, 2] * 1.13,
    label_coords[5, 2] * 1.27,
    label_coords[6, 2] * 1.13,
    label_coords[c(7:10), 2] * 1.13,
    label_coords[11, 2] * 1.2,
    label_coords[12:13, 2] * 1.13
  )

  node_sizes <- diag(as.matrix(incidents_matrix[, -1]))

  plot(
    g,
    layout = layout,
    edge.width = E(layout_g)$weight,
    edge.color = met.brewer("Navajo")[5],
    vertex.size = node_sizes,
    vertex.label = NA,
    vertex.color = met.brewer("Navajo")[4],
    vertex.frame.width = 0
  )

  text(
    x = label_coords[, 1],
    y = label_coords[, 2],
    labels = paste0(str_wrap(V(layout_g)$name, width = 15), "\n(J = ", node_sizes, ")"),
    cex = 0.6,
    col = "black",
    xpd = NA
  )

}

network_plot(g, outcome_construct_incidents_matrix)
```

#### Diagnosis

#### Type of intervention




- Diagnosis 
- CBT vs. rest

### Methodological 
- ITT vs. TOT
- RCT vs. QES
- Type of control
- Low vs. high rob
- Preregistration vs. not preregistered

#### Preregistered vs. not preregistered studies {.tabset}

```{r prereg-status-dependency-table}

prereg_dat_cross <- cat_dat_cross(
  data = reintergation_dat,
  variable = prereg_chr,
  study_id = study
)

#| tbl-cap-location: top
#| label: tab-published

prereg_dat_cross |>
  knitr::kable(
    "html",
    col.names = c(
      "Preregistration status",
      colnames(prereg_dat_cross)[-1]
    ),
    caption = "Dependency table for preregistration status (reintegration)"
  ) |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::footnote(
    "Values outside the parentheses are number of studies, with the number of samples and effect size estimates shown in the parentheses.",
    footnote_as_chunk = T
  ) |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T)
```

```{r}

gb_dat |> 
  summarise(
    prereg_chr = unique(prereg_chr),
    n_es = n(),
    .by = study
  ) |> 
  summarise(
    N_studies = n_distinct(study),
    N_es = sum(n_es),
    .by = prereg_chr
  )


```

::: {.panel-tabset}
### Reintegration 
```{r}
reintergation_dat |> 
  summarise(
    prereg_chr = unique(prereg_chr),
    n_es = n(),
    .by = study
  ) |> 
  summarise(
    N_studies = n_distinct(study),
    N_es = sum(n_es),
    .by = prereg_chr
  )
```

### Mental health
```{r}
mental_health_dat |> 
  summarise(
    prereg_chr = unique(prereg_chr),
    n_es = n(),
    .by = study
  ) |> 
  summarise(
    N_studies = n_distinct(study),
    N_es = sum(n_es),
    .by = prereg_chr
  )
```

:::

## Continuous moderators

::: {.columns}

::: {.column width="95%"}
```{r, continuous-mod-reint}

var_labels <- c(
  "Mean age" = "age",
  "Percent Male" = "male_pct",
  "Total Number of Sessions" = "sessions",
  "Sessions per Week" = "intensity",
  "Length of Intervention (in Weeks)" = "duration",
  "Weeks After End of Intervention" = "timing",
  "Weeks from Baseline" = "weeks_from_baseline"
)

continuous_descriptives <- 
 reintergation_dat |> 
  summarise(
    age = mean(age_mean),
    male_pct = mean(male_pct),
    sessions = mean(total_number_of_sessions),
    intensity = mean(sessions_per_week),
    duration = mean(duration_in_weeks),
    timing = mean(time_after_end_intervention_weeks),
    weeks_from_baseline = mean(time_from_baseline_weeks),
    .by = study
  ) 

continuous_descriptives_tab <- 
  continuous_descriptives |> 
  #pivot_longer(
  #  cols = age:male_pct,
  #  names_to = "var",
  #  values_to = "val"
  #) |> 
  #arrange(var)
  gather(var, val, age, male_pct, sessions, intensity, duration, timing, weeks_from_baseline) |>
  summarise(
    `% Missing` = 100 * mean(is.na(val)),
    Mean = mean(val, na.rm = TRUE),
    SD = sd(val, na.rm = TRUE),
    Min = min(val, na.rm = TRUE),
    LQ = quantile(val, na.rm = TRUE)[2],
    Median = median(val, na.rm = TRUE),
    UQ = quantile(val, na.rm = TRUE)[4],
    Max = max(val, na.rm = TRUE),
    .by = var
  ) |> 
  mutate(
    var = factor(var, levels = var_labels, labels = names(var_labels))
  )

#| tbl-cap-location: top
#| label: tab-continuous-characteristics-reint
knitr::kable(
  continuous_descriptives_tab, 
  caption = "Distribution of continuous moderators (reintegration)",
  col.names = c("Variable", colnames(continuous_descriptives_tab)[-1]),
  digits = 1,
  booktabs = TRUE
) |>
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) |>
  collapse_rows(1, valign = "top")

```
:::

::: {.column-margin}
```{r, continuous-mod-mental}

var_labels_mental <- c(
  "Mean age" = "age",
  "Percent Male" = "male_pct",
  "N Sessions" = "sessions",
  "Sessions Week" = "intensity",
  "Length" = "duration",
  "Weeks After Intervention" = "timing",
  "Weeks Baseline" = "weeks_from_baseline"
)

continuous_descriptives_mental <- 
 mental_health_dat |> 
  summarise(
    age = mean(age_mean),
    male_pct = mean(male_pct),
    sessions = mean(total_number_of_sessions),
    intensity = mean(sessions_per_week),
    duration = mean(duration_in_weeks),
    timing = mean(time_after_end_intervention_weeks),
    weeks_from_baseline = mean(time_from_baseline_weeks),
    .by = study
  ) 

continuous_descriptives_tab_mental <- 
  continuous_descriptives_mental |> 
  #pivot_longer(
  #  cols = age:male_pct,
  #  names_to = "var",
  #  values_to = "val"
  #) |> 
  #arrange(var)
  gather(var, val, age, male_pct, sessions, intensity, duration, timing, weeks_from_baseline) |>
  summarise(
    `% Missing` = 100 * mean(is.na(val)),
    Mean = mean(val, na.rm = TRUE),
    SD = sd(val, na.rm = TRUE),
    Min = min(val, na.rm = TRUE),
    LQ = quantile(val, na.rm = TRUE)[2],
    Median = median(val, na.rm = TRUE),
    UQ = quantile(val, na.rm = TRUE)[4],
    Max = max(val, na.rm = TRUE),
    .by = var
  ) |> 
  mutate(
    var = factor(var, levels = var_labels_mental, labels = names(var_labels_mental))
  )

#| tbl-cap-location: top
#| label: tab-continuous-characteristics-mental
knitr::kable(
  continuous_descriptives_tab_mental, 
  caption = "Distribution of continuous moderators (mental health)",
  col.names = c("Variable", colnames(continuous_descriptives_tab)[-1]),
  digits = 1,
  booktabs = TRUE
) |>
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) |>
  collapse_rows(1, valign = "top")

```
:::

:::

### Density Plots

#### Age distribution across studies
```{r density-plot-function}
density_plot <- function(variable, x_title, data, color = "cornflowerblue") {
  require(dplyr)
  require(tidyr)
  require(ggplot2)
  require(rlang)
  require(MetBrewer)
  
  var_exp <- enquo(variable)
  var_str <- as_label(var_exp)
  
  data |>
    ggplot(aes(x = !!var_exp)) +
    geom_density(fill = color, alpha = 0.8) +
    geom_rug(alpha = 0.7, length = unit(0.04, "npc")) +
    scale_y_continuous(labels = scales::label_number(accuracy = 10^(-3))) +
    theme_minimal() +
    labs(x = x_title, y = "")
}
```

::: {.columns}

::: {.column width="95%"}
```{r age-density-reint}
#| label: fig-age-density-reint
#| fig-cap: "Distribution of average age in a study (reintegrational)."
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

age_density <- density_plot(age, "Mean Age", continuous_descriptives)

age_density + expand_limits(x = 70)
```
:::

::: {.column-margin}
```{r age-density-mental}
#| label: fig-age-density-mental
#| fig-cap: "Distribution of average age in a study (mental health)."
#| fig.height: 6.5
#| fig.retina: 2
#| message: false

age_density_mental <- density_plot(age, "Mean Age", continuous_descriptives_mental, color = "gray")

age_density_mental + expand_limits(x = 70)
```
:::

:::

#### Percent males in sample distribution across studies
::: {.columns}

::: {.column width="95%"}
```{r males-density-reint}
#| label: fig-males-density-reint
#| fig-cap: "Distribution proportion of males in each study (reintegration)."
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| message: false

male_density <- suppressWarnings(density_plot(male_pct, "Proportion Male", continuous_descriptives))
male_density 
```
:::

::: {.column-margin}
```{r males-density-mental}
#| label: fig-males-density-mental
#| fig-cap: "Distribution proportion of males in each study (mental health)."
#| fig.height: 6.5
#| fig.retina: 2
#| message: false

male_density_mental <- suppressWarnings(density_plot(male_pct, "Proportion Male", continuous_descriptives_mental, color = "gray"))
male_density_mental 
```
:::

:::


### Histogram

```{r hist-plot-function}
hist_plot <- function(variable, x_title, data, color = "cornflowerblue") {
  require(dplyr)
  require(tidyr)
  require(ggplot2)
  require(rlang)
  require(MetBrewer)
  
  var_exp <- enquo(variable)
  var_str <- as_label(var_exp)
  
  x_vals <- data[[var_str]]
  min_val <- floor(min(x_vals, na.rm = TRUE))
  max_val <- ceiling(max(x_vals, na.rm = TRUE))
  
  data |>
    ggplot(aes(x = !!var_exp)) +
    geom_histogram(binwidth = 1, boundary = 0, fill = color, alpha = 0.8) +
    scale_x_continuous(breaks = pretty(seq(min_val, max_val, by = 1), n = 5)) +
    scale_y_continuous(breaks = seq(0, 10, 2)) +
    theme_minimal() +
    labs(x = x_title, y = "")
}
```

::: {.columns}

::: {.column width="95%"}
```{r sessions-hist-reint}
#| label: fig-sessions-hist-reint
#| fig-cap: "Distribution of study sessions (reintegration)."
#| fig.width: 7
#| fig.height: 4
#| fig.retina: 2
#| message: false

sessions_hist <- hist_plot(sessions, "Total Number of Sessions in Intervention", continuous_descriptives)
sessions_hist + labs(title = "Reintegration") + theme(plot.title = element_text(hjust = 0.5))
```
:::

::: {.column-margin}
```{r sessions-hist-mental}
#| label: fig-sessions-hist-mental
#| fig-cap: "Distribution of study sessions (mental health)."
#| fig.height: 6.5
#| fig.retina: 2
#| message: false

sessions_hist_mental <- hist_plot(sessions, "Total Number of Sessions in Intervention", continuous_descriptives_mental, color = "gray")
sessions_hist_mental + labs(title = "Mental Health") + theme(plot.title = element_text(hjust = 0.5))
```
:::

:::

### Lollipop Plot

#### Duration and intensity (number of sessions per week)
::: {.columns}

::: {.column width="95%"}
```{r duration-plot-reint}
#| label: fig-duration-reint
#| fig-cap: "Length of intervention in weeks (reintegration)"
#| fig.width: 6.8
#| fig.height: 7
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

reintergation_dat |>
  select(study, duration_in_weeks, sessions_per_week, N_total) |> 
  filter(!is.na(sessions_per_week)) |>  
  arrange(desc(duration_in_weeks)) |> 
  mutate(
    study = factor(study, levels = unique(study)),
    sessions = case_when(
      sessions_per_week < 1 ~ "1<",
      sessions_per_week == 1 ~ "1",
      sessions_per_week == 1.5 ~ "1.5",
      sessions_per_week == 2 ~ "2",
      sessions_per_week == 2.5 ~ "2.5",
      sessions_per_week > 2 ~ ">10"
    ),
    sessions = factor(sessions, levels = unique(sessions))
  ) |> 
  ggplot(aes(y = study, x = duration_in_weeks, color = study)) +
  geom_segment(aes(x = 0, xend = duration_in_weeks, y = study, yend = study)) +
  geom_vline(xintercept = c(13, 26, 52, 78), linetype = "dashed", alpha = 0.5) +
  geom_point(
    aes(size = N_total)
  ) +
  scale_x_continuous(breaks = seq(0, 80, 10)) +
  facet_grid(vars(sessions_per_week), scales = "free_y", space = "free_y", switch = "y") + 
  #scale_size(breaks = c(0.5, 1, 1.5, 2, 10.5), limits = c(0, 10.5)) +
  labs(
    x = "Lenght of intervention in weeks", 
    y = "", 
    caption = paste0(
      "The light gray facet grids indicate the average number of sessions per week.\n", 
      "The dashed lines indicate 3 months, 6 months, 1 year, and 1.5 years, respectively.\n",
      "The point sizes are weighted by the study sample sizes."
      )
  ) +
  theme_minimal() + 
  scale_colour_discrete(guide = "none") +
  theme(
    legend.position = "none", 
    strip.text = element_text(color = "black"),
    strip.background.y = element_rect(fill = "gray93", color = "white"),
    strip.text.y.left = element_text(angle = 0),
    plot.caption = element_text(hjust = 0)
  ) 
```
:::

::: {.column-margin}
```{r duration-plot-mental}
#| label: fig-duration-mental
#| fig-cap: "Length of intervention in weeks (mental health)"
#| fig.height: 11
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

mental_health_dat |>
  select(study, duration_in_weeks, sessions_per_week, N_total) |> 
  filter(!is.na(sessions_per_week)) |>  
  arrange(desc(duration_in_weeks)) |> 
  mutate(
    study = factor(study, levels = unique(study)),
    sessions = case_when(
      sessions_per_week < 1 ~ "Less than 1",
      sessions_per_week == 1 ~ "1 per week",
      sessions_per_week == 2 ~ "2 per week",
      sessions_per_week > 2 ~ ">10"
    ),
    sessions = factor(sessions, levels = unique(sessions))
  ) |> 
  ggplot(aes(y = study, x = duration_in_weeks, color = study)) +
  geom_segment(aes(x = 0, xend = duration_in_weeks, y = study, yend = study)) +
  geom_vline(xintercept = c(13, 26, 52, 78), linetype = "dashed", alpha = 0.5) +
  geom_point(
    aes(size = N_total)
  ) +
  scale_x_continuous(breaks = seq(0, 80, 10)) +
  facet_grid(vars(sessions_per_week), scales = "free_y", space = "free_y", switch = "y") + 
  #scale_size(breaks = c(0.5, 1, 1.5, 2, 10.5), limits = c(0, 10.5)) +
  labs(
    x = "Lenght of intervention in weeks", 
    y = "", 
    caption = 
      paste0(
      "The light gray facet grids indicate the average number of sessions per week.\n", 
      "The dashed lines indicate 3 months, 6 months, 1 year, and 1.5 years, respectively.\n",
      "The point sizes are weighted by the study sample sizes."
      )
  ) +
  theme_minimal() + 
  scale_colour_discrete(guide = "none") +
  theme(
    legend.position = "none", 
    strip.text = element_text(color = "black"),
    strip.background.y = element_rect(fill = "gray93", color = "white"),
    strip.text.y.left = element_text(angle = 0),
    plot.caption = element_text(hjust = 0)
  )  
```
::: 

:::

### Buble Plot

#### Weeks after end of intervention

::: {.columns}

::: {.column width="95%"}
```{r follow-up-plot-connected-reint}
#| label: fig-follow-up-connected-reint
#| fig-cap: "Weeks after end of interventions for all studies (reintegration)"
#| fig.width: 6.5
#| fig.height: 7
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

reintergation_dat |>
  select(study, time_after_end_intervention_weeks, N_total) |> 
  arrange(desc(study)) |> 
  mutate(study = factor(study, levels = unique(study))) |> 
  ggplot(aes(y = study, x = time_after_end_intervention_weeks, color = study)) +
  geom_point(aes(size = N_total),
             alpha = 0.5) +
  geom_line() +
  labs(x = "Weeks after end of intervention all studies", y = "")+
  theme_minimal() + 
  theme(legend.position = "none")
```
:::

::: {.column-margin}
```{r follow-up-plot-connected-mental}
#| label: fig-follow-up-connected-mental
#| fig-cap: "Weeks after end of interventions for all studies (mental health)"
#| fig.height: 11
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

mental_health_dat |>
  select(study, time_after_end_intervention_weeks, N_total) |> 
  arrange(desc(study)) |> 
  mutate(study = factor(study, levels = unique(study))) |> 
  ggplot(aes(y = study, x = time_after_end_intervention_weeks, color = study)) +
  geom_point(aes(size = N_total),
             alpha = 0.5) +
  geom_line() +
  labs(x = "Weeks after end of intervention all studies", y = "")+
  theme_minimal() + 
  theme(legend.position = "none")
```
::: 

:::

#### Correlation between effect size estimates and measurement timing
::: {.columns}

::: {.column width="95%"}
```{r es-time-plot-reint}
#| label: fig-es-time-reint
#| fig-cap: "Length of intervention in weeks (reintegration)"
#| fig.width: 6
#| fig.height: 4
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

reintergation_dat |> 
  select(study, gt_pop, vgt_pop, time_after_end_intervention_weeks) |> 
  ggplot() +
  aes(x = time_after_end_intervention_weeks, y = gt_pop, color = study) +
  geom_vline(xintercept = 0) + 
  geom_hline(yintercept = 0) + 
  geom_point(aes(size = 1/vgt_pop), alpha = 0.30) + 
  geom_smooth(method = "lm", formula = y ~ x, color = "yellow") + 
  scale_x_continuous(breaks = seq(0, 55, 5)) +
  theme_minimal() + 
  theme(legend.position = "none") + 
  labs(x = "Follow-up duration (months)", y = "Hedges' g")

```
:::

::: {.column-margin}
```{r es-time-plot-mental}
#| label: fig-es-time-mental
#| fig-cap: "Length of intervention in weeks (mental health)"
#| fig.height: 6
#| fig.retina: 2
#| fig.topcaption: TRUE
#| message: false

mental_health_dat |> 
  select(study, gt_pop, vgt_pop, time_after_end_intervention_weeks) |> 
  ggplot() +
  aes(x = time_after_end_intervention_weeks, y = gt_pop, color = study) +
  geom_vline(xintercept = 0) + 
  geom_hline(yintercept = 0) + 
 geom_point(aes(size = 1/vgt_pop), alpha = 0.30) + 
  geom_smooth(method = "lm", formula = y ~ x, color = "yellow") + 
  scale_x_continuous(breaks = seq(0, 55, 5)) +
  theme_minimal() + 
  theme(legend.position = "none") + 
  labs(x = "Follow-up duration (months)", y = "Hedges' g")

```
:::

:::


## Multivariate structure

See spirtual study

# Step 3 - Standard Errors and Other Auxiliary Data

# Step 4 - Visualization of the Distribution of Effect Size Estimates

# Colophon

::: {.callout-note icon=false appearance="simple" title="Session Information" collapse=true #session-info}


```{r}
#| code-fold: false
#| echo: false 
sessioninfo::session_info()
```

:::

