---
title: "Publication bias testing in Dalgaard et al. (2025)"
date: "Last updated `r format(Sys.time(), '%Y.%m.%d')`"
format:
  html:
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    toc: true
execute: 
  echo: fenced
  warning: false
  message: false
knitr:
  opts_chunk: 
    fig.pos: "H"
    fig.retina: 2
    cache: FALSE
    R.options:
      knitr.graphics.auto_pdf: true
      width: 100
      knitr.kable.NA: "-"
      dplyr.summarise.inform: FALSE
      scipen: 10
      pillar.sigfig: 4 
editor_options: 
  chunk_output_type: console
---

# Used package

```{r packages}
#| code-fold: false

library(tidyverse)
library(robvis)
library(purrr)
library(metafor)
library(patchwork)
library(clubSandwich)
library(wildmeta)
library(gt)
library(metaselection)
library(DT)
library(kableExtra)
library(ggh4x)
library(future)

library(puniform)
library(PublicationBias)
library(tidyverse) # for tidying
library(janitor)   # for tidying variable names
library(boot)      # for bootstrapping
library(tictoc) 

# Loading in helper function used to calculate effect size and conduct the analysis
source("Helpers.R")
source("pub-bias-test-helpers.R")
```

# **Reintegration**

## Data
```{r load-data}
#| code-fold: false

reint_ma_dat <- 
  readRDS("reint_ma_dat.rds") |> 
  mutate(
    esid = 1:n(),
    se_gt_pop = sqrt(vgt_pop), 
    Wse_pop = sqrt(Wgt_pop),
    t_i = gt_pop/sqrt(Wgt)
  )

#Secondary analysis
#mental_health_dat <- 
#  readRDS("mental_health_dat.rds") |> 
#  mutate(
#    esid = 1:n(),
#    se_gt_pop = sqrt(vgt_pop), 
#    Wse_pop = sqrt(Wgt_pop)
#    )
```


## Funnel plots
```{r, main-res}
#| eval: false
rho <- 0.8

V_mat <- 
  metafor::vcalc(
    data = reint_ma_dat,
    vi = vgt_pop, 
    cluster = study,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  )

overall_res <- 
  rma.mv(
    gt_pop,
    V = V_mat, 
    random = ~ 1 | study / esid,
    data = reint_ma_dat,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

overall_res

V_mat_outcome <- 
  metafor::vcalc(
    data = reint_ma_dat,
    vi = vgt_pop, 
    cluster = study,
    subgroup = outcome_type,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  )


sub_res <- 
  rma.mv(
    gt_pop ~ outcome_type - 1,
    V = V_mat_outcome, 
    random = list(~ outcome_type | study, ~ outcome_type | esid),
    struct = c("DIAG", "DIAG"),
    data = reint_ma_dat,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

sub_res

# Mental health
# MHV: Conduct these tests, when the main analyses has been made

#V_mat_mental <- metafor::vcalc(
#    data = mental_health_dat,
#    vi = vgt_pop, 
#    cluster = study,
#    type = outcome_time, 
#    grp1 = trt_name,
#    w1 = N_t, 
#    grp2 = control,
#    w2 = N_c, 
#    rho = rho
#  )
#
#overall_res_mental <- 
#  rma.mv(
#    gt_pop ~ + 1,
#    V = V_mat_mental, 
#    random = ~ 1 | study / esid,
#    data = mental_health_dat,
#    sparse = TRUE
#  ) |> 
#  robust(cluster = study, clubSandwich = TRUE)
#
#overall_res_mental
#
#sub_res_mental <- 
#  rma.mv(
#    gt_pop ~ -1 + analysis_plan,
#    V = V_mat_mental, 
#    random = list(~ analysis_plan | study, ~ analysis_plan | esid),
#    struct = c("DIAG", "DIAG"),
#    data = mental_health_dat,
#    sparse = TRUE
#  )
#
#sub_res_mental


```
### Overall 

```{r reint-overall-fp}
#| label: fig-reint-overall-fp
#| fig-cap: "Funnel plot across all reintegrational outcomes"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false

## Overall average effect

rho <- 0.8

# CHE-ISCW
V_mat_mod <- metafor::vcalc(
  data = reint_ma_dat,
  vi = Wgt_pop, 
  cluster = study,
  type = outcome_time, 
  grp1 = trt_name,
  w1 = N_t, 
  grp2 = control,
  w2 = N_c, 
  rho = rho
)

W <- solve(V_mat_mod)

# CHE
che <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mod,
    random = ~ 1 | study / esid,
    data = reint_ma_dat,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

# ISCW

# CHE-ISCW-RVE
che_iscw <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mod,
    W = W,
    mods = ~ prereg_chr + Wse_pop - 1,
    random = ~ 1 | study / esid,
    data = reint_ma_dat,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)


## Preregistered vs. not preregistered 

prereg_dat <-  
  reint_ma_dat |> 
  filter(conventional == 0)

V_mat_prereg <- 
  metafor::vcalc(
    data = prereg_dat,
    vi = Wgt_pop, 
    cluster = study,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  )

W_prereg <- solve(V_mat_prereg)

egg_prereg <-
  rma.mv(
    yi = gt_pop,
    V = V_mat_prereg,
    W = W_prereg,
    mods = ~ Wse_pop,
    random = ~ 1 | study / esid,
    data = prereg_dat,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

egg_prereg_res <- 
  tibble(
    subgroup = "Preregistered",
    egg_intercept = as.numeric(egg_prereg$b[1]),
    egg_slope = as.numeric(egg_prereg$b[2])
  )

notprereg_dat <-  
  reint_ma_dat |> 
  filter(conventional == 1)


V_mat_notprereg <-  
  metafor::vcalc(
    data = notprereg_dat,
    vi = Wgt_pop, 
    cluster = study,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  )

W_notprereg <- solve(V_mat_notprereg)

egg_notprereg <-
  rma.mv(
    yi = gt_pop,
    V = V_mat_notprereg,
    W = W_notprereg,
    mods = ~ Wse_pop,
    random = ~ 1 | study / esid,
    data = notprereg_dat,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)


egg_notprereg_res <- 
  tibble(
    subgroup = "Not preregistered",
    egg_intercept = as.numeric(egg_notprereg$b[1]),
    egg_slope = as.numeric(egg_notprereg$b[2])
  )

egg_res_subgrouped <- bind_rows(egg_prereg_res, egg_notprereg_res)
egg_res_subgrouped


# PESCE+ model

prereg_arg <- 
  .rma_arg_tbl(
    yi = "gt_pop", 
    vi = "vgt_pop", 
    covars = "prereg_chr",
    model = "SCEp",
    r = 0.8, 
    data = reint_ma_dat,
    type = "categorical"
  ); prereg_arg

# PESCEp+ 
subgroup_means <- pmap(.l = prereg_arg, .f = .PESCE_RVE) |> list_rbind()

#subgroup_means <- .SCEp(mod = prereg_chr, data = reint_ma_dat)

subgroup_dat <- 
  reint_ma_dat |> 
  summarise(
    gt_pop = mean(gt_pop),
    Wse_pop = mean(Wse_pop),
    outcome_type = outcome_type[1],
    .by = prereg_chr
  ) |> 
  bind_cols(subgroup_means[c(3,2), c(2, 14:18)], egg_res_subgrouped) |> 
  mutate(slope_low = qnorm(0.025), slope_high = qnorm(0.975), level = "Effect size level") 



y_lim_exp1 <- max(reint_ma_dat$Wse_pop) + 0.02 

funnel_exp1 <-  tribble(
  ~ x90, ~ x95, ~ x99, ~ y,
  0,     0,     0,     0,
  qnorm(0.05) * y_lim_exp1, qnorm(0.025) * y_lim_exp1, qnorm(0.005) * y_lim_exp1, y_lim_exp1,
  qnorm(0.95) * y_lim_exp1, qnorm(0.975) * y_lim_exp1, qnorm(0.995) * y_lim_exp1, y_lim_exp1,
  0,     0,     0,     0
) 



alpha_line <- 0.5
polygon_fill <- c("grey", "grey10", "lightcyan")
mean_line <- "dashed"
reg_test <- TRUE
reg_line <- "longdash"
reg_color <- "blue"
breaks_y <- seq(-3, 3, 0.5)


es_level_fp <- 
  reint_ma_dat |> 
  mutate(
    level = "Effect size level",
    report_bias = case_when(
      rob_tool == "RoB2" & D5 == "Low" ~ "Low",
      rob_tool == "RoB2" & str_detect(D5, "Some") ~ "Moderate",
      rob_tool == "RoB2" & str_detect(D5, "High") ~ "Serious",
      .default = D7
    ),
    
    report_bias = factor(report_bias, levels =  c("Low", "Moderate", "Serious"))
    
  ) |> 
  ggplot() + 
  geom_polygon(data = funnel_exp1, aes(x = y, y = x99), fill = polygon_fill[1], alpha = 0.5) + 
  geom_polygon(data = funnel_exp1, aes(x = y, y = x95), fill = polygon_fill[2], alpha = 0.5) + 
  geom_polygon(data = funnel_exp1, aes(x = y, y = x90), fill = polygon_fill[3], alpha = 0.7) + 
  geom_abline(data = subgroup_dat, aes(slope = slope_high, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_hline(data = subgroup_dat, aes(yintercept = avg_effect), linetype = mean_line, alpha = alpha_line) +  
  geom_abline(data = subgroup_dat, aes(slope = slope_low, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_abline(data = subgroup_dat, aes(slope = -egg_slope, intercept = egg_intercept), linetype = reg_line, color = reg_color) +
  geom_point(aes(Wse_pop, gt_pop, color = overall_rob), alpha = 1, size = 1.5) +
  coord_flip() +
  facet_grid(level~prereg_chr) +
  scale_x_reverse(limits = c(y_lim_exp1, 0.0), expand = c(0,0)) + 
  scale_y_continuous(breaks = breaks_y) + 
  scale_color_manual(
    values = c("Low" = "green3", "Some concerns/Moderate" = "yellow2", "Serious/High" = "red")
  ) + 
  theme_bw() + 
  labs(x = "Modified standard error", 
       y = "Standardized mean difference (Hedges' g)", 
       color = "", shape = "") +
  theme(
    legend.position = "bottom",
    strip.text.x = element_blank()
  ) +
  labs(color = "Overall risk of bias") +
  guides(col = guide_legend(nrow = 1))


# Make aggregate plot

reint_dat_agg <- 
  reint_ma_dat |> 
  escalc(measure = "SMD", yi = gt_pop, vi = Wgt_pop, data = _) |> 
  aggregate.escalc(cluster = study, rho = 0.8) |> 
  mutate(
    Wse_pop = sqrt(vi)
  )

prereg_dat_agg <-  
  reint_dat_agg |> 
  as_tibble() |> 
  dplyr::filter(conventional == 0)

egg_prereg_agg <- 
  rma(yi = yi, vi = vi, data = prereg_dat_agg, control=list(stepadj=0.5, maxiter=1000)) |> 
  regtest()

egg_prereg_agg_res <- 
  tibble(
    subgroup = "Preregistered",
    egg_intercept = as.numeric(egg_prereg_agg$fit$b[1]),
    egg_slope = as.numeric(egg_prereg_agg$fit$b[2])
  )

notprereg_dat_agg <-  
  reint_dat_agg |> 
  as_tibble() |> 
  dplyr::filter(conventional == 1)

egg_notprereg_agg <- 
  rma(yi = yi, vi = vi, data = notprereg_dat_agg) |> 
  regtest()

egg_notprereg_agg_res <- 
  tibble(
    subgroup = "Not preregistered",
    egg_intercept = as.numeric(egg_notprereg_agg$fit$b[1]),
    egg_slope = as.numeric(egg_notprereg_agg$fit$b[2])
  )

egg_res_agg_subgrouped <- bind_rows(egg_notprereg_agg_res, egg_prereg_agg_res)


means_agg <- 
  rma(yi, vi, mods = ~ prereg_chr - 1, data = reint_dat_agg) |> 
  robust(cluster = study, clubSandwich = TRUE)

subgroup_means_agg <- 
  tibble(
    Moderator = c("Not preregistered", "Preregistered"),
    avg_effect = as.numeric(means_agg$b), 
    LL = as.numeric(means_agg$ci.lb), 
    UL = as.numeric(means_agg$ci.ub)
  )

subgroup_dat_agg <- 
  reint_dat_agg |> 
  summarise(
    gt_pop = mean(gt_pop),
    Wse_pop = mean(Wse_pop),
    outcome_type = outcome_type[1],
    .by = prereg_chr
  ) |> 
  arrange(prereg_chr) |> 
  bind_cols(subgroup_means_agg, egg_res_agg_subgrouped) |> 
  mutate(slope_low = qnorm(0.025), slope_high = qnorm(0.975), level = "Study level") 


#subgroup_dat <- 
#  reintergation_dat |> 
#  summarise(
#    gt = mean(gt),
#    Wse = mean(Wse),
#    analysis_plan = analysis_plan[1],
#    .by = prereg_chr
#  ) |> 
#  bind_cols(subgroup_means[2:3,], egg_res_subgrouped) |> 
#  mutate(slope_low = qnorm(0.025), slope_high = qnorm(0.975), level = "Effect size level") 



y_lim_exp2 <- max(reint_dat_agg$Wse_pop) + 0.02 
y_lim_exp2  

funnel_exp2 <-  tribble(
  ~ x90, ~ x95, ~ x99, ~ y,
  0,     0,     0,     0,
  qnorm(0.05) * y_lim_exp2, qnorm(0.025) * y_lim_exp2, qnorm(0.005) * y_lim_exp2, y_lim_exp2,
  qnorm(0.95) * y_lim_exp2, qnorm(0.975) * y_lim_exp2, qnorm(0.995) * y_lim_exp2, y_lim_exp2,
  0,     0,     0,     0
) 

study_level_fp <- 
  reint_dat_agg |> 
  mutate(level = "Study level") |> 
  ggplot() + 
  geom_polygon(data = funnel_exp2, aes(x = y, y = x99), fill = polygon_fill[1], alpha = 0.5) + 
  geom_polygon(data = funnel_exp2, aes(x = y, y = x95), fill = polygon_fill[2], alpha = 0.5) + 
  geom_polygon(data = funnel_exp2, aes(x = y, y = x90), fill = polygon_fill[3], alpha = 0.7) + 
  geom_abline(data = subgroup_dat_agg, aes(slope = slope_high, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_hline(data = subgroup_dat_agg, aes(yintercept = avg_effect), linetype = mean_line, alpha = alpha_line) +  
  geom_abline(data = subgroup_dat_agg, aes(slope = slope_low, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_abline(data = subgroup_dat_agg, aes(slope = -egg_slope, intercept = egg_intercept), linetype = reg_line, color = reg_color) +
  geom_point(aes(Wse_pop, gt_pop), alpha = 1, size = 1.5) +
  scale_color_brewer(type = "qual", palette = 2) + 
  coord_flip() +
  facet_grid(level~prereg_chr) +
  scale_x_reverse(limits = c(y_lim_exp2, 0.0), expand = c(0,0)) + 
  scale_y_continuous(breaks = breaks_y) + 
  theme_bw() +
  theme(
    axis.title = element_blank()
  )

ylab <- es_level_fp$labels$x

study_level_fp$labels$x <- es_level_fp$labels$x <- "" 

#png("plots/funnel plots (overall effect) across type of registration.png", width = 6.5, height = 5, res = 300, unit = "in")
study_level_fp / es_level_fp
grid::grid.draw(grid::textGrob(ylab, y = 0.6, x = 0.02, rot = 90))
#dev.off()

```

### Investigating the impact of Cano-Vindel et al.

```{r reint-overall-fp}
prereg_dat_cano <-  
  reint_ma_dat |> 
  filter(conventional == 0) |>
  mutate(
    cano_vindel = if_else(str_detect(study, "Cano"), 1, 0),
    cano_vindel = factor(cano_vindel)
  )

V_mat_prereg_cano <- 
  metafor::vcalc(
    data = prereg_dat_cano,
    vi = Wgt_pop, 
    cluster = study,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  )

W_prereg_cano <- solve(V_mat_prereg_cano)

egg_prereg_cano <-
  rma.mv(
    yi = gt_pop,
    V = V_mat_prereg_cano,
    W = W_prereg_cano,
    mods = ~ Wse_pop + cano_vindel,
    random = ~ 1 | study / esid,
    data = prereg_dat_cano,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

egg_prereg_res_cano <- 
  tibble(
    subgroup = "Preregistered",
    egg_intercept = as.numeric(egg_prereg_cano $b[1]),
    egg_slope = as.numeric(egg_prereg_cano$b[2])
  )


subgroup_dat_cano <- 
  prereg_dat_cano |> 
  summarise(
    gt_pop = mean(gt_pop),
    Wse = mean(Wse_pop),
    outcome_type = outcome_type[1],
    .by = prereg_chr
  ) |> 
  bind_cols(subgroup_means[3, c(2, 14:18)], egg_prereg_res_cano) |> 
  mutate(slope_low = qnorm(0.025), slope_high = qnorm(0.975)) 



y_lim_exp_cano <- max(prereg_dat_cano$Wse_pop) + 0.02 
y_lim_exp_cano  

funnel_exp_cano <-  tribble(
  ~ x90, ~ x95, ~ x99, ~ y,
  0,     0,     0,     0,
  qnorm(0.05) * y_lim_exp_cano, qnorm(0.025) * y_lim_exp_cano, qnorm(0.005) * y_lim_exp_cano, y_lim_exp_cano,
  qnorm(0.95) * y_lim_exp_cano, qnorm(0.975) * y_lim_exp_cano, qnorm(0.995) * y_lim_exp_cano, y_lim_exp_cano,
  0,     0,     0,     0
) 



alpha_line <- 0.5
polygon_fill <- c("grey", "grey10", "lightcyan")
mean_line <- "dashed"
reg_test <- TRUE
reg_line <- "longdash"
reg_color <- "blue"
breaks_y <- seq(-3, 3, 0.5)


cano_fp <- 
  prereg_dat_cano |> 
  mutate(alpha_val = if_else(cano_vindel == 1, 0.9, 1)) |>
  ggplot() + 
  geom_polygon(data = funnel_exp_cano, aes(x = y, y = x99), fill = polygon_fill[1], alpha = 0.5) + 
  geom_polygon(data = funnel_exp_cano, aes(x = y, y = x95), fill = polygon_fill[2], alpha = 0.5) + 
  geom_polygon(data = funnel_exp_cano, aes(x = y, y = x90), fill = polygon_fill[3], alpha = 0.7) + 
  geom_abline(data = subgroup_dat_cano, aes(slope = slope_high, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_hline(data = subgroup_dat_cano, aes(yintercept = avg_effect), linetype = mean_line, alpha = alpha_line) +  
  geom_abline(data = subgroup_dat_cano, aes(slope = slope_low, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_abline(data = subgroup_dat_cano, aes(slope = -egg_slope, intercept = egg_intercept), linetype = reg_line, color = reg_color) +
  geom_point(aes(Wse_pop, gt_pop, col = cano_vindel, alpha = alpha_val), size = 1.5) +
  scale_color_brewer(type = "qual", palette = 2) + 
  coord_flip() +
  facet_grid(~prereg_chr) +
  scale_x_reverse(limits = c(y_lim_exp_cano, 0.0), expand = c(0,0)) + 
  scale_y_continuous(breaks = breaks_y) + 
  theme_bw() + 
  labs(x = "Modified standard error", 
       y = "Standardized mean difference (Hedges' g)", 
       color = "", shape = "") +
  theme(
    legend.position = "bottom"
  ) +
  labs(color = "Cano-vindel") +
  guides(col = "none", alpha = "none")

#png("plots/funnel plots (overall effect) without Cano-Vindel.png", width = 8, height = 5.5, res = 300, unit = "in")
cano_fp
#dev.off()




```

### Funnel plot across outcomes


## Publication bias tests
```{r, tab-func-overall-pub-bias}

.pubbias_overall_tab <- 
  function(
    rma_obj, 
    test,
    studies = n_distinct(reint_ma_dat$study), 
    effects = nrow(reint_ma_dat)
  ){
    
    tibble(
    test = test,
    J = studies,
    K = effects,
    est_ci = paste0(
      round(as.numeric(rma_obj$b[1]), 3), 
      " [", 
      round(rma_obj$ci.lb[1], 3),
      ", ",
      round(rma_obj$ci.ub[1], 3),
      "]"
    ),
    pval = rma_obj$pval[1],
    tau = round(sqrt(rma_obj$sigma2[1]), 3),
    omega = round(sqrt(rma_obj$sigma2[2]), 3),
    total_SD = round(sqrt(sum(rma_obj$sigma2)), 3)
  )

}

```


### HYEMA

```{r}
hyema_overall <- readRDS("Bootstrap results/hyema_overall_reint.rds")

# Overall res (Robust HYEMA)
hyema_tab_res <- 
  tibble(
    test = "Robust HYEMA",
    J = n_distinct(reint_ma_dat$study),
    K = nrow(reint_ma_dat),
    est_ci = paste0(
      round(as.numeric(hyema_overall$Est[1]), 3), 
      " [", 
      round(hyema_overall$CIL_bootstrap[1], 3),
      ", ",
      round(hyema_overall$CIU_bootstrap[2], 3),
      "]"
    ),
    pval = NA_real_,
    tau = round(hyema_overall$Est[2], 3),
    omega = NA_real_,
    total_SD = hyema_overall$Est[2]
  )

# HYEMA across outcome
hyema_outcome <- readRDS("Bootstrap results/hyema_overcome.rds")
hyema_outcome_f_stat <- readRDS("Bootstrap results/F_boot_pval_outcome.rds")

# To temporarily get tau
hyema_obj <- 
  puniform::hybrid(
    yi = reint_ma_dat$gt_pop, 
    vi = reint_ma_dat$Wgt_pop, 
    conventional = reint_ma_dat$conventional, 
    side = "right",
    mods = ~ reint_ma_dat$outcome_type -1
  ) |> 
  suppressWarnings()

hyema_outcome_tab <- 
  tibble(
    coefficient = c(
      hyema_outcome$Parameter, "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"),
    est_ci = c(
      paste0(
        round(as.numeric(hyema_outcome$Est), 3), 
        " [", 
        round(hyema_outcome$CIL_bootstrap, 3),
        ", ",
        round(hyema_outcome$CIU_bootstrap, 3),
        "]"
      ),
      as.character(round(hyema_outcome_f_stat, 3)),
      as.character(round(sqrt(hyema_obj$tau2), 3)),
      NA_character_,
      as.character(round(sqrt(hyema_obj$tau2), 3)),
      as.character(n_distinct(reint_ma_dat$study)),
      as.character(nrow(reint_ma_dat))
    ),
    
    method = "hyema"
    
  )



```

### Puniform*

```{r puniform}
# Not corrected for clustering as it has showed acceptable performance in
# dependent effect size data
puniform_star_res <- 
  puniform::puni_star(
    tobs = reint_ma_dat$t_i, 
    n1i = reint_ma_dat$N_t, 
    n2i = reint_ma_dat$N_c, 
    side = "right"
  )

puniform_tab_res <- 
  tibble(
    test = "puniform star",
    J = n_distinct(reint_ma_dat$study),
    K = nrow(reint_ma_dat),
    est_ci = paste0(
      round(as.numeric(puniform_star_res$est), 3), 
      " [", 
      round(puniform_star_res$ci.lb, 3),
      ", ",
      round(puniform_star_res$ci.ub, 3),
      "]"
    ),
    pval = puniform_star_res$pval.0,
    tau = round(sqrt(puniform_star_res$tau2), 3),
    omega = NA_real_,
    total_SD = tau
    
  )



```


### Worst-case meta-analysis

```{r}

worst_dat_reint <- 
  reint_ma_dat |>  
  mutate(
    pval = 2 * ( 1 - pnorm( abs(gt_pop) / sqrt(vgt_pop) ) ),
    affirmativity = if_else(pval < .05 & gt_pop > 0, "affirmative", "nonaffirmative")
    
  ) %>% 
  filter(affirmativity == "nonaffirmative")

wc_prereg_studies <- 
  worst_dat_reint |> 
  summarise(
    n = n(), 
    .by = c(prereg_chr, study)
  ) |> 
  summarise(
    n_studies = n(),
    .by = prereg_chr
  ) |> 
  arrange(prereg_chr)

wc_prereg_es <- 
  worst_dat_reint |> 
  summarise(n_effects = n(), .by = prereg_chr) |> 
  arrange(prereg_chr) 

# Outcome
wc_outcome_studies <- 
  worst_dat_reint |> 
  summarise(
    n = n(), 
    .by = c(outcome_type, study)
  ) |> 
  summarise(
    n_studies = n(),
    .by = outcome_type
  ) |> 
  arrange(outcome_type)

wc_outcome_es <- 
  worst_dat_reint |> 
  summarise(n_effects = n(), .by = outcome_type) |> 
  arrange(outcome_type) 


```

```{r}
res_PubBias <- 
  pubbias_svalue(
  yi = reint_ma_dat$gt_pop,
  vi = reint_ma_dat$Wgt_pop,
  cluster = reint_ma_dat$study,
  q = 0,
  model_type = "robust",
  favor_positive = TRUE,
  return_worst_meta = TRUE
)

res_PubBias$stats

rho <- 0.8

pubbias_plot <- 
  PublicationBias::significance_funnel(
  yi = reint_ma_dat$gt_pop,
  vi = reint_ma_dat$Wgt_pop,
  favor_positive = TRUE,
  alpha_select = 0.05
)

pubbias_plot
```


```{r}
#wc = worst_case
V_mat_wc <- 
  metafor::vcalc(
    data = worst_dat_reint,
    vi = vgt_pop, 
    cluster = study,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  )

#############
# Overall res
#############

wc_overall<- 
  rma.mv(
    gt_pop,
    V = V_mat_wc, 
    random = ~ 1 | study / esid,
    data = worst_dat_reint,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

wc_overall

wc_tab_res <- 
  .pubbias_overall_tab(rma_obj = wc_overall, test = "Worst case") |> 
  mutate(
    J = n_distinct(worst_dat_reint$study),
    K = nrow(worst_dat_reint)
  )

###########
# Pregreg
###########

wc_prereg_raw <- 
  rma.mv(
    gt_pop ~ prereg_chr - 1,
    V = V_mat_wc, 
    random = ~ 1 | study / esid,
    data = worst_dat_reint,
    sparse = TRUE
  ) 

wc_prereg <- 
  wc_prereg_raw |> 
  robust(cluster = study, clubSandwich = TRUE)

#tic()
#plan(multisession)
#wc_prereg_cwb <- 
#  wildmeta::Wald_test_cwb(
#    full_model = wc_prereg_raw,
#    constraints = constrain_equal(1:2),
#    R = 1999
#  )
#plan(sequential)
#toc()
#
#saveRDS(wc_prereg_cwb, "Bootstrap results/wc_prereg_cwb.rds")
wc_prereg_cwb <- readRDS("Bootstrap results/wc_prereg_cwb.rds")

wc_prereg_tab <- 
   tibble(
    coefficient = c(
      "Not preregistered", "Preregistered", 
      "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(as.numeric(wc_prereg$b[1:2]), 3), 
        " [", 
        round(wc_prereg$ci.lb[1:2], 3),
        ", ",
        round(wc_prereg$ci.ub[1:2], 3),
        "]"
      ),
      as.character(round(wc_prereg_cwb$p_val, 3)),
      as.character(round(sqrt(wc_prereg$sigma2[1]), 3)),
      as.character(round(sqrt(wc_prereg$sigma2[2]), 3)),
      as.character(round(sqrt(sum(wc_prereg$sigma2)), 3)),
      as.character(n_distinct(worst_dat_reint$study)),
      as.character(nrow(worst_dat_reint))
    ),
    
    method = "worstcase"
    
  )

# Sensitivity analysis of prereg using the PESCE+ model. 
V_mat_wc_prereg <- 
  metafor::vcalc(
    data = worst_dat_reint,
    vi = vgt_pop, 
    cluster = study,
    subgroup = prereg_chr,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  )

wc_prereg_raw_sensi <- 
  rma.mv(
    gt_pop ~ prereg_chr - 1,
    V = V_mat_wc_prereg, 
    random = list(~ prereg_chr | study, ~ prereg_chr | esid),
    struct = c("DIAG", "DIAG"),
    data = worst_dat_reint,
    sparse = TRUE
  ) 

wc_prereg_sensi <- 
  wc_prereg_raw_sensi |> 
  robust(cluster = study, clubSandwich = TRUE)

############
# wc outcome
############
wc_outcome_raw <- 
  rma.mv(
    gt_pop ~ outcome_type + prereg_c - 1,
    V = V_mat_wc, 
    random = ~ 1 | study / esid,
    data = worst_dat_reint,
    sparse = TRUE
  ) 

wc_outcome <- 
  wc_outcome_raw |> 
  robust(cluster = study, clubSandwich = TRUE)

# CWB
#tic()
#plan(multisession, workers = 7L)
#wc_outcome_cwb <- 
#  wildmeta::Wald_test_cwb(
#    full_model = wc_outcome_raw,
#    constraints = constrain_equal(1:7),
#    R = 1999
#  )
#plan(sequential)
#toc()
#
#saveRDS(wc_outcome_cwb, "Bootstrap results/wc_outcome_cwb.rds")
wc_outcome_cwb <- readRDS("Bootstrap results/wc_outcome_cwb.rds")

wc_outcome_tab <- 
  tibble(
    coefficient = c(
      hyema_outcome$Parameter, "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(as.numeric(wc_outcome$b[-8]), 3), 
        " [", 
        round(wc_outcome$ci.lb[-8], 3),
        ", ",
        round(wc_outcome$ci.ub[-8], 3),
        "]"
      ),
      as.character(round(wc_outcome_cwb$p_val, 3)),
      as.character(round(sqrt(wc_outcome$sigma2[1]), 3)),
      as.character(round(sqrt(wc_outcome$sigma2[2]), 3)),
      as.character(round(sqrt(sum(wc_outcome$sigma2)), 3)),
      as.character(n_distinct(worst_dat_reint$study)),
      as.character(nrow(worst_dat_reint))
    ),
    
    method = "worstcase"
    
  )

# Sensitivity analyses using the PESCE+ model
V_mat_wc_outcome <- 
  metafor::vcalc(
    data = worst_dat_reint,
    vi = vgt_pop, 
    cluster = study,
    subgroup = outcome_type,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  )

wc_outcome_raw_sensi <- 
  rma.mv(
    gt_pop ~ outcome_type + prereg_c - 1,
    V = V_mat_wc, 
    random = list(~ outcome_type | study, ~ outcome_type | esid),
    struct = c("DIAG", "DIAG"),
    data = worst_dat_reint,
    sparse = TRUE
  ) 

wc_outcome_sensi <- 
  wc_outcome_raw_sensi |> 
  robust(cluster = study, clubSandwich = TRUE)



```


### CHE-ISCW 

```{r che-iscw}
rho <- 0.8

V_mat_mod <- metafor::vcalc(
  data = reint_ma_dat,
  vi = Wgt_pop, 
  cluster = study,
  type = outcome_time, 
  grp1 = trt_name,
  w1 = N_t, 
  grp2 = control,
  w2 = N_c, 
  rho = rho
)

W <- solve(V_mat_mod)

# CHE-ISCW
## Overall
che_iscw <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mod,
    W = W,
    random = ~ 1 | study / esid,
    data = reint_ma_dat,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

iscw_tab_res <- .pubbias_overall_tab(rma_obj = che_iscw, test = "CHE-ISCW")

## Preregistration
che_iscw_prereg_raw <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mod,
    W = W,
    mods = ~ prereg_chr - 1,
    random = ~ 1 | study / esid,
    data = reint_ma_dat,
    sparse = TRUE
  ) 

che_iscw_prereg <- 
  che_iscw_prereg_raw |> 
  robust(cluster = study, clubSandwich = TRUE)

#tic()
#plan(multisession, workers = 7L)
#che_iscw_prereg_cwb <- 
#  wildmeta::Wald_test_cwb(
#    full_model = che_iscw_prereg_raw,
#    constraints = constrain_equal(1:2),
#    R = 1999
#  )
#plan(sequential)
#toc()
#
#saveRDS(che_iscw_prereg_cwb, "Bootstrap results/che_iscw_prereg_cwb.rds")
che_iscw_prereg_cwb <- readRDS("Bootstrap results/che_iscw_prereg_cwb.rds")

che_iscw_prereg_tab <- 
  tibble(
    coefficient = c(
      "Not preregistered", "Preregistered", 
      "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(as.numeric(che_iscw_prereg$b[1:2]), 3), 
        " [", 
        round(che_iscw_prereg$ci.lb[1:2], 3),
        ", ",
        round(che_iscw_prereg$ci.ub[1:2], 3),
        "]"
      ),
      as.character(round(che_iscw_prereg_cwb$p_val, 3)),
      as.character(round(sqrt(che_iscw_prereg$sigma2[1]), 3)),
      as.character(round(sqrt(che_iscw_prereg$sigma2[2]), 3)),
      as.character(round(sqrt(sum(che_iscw_prereg$sigma2)), 3)),
      as.character(n_distinct(reint_ma_dat$study)),
      as.character(nrow(reint_ma_dat))
    ),
    
    method = "iscw"
    
  )


## Outcome
che_iscw_outcome_raw <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mod,
    W = W,
    mods = ~ outcome_type + prereg_c - 1,
    random = ~ 1 | study / esid,
    data = reint_ma_dat,
    sparse = TRUE
  ) 

che_iscw_outcome <- 
  che_iscw_outcome_raw |> 
  robust(cluster = study, clubSandwich = TRUE)

#tic()
#plan(multisession, workers = 7L)
#che_iscw_outcome_cwb <- 
#  wildmeta::Wald_test_cwb(
#    full_model = che_iscw_outcome_raw,
#    constraints = constrain_equal(1:7),
#    R = 1999
#  )
#plan(sequential)
#toc()
#
#saveRDS(che_iscw_outcome_cwb, "Bootstrap results/che_iscw_outcome_cwb.rds")
che_iscw_outcome_cwb <- readRDS("Bootstrap results/che_iscw_outcome_cwb.rds")

#MHV CHECK THIS
che_iscw_outcome_tab <- 
  tibble(
    coefficient = c(
      hyema_outcome$Parameter, "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(as.numeric(che_iscw_outcome$b[-8]), 3), 
        " [", 
        round(che_iscw_outcome$ci.lb[-8], 3),
        ", ",
        round(che_iscw_outcome$ci.ub[-8], 3),
        "]"
      ),
      as.character(round(che_iscw_outcome_cwb$p_val, 3)), 
      as.character(round(sqrt(che_iscw_outcome$sigma2[1]), 3)),
      as.character(round(sqrt(che_iscw_outcome$sigma2[2]), 3)),
      as.character(round(sqrt(sum(che_iscw_outcome$sigma2)), 3)),
      as.character(n_distinct(reint_ma_dat$study)),
      as.character(nrow(reint_ma_dat))
    ),
    
    method = "iscw"
    
  )
```

### PET/PEESE

```{r che-iscw}

## PET/PEESE overall
che_pet <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mod,
    W = W,
    mods = ~ Wse_pop + prereg_c,
    random = ~ 1 | study / esid,
    data = reint_ma_dat,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

che_peese <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mod,
    W = W,
    mods = ~ Wgt_pop + prereg_c,
    random = ~ 1 | study / esid,
    data = reint_ma_dat,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

pet_peese <- if (che_pet$pval[1] < 0.1 & as.numeric(che_pet$b[1]) > 0) che_peese else che_pet

pet_peese_tab_res <- .pubbias_overall_tab(rma_obj = pet_peese, test = "PET/PEESE")

## PET/PEESE preregistration
che_pet_prereg_raw <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mod,
    W = W,
    mods = ~ prereg_chr + Wse_pop - 1,
    random = ~ 1 | study / esid,
    data = reint_ma_dat,
    sparse = TRUE
  ) 

che_pet_prereg <- 
  che_pet_prereg_raw |> 
  robust(cluster = study, clubSandwich = TRUE)



#tic()
#plan(multisession, workers = 7L)
#che_pet_prereg_cwb <- 
#  wildmeta::Wald_test_cwb(
#    full_model = che_pet_prereg_raw,
#    constraints = constrain_equal(1:2),
#    R  = 1999
#  )
#plan(sequential)
#toc()
#
#saveRDS(che_pet_prereg_cwb, "Bootstrap results/che_pet_prereg_cwb.rds")
che_pet_prereg_cwb <- readRDS("Bootstrap results/che_pet_prereg_cwb.rds")

che_pet_prereg_tab <- 
  tibble(
    coefficient = c(
      "Not preregistered", "Preregistered",
      "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(as.numeric(che_pet_prereg$b[1:2]), 3), 
        " [", 
        round(che_pet_prereg$ci.lb[1:2], 3),
        ", ",
        round(che_pet_prereg$ci.ub[1:2], 3),
        "]"
      ),
      as.character(round(che_pet_prereg_cwb$p_val,3)),
      as.character(round(sqrt(che_pet_prereg$sigma2[1]), 3)),
      as.character(round(sqrt(che_pet_prereg$sigma2[2]), 3)),
      as.character(round(sqrt(sum(che_pet_prereg$sigma2)), 3)),
      as.character(n_distinct(reint_ma_dat$study)),
      as.character(nrow(reint_ma_dat))
    ),
    
    method = "petpesse"
    
  )


## PET/PEESE outcome
che_pet_outcome_raw <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mod,
    W = W,
    mods = ~ outcome_type + Wse_pop + prereg_c - 1,
    random = ~ 1 | study / esid,
    data = reint_ma_dat,
    sparse = TRUE
  ) 

che_pet_outcome <- 
  che_pet_outcome_raw |> 
  robust(cluster = study, clubSandwich = TRUE)



#tic()
#plan(multisession, workers = 7L)
#che_pet_outcome_cwb <- 
#  wildmeta::Wald_test_cwb(
#    full_model = che_pet_outcome_raw,
#    constraints = constrain_equal(1:7),
#    R  = 1999
#  )
#plan(sequential)
#toc()

#saveRDS(che_pet_outcome_cwb, "Bootstrap results/che_pet_outcome_cwb.rds")
che_pet_outcome_cwb <- readRDS("Bootstrap results/che_pet_outcome_cwb.rds")

che_pet_outcome_tab <- 
  tibble(
    coefficient = c(
      hyema_outcome$Parameter, "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(as.numeric(che_pet_outcome$b[-c(8:9)]), 3), 
        " [", 
        round(che_pet_outcome$ci.lb[-c(8:9)], 3),
        ", ",
        round(che_pet_outcome$ci.ub[-c(8:9)], 3),
        "]"
      ),
      as.character(round(che_pet_outcome_cwb$p_val, 3)),
      as.character(round(sqrt(che_pet_outcome$sigma2[1]), 3)),
      as.character(round(sqrt(che_pet_outcome$sigma2[2]), 3)),
      as.character(round(sqrt(sum(che_pet_outcome$sigma2)), 3)),
      as.character(n_distinct(reint_ma_dat$study)),
      as.character(nrow(reint_ma_dat))
    ),
    
    method = "petpesse"
    
  )

```

### Selection models

```{r, selmodel}

set.seed(29092025)

library(future)

cores <- parallel::detectCores() - 1

# Overall reintegration
#plan(multisession, workers = cores)
#
#mod_3PSM_overall <- 
#  metaselection::selection_model(
#    data = reint_ma_dat, 
#    yi = gt_pop,
#    sei = Wse_pop,
#    cluster = study,
#    selection_type = "step",
#    steps = 0.025,
#    estimator = "CML",
#    vcov_type = "robust",
#    CI_type = "percentile",
#    bootstrap = "two-stage",
#    R = 1999
#  )
#plan(sequential)
#
#saveRDS(mod_3PSM_overall, "Bootstrap results/mod_3PSM_overall.rds")
mod_3PSM_overall <- readRDS("Bootstrap results/mod_3PSM_overall.rds")

#selection_plot(mod_3PSM_overall)
#
#plan(multisession, workers = cores)
#
#mod_4PSM_overall <- 
#  metaselection::selection_model(
#    data = reint_ma_dat, 
#    yi = gt_pop,
#    sei = Wse_pop,
#    cluster = study,
#    selection_type = "step",
#    steps = c(0.025, 0.500),
#    estimator = "CML",
#    vcov_type = "robust",
#    CI_type = "percentile",
#    bootstrap = "two-stage",
#    R = 1999
#  )
#plan(sequential)
#
#saveRDS(mod_4PSM_overall, "Bootstrap results/mod_4PSM_overall.rds")
mod_4PSM_overall <- readRDS("Bootstrap results/mod_4PSM_overall.rds")


#save(
#  mod_3PSM_overall,
#  mod_4PSM_overall,
#  file = "selmodel_res.RData"
#)

##############################
# Across type of registration
##############################

## Only not preregistered outcome
#plan(multisession, workers = 7L)
#
#
#mod_3PSM_not_prereg <- 
#  metaselection::selection_model(
#    data = reint_ma_dat, 
#    yi = gt_pop,
#    sei = Wse_pop,
#    cluster = study,
#    selection_type = "step",
#    steps = 0.025,
#    estimator = "CML",
#    vcov_type = "robust",
#    CI_type = "percentile",
#    bootstrap = "two-stage",
#    R = 1999,
#    subset = conventional == 0
#  )
#plan(sequential)

## Prereg_chr as subgroup factor
  
#plan(multisession, workers = cores)
#
#mod_3PSM_prereg <- 
#  metaselection::selection_model(
#    data = reint_ma_dat, 
#    yi = gt_pop,
#    sei = Wse_pop,
#    cluster = study,
#    selection_type = "step",
#    steps = 0.025,
#    estimator = "CML",
#    vcov_type = "robust",
#    CI_type = "percentile",
#    bootstrap = "two-stage",
#    mean_mods = ~ prereg_chr - 1,
#    R = 1999
#  )
#plan(sequential)
#
#saveRDS(mod_3PSM_prereg, "Bootstrap results/mod_3PSM_prereg.rds")
mod_3PSM_prereg <- readRDS("Bootstrap results/mod_3PSM_prereg.rds")
  
  
#plan(multisession, workers = cores)
#
#mod_4PSM_prereg <- 
#  metaselection::selection_model(
#    data = reint_ma_dat, 
#    yi = gt_pop,
#    sei = Wse_pop,
#    cluster = study,
#    selection_type = "step",
#    steps = c(0.025, 0.500),
#    estimator = "CML",
#    vcov_type = "robust",
#    CI_type = "percentile",
#    bootstrap = "two-stage",
#    mean_mods = ~ prereg_chr - 1,
#    R = 1999
#  )
#plan(sequential)
#
#saveRDS(mod_4PSM_prereg, "Bootstrap results/mod_4PSM_prereg.rds")
mod_4PSM_prereg <- readRDS("Bootstrap results/mod_4PSM_prereg.rds")

###################
# Across outcomes
###################

#plan(multisession, workers = cores)
#
#mod_3PSM_outcome <- 
#  metaselection::selection_model(
#    data = reint_ma_dat, 
#    yi = gt_pop,
#    sei = Wse_pop,
#    cluster = study,
#    selection_type = "step",
#    steps = 0.025,
#    estimator = "CML",
#    vcov_type = "robust",
#    CI_type = "percentile",
#    bootstrap = "two-stage",
#    mean_mods = ~ outcome_type + prereg_c - 1,
#    R = 1999
#  )
#plan(sequential)
#
#saveRDS(mod_3PSM_outcome, "Bootstrap results/mod_3PSM_outcome.rds")
mod_3PSM_outcome <- readRDS("Bootstrap results/mod_3PSM_outcome.rds")

#selection_plot(mod_3PSM_overall)

#plan(multisession, workers = cores)
#
#mod_4PSM_outcome <- 
#  metaselection::selection_model(
#    data = reint_ma_dat, 
#    yi = gt_pop,
#    sei = Wse_pop,
#    cluster = study,
#    selection_type = "step",
#    steps = c(0.025, 0.500),
#    estimator = "CML",
#    vcov_type = "robust",
#    CI_type = "percentile",
#    bootstrap = "two-stage",
#    mean_mods = ~ outcome_type + prereg_c - 1,
#    R = 1999
#  )
#plan(sequential)
#
#saveRDS(mod_4PSM_outcome, "Bootstrap results/mod_4PSM_outcome.rds")
mod_4PSM_outcome <- readRDS("Bootstrap results/mod_4PSM_outcome.rds")

```


```{r tab-metaselection}

PSM3_tab_res <- 
  tibble(
    test = "Cluster selmodel (3PSM)",
    J = n_distinct(reint_ma_dat$study),
    K = nrow(reint_ma_dat),
    est_ci = paste0(
      round(as.numeric(mod_3PSM_overall$est$Est[1]), 3), 
      " [", 
      round(mod_3PSM_overall$est$percentile_lower[1], 3),
      ", ",
      round(mod_3PSM_overall$est$percentile_upper[1], 3),
      "]"
    ),
    pval = NA_real_,
    tau = sqrt(mod_3PSM_overall$predictions$tausq),
    omega = NA_real_,
    total_SD = tau
  )

PSM4_tab_res <- 
  tibble(
    test = "Cluster selmodel (4PSM)",
    J = n_distinct(reint_ma_dat$study),
    K = nrow(reint_ma_dat),
    est_ci = paste0(
      round(as.numeric(mod_4PSM_overall$est$Est[1]), 3), 
      " [", 
      round(mod_4PSM_overall$est$percentile_lower[1], 3),
      ", ",
      round(mod_4PSM_overall$est$percentile_upper[1], 3),
      "]"
    ),
    pval = NA_real_,
    tau = sqrt(mod_4PSM_overall$predictions$tausq),
    omega = NA_real_,
    total_SD = tau
  )

# Prereg
PSM3_prereg_tab <- 
  tibble(
    coefficient = c(
      "Not preregistered", "Preregistered", 
      "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(mod_3PSM_prereg$est$Est[1:2], 3), 
        " [", 
        round(mod_3PSM_prereg$est$percentile_lower[1:2], 3),
        ", ",
        round(mod_3PSM_prereg$est$percentile_upper[1:2], 3),
        "]"
      ),
      NA_character_,
      as.character(round(sqrt(mod_3PSM_prereg$predictions$tausq), 3)),
      NA_character_,
      as.character(round(sqrt(mod_3PSM_prereg$predictions$tausq), 3)),
      as.character(n_distinct(reint_ma_dat$study)),
      as.character(nrow(reint_ma_dat))
    ),
    
    method = "PSM3"
    
  )

PSM4_prereg_tab <- 
  tibble(
    coefficient = c(
      "Not preregistered", "Preregistered", 
      "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(mod_4PSM_prereg$est$Est[1:2], 3), 
        " [", 
        round(mod_4PSM_prereg$est$percentile_lower[1:2], 3),
        ", ",
        round(mod_4PSM_prereg$est$percentile_upper[1:2], 3),
        "]"
      ),
      NA_character_,
      as.character(round(sqrt(mod_4PSM_prereg$predictions$tausq), 3)),
      NA_character_,
      as.character(round(sqrt(mod_4PSM_prereg$predictions$tausq), 3)),
      as.character(n_distinct(reint_ma_dat$study)),
      as.character(nrow(reint_ma_dat))
    ),
    
    method = "PSM4"
    
  )


# Outcome
PSM3_outcome_tab <- 
  tibble(
    coefficient = c(
      hyema_outcome$Parameter, "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(mod_3PSM_outcome$est$Est[1:7], 3), 
        " [", 
        round(mod_3PSM_outcome$est$percentile_lower[1:7], 3),
        ", ",
        round(mod_3PSM_outcome$est$percentile_upper[1:7], 3),
        "]"
      ),
      NA_character_,
      as.character(round(sqrt(mod_3PSM_outcome$predictions$tausq), 3)),
      NA_character_,
      as.character(round(sqrt(mod_3PSM_outcome$predictions$tausq), 3)),
      as.character(n_distinct(reint_ma_dat$study)),
      as.character(nrow(reint_ma_dat))
    ),
    
    method = "PSM3"
    
  )

PSM4_outcome_tab <- 
  tibble(
    coefficient = c(
      hyema_outcome$Parameter, "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(mod_4PSM_outcome$est$Est[1:7], 3), 
        " [", 
        round(mod_4PSM_outcome$est$percentile_lower[1:7], 3),
        ", ",
        round(mod_4PSM_outcome$est$percentile_upper[1:7], 3),
        "]"
      ),
      NA_character_,
      as.character(round(sqrt(mod_4PSM_outcome$predictions$tausq), 3)),
      NA_character_,
      as.character(round(sqrt(mod_4PSM_outcome$predictions$tausq), 3)),
      as.character(n_distinct(reint_ma_dat$study)),
      as.character(nrow(reint_ma_dat))
    ),
    
    method = "PSM4"
    
  )

```


# **Mental health**
## Data
```{r load-data-mental}
#| code-fold: false

mental_ma_dat <- 
  readRDS("mental_ma_dat.rds") |> 
  mutate(
    esid = 1:n(),
    se_gt_pop = sqrt(vgt_pop), 
    Wse_pop = sqrt(Wgt_pop),
    t_i = gt_pop/sqrt(Wgt) # Following Chen and Pustejovsky (2025)
  )

```


## Funnel plots
```{r, main-res-mental}
#| eval: false
rho <- 0.8

V_mat_mental <- 
  metafor::vcalc(
    data = mental_ma_dat,
    vi = vgt_pop, 
    cluster = study,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  )

overall_res_mental <- 
  metafor::rma.mv(
    gt_pop,
    V = V_mat_mental, 
    random = ~ 1 | study / esid,
    data = mental_ma_dat,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

overall_res_mental

V_mat_outcome_mental <- 
  metafor::vcalc(
    data = mental_ma_dat,
    vi = vgt_pop, 
    cluster = study,
    subgroup = outcome_type,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  )


sub_res_mental <- 
  rma.mv(
    gt_pop ~ outcome_type - 1,
    V = V_mat_outcome_mental, 
    random = list(~ outcome_type | study, ~ outcome_type | esid),
    struct = c("DIAG", "DIAG"),
    data = mental_ma_dat,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

sub_res_mental

# Mental health
# MHV: Conduct these tests, when the main analyses has been made

#V_mat_mental <- metafor::vcalc(
#    data = mental_health_dat,
#    vi = vgt_pop, 
#    cluster = study,
#    type = outcome_time, 
#    grp1 = trt_name,
#    w1 = N_t, 
#    grp2 = control,
#    w2 = N_c, 
#    rho = rho
#  )
#
#overall_res_mental <- 
#  rma.mv(
#    gt_pop ~ + 1,
#    V = V_mat_mental, 
#    random = ~ 1 | study / esid,
#    data = mental_health_dat,
#    sparse = TRUE
#  ) |> 
#  robust(cluster = study, clubSandwich = TRUE)
#
#overall_res_mental
#
#sub_res_mental <- 
#  rma.mv(
#    gt_pop ~ -1 + analysis_plan,
#    V = V_mat_mental, 
#    random = list(~ analysis_plan | study, ~ analysis_plan | esid),
#    struct = c("DIAG", "DIAG"),
#    data = mental_health_dat,
#    sparse = TRUE
#  )
#
#sub_res_mental


```
### Overall 

```{r mental-overall-fp}
#| label: fig-mental-overall-fp
#| fig-cap: "Funnel plot across all mental health outcomes"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false

## Overall average effect

rho <- 0.8

# CHE-ISCW
V_mat_mental <- 
  metafor::vcalc(
    data = mental_ma_dat,
    vi = Wgt_pop, 
    cluster = study,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  )

blsplit(V_mat_mental, mental_ma_dat$study) |> 
  lapply(cov2cor) |> 
  map(~ round(.x, 2))


W_mental <- solve(V_mat_mental) |> round(3)

# CHE
che_mental <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mental,
    random = ~ 1 | study / esid,
    data = mental_ma_dat,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

# ISCW

# CHE-ISCW-RVE
che_iscw_mental <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mental,
    W = W_mental,
    random = ~ 1 | study / esid,
    data = mental_ma_dat,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)


## Preregistered vs. not preregistered 

prereg_dat_mental <-  
  mental_ma_dat |> 
  filter(conventional == 0)

V_mat_prereg_mental <- 
  metafor::vcalc(
    data = prereg_dat_mental,
    vi = Wgt_pop, 
    cluster = study,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  ) 

W_prereg_mental <- solve(V_mat_prereg_mental) |> round(3)

egg_prereg_mental <-
  rma.mv(
    yi = gt_pop,
    V = V_mat_prereg_mental,
    #W = W_prereg_mental,
    mods = ~ Wse_pop,
    random = ~ 1 | study / esid,
    data = prereg_dat_mental,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

egg_prereg_res_mental <- 
  tibble(
    subgroup = "Preregistered",
    egg_intercept = as.numeric(egg_prereg_mental$b[1]),
    egg_slope = as.numeric(egg_prereg_mental$b[2])
  )

notprereg_dat_mental <-  
  mental_ma_dat |> 
  filter(conventional == 1)


V_mat_notprereg_mental <-  
  metafor::vcalc(
    data = notprereg_dat_mental,
    vi = Wgt_pop, 
    cluster = study,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  )

W_notprereg_mental <- solve(V_mat_notprereg_mental) |> round(3)

egg_notprereg_mental <-
  rma.mv(
    yi = gt_pop,
    V = V_mat_notprereg_mental,
    W = W_notprereg_mental,
    mods = ~ Wse_pop,
    random = ~ 1 | study / esid,
    data = notprereg_dat_mental,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)


egg_notprereg_res_mental <- 
  tibble(
    subgroup = "Not preregistered",
    egg_intercept = as.numeric(egg_notprereg_mental$b[1]),
    egg_slope = as.numeric(egg_notprereg_mental$b[2])
  )

egg_res_subgrouped_mental <- bind_rows(egg_prereg_res_mental, egg_notprereg_res_mental)
egg_res_subgrouped_mental


# PESCE+ model

prereg_arg_mental <- 
  .rma_arg_tbl(
    yi = "gt_pop", 
    vi = "vgt_pop", 
    covars = "prereg_chr",
    model = "SCEp",
    r = 0.8, 
    data = mental_ma_dat,
    type = "categorical"
  ); prereg_arg_mental

# PESCEp+ 
subgroup_means_mental <- pmap(.l = prereg_arg_mental, .f = .PESCE_RVE) |> list_rbind()

#subgroup_means <- .SCEp(mod = prereg_chr, data = reint_ma_dat)

subgroup_dat_mental <- 
  mental_ma_dat |> 
  summarise(
    gt_pop = mean(gt_pop),
    Wse_pop = mean(Wse_pop),
    outcome_type = outcome_type[1],
    .by = prereg_chr
  ) |> 
  bind_cols(subgroup_means_mental[c(3,2), c(2, 14:18)], egg_res_subgrouped_mental) |> 
  mutate(
    slope_low = qnorm(0.025), 
    slope_high = qnorm(0.975), 
    level = "Effect size level"
  ) 



y_lim_exp1_mental <- max(mental_ma_dat$Wse_pop) + 0.02 

funnel_exp1_mental <-  
  tribble(
    ~ x90, ~ x95, ~ x99, ~ y,
    0,     0,     0,     0,
    qnorm(0.05) * y_lim_exp1_mental, qnorm(0.025) * y_lim_exp1_mental, qnorm(0.005) * y_lim_exp1_mental, y_lim_exp1_mental,
    qnorm(0.95) * y_lim_exp1_mental, qnorm(0.975) * y_lim_exp1_mental, qnorm(0.995) * y_lim_exp1_mental, y_lim_exp1_mental,
    0,     0,     0,     0
  ) 



alpha_line <- 0.5
polygon_fill <- c("grey", "grey10", "lightcyan")
mean_line <- "dashed"
reg_test <- TRUE
reg_line <- "longdash"
reg_color <- "blue"
breaks_y <- seq(-3, 3, 0.5)


es_level_fp_mental <- 
  mental_ma_dat |> 
  mutate(
    level = "Effect size level",
    report_bias = case_when(
      rob_tool == "RoB2" & D5 == "Low" ~ "Low",
      rob_tool == "RoB2" & str_detect(D5, "Some") ~ "Moderate",
      rob_tool == "RoB2" & str_detect(D5, "High") ~ "Serious",
      .default = D7
    ),
    
    report_bias = factor(report_bias, levels =  c("Low", "Moderate", "Serious")),
    
    large_sample = if_else(N_total > 100, "Sample above 100", "Sample below 100")
    
  ) |> 
  ggplot() + 
  geom_polygon(data = funnel_exp1_mental, aes(x = y, y = x99), fill = polygon_fill[1], alpha = 0.5) + 
  geom_polygon(data = funnel_exp1_mental, aes(x = y, y = x95), fill = polygon_fill[2], alpha = 0.5) + 
  geom_polygon(data = funnel_exp1_mental, aes(x = y, y = x90), fill = polygon_fill[3], alpha = 0.7) + 
  geom_abline(data = subgroup_dat_mental, aes(slope = slope_high, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_hline(data = subgroup_dat_mental, aes(yintercept = avg_effect), linetype = mean_line, alpha = alpha_line) +  
  geom_abline(data = subgroup_dat_mental, aes(slope = slope_low, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_abline(data = subgroup_dat_mental, aes(slope = -egg_slope, intercept = egg_intercept), linetype = reg_line, color = reg_color) +
  geom_point(aes(Wse_pop, gt_pop, color = overall_rob), alpha = 1, size = 1.5) +
  coord_flip() +
  facet_grid(level~prereg_chr) +
  scale_x_reverse(limits = c(y_lim_exp1_mental, 0.0), expand = c(0,0)) + 
  scale_y_continuous(breaks = breaks_y) + 
  scale_color_manual(
    values = c("Low" = "green3", "Some concerns/Moderate" = "yellow2", "Serious/High" = "red")
  ) + 
  theme_bw() + 
  labs(x = "Modified standard error", 
       y = "Standardized mean difference (Hedges' g)", 
       color = "") +
  theme(
    legend.position = "bottom",
    strip.text.x = element_blank()
  ) +
  labs(color = "Overall risk of bias") +
  guides(col = guide_legend(nrow = 1))


# Make aggregate plot

mental_dat_agg <- 
  mental_ma_dat |> 
  escalc(measure = "SMD", yi = gt_pop, vi = Wgt_pop, data = _) |> 
  aggregate.escalc(cluster = study, rho = 0.8) |> 
  mutate(
    Wse_pop = sqrt(vi)
  )

prereg_dat_agg_mental <-  
  mental_dat_agg |> 
  as_tibble() |> 
  dplyr::filter(conventional == 0)

egg_prereg_agg_mental <- 
  rma(yi = yi, vi = vi, data = prereg_dat_agg_mental, control=list(stepadj=0.5, maxiter=1000)) |> 
  regtest()

egg_prereg_agg_res_mental <- 
  tibble(
    subgroup = "Preregistered",
    egg_intercept = as.numeric(egg_prereg_agg_mental$fit$b[1]),
    egg_slope = as.numeric(egg_prereg_agg_mental$fit$b[2])
  )

notprereg_dat_agg_mental <-  
  mental_dat_agg |> 
  as_tibble() |> 
  dplyr::filter(conventional == 1)

egg_notprereg_agg_mental <- 
  rma(yi = yi, vi = vi, data = notprereg_dat_agg_mental) |> 
  regtest()

egg_notprereg_agg_res_mental <- 
  tibble(
    subgroup = "Not preregistered",
    egg_intercept = as.numeric(egg_notprereg_agg_mental$fit$b[1]),
    egg_slope = as.numeric(egg_notprereg_agg_mental$fit$b[2])
  )

egg_res_agg_subgrouped_mental <- 
  bind_rows(
    egg_notprereg_agg_res_mental, 
    egg_prereg_agg_res_mental
  )


means_agg_mental <- 
  rma(yi, vi, mods = ~ prereg_chr - 1, data = mental_dat_agg) |> 
  robust(cluster = study, clubSandwich = TRUE)

subgroup_means_agg_mental <- 
  tibble(
    Moderator = c("Not preregistered", "Preregistered"),
    avg_effect = as.numeric(means_agg_mental$b), 
    LL = as.numeric(means_agg_mental$ci.lb), 
    UL = as.numeric(means_agg_mental$ci.ub)
  )

subgroup_dat_agg_mental <- 
  mental_dat_agg |> 
  summarise(
    gt_pop = mean(gt_pop),
    Wse_pop = mean(Wse_pop),
    outcome_type = outcome_type[1],
    .by = prereg_chr
  ) |> 
  arrange(prereg_chr) |> 
  bind_cols(subgroup_means_agg_mental, egg_res_agg_subgrouped_mental) |> 
  mutate(slope_low = qnorm(0.025), slope_high = qnorm(0.975), level = "Study level") 


#subgroup_dat <- 
#  reintergation_dat |> 
#  summarise(
#    gt = mean(gt),
#    Wse = mean(Wse),
#    analysis_plan = analysis_plan[1],
#    .by = prereg_chr
#  ) |> 
#  bind_cols(subgroup_means[2:3,], egg_res_subgrouped) |> 
#  mutate(slope_low = qnorm(0.025), slope_high = qnorm(0.975), level = "Effect size level") 



y_lim_exp2_mental <- max(mental_dat_agg$Wse_pop) + 0.02 
y_lim_exp2_mental  

funnel_exp2_mental <-  tribble(
  ~ x90, ~ x95, ~ x99, ~ y,
  0,     0,     0,     0,
  qnorm(0.05) * y_lim_exp2_mental, qnorm(0.025) * y_lim_exp2_mental, qnorm(0.005) * y_lim_exp2_mental, y_lim_exp2_mental,
  qnorm(0.95) * y_lim_exp2_mental, qnorm(0.975) * y_lim_exp2_mental, qnorm(0.995) * y_lim_exp2_mental, y_lim_exp2_mental,
  0,     0,     0,     0
) 

study_level_fp_mental <- 
  mental_dat_agg |> 
  mutate(level = "Study level") |> 
  ggplot() + 
  geom_polygon(data = funnel_exp2_mental, aes(x = y, y = x99), fill = polygon_fill[1], alpha = 0.5) + 
  geom_polygon(data = funnel_exp2_mental, aes(x = y, y = x95), fill = polygon_fill[2], alpha = 0.5) + 
  geom_polygon(data = funnel_exp2_mental, aes(x = y, y = x90), fill = polygon_fill[3], alpha = 0.7) + 
  geom_abline(data = subgroup_dat_agg_mental, aes(slope = slope_high, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_hline(data = subgroup_dat_agg_mental, aes(yintercept = avg_effect), linetype = mean_line, alpha = alpha_line) +  
  geom_abline(data = subgroup_dat_agg_mental, aes(slope = slope_low, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_abline(data = subgroup_dat_agg_mental, aes(slope = -egg_slope, intercept = egg_intercept), linetype = reg_line, color = reg_color) +
  geom_point(aes(Wse_pop, gt_pop), alpha = 1, size = 1.5) +
  scale_color_brewer(type = "qual", palette = 2) + 
  coord_flip() +
  facet_grid(level~prereg_chr) +
  scale_x_reverse(limits = c(y_lim_exp2_mental, 0.0), expand = c(0,0)) + 
  scale_y_continuous(breaks = breaks_y) + 
  theme_bw() +
  theme(
    axis.title = element_blank()
  )

ylab_mental <- es_level_fp_mental$labels$x

study_level_fp_mental$labels$x <- es_level_fp_mental$labels$x <- "" 

#png("plots/funnel plots (overall effect) across type of mental health.png", width = 6.5, height = 5, res = 300, unit = "in")
study_level_fp_mental / es_level_fp_mental
grid::grid.draw(grid::textGrob(ylab_mental, y = 0.6, x = 0.02, rot = 90))
#dev.off()

```

### Investigating the impact of Cano-Vindel et al.

```{r reint-overall-fp}
prereg_dat_cano_mental <-  
  mental_ma_dat |> 
  filter(conventional == 0) |>
  mutate(
    cano_vindel = if_else(str_detect(study, "Cano"), 1, 0),
    cano_vindel = factor(cano_vindel)
  )

V_mat_prereg_cano_mental <- 
  metafor::vcalc(
    data = prereg_dat_cano_mental,
    vi = Wgt_pop, 
    cluster = study,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  )

W_prereg_cano_mental <- solve(V_mat_prereg_cano_mental) |> round(3)

egg_prereg_cano_mental <-
  rma.mv(
    yi = gt_pop,
    V = V_mat_prereg_cano_mental,
    #W = W_prereg_cano_mental,
    mods = ~ Wse_pop + cano_vindel,
    random = ~ 1 | study / esid,
    data = prereg_dat_cano_mental,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

egg_prereg_res_cano_mental <- 
  tibble(
    subgroup = "Preregistered",
    egg_intercept = as.numeric(egg_prereg_cano_mental$b[1]),
    egg_slope = as.numeric(egg_prereg_cano_mental$b[2])
  )


subgroup_dat_cano_mental <- 
  prereg_dat_cano_mental |> 
  summarise(
    gt_pop = mean(gt_pop),
    Wse = mean(Wse_pop),
    outcome_type = outcome_type[1],
    .by = prereg_chr
  ) |> 
  bind_cols(subgroup_means_mental[3, c(2, 14:18)], egg_prereg_res_cano_mental) |> 
  mutate(slope_low = qnorm(0.025), slope_high = qnorm(0.975)) 



y_lim_exp_cano_mental <- max(prereg_dat_cano_mental$Wse_pop) + 0.02 
y_lim_exp_cano_mental  

funnel_exp_cano_mental <-  tribble(
  ~ x90, ~ x95, ~ x99, ~ y,
  0,     0,     0,     0,
  qnorm(0.05) * y_lim_exp_cano_mental, qnorm(0.025) * y_lim_exp_cano_mental, qnorm(0.005) * y_lim_exp_cano_mental, y_lim_exp_cano_mental,
  qnorm(0.95) * y_lim_exp_cano_mental, qnorm(0.975) * y_lim_exp_cano_mental, qnorm(0.995) * y_lim_exp_cano_mental, y_lim_exp_cano_mental,
  0,     0,     0,     0
) 



alpha_line <- 0.5
polygon_fill <- c("grey", "grey10", "lightcyan")
mean_line <- "dashed"
reg_test <- TRUE
reg_line <- "longdash"
reg_color <- "blue"
breaks_y <- seq(-3, 3, 0.5)


cano_fp_mental <- 
  prereg_dat_cano_mental |> 
  mutate(alpha_val = if_else(cano_vindel == 1, 0.9, 1)) |>
  ggplot() + 
  geom_polygon(data = funnel_exp_cano_mental, aes(x = y, y = x99), fill = polygon_fill[1], alpha = 0.5) + 
  geom_polygon(data = funnel_exp_cano_mental, aes(x = y, y = x95), fill = polygon_fill[2], alpha = 0.5) + 
  geom_polygon(data = funnel_exp_cano_mental, aes(x = y, y = x90), fill = polygon_fill[3], alpha = 0.7) + 
  geom_abline(data = subgroup_dat_cano_mental, aes(slope = slope_high, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_hline(data = subgroup_dat_cano_mental, aes(yintercept = avg_effect), linetype = mean_line, alpha = alpha_line) +  
  geom_abline(data = subgroup_dat_cano_mental, aes(slope = slope_low, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_abline(data = subgroup_dat_cano_mental, aes(slope = -egg_slope, intercept = egg_intercept), linetype = reg_line, color = reg_color) +
  geom_point(aes(Wse_pop, gt_pop, col = cano_vindel, alpha = alpha_val), size = 1.5) +
  scale_color_brewer(type = "qual", palette = 2) + 
  coord_flip() +
  facet_grid(~prereg_chr) +
  scale_x_reverse(limits = c(y_lim_exp_cano_mental, 0.0), expand = c(0,0)) + 
  scale_y_continuous(breaks = breaks_y) + 
  theme_bw() + 
  labs(x = "Modified standard error", 
       y = "Standardized mean difference (Hedges' g)", 
       color = "", shape = "") +
  theme(
    legend.position = "bottom"
  ) +
  labs(color = "Cano-vindel") +
  guides(col = "none", alpha = "none")

#png("plots/funnel plots (overall effect) without Cano-Vindel.png", width = 8, height = 5.5, res = 300, unit = "in")
cano_fp_mental
#dev.off()




```

## Publication bias tests (mental health)

### HYEMA

```{r hyema-mental}
hyema_overall_mental <- readRDS("Bootstrap results/hyema_overall_mental.rds")

# Overall res mental health (Robust HYEMA)
hyema_tab_res_mental <- 
  tibble(
    test = "Robust HYEMA",
    J = n_distinct(mental_ma_dat$study),
    K = nrow(mental_ma_dat),
    est_ci = paste0(
      round(as.numeric(hyema_overall_mental$Est[1]), 3), 
      " [", 
      round(hyema_overall_mental$CIL_bootstrap[1], 3),
      ", ",
      round(hyema_overall_mental$CIU_bootstrap[2], 3),
      "]"
    ),
    pval = NA_real_,
    tau = round(hyema_overall_mental$Est[2], 3),
    omega = NA_real_,
    total_SD = hyema_overall_mental$Est[2]
  )

# HYEMA across outcome
hyema_outcome_mental <- readRDS("Bootstrap results/hyema_overcome_mental.rds")
hyema_outcome_f_stat_mental <- readRDS("Bootstrap results/F_boot_pval_outcome_mental.rds")

# To temporarily get tau
#hyema_obj_mental <- 
#  puniform::hybrid(
#    yi = mental_ma_dat$gt_pop, 
#    vi = mental_ma_dat$Wgt_pop, 
#    conventional = mental_ma_dat$conventional, 
#    side = "right",
#    mods = ~ mental_ma_dat$outcome_type - 1
#  ) |> 
#  suppressWarnings()

hyema_outcome_tab_mental <- 
  tibble(
    coefficient = c(
      hyema_outcome_mental$Parameter[-5], "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"),
    est_ci = c(
      paste0(
        round(as.numeric(hyema_outcome_mental$Est[-5]), 3), 
        " [", 
        round(hyema_outcome_mental$CIL_bootstrap[-5], 3),
        ", ",
        round(hyema_outcome_mental$CIU_bootstrap[-5], 3),
        "]"
      ),
      as.character(round(hyema_outcome_f_stat_mental, 3)),
      as.character(round(hyema_outcome_mental$Est[5], 3)),
      NA_character_,
      as.character(round( hyema_outcome_mental$Est[5], 3)),
      as.character(n_distinct(mental_ma_dat$study)),
      as.character(nrow(mental_ma_dat))
    ),
    
    method = "hyema"
    
  )



```

### Puniform*

```{r puniform-mental}
# Not corrected for clustering as it has showed acceptable performance in
# dependent effect size data
puniform_star_res_mental <- 
  puniform::puni_star(
    tobs = mental_ma_dat$t_i, 
    n1i = mental_ma_dat$N_t, 
    n2i = mental_ma_dat$N_c, 
    side = "right"
  )

puniform_tab_res_mental <- 
  tibble(
    test = "puniform star",
    J = n_distinct(mental_ma_dat$study),
    K = nrow(mental_ma_dat),
    est_ci = paste0(
      round(as.numeric(puniform_star_res_mental$est), 3), 
      " [", 
      round(puniform_star_res_mental$ci.lb, 3),
      ", ",
      round(puniform_star_res_mental$ci.ub, 3),
      "]"
    ),
    pval = puniform_star_res_mental$pval.0,
    tau = round(sqrt(puniform_star_res_mental$tau2), 3),
    omega = NA_real_,
    total_SD = tau
    
  )



```


### Worst-case meta-analysis

```{r wc-mental}

worst_dat_mental <- 
  mental_ma_dat |>  
  mutate(
    pval = 2 * ( 1 - pnorm( abs(gt_pop) / sqrt(vgt_pop) ) ),
    affirmativity = if_else(pval < .05 & gt_pop > 0, "affirmative", "nonaffirmative")
    
  ) %>% 
  filter(affirmativity == "nonaffirmative")

wc_prereg_studies_mental <- 
  worst_dat_mental |> 
  summarise(
    prereg_chr = unique(prereg_chr),
    .by = study
  ) |> 
  summarise(
    n_studies = n(),
    .by = prereg_chr
  ) |> 
  arrange(prereg_chr)

wc_prereg_es_mental <- 
  worst_dat_mental |> 
  summarise(n_effects = n(), .by = prereg_chr) |> 
  arrange(prereg_chr) 

# Outcome
wc_outcome_studies_mental <- 
  worst_dat_mental |> 
  summarise(
    n = n(), 
    .by = c(outcome_type, study)
  ) |> 
  summarise(
    n_studies = n(),
    .by = outcome_type
  ) |> 
  arrange(outcome_type)

wc_outcome_es_mental <- 
  worst_dat_mental |> 
  summarise(n_effects = n(), .by = outcome_type) |> 
  arrange(outcome_type) 


```

```{r}
res_PubBias_mental <- 
  pubbias_svalue(
  yi = mental_ma_dat$gt_pop,
  vi = mental_ma_dat$Wgt_pop,
  cluster = mental_ma_dat$study,
  q = 0,
  model_type = "robust",
  favor_positive = TRUE,
  return_worst_meta = TRUE
)

res_PubBias_mental$stats

rho <- 0.8

pubbias_plot_mental <- 
  PublicationBias::significance_funnel(
  yi = mental_ma_dat$gt_pop,
  vi = mental_ma_dat$Wgt_pop,
  favor_positive = TRUE,
  alpha_select = 0.05
)

pubbias_plot_mental
```


```{r}
#wc = worst_case
V_mat_wc_mental <- 
  metafor::vcalc(
    data = worst_dat_mental,
    vi = vgt_pop, 
    cluster = study,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  )

#############
# Overall res
#############

wc_overall_mental <- 
  rma.mv(
    gt_pop,
    V = V_mat_wc_mental, 
    random = ~ 1 | study / esid,
    data = worst_dat_mental,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

wc_overall_mental

wc_tab_res_mental <- 
  .pubbias_overall_tab(
    rma_obj = wc_overall_mental, 
    test = "Worst case",
    studies = n_distinct(worst_dat_mental$study),
    effects = nrow(worst_dat_mental)
    ) 

###########
# Pregreg
###########

wc_prereg_raw_mental <- 
  rma.mv(
    gt_pop ~ prereg_chr - 1,
    V = V_mat_wc_mental, 
    random = ~ 1 | study / esid,
    data = worst_dat_mental,
    sparse = TRUE
  ) 

wc_prereg_mental <- 
  wc_prereg_raw_mental |> 
  robust(cluster = study, clubSandwich = TRUE)

#tic()
#plan(multisession)
#wc_prereg_cwb_mental <- 
#  wildmeta::Wald_test_cwb(
#    full_model = wc_prereg_raw_mental,
#    constraints = constrain_equal(1:2),
#    R = 1999
#  )
#plan(sequential)
#toc()
#
#saveRDS(wc_prereg_cwb_mental, "Bootstrap results/wc_prereg_cwb_mental.rds")
wc_prereg_cwb_mental <- readRDS("Bootstrap results/wc_prereg_cwb_mental.rds")

wc_prereg_tab_mental <- 
   tibble(
    coefficient = c(
      "Not preregistered", "Preregistered", 
      "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(as.numeric(wc_prereg_mental$b[1:2]), 3), 
        " [", 
        round(wc_prereg_mental$ci.lb[1:2], 3),
        ", ",
        round(wc_prereg_mental$ci.ub[1:2], 3),
        "]"
      ),
      as.character(round(wc_prereg_cwb_mental$p_val, 3)),
      as.character(round(sqrt(wc_prereg_mental$sigma2[1]), 3)),
      as.character(round(sqrt(wc_prereg_mental$sigma2[2]), 3)),
      as.character(round(sqrt(sum(wc_prereg_mental$sigma2)), 3)),
      as.character(n_distinct(worst_dat_mental$study)),
      as.character(nrow(worst_dat_mental))
    ),
    
    method = "worstcase"
    
  )

# Sensitivity analysis of prereg using the PESCE+ model. 
V_mat_wc_prereg_mental <- 
  metafor::vcalc(
    data = worst_dat_mental,
    vi = vgt_pop, 
    cluster = study,
    subgroup = prereg_chr,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  )

wc_prereg_raw_sensi_mental <- 
  rma.mv(
    gt_pop ~ prereg_chr - 1,
    V = V_mat_wc_prereg_mental, 
    random = list(~ prereg_chr | study, ~ prereg_chr | esid),
    struct = c("DIAG", "DIAG"),
    data = worst_dat_mental,
    sparse = TRUE
  ) 

wc_prereg_sensi_mental <- 
  wc_prereg_raw_sensi_mental |> 
  robust(cluster = study, clubSandwich = TRUE)

############
# wc outcome
############
wc_outcome_raw_mental <- 
  rma.mv(
    gt_pop ~ outcome_type + prereg_c - 1,
    V = V_mat_wc_mental, 
    random = ~ 1 | study / esid,
    data = worst_dat_mental,
    sparse = TRUE
  ) 

wc_outcome_mental <- 
  wc_outcome_raw_mental |> 
  robust(cluster = study, clubSandwich = TRUE)

# CWB
#tic()
#plan(multisession, workers = 7L)
#wc_outcome_cwb_mental <- 
#  wildmeta::Wald_test_cwb(
#    full_model = wc_outcome_raw_mental,
#    constraints = constrain_equal(1:4),
#    R = 1999
#  )
#plan(sequential)
#toc()
#
#saveRDS(wc_outcome_cwb_mental, "Bootstrap results/wc_outcome_cwb_mental.rds")
wc_outcome_cwb_mental <- readRDS("Bootstrap results/wc_outcome_cwb_mental.rds")

wc_outcome_tab_mental <- 
  tibble(
    coefficient = c(
      hyema_outcome_mental$Parameter[-5], "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(as.numeric(wc_outcome_mental$b[-c(5:6)]), 3), 
        " [", 
        round(wc_outcome_mental$ci.lb[-c(5:6)], 3),
        ", ",
        round(wc_outcome_mental$ci.ub[-c(5:6)], 3),
        "]"
      ),
      as.character(round(wc_outcome_cwb_mental$p_val, 3)),
      as.character(round(sqrt(wc_outcome_mental$sigma2[1]), 3)),
      as.character(round(sqrt(wc_outcome_mental$sigma2[2]), 3)),
      as.character(round(sqrt(sum(wc_outcome_mental$sigma2)), 3)),
      as.character(n_distinct(worst_dat_mental$study)),
      as.character(nrow(worst_dat_mental))
    ),
    
    method = "worstcase"
    
  )

# Sensitivity analyses using the PESCE+ model
V_mat_wc_outcome_mental <- 
  metafor::vcalc(
    data = worst_dat_mental,
    vi = vgt_pop, 
    cluster = study,
    subgroup = outcome_type,
    type = outcome_time, 
    grp1 = trt_name,
    w1 = N_t, 
    grp2 = control,
    w2 = N_c, 
    rho = rho
  )

wc_outcome_raw_sensi_mental <- 
  rma.mv(
    gt_pop ~ outcome_type + prereg_c - 1,
    V = V_mat_wc_mental, 
    random = list(~ outcome_type | study, ~ outcome_type | esid),
    struct = c("DIAG", "DIAG"),
    data = worst_dat_mental,
    sparse = TRUE
  ) 

wc_outcome_sensi_mental <- 
  wc_outcome_raw_sensi_mental |> 
  robust(cluster = study, clubSandwich = TRUE)

clubSandwich::Wald_test(
  wc_outcome_sensi_mental, 
  constraints = constrain_equal(1:4), 
  vcov = "CR2"
)

```


### CHE-ISCW 

```{r che-iscw-mental}
rho <- 0.8

V_mat_mod_mental <- metafor::vcalc(
  data = mental_ma_dat,
  vi = Wgt_pop, 
  cluster = study,
  type = outcome_time, 
  grp1 = trt_name,
  w1 = N_t, 
  grp2 = control,
  w2 = N_c, 
  rho = rho
)

W_mental <- solve(V_mat_mod_mental) |> round(3)

# CHE-ISCW
## Overall
che_iscw_mental <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mod_mental,
    W = W_mental,
    random = ~ 1 | study / esid,
    data = mental_ma_dat,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

iscw_tab_res_mental <- .pubbias_overall_tab(
  rma_obj = che_iscw_mental, 
  test = "CHE-ISCW",
  studies = n_distinct(mental_ma_dat$study),
  effects = nrow(mental_ma_dat)
  )

## Preregistration
che_iscw_prereg_raw_mental <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mod_mental,
    W = W_mental,
    mods = ~ prereg_chr - 1,
    random = ~ 1 | study / esid,
    data = mental_ma_dat,
    sparse = TRUE
  ) 

che_iscw_prereg_mental <- 
  che_iscw_prereg_raw_mental |> 
  robust(cluster = study, clubSandwich = TRUE)

#tic()
#plan(multisession, workers = 7L)
#che_iscw_prereg_cwb_mental <- 
#  wildmeta::Wald_test_cwb(
#    full_model = che_iscw_prereg_raw_mental,
#    constraints = constrain_equal(1:2),
#    R = 1999
#  )
#plan(sequential)
#toc()
#
#saveRDS(che_iscw_prereg_cwb_mental, "Bootstrap results/che_iscw_prereg_cwb_mental.rds")
che_iscw_prereg_cwb_mental <- readRDS("Bootstrap results/che_iscw_prereg_cwb_mental.rds")

che_iscw_prereg_tab_mental <- 
  tibble(
    coefficient = c(
      "Not preregistered", "Preregistered", 
      "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(as.numeric(che_iscw_prereg_mental$b[1:2]), 3), 
        " [", 
        round(che_iscw_prereg_mental$ci.lb[1:2], 3),
        ", ",
        round(che_iscw_prereg_mental$ci.ub[1:2], 3),
        "]"
      ),
      as.character(round(che_iscw_prereg_cwb_mental$p_val, 3)),
      as.character(round(sqrt(che_iscw_prereg_mental$sigma2[1]), 3)),
      as.character(round(sqrt(che_iscw_prereg_mental$sigma2[2]), 3)),
      as.character(round(sqrt(sum(che_iscw_prereg_mental$sigma2)), 3)),
      as.character(n_distinct(mental_ma_dat$study)),
      as.character(nrow(mental_ma_dat))
    ),
    
    method = "iscw"
    
  )


## Outcome
che_iscw_outcome_raw_mental <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mod_mental,
    W = W_mental,
    mods = ~ outcome_type + prereg_c - 1,
    random = ~ 1 | study / esid,
    data = mental_ma_dat,
    sparse = TRUE
  ) 

che_iscw_outcome_mental <- 
  che_iscw_outcome_raw_mental |> 
  robust(cluster = study, clubSandwich = TRUE)

#tic()
#plan(multisession, workers = 7L)
#che_iscw_outcome_cwb_mental <- 
#  wildmeta::Wald_test_cwb(
#    full_model = che_iscw_outcome_raw_mental,
#    constraints = constrain_equal(1:4),
#    R = 1999
#  )
#plan(sequential)
#toc()
#
#saveRDS(che_iscw_outcome_cwb_mental, "Bootstrap results/che_iscw_outcome_cwb_mental.rds")
che_iscw_outcome_cwb_mental <- readRDS("Bootstrap results/che_iscw_outcome_cwb_mental.rds")

che_iscw_outcome_tab_mental <- 
  tibble(
    coefficient = c(
      hyema_outcome_mental$Parameter[-5], "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(as.numeric(che_iscw_outcome_mental$b[-5]), 3), 
        " [", 
        round(che_iscw_outcome_mental$ci.lb[-5], 3),
        ", ",
        round(che_iscw_outcome_mental$ci.ub[-5], 3),
        "]"
      ),
      as.character(round(che_iscw_outcome_cwb_mental$p_val, 3)), 
      as.character(round(sqrt(che_iscw_outcome_mental$sigma2[1]), 3)),
      as.character(round(sqrt(che_iscw_outcome_mental$sigma2[2]), 3)),
      as.character(round(sqrt(sum(che_iscw_outcome_mental$sigma2)), 3)),
      as.character(n_distinct(mental_ma_dat$study)),
      as.character(nrow(mental_ma_dat))
    ),
    
    method = "iscw"
    
  )
```

### PET/PEESE

```{r che-iscw-mental}

## PET/PEESE overall
che_pet_mental <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mod_mental,
    W = W_mental,
    mods = ~ Wse_pop + prereg_c,
    random = ~ 1 | study / esid,
    data = mental_ma_dat,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

che_peese_mental <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mod_mental,
    W = W_mental,
    mods = ~ Wgt_pop + prereg_c,
    random = ~ 1 | study / esid,
    data = mental_ma_dat,
    sparse = TRUE
  ) |> 
  robust(cluster = study, clubSandwich = TRUE)

pet_peese_mental <- 
  if (che_pet_mental$pval[1] < 0.1 & as.numeric(che_pet_mental$b[1]) > 0) che_peese_mental else che_pet_mental

pet_peese_tab_res_mental <- 
  .pubbias_overall_tab(
    rma_obj = pet_peese_mental, 
    test = "PET/PEESE",
    studies = n_distinct(mental_ma_dat$study),
    effects = nrow(mental_ma_dat)
    )

## PET/PEESE preregistration
che_pet_prereg_raw_mental <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mod_mental,
    W = W_mental,
    mods = ~ prereg_chr + Wse_pop - 1,
    random = ~ 1 | study / esid,
    data = mental_ma_dat,
    sparse = TRUE
  ) 

che_pet_prereg_mental <- 
  che_pet_prereg_raw_mental |> 
  robust(cluster = study, clubSandwich = TRUE)



#tic()
#plan(multisession, workers = 7L)
#che_pet_prereg_cwb_mental <- 
#  wildmeta::Wald_test_cwb(
#    full_model = che_pet_prereg_raw_mental,
#    constraints = constrain_equal(1:2),
#    R  = 1999
#  )
#plan(sequential)
#toc()
#
#saveRDS(che_pet_prereg_cwb_mental, "Bootstrap results/che_pet_prereg_cwb_mental.rds")
che_pet_prereg_cwb_mental <- readRDS("Bootstrap results/che_pet_prereg_cwb_mental.rds")

che_pet_prereg_tab_mental <- 
  tibble(
    coefficient = c(
      "Not preregistered", "Preregistered",
      "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(as.numeric(che_pet_prereg_mental$b[1:2]), 3), 
        " [", 
        round(che_pet_prereg_mental$ci.lb[1:2], 3),
        ", ",
        round(che_pet_prereg_mental$ci.ub[1:2], 3),
        "]"
      ),
      as.character(round(che_pet_prereg_cwb_mental$p_val,3)),
      as.character(round(sqrt(che_pet_prereg_mental$sigma2[1]), 3)),
      as.character(round(sqrt(che_pet_prereg_mental$sigma2[2]), 3)),
      as.character(round(sqrt(sum(che_pet_prereg_mental$sigma2)), 3)),
      as.character(n_distinct(mental_ma_dat$study)),
      as.character(nrow(mental_ma_dat))
    ),
    
    method = "petpesse"
    
  )


## PET/PEESE outcome
che_pet_outcome_raw_mental <- 
  rma.mv(
    yi = gt_pop,
    V = V_mat_mod_mental,
    W = W_mental,
    mods = ~ outcome_type + Wse_pop + prereg_c - 1,
    random = ~ 1 | study / esid,
    data = mental_ma_dat,
    sparse = TRUE
  ) 

che_pet_outcome_mental <- 
  che_pet_outcome_raw_mental |> 
  robust(cluster = study, clubSandwich = TRUE)



#tic()
#plan(multisession, workers = 13L)
#che_pet_outcome_cwb_mental <- 
#  wildmeta::Wald_test_cwb(
#    full_model = che_pet_outcome_raw_mental,
#    constraints = constrain_equal(1:4),
#    R  = 1999
#  )
#plan(sequential)
#toc()
#
#saveRDS(che_pet_outcome_cwb_mental, "Bootstrap results/che_pet_outcome_cwb_mental.rds")
che_pet_outcome_cwb_mental <- readRDS("Bootstrap results/che_pet_outcome_cwb_mental.rds")

che_pet_outcome_tab_mental <- 
  tibble(
    coefficient = c(
      hyema_outcome_mental$Parameter[-5], "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(as.numeric(che_pet_outcome_mental$b[-c(5:6)]), 3), 
        " [", 
        round(che_pet_outcome_mental$ci.lb[-c(5:6)], 3),
        ", ",
        round(che_pet_outcome_mental$ci.ub[-c(5:6)], 3),
        "]"
      ),
      as.character(round(che_pet_outcome_cwb_mental$p_val, 3)),
      as.character(round(sqrt(che_pet_outcome_mental$sigma2[1]), 3)),
      as.character(round(sqrt(che_pet_outcome_mental$sigma2[2]), 3)),
      as.character(round(sqrt(sum(che_pet_outcome_mental$sigma2)), 3)),
      as.character(n_distinct(mental_ma_dat$study)),
      as.character(nrow(mental_ma_dat))
    ),
    
    method = "petpesse"
    
  )

```

### Selection models

```{r, selmodel-mental}

set.seed(29092025)

library(future)

cores <- parallel::detectCores() - 1

# Overall reintegration
#plan(multisession, workers = cores)
#
#mod_3PSM_overall_mental <- 
#  metaselection::selection_model(
#    data = mental_ma_dat, 
#    yi = gt_pop,
#    sei = Wse_pop,
#    cluster = study,
#    selection_type = "step",
#    steps = 0.025,
#    estimator = "CML",
#    vcov_type = "robust",
#    CI_type = "percentile",
#    bootstrap = "two-stage",
#    R = 1999
#  )
#plan(sequential)
#
#saveRDS(mod_3PSM_overall_mental, "Bootstrap results/mod_3PSM_overall_mental.rds")
mod_3PSM_overall_mental <- readRDS("Bootstrap results/mod_3PSM_overall_mental.rds")

#selection_plot(mod_3PSM_overall)
#
#plan(multisession, workers = cores)
#
#mod_4PSM_overall_mental <- 
#  metaselection::selection_model(
#    data = mental_ma_dat, 
#    yi = gt_pop,
#    sei = Wse_pop,
#    cluster = study,
#    selection_type = "step",
#    steps = c(0.025, 0.500),
#    estimator = "CML",
#    vcov_type = "robust",
#    CI_type = "percentile",
#    bootstrap = "two-stage",
#    R = 1999
#  )
#plan(sequential)
#
#saveRDS(mod_4PSM_overall_mental, "Bootstrap results/mod_4PSM_overall_mental.rds")
mod_4PSM_overall_mental <- readRDS("Bootstrap results/mod_4PSM_overall_mental.rds")


#save(
#  mod_3PSM_overall,
#  mod_4PSM_overall,
#  file = "selmodel_res.RData"
#)

##############################
# Across type of registration
##############################

## Only not preregistered outcome
#plan(multisession, workers = cores)
#
#
#mod_3PSM_not_prereg_mental <- 
#  metaselection::selection_model(
#    data = mental_ma_dat, 
#    yi = gt_pop,
#    sei = Wse_pop,
#    cluster = study,
#    selection_type = "step",
#    steps = 0.025,
#    estimator = "CML",
#    vcov_type = "robust",
#    CI_type = "percentile",
#    bootstrap = "two-stage",
#    R = 1999,
#    subset = conventional == 0
#  )
#plan(sequential)

## Prereg_chr as subgroup factor
  
#plan(multisession, workers = cores)
#
#mod_3PSM_prereg_mental <- 
#  metaselection::selection_model(
#    data = mental_ma_dat, 
#    yi = gt_pop,
#    sei = Wse_pop,
#    cluster = study,
#    selection_type = "step",
#    steps = 0.025,
#    estimator = "CML",
#    vcov_type = "robust",
#    CI_type = "percentile",
#    bootstrap = "two-stage",
#    mean_mods = ~ prereg_chr - 1,
#    R = 1999
#  )
#plan(sequential)
#
#saveRDS(mod_3PSM_prereg_mental, "Bootstrap results/mod_3PSM_prereg_mental.rds")
mod_3PSM_prereg_mental <- readRDS("Bootstrap results/mod_3PSM_prereg_mental.rds")
  
  
#plan(multisession, workers = cores)
#
#mod_4PSM_prereg_mental <- 
#  metaselection::selection_model(
#    data = mental_ma_dat, 
#    yi = gt_pop,
#    sei = Wse_pop,
#    cluster = study,
#    selection_type = "step",
#    steps = c(0.025, 0.500),
#    estimator = "CML",
#    vcov_type = "robust",
#    CI_type = "percentile",
#    bootstrap = "two-stage",
#    mean_mods = ~ prereg_chr - 1,
#    R = 1999
#  )
#plan(sequential)
#
#saveRDS(mod_4PSM_prereg_mental, "Bootstrap results/mod_4PSM_prereg_mental.rds")
mod_4PSM_prereg_mental <- readRDS("Bootstrap results/mod_4PSM_prereg_mental.rds")

###################
# Across outcomes
###################

#plan(multisession, workers = cores)
#
#mod_3PSM_outcome_mental <- 
#  metaselection::selection_model(
#    data = mental_ma_dat, 
#    yi = gt_pop,
#    sei = Wse_pop,
#    cluster = study,
#    selection_type = "step",
#    steps = 0.025,
#    estimator = "CML",
#    vcov_type = "robust",
#    CI_type = "percentile",
#    bootstrap = "two-stage",
#    mean_mods = ~ outcome_type + prereg_c - 1,
#    R = 1999
#  )
#plan(sequential)
#
#saveRDS(mod_3PSM_outcome_mental, "Bootstrap results/mod_3PSM_outcome_mental.rds")
mod_3PSM_outcome_mental <- readRDS("Bootstrap results/mod_3PSM_outcome_mental.rds")

#selection_plot(mod_3PSM_overall)

#plan(multisession, workers = cores)
#
#mod_4PSM_outcome_mental <- 
#  metaselection::selection_model(
#    data = mental_ma_dat, 
#    yi = gt_pop,
#    sei = Wse_pop,
#    cluster = study,
#    selection_type = "step",
#    steps = c(0.025, 0.500),
#    estimator = "CML",
#    vcov_type = "robust",
#    CI_type = "percentile",
#    bootstrap = "two-stage",
#    mean_mods = ~ outcome_type + prereg_c - 1,
#    R = 1999
#  )
#plan(sequential)
#
#saveRDS(mod_4PSM_outcome_mental, "Bootstrap results/mod_4PSM_outcome_mental.rds")
mod_4PSM_outcome_mental <- readRDS("Bootstrap results/mod_4PSM_outcome_mental.rds")

```


```{r tab-metaselection-mental}

PSM3_tab_res_mental <- 
  tibble(
    test = "Cluster selmodel (3PSM)",
    J = n_distinct(mental_ma_dat$study),
    K = nrow(mental_ma_dat),
    est_ci = paste0(
      round(as.numeric(mod_3PSM_overall_mental$est$Est[1]), 3), 
      " [", 
      round(mod_3PSM_overall_mental$est$percentile_lower[1], 3),
      ", ",
      round(mod_3PSM_overall_mental$est$percentile_upper[1], 3),
      "]"
    ),
    pval = NA_real_,
    tau = sqrt(mod_3PSM_overall_mental$predictions$tausq),
    omega = NA_real_,
    total_SD = tau
  )

PSM4_tab_res_mental <- 
  tibble(
    test = "Cluster selmodel (4PSM)",
    J = n_distinct(mental_ma_dat$study),
    K = nrow(mental_ma_dat),
    est_ci = paste0(
      round(as.numeric(mod_4PSM_overall_mental$est$Est[1]), 3), 
      " [", 
      round(mod_4PSM_overall_mental$est$percentile_lower[1], 3),
      ", ",
      round(mod_4PSM_overall_mental$est$percentile_upper[1], 3),
      "]"
    ),
    pval = NA_real_,
    tau = sqrt(mod_4PSM_overall_mental$predictions$tausq),
    omega = NA_real_,
    total_SD = tau
  )

# Prereg
PSM3_prereg_tab_mental <- 
  tibble(
    coefficient = c(
      "Not preregistered", "Preregistered", 
      "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(mod_3PSM_prereg_mental$est$Est[1:2], 3), 
        " [", 
        round(mod_3PSM_prereg_mental$est$percentile_lower[1:2], 3),
        ", ",
        round(mod_3PSM_prereg_mental$est$percentile_upper[1:2], 3),
        "]"
      ),
      NA_character_,
      as.character(round(sqrt(mod_3PSM_prereg_mental$predictions$tausq), 3)),
      NA_character_,
      as.character(round(sqrt(mod_3PSM_prereg_mental$predictions$tausq), 3)),
      as.character(n_distinct(mental_ma_dat$study)),
      as.character(nrow(mental_ma_dat))
    ),
    
    method = "PSM3"
    
  )

PSM4_prereg_tab_mental <- 
  tibble(
    coefficient = c(
      "Not preregistered", "Preregistered", 
      "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(mod_4PSM_prereg_mental$est$Est[1:2], 3), 
        " [", 
        round(mod_4PSM_prereg_mental$est$percentile_lower[1:2], 3),
        ", ",
        round(mod_4PSM_prereg_mental$est$percentile_upper[1:2], 3),
        "]"
      ),
      NA_character_,
      as.character(round(sqrt(mod_4PSM_prereg_mental$predictions$tausq), 3)),
      NA_character_,
      as.character(round(sqrt(mod_4PSM_prereg_mental$predictions$tausq), 3)),
      as.character(n_distinct(mental_ma_dat$study)),
      as.character(nrow(mental_ma_dat))
    ),
    
    method = "PSM4"
    
  )


# Outcome
PSM3_outcome_tab_mental <- 
  tibble(
    coefficient = c(
      hyema_outcome_mental$Parameter[-5], "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(mod_3PSM_outcome_mental$est$Est[1:4], 3), 
        " [", 
        round(mod_3PSM_outcome_mental$est$percentile_lower[1:4], 3),
        ", ",
        round(mod_3PSM_outcome_mental$est$percentile_upper[1:4], 3),
        "]"
      ),
      NA_character_,
      as.character(round(sqrt(mod_3PSM_outcome_mental$predictions$tausq), 3)),
      NA_character_,
      as.character(round(sqrt(mod_3PSM_outcome_mental$predictions$tausq), 3)),
      as.character(n_distinct(mental_ma_dat$study)),
      as.character(nrow(mental_ma_dat))
    ),
    
    method = "PSM3"
    
  )

PSM4_outcome_tab_mental <- 
  tibble(
    coefficient = c(
      hyema_outcome_mental$Parameter[-5], "Wald test p value", "tau", "omega", "Total SD", "Studies", "Effects"
      ),
    est_ci = c(
      paste0(
        round(mod_4PSM_outcome_mental$est$Est[1:4], 3), 
        " [", 
        round(mod_4PSM_outcome_mental$est$percentile_lower[1:4], 3),
        ", ",
        round(mod_4PSM_outcome_mental$est$percentile_upper[1:4], 3),
        "]"
      ),
      NA_character_,
      as.character(round(sqrt(mod_4PSM_outcome_mental$predictions$tausq), 3)),
      NA_character_,
      as.character(round(sqrt(mod_4PSM_outcome_mental$predictions$tausq), 3)),
      as.character(n_distinct(mental_ma_dat$study)),
      as.character(nrow(mental_ma_dat))
    ),
    
    method = "PSM4"
    
  )

```


#Publication and small study bias tests for overall average effects

## Reintegration
```{r pub-bias-tab-overall-eff-reint}
#| label: tab-pub-bias-tab-overall-eff-reint
#| fig-cap: "Overall average effect size estimates corrected for publication bias"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false

overall_pub_bias_tab <- 
  list(
    hyema_tab_res,
    puniform_tab_res,
    wc_tab_res,
    iscw_tab_res,
    pet_peese_tab_res,
    PSM3_tab_res,
    PSM4_tab_res
  ) |> 
  list_rbind() |> 
  mutate(
    across(pval:total_SD, ~ round(.x, 3))
  )

gt_tab_overall <- 
  overall_pub_bias_tab |> 
  gt() |> 
  sub_missing(
    columns = everything(),   
    missing_text = ""         
  )

gt_tab_overall

#gt_tab_overall |> gtsave("Tables/overall publication bias table.docx")
```


## Mental health
```{r pub-bias-tab-overall-eff-mental}
#| label: tab-pub-bias-tab-overall-eff-mental
#| fig-cap: "Overall average mental health effect size estimates corrected for publication bias"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false

overall_pub_bias_tab_mental <- 
  list(
    hyema_tab_res_mental,
    puniform_tab_res_mental,
    wc_tab_res_mental,
    iscw_tab_res_mental,
    pet_peese_tab_res_mental,
    PSM3_tab_res_mental,
    PSM4_tab_res_mental
  ) |> 
  list_rbind() |> 
  mutate(
    across(pval:total_SD, ~ round(.x, 3))
  )

gt_tab_overall_mental <- 
  overall_pub_bias_tab_mental |> 
  gt() |> 
  sub_missing(
    columns = everything(),   
    missing_text = ""         
  )

gt_tab_overall_mental

#gt_tab_overall_mental |> gtsave("Tables/overall publication bias table mental.docx")
```

 
# Publication and small study bias tests across type of registration

## Reintegration
```{r pub-bias-tab-prereg-reint}
#| label: tab-pub-bias-tab-prereg-reint
#| fig-cap: "Preregistration subgroup estimates corrected for publication bias"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false

prereg_tab_pub_bias <- 
  list(
  wc_prereg_tab,
  che_iscw_prereg_tab,
  che_pet_prereg_tab,
  PSM3_prereg_tab,
  PSM4_prereg_tab
) |> 
list_rbind() |> 
pivot_wider(names_from = method, values_from = est_ci)

prereg_tab_pub_bias_gt <- 
  prereg_tab_pub_bias  |> 
  gt() |> 
  sub_missing(
    columns = everything(),   
    missing_text = ""         
  )

prereg_tab_pub_bias_gt
#prereg_tab_pub_bias_gt |> gtsave(file = "Tables/Publication bias table across preregistration status.docx")
```

## Mental health
```{r pub-bias-tab-prereg-mental}
#| label: tab-pub-bias-tab-prereg-mental
#| fig-cap: "Preregistration subgroup estimates corrected for publication bias (mental health outcomes)"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false

prereg_tab_pub_bias_mental <- 
  list(
  wc_prereg_tab_mental,
  che_iscw_prereg_tab_mental,
  che_pet_prereg_tab_mental,
  PSM3_prereg_tab_mental,
  PSM4_prereg_tab_mental
) |> 
list_rbind() |> 
pivot_wider(names_from = method, values_from = est_ci)

prereg_tab_pub_bias_gt_mental <- 
  prereg_tab_pub_bias_mental  |> 
  gt() |> 
  sub_missing(
    columns = everything(),   
    missing_text = ""         
  )

prereg_tab_pub_bias_gt_mental
prereg_tab_pub_bias_gt_mental |> 
gtsave(file = "Tables/Publication bias table across preregistration status mental.docx")
```

# Publication and small study bias tests across types of outcomes

## Reintegration
```{r pub-bias-tab-outcome-reint}
#| label: tab-pub-bias-tab-outcome-reint
#| fig-cap: "Outcome subgroup estimates corrected for publication bias"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false

outcome_tab_pub_bias <- 
  list(
  hyema_outcome_tab,
  wc_outcome_tab,
  che_iscw_outcome_tab,
  che_pet_outcome_tab,
  PSM3_outcome_tab,
  PSM4_outcome_tab
) |> 
list_rbind() |> 
pivot_wider(names_from = method, values_from = est_ci)

outcome_tab_pub_bias_gt <- 
  outcome_tab_pub_bias |> 
  gt() |> 
  sub_missing(
    columns = everything(),   
    missing_text = ""         
  )
  
outcome_tab_pub_bias_gt
outcome_tab_pub_bias_gt |> gtsave(file = "Tables/Publication bias table across outcomes.docx")

```

## Mental health
```{r pub-bias-tab-outcome-mental}
#| label: tab-pub-bias-tab-outcome-mental
#| fig-cap: "Mental health outcome subgroup estimates corrected for publication bias"
#| fig.width: 9
#| fig.height: 6
#| fig.retina: 2
#| message: false

outcome_tab_pub_bias_mental <- 
  list(
  hyema_outcome_tab_mental,
  wc_outcome_tab_mental,
  che_iscw_outcome_tab_mental,
  che_pet_outcome_tab_mental,
  PSM3_outcome_tab_mental,
  PSM4_outcome_tab_mental
) |> 
list_rbind() |> 
pivot_wider(names_from = method, values_from = est_ci)

outcome_tab_pub_bias_gt_mental <- 
  outcome_tab_pub_bias_mental |> 
  gt() |> 
  sub_missing(
    columns = everything(),   
    missing_text = ""         
  )
  
outcome_tab_pub_bias_gt_mental
#outcome_tab_pub_bias_gt_mental |> gtsave(file = "Tables/Publication bias table across outcomes mental.docx")

```

 
# References
Dalgaard, N. T., Flensborg Jensen, M. C., Bengtsen, E., Krassel, K. F., & Vembye, M. H. (2025) Groupbased community interventions to support the social reintegration of marginalised adults with mental illness. A Systematic Review and meta-analysus. *Campbell Systematic Reviews*, 18(3), e1254. https://doi.org/10.1002/cl2.1254

::: {.callout-note icon=false appearance="simple" title="Session Information" collapse=true}

## Session Information

```{r}
#| code-fold: false
sessioninfo::session_info()
```

:::