---
title: "Statistical Analysis for 'Group-based community interventions to support
  the social reintegration of marginalised adults with mental illness' (til Nina)"
date: "Last updated `r format(Sys.time(), '%Y.%m.%d')`"
output: 
  html_document:
    toc: true
    code_folding: hide
    code_download: true
    css: styles.css
fontsize: 11pt
spacing: single
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
#knitr::opts_chunk$set(eval = FALSE)

options(pillar.sigfig = 4) # ensure tibble include 4 digits
options(tibble.width = Inf)
options(dplyr.print_min = 310)
options(scipen = 10)
options(dplyr.summarise.inform = FALSE) # Avoids summarize info from tidyverse

```


```{r, echo=FALSE}

library(dplyr)
library(tibble)
library(ggplot2)
library(stringr)
library(robvis)
library(tidyr)
library(rempsyc)
library(flextable)
library(purrr)
library(metafor)
library(patchwork)
library(clubSandwich)
library(wildmeta)
library(gt)


# Loading in helper function used to calculate effect size and conduct the analysis
source_path <- if (isTRUE(getOption('knitr.in.progress'))) "Helpers.R" else "ES calc/Helpers.R"

source(source_path)

```


```{r, eval = TRUE, echo = FALSE}
# Loading the needed data for analysis
group_based_dat <- readRDS("Group-based interventions data.RDS") |> 
  # The post-measurement of Empowerment Scale seems flawed for the study by 
  # Barbic et al. 2009 we therefore we exclude it from the analysis
  #filter(!(authors == "Barbic et al." & test_name == "The Empowerment Scale")) |> 
  mutate(
    author_year = paste(authors, year)
  ) |> 
 # Remove unused outcomes
 filter(!str_detect(analysis_plan, "Unused"))

```

## Number effect size across standardized mean differences (SMD) and odds ratios (OR) 

```{r}
# Number of studies reporting OR
group_based_dat |> 
  summarise(
    n = n(), 
    .by = c(author_year, effect_size)
  ) |> 
  summarise(
    n_studies = length(effect_size), 
    n_es = sum(n),
    .by = effect_size
  )
```


## Filter out apparently flawed results

```{r}

group_based_dat <- 
  group_based_dat |> 
  # The post-measurement of Empowerment Scale seems flawed for the study by 
  # Barbic et al. 2009 we therefore we exclude it from the analysis
  filter(!(authors == "Barbic et al." & test_name == "The Empowerment Scale"))

```



# Timeline

```{r, eval=TRUE, fig.cap='FIGURE 1:  Number of studies included in meta-analysis by year'}
# Figure 1: Number of included studies in the meta-analysis by year
G_timepllot <- group_based_dat |> 
  summarise(year = unique(year), .by =  author_year)

# DONE
timeline_plot <-  ggplot(G_timepllot, aes(x = year)) + 
  geom_bar(colour = "black", fill = "cornflowerblue", alpha = 1, width = 1) +
  scale_x_continuous(breaks = seq(2000, 2022, 1)) + 
  scale_y_continuous(breaks = seq(0, 6.5, 1), limits = c(0, 7), expand = c(0,0)) + 
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    panel.border = element_blank(),
    legend.position = "none",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    axis.line = element_line(colour = "black")
  ) +
  labs(
    x = "Year of Publication",
    y = "Number of Studies"
  )

timeline_plot

```


```{r, echo = FALSE}
GBD_effect <- 
  group_based_dat |> 
  filter(variable_type != "Binary") |>
  mutate(
    es_id = 1:n(),
    esid = es_id,
    
    # Main covariate adjusted effect cluster adjusted 
    gt = if_else(!is.na(gt_post), gt_post, NA_real_),
    gt = if_else(!is.na(gt_DD), gt_DD, gt),
    gt = if_else(!is.na(gt_adj), gt_adj, gt),
    gt = if_else(!is.na(gt_reg), gt_reg, gt),
    
    vgt = if_else(!is.na(vgt_post), vgt_post, NA_real_),
    vgt = if_else(!is.na(vgt_DD), vgt_DD, vgt),
    vgt = if_else(!is.na(vgt_adj), vgt_adj, vgt),
    vgt = if_else(!is.na(vgt_reg), vgt_reg, vgt),
    
    Wgt = if_else(!is.na(Wgt_post), Wgt_post, NA_real_),
    Wgt = if_else(!is.na(Wgt_DD), Wgt_DD, Wgt),
    Wgt = if_else(!is.na(Wgt_adj), Wgt_adj, Wgt),
    Wgt = if_else(!is.na(Wgt_reg), Wgt_reg, Wgt),
    
    # Hedges g posttest only, adjusted for clustering
    # Imputing covariate-adjusted estimate when posttest calculation was not possible
    gt_post = if_else(is.na(gt_post) & !is.na(gt_reg), gt_reg, gt_post),
    gt_post = if_else(is.na(gt_post) & !is.na(gt_adj), gt_adj, gt_post),
    gt_post = if_else(is.na(gt_post) & !is.na(gt_DD), gt_DD, gt_post),
    
    vgt_post = if_else(is.na(vgt_post) & !is.na(vgt_reg), vgt_reg, vgt_post),
    vgt_post = if_else(is.na(vgt_post) & !is.na(vgt_adj), vgt_adj, vgt_post),
    vgt_post = if_else(is.na(vgt_post) & !is.na(vgt_DD), vgt_DD, vgt_post),
    
    Wgt_post = if_else(is.na(Wgt_post) & !is.na(Wgt_reg), Wgt_reg, Wgt_post),
    Wgt_post = if_else(is.na(Wgt_post) & !is.na(Wgt_adj), Wgt_adj, Wgt_post),
    Wgt_post = if_else(is.na(Wgt_post) & !is.na(Wgt_DD), Wgt_DD, Wgt_post),
    
    # Hedges' g posttest only, not-adjusted for clustering
    # Imputing covariate-adjusted estimate when posttest calculation was not possible
    g_post = if_else(is.na(g_post) & !is.na(g_reg), g_reg, g_post),
    g_post = if_else(is.na(g_post) & !is.na(g_adj), g_adj, g_post),
    g_post = if_else(is.na(g_post) & !is.na(g_DD), g_DD, g_post),
    
    vg_post = if_else(is.na(vg_post) & !is.na(vg_reg), vg_reg, vg_post),
    vg_post = if_else(is.na(vg_post) & !is.na(vg_adj), vg_adj, vg_post),
    vg_post = if_else(is.na(vg_post) & !is.na(vg_DD), vg_DD, vg_post),
    
    Wg_post = if_else(is.na(Wg_post) & !is.na(Wg_reg), Wg_reg, Wg_post),
    Wg_post = if_else(is.na(Wg_post) & !is.na(Wg_adj), Wg_adj, Wg_post),
    Wg_post = if_else(is.na(Wg_post) & !is.na(Wg_DD), Wg_DD, Wg_post),
    
    # Cohen's d posttest only, not-adjusted for clustering
    # Imputing covariate-adjusted estimate when posttest calculation was not possible
    d_post = if_else(is.na(d_post) & !is.na(d_reg), d_reg, d_post),
    d_post = if_else(is.na(d_post) & !is.na(d_adj), d_adj, d_post),
    d_post = if_else(is.na(d_post) & !is.na(d_DD), d_DD, d_post),
    
    vd_post = if_else(is.na(vd_post) & !is.na(vd_reg), vd_reg, vd_post),
    vd_post = if_else(is.na(vd_post) & !is.na(vd_adj), vd_adj, vd_post),
    vd_post = if_else(is.na(vd_post) & !is.na(vd_DD), vd_DD, vd_post),
    
    Wd_post = if_else(is.na(Wd_post) & !is.na(Wd_reg), Wd_reg, Wd_post),
    Wd_post = if_else(is.na(Wd_post) & !is.na(Wd_adj), Wd_adj, Wd_post),
    Wd_post = if_else(is.na(Wd_post) & !is.na(Wd_DD), Wd_DD, Wd_post),
    
    
    # Covariate adjusted Hedges' g, not cluster adjusted 
    g = if_else(!is.na(g_post), g_post, NA_real_),
    g = if_else(!is.na(g_DD), g_DD, g),
    g = if_else(!is.na(g_adj), g_adj, g),
    g = if_else(!is.na(g_reg), g_reg, g),
    
    vg = if_else(!is.na(vg_post), vg_post, NA_real_),
    vg = if_else(!is.na(vg_DD), vg_DD, vg),
    vg = if_else(!is.na(vg_adj), vg_adj, vg),
    vg = if_else(!is.na(vg_reg), vg_reg, vg),
    
    Wg = if_else(!is.na(Wg_post), Wg_post, NA_real_),
    Wg = if_else(!is.na(Wg_DD), Wg_DD, Wg),
    Wg = if_else(!is.na(Wg_adj), Wg_adj, Wg),
    Wg = if_else(!is.na(Wg_reg), Wg_reg, Wg),
    
    # Covariate-adjusted version of Cohen's d, neither cluster nor small sample adjusted
    d = if_else(!is.na(d_post), d_post, NA_real_),
    d = if_else(!is.na(d_DD), d_DD, d),
    d = if_else(!is.na(d_adj), d_adj, d),
    d = if_else(!is.na(d_reg), d_reg, d),
    
    vd = if_else(!is.na(vd_post), vd_post, NA_real_),
    vd = if_else(!is.na(vd_DD), vd_DD, vd),
    vd = if_else(!is.na(vd_adj), vd_adj, vd),
    vd = if_else(!is.na(vd_reg), vd_reg, vd),
    
    Wd = if_else(!is.na(Wd_post), Wd_post, NA_real_),
    Wd = if_else(!is.na(Wd_DD), Wd_DD, Wd),
    Wd = if_else(!is.na(Wd_adj), Wd_adj, Wd),
    Wd = if_else(!is.na(Wd_reg), Wd_reg, Wd),
    
    inv_sample_size = (1/N_t + 1/N_c),
    
    # ESS = round(4/vgt), # Using cluster bias corrected sampling variance
    
    studyid = if_else(authors == "Gonzalez & Prihoda", 500, studyid), 
    
    cnt = if_else(cnt == "USA", "US", cnt),
    
    design = if_else(design  == "QES-pretest", "QES", design),
    
    # MHV: Jeg synes ikke det er en god ide at ændre CRCT til RCT. Jeg vil gerne kunne se forskel.  
    # design = ifelse(design  == "CRCT", "RCT", design), 
    
    assessment = if_else(assessment == "Self  assesment", "Self assesment", assessment),
    
    randomization = if_else(randomization == "Simple Block Randomization", "Block randomized",
                           randomization),
    randomization = if_else(randomization == "Simple with permuted blocks, stratified by site",
                           "Stratified randomization", randomization),
   
    randomization = if_else(randomization == "Stratified?",
                           "Stratified randomization", randomization),
   
    randomization = if_else(is.na(randomization) & studyid == 102, 
                            "Stratified randomization", randomization),
   
    randomization = if_else(randomization == "Ratio and block randomized",
                           "Block randomized", randomization),
   
    randomization = if_else(randomization == "Block randomized stratified by site",
                           "Block randomized", randomization),
    
    randomization = if_else(randomization == "Resticted and adapted randomization (i.e. minimization)",
                           "Stratified randomization", randomization),
   
    randomization = if_else(randomization == "Unequal simple randomization",
                           "Block randomized", randomization),
   
    randomization = if_else(randomization == "Within-site basis and unequal allocation ratio",
                           "Stratified randomization", randomization),
    
    trt_type = if_else(trt_type == "Group-based  Cognitive Behavioral Therapy", 
                      "Group based Cognitive Behavioural Therapy", trt_type),
    trt_type = if_else(trt_type == "Group-based Cognitive Behavioral Therapy", 
                      "Group based Cognitive Behavioural Therapy", trt_type),
    trt_type = if_else(trt_type =="Group psychoeducation & Social skill training", 
                      "Group psychoeducation & Social Skill Training", trt_type),
    trt_type = if_else(trt_type =="Group psychoeducation", 
                      "Group Psychoeducation", trt_type),
    trt_type = if_else(trt_type =="Group psychoeducation & Social Skill Training", 
                      "Group Psychoeducation & Social Skill Training", trt_type),
    trt_type = if_else(trt_type =="Education and Illness Management", 
                      "Group Psychoeducation & Social Skill Training", trt_type),
    trt_type = if_else(trt_type =="Illness management", 
                      "Illness Management", trt_type),
    
    sample_factors = if_else(sample_factors =="Older with depression and anxiety", 
                            "Mixed", sample_factors), 
    sample_factors = if_else(sample_factors =="All suffered from severe mental illness", 
                            "Shared Social problem(s)/challenge(s)", sample_factors),
    sample_factors = if_else(sample_factors =="Shared origin and psychological distress", 
                            "Mixed", sample_factors),
    sample_factors = if_else(sample_factors =="persons with major psychiatric problems", 
                            "Shared Social problem(s)/challenge(s)", sample_factors),
    
    analysis_plan = if_else(analysis_plan == "Unused", "Unused outcomes", analysis_plan), 
    analysis_plan = case_match(
      analysis_plan,
      "Hope, Empowerment & Self-efficacy" ~ "Hope, empowerment & self-efficacy",
      "Wellbeing and Quality of Life" ~ "Wellbeing and quality of life",
      .default = analysis_plan
    ),
    
    test_type = if_else(test_type == "Clinical administered", "Clinician-rated measure", test_type),
    test_type = if_else(test_type == "Clinical interviews", "Clinician-rated measure", test_type),
    test_type = if_else(test_type == "Self report", "Self-reported", test_type),
    test_type = if_else(test_type == "Self report through clinical interview", "Self-reported", test_type),
    test_type = if_else(test_type == "Self-reported via diagnostic interview", "Self-reported", test_type), 
    
    measure_type = if_else(measure_type == "Pre-post with controls", "Post-intervention", measure_type),
   
    cluster_treatment = if_else(cluster_treatment == "Hierarchical mixed models", "Mixed-model", cluster_treatment),
   
    cluster_treatment = if_else(cluster_treatment == "Multilevel analysis and clustered standard errors", 
                        "Multilevel analysis", cluster_treatment),
   
    rob_tool = if_else(rob_tool == "Rob2", "RoB2", rob_tool),
    rob_tool = if_else(rob_tool == "Rob2 CRCT", "RoB2", rob_tool),
   
    timing = if_else(study == "Acarturk et al. 2022" & timing == "Followup", "3m", timing),
    timing = if_else(Author == "Barbic et al. 2009", "post", timing), 
    timing = if_else(Author == "Bond et al. 2015", "post", timing),
    timing = if_else(Author == "Craigie & Nathan 2009", "post", timing),
    timing = if_else(Author == "Gatz et al. 2007", "post", timing),
    timing = if_else(Author == "Gordon et al. 2018", "post", timing), 
    timing = if_else(Author == "Gutman et al. 2019", "post", timing),
    timing = if_else(Author == "Bond et al. 2015", "post", timing), 
    timing = if_else(Author == "Hagen et al. 2005", "post", timing),
    timing = if_else(Author == "Haslam et al. 2019", "post", timing),
    timing = if_else(Author == "Hilden et al. 2021", "post", timing),
    timing = if_else(Author == "James et al. 2004", "post", timing),
    timing = if_else(Author == "Lim et al. 2020", "post", timing),
    timing = if_else(Author == "Lloyd-Evans et al. 2020", "post", timing),
    timing = if_else(Author == "McCay et al. 2006", "post", timing),
    timing = if_else(Author == "McCay et al. 2007", "post", timing),
    timing = if_else(Author == "Michalak et al. 2015", "post", timing),
    timing = if_else(Author == "Morley et al. 2024", "post", timing),
    timing = if_else(Author == "Morton et al. 2012", "post", timing),
    timing = if_else(Author == "Popolo et al. 2019", "post", timing),
    timing = if_else(Author == "Rabenstein et al. 2015", "post", timing),
    timing = if_else(Author == "Rosenblum et al. 2014", "3", timing),
    timing = if_else(Author == "Sacks et al. 2011", "post", timing), 
    timing = if_else(Author == "Schrank et al. 2016", "post", timing),
    timing = if_else(Author == "Somers et al. 2017", "post", timing),
    timing = if_else(Author == "Valiente et al. 2022", "post", timing),
    timing = if_else(Author == "Volpe et al. 2015", "post", timing),
    timing = if_else(Author == "Wojtalik et al. 2022", "post", timing),
    timing = if_else(Author == "Wuthrich et al. 2013/2021", "post", timing),
    timing = if_else(Author == "Druss et al. 2010", "post", timing),
    timing = if_else(Author == "Gonzales & Prihoda 2007", "post", timing),
    timing = if_else(Author == "Dyck et al. 2000", "post", timing),
   
    analysis_strategy = if_else(str_detect(author_year, "Michalak"), "ITT", analysis_strategy),
   
    conventional = if_else(protocol != "Yes", 1, 0),
    prereg_text = if_else(conventional == 0, "Preregistered", "Not preregistered"),
   
   # For publication/selection/small study bias testing
    Wse = sqrt(Wgt),
    t_i = gt/sqrt(Wgt)
   
 ) |> 
  mutate(
    # Used to remove ITT outcomes from Cano-Vindel et al. 2021 and Craigie & Nathan 2009 
    n_analysis_strategies = n_distinct(analysis_strategy),
    .by = author_year
  )

#GBD_effect |> mutate(invsample = (1/N_t + 1/N_c), prop_wgt = Wgt/invsample) |> filter(prop_wgt > 1.5, Wgt >= 0.1) |> #select(author_year, Wgt, Wd, invsample, prop_wgt, contains("adj_val"))
```


```{r, echo = FALSE}
# Removing ITT analyses from Cano-Vindel et al. 2021 and Craigie & Nathan 2009 

gb_dat <- 
  GBD_effect |> 
  filter(!c(str_detect(author_year, "Cano|Craigie|Woj") & analysis_strategy == "ITT")) 
```

# Preregistered studies

```{r}

gb_dat |> 
  summarise(
    prereg_text = unique(prereg_text),
    n_es = n(),
    .by = author_year
  ) |> 
  summarise(
    N_studies = n_distinct(author_year),
    N_es = sum(n_es),
    .by = prereg_text
  )


```


# Number of studies and effect sizes {.tabset}

## Entire data

```{r}
gb_dat |> 
  summarise(
    N_studies = n_distinct(author_year),
    N_ES = n()
  )
```


## Reintegrational outcomes
```{r}

gb_dat |> 
  filter(!str_detect(analysis_plan, "mental|used|hospi")) |> 
  summarise(
    n_es = n(),
    .by = c(analysis_plan, studyid)
  ) |> 
  summarise(
    N_studies = length(studyid),
    N_es = sum(n_es),
    .by = analysis_plan
  ) |> 
  rename(
    outcome = analysis_plan
  )

```

## All mental health outcomes

```{r}

gb_dat |> 
  filter(str_detect(analysis_plan, "mental")) |> 
  filter(!str_detect(analysis_plan, "Unused")) |> 
  mutate(
    analysis_plan = case_when(
  str_detect(analysis_plan, "Symptoms of psychosis|Negative symptoms") ~ "All mental health outcomes/Symptoms of psychosis",
   TRUE ~ analysis_plan
    )
  ) |> 
  summarise(
    n_es = n(),
    .by = c(analysis_plan, studyid)
  ) |> 
  summarise(
    N_studies = length(studyid),
    N_es = sum(n_es),
    .by = analysis_plan
  ) |> 
  rename(
    outcome = analysis_plan
  ) |> 
  mutate(
    outcome = str_remove_all(outcome, "All mental health outcomes"),
    outcome = if_else(outcome == "", "General mental health", outcome),
    outcome = str_remove(outcome, "/")
  )

```

## Number of individual in the total data

```{r}
gb_dat |> 
  summarise(
    N = max(N_total),
    .by = author_year
  ) |> 
  pull(N) |> 
  sum()
```


## Average group size across group treatment

```{r}
gb_dat |> 
  filter(str_detect(avg_cl_type, "study")) |> 
  select(avg_cl_size) |> 
  pull(avg_cl_size) |> 
  mean()
```


# Overall means and contrast test using SCE+ models {.tabset}

## Reintegrational outcomes
```{r}
# We remove physical health, employment, self-esteem, and loneliness outcome since
# only few studies reported these outcomes. 
reintergation_dat <- 
  gb_dat |> 
  filter(!str_detect(analysis_plan, "mental|used|hospi|esteem|Physical|Employ|Loneli"))

saveRDS(reintergation_dat, "reintergation_dat.rds")

# overall_mean
reintegration_che_res <- .CHE_RVE(reintergation_dat) 

reintegration_che_res |> 
select(studies:UL, tau:sd_total, I2) |>
gt() |> 
fmt_number(columns = 3:9, decimals = 3) |> 
tab_header(
  title = "Overall average effect size",
  subtitle = "Across all reintegrational outcomes"
) 
  

# Overall means across outcomes
reintegration_sce_res <- 
  .SCEp(mod = analysis_plan, data = reintergation_dat) 

reintegration_sce_res |> 
select(Moderator:pval) |> 
gt()|> 
fmt_number(columns = 4:10, decimals = 3) |> 
tab_header(
  title = "Overall average effect sizes",
  subtitle = "Across reintegrational subgroups"
) 
```

## All mental health outcomes
```{r}
# We remove physical health, employment, self-esteem, and loneliness outcome since
# only few studies reported these outcomes. 
mental_health_dat <- 
  gb_dat |> 
  filter(str_detect(analysis_plan, "mental")) |> 
  filter(!str_detect(analysis_plan, "Unused")) |> 
  mutate(
    analysis_plan = case_match(
      analysis_plan,
      "All mental health outcomes" ~ "General mental health",
      "All mental health outcomes/Anxiety" ~ "Anxiety",
      "All mental health outcomes/Depression" ~ "Depression",
      .default = "Symptoms of psychosis"
    )
  )

#saveRDS(mental_health_dat, "mental_health_dat.rds")

# overall_mean
mental_che_res <- .CHE_RVE(mental_health_dat) 
  
mental_che_res |> 
select(studies:UL, tau:sd_total, I2) |> 
gt() |>
fmt_number(columns = 3:9, decimals = 3) |> 
tab_header(
  title = "Overall average effect size",
  subtitle = "Across all mental health outcomes"
) 
  

# Overall means across outcomes
mental_sce_res <- 
  .SCEp(mod = analysis_plan, data = mental_health_dat)

mental_sce_res |> 
select(Moderator:pval) |> 
gt()|> 
fmt_number(columns = 4:10, decimals = 3) |> 
tab_header(
  title = "Overall average effect sizes",
  subtitle = "Across mental health subgroups"
) 

```

## Difference-in-differences effect sizes

```{r}
gb_dat |> 
  filter(str_detect(main_es_method, "diff-in-diffs")) |> 
  summarise(n = n(), .by = author_year) |> 
  summarise(n_studies = length(author_year), n_es = sum(n))
```



# Forest plots {.tabset}

## Reintegrational outcomes {.tabset}
```{r, echo = FALSE}
outcome_group <- unique(reintergation_dat$analysis_plan)
```

### Overall

```{r, fig.height=10, fig.width=9}
forest_plot_de(data = reintergation_dat, che_data = reintegration_che_res)
```


### Wellbeing and quality of life
```{r, fig.height=10, fig.width=9}

forest_plot_de(outcome_group = outcome_group[1], data = reintergation_dat, sce_data = reintegration_sce_res)

```

### Hope, Empowerment & Self-efficacy

```{r, fig.height=10, fig.width=9}
forest_plot_de(outcome_group = outcome_group[2], data = reintergation_dat, sce_data = reintegration_sce_res)
```

### Social functioning (degree of impairment)

```{r, fig.height=10, fig.width=9}
forest_plot_de(outcome_group = outcome_group[3], data = reintergation_dat, sce_data = reintegration_sce_res)
```

### Alcohol and drug abuse/misuse

```{r, fig.height=6, fig.width=9}
forest_plot_de(outcome_group = outcome_group[4], data = reintergation_dat, sce_data = reintegration_sce_res)
```

## All mental health outcomes {.tabset}

```{r, echo = FALSE}
outcome_group_mental <- unique(mental_health_dat$analysis_plan)
```

### Overall

```{r, fig.height=10, fig.width=9}
forest_plot_de(data = mental_health_dat, che_data = mental_che_res)
```

### General mental health

```{r, fig.height=10, fig.width=9}
forest_plot_de(
  outcome_group = outcome_group_mental[1], 
  data = mental_health_dat, 
  sce_data = mental_sce_res
)
```

### Anxiety

```{r, fig.height=6, fig.width=9}
forest_plot_de(
  outcome_group = outcome_group_mental[2], 
  data = mental_health_dat, 
  sce_data = mental_sce_res
)
```

### Depression

```{r, fig.height=10, fig.width=9}
forest_plot_de(
  outcome_group = outcome_group_mental[3], 
  data = mental_health_dat, 
  sce_data = mental_sce_res
)
```

### Symptoms of psychosis

```{r, fig.height=6, fig.width=9}
forest_plot_de(
  outcome_group = outcome_group_mental[4], 
  data = mental_health_dat, 
  sce_data = mental_sce_res
)
```