---
title: "Statistical Analysis for 'Group-based community interventions to support
  the social reintegration of marginalised adults with mental illness'"
date: "Last updated `r format(Sys.time(), '%Y.%m.%d')`"
output: 
  html_document:
    toc: true
    code_folding: show
    code_download: true
fontsize: 11pt
spacing: single
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(eval = FALSE)

options(pillar.sigfig = 4) # ensure tibble include 4 digits
options(tibble.width = Inf)
options(dplyr.print_min = 310)
options(scipen = 10)
options(dplyr.summarise.inform = FALSE) # Avoids summarize info from tidyverse

```

# R package

```{r}

library(dplyr)
library(tibble)
library(ggplot2)
library(stringr)
library(robvis)
library(tidyr)

```

# Load data

```{r, eval = TRUE}
# Loading the needed data for analysis
group_based_dat <- readRDS("ES calc/Group-based interventions data.RDS") |> 
  # The post-measurement of Empowerment Scale seems flawed for the study by 
  # Barbic et al. 2009 we therefore we exclude it from the analysis
  filter(!(authors == "Barbic et al." & test_name == "The Empowerment Scale")) |> 
  mutate(
    author_year = paste(authors, year)
  )

```

# Descriptive plots

## Timeline

```{r, echo=FALSE, eval=TRUE, fig.cap='FIGURE 1:  Number of studies included in the meta-analysis by year'}
# Figure 1: Number of included studies in the meta-analysis by year
G_timepllot <- group_based_dat |> 
  summarise(year = unique(year), .by =  author_year)

# DONE
timeline_plot <-  ggplot(G_timepllot,aes(x = year)) + 
  geom_bar(colour = "black", fill = "cornflowerblue", alpha = 1, width = 1) +
  scale_x_continuous(breaks = seq(2000, 2022, 1)) + 
  scale_y_continuous(breaks = seq(0, 6.5, 1), limits = c(0, 7), expand = c(0,0)) + 
  theme_bw() + 
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    panel.border = element_blank(),
    legend.position = "none",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    axis.line = element_line(colour = "black")
  ) +
  labs(
    x = "Year of Publication",
    y = "Number of Studies"
  )

timeline_plot

```

## Primary study sample size and effective sample sizes (SUPPLEMENTARY MATERIAL)

### Making a effetive sample size (ESS)

```{r}
GBD_effect <- 
  group_based_dat |> 
  filter(variable_type != "Binary") |>
  mutate(
    es_id = 1:n(),
    gt = if_else(!is.na(gt_post), gt_post, NA_real_),
    gt = if_else(!is.na(gt_DD), gt_DD, gt),
    gt = if_else(!is.na(gt_adj), gt_adj, gt),
    gt = if_else(!is.na(gt_reg), gt_reg, gt),
    
    vgt = if_else(!is.na(vgt_post), vgt_post, NA_real_),
    vgt = if_else(!is.na(vgt_DD), vgt_DD, vgt),
    vgt = if_else(!is.na(vgt_adj), vgt_adj, vgt),
    vgt = if_else(!is.na(vgt_reg), vgt_reg, vgt),
    
    Wgt = if_else(!is.na(Wgt_post), Wgt_post, NA_real_),
    Wgt = if_else(!is.na(Wgt_DD), Wgt_DD, Wgt),
    Wgt = if_else(!is.na(Wgt_adj), Wgt_adj, Wgt),
    Wgt = if_else(!is.na(Wgt_reg), Wgt_reg, Wgt),
    
   # ESS = round(4/vgt), # Using cluster bias corrected sampling variance
    
    studyid = if_else(authors == "Gonzalez & Prihoda", 500, studyid), 
    
    cnt = if_else(cnt == "USA", "US", cnt),
    
    design = if_else(design  == "QES-pretest", "QES", design),
    
    # MHV: Jeg synes ikke det er en god ide at ændre CRCT til RCT. Jeg vil gerne kunne se forskel.  
    # design = ifelse(design  == "CRCT", "RCT", design), 
    
    assessment = if_else(assessment == "Self  assesment", "Self assesment", assessment),
    
    randomization = if_else(randomization == "Simple Block Randomization", "Block randomized",
                           randomization),
    randomization = if_else(randomization == "Simple with permuted blocks, stratified by site",
                           "Stratified randomization", randomization),
   
    randomization = if_else(is.na(randomization) & studyid == 102, 
                            "Stratified randomization", randomization),
   
    randomization = if_else(randomization == "Ratio and block randomized",
                           "Block randomized", randomization),
   
   randomization = if_else(randomization == "Block randomized stratified by site",
                           "Block randomized", randomization),
    
   randomization = if_else(randomization == "Resticted and adapted randomization (i.e. minimization)",
                           "Stratified randomization", randomization),
   
   randomization = if_else(randomization == "Unequal simple randomization",
                           "Block randomized", randomization),
   
   randomization = if_else(randomization == "Within-site basis and unequal allocation ratio",
                           "Stratified randomization", randomization),
    
    trt_type = if_else(trt_type == "Group-based  Cognitive Behavioral Therapy", 
                      "Group based Cognitive Behavioural Therapy", trt_type),
    trt_type = if_else(trt_type == "Group-based Cognitive Behavioral Therapy", 
                      "Group based Cognitive Behavioural Therapy", trt_type),
    trt_type = if_else(trt_type =="Group psychoeducation & Social skill training", 
                      "Group psychoeducation & Social Skill Training", trt_type),
    trt_type = if_else(trt_type =="Group psychoeducation", 
                      "Group Psychoeducation", trt_type),
    trt_type = if_else(trt_type =="Group psychoeducation & Social Skill Training", 
                      "Group Psychoeducation & Social Skill Training", trt_type),
    trt_type = if_else(trt_type =="Education and Illness Management", 
                      "Group Psychoeducation & Social Skill Training", trt_type),
    trt_type = if_else(trt_type =="Illness management", 
                      "Illness Management", trt_type),
    
    sample_factors = if_else(sample_factors =="Older with depression and anxiety", 
                            "Mixed", sample_factors), 
    sample_factors = if_else(sample_factors =="All suffered from severe mental illness", 
                            "Shared Social problem(s)/challenge(s)", sample_factors),
    sample_factors = if_else(sample_factors =="Shared origin and psychological distress", 
                            "Mixed", sample_factors),
    sample_factors = if_else(sample_factors =="persons with major psychiatric problems", 
                            "Shared Social problem(s)/challenge(s)", sample_factors),
    
    analysis_plan = if_else(analysis_plan == "Unused", "Unused outcomes", analysis_plan), 
    
    test_type = if_else(test_type == "Clinical administered", "Clinician-rated measure", test_type),
    test_type = if_else(test_type == "Clinical interviews", "Clinician-rated measure", test_type),
    test_type = if_else(test_type == "Self report", "Self-reported", test_type),
    test_type = if_else(test_type == "Self report through clinical interview", "Self-reported", test_type),
    test_type = if_else(test_type == "Self-reported via diagnostic interview", "Self-reported", test_type), 
    
    measure_type = if_else(measure_type == "Pre-post with controls", "Post-intervention", measure_type),
   
   cluster_treatment = if_else(cluster_treatment == "Hierarchical mixed models", "Mixed-model", cluster_treatment),
   
   cluster_treatment = if_else(cluster_treatment == "Multilevel analysis and clustered standard errors", 
                        "Multilevel analysis", cluster_treatment),
   
   rob_tool = if_else(rob_tool == "Rob2", "RoB2", rob_tool),
   rob_tool = if_else(rob_tool == "Rob2 CRCT", "RoB2", rob_tool)
   
 ) |> 
 # Remove unused outcomes
 filter(!str_detect(analysis_plan, "Unused"))
```

```{r}
sample_size_dat <- 
  GBD_effect |> 
  group_by(year, studyid, sample_id) |> 
  summarise_at(
    vars(N_t, N_c, N_total), list(mean = mean)
  )

sample_size_dat |> 
  pivot_longer(
        cols = N_t_mean:ESS_mean,
    names_to = "sample_sizes_char",
    values_to = "sample_size"
  ) |> 
  group_by(sample_sizes_char) |> 
  summarise(
    mean = mean(sample_size, na.rm = TRUE),
    sd = sd(sample_size, na.rm = TRUE),
    q = list(quantile(sample_size, na.rm = TRUE))
  ) |> 
  unnest_wider(q, names_repair = ~paste0('Q_', sub('%', '', .))) |> 
  rename(mean = Q_mean, sd = Q_sd) |> 
  mutate(
    id = rev(1:4)
  ) |> 
  arrange(id) |> 
  select(-id)

SS1 <- ggplot(sample_size_dat, aes(N_t_mean)) + 
  geom_density(fill = "cornflowerblue", trim = TRUE) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug() + 
  theme_minimal() + 
  theme(axis.title.y = element_blank()) +
  labs(x = "Treatment group sample size")

SS2 <- ggplot(sample_size_dat, aes(N_c_mean)) + 
  geom_density(fill = "cornflowerblue", trim = TRUE) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug() + 
  theme_minimal() +
  theme(axis.title.y = element_blank()) +
  labs(x = "Control group sample size")

SS3 <- ggplot(sample_size_dat, aes(N_total_mean)) + 
  geom_density(fill = "cornflowerblue", trim = TRUE) + 
  geom_blank(aes(x = 0, y = 0)) + 
  geom_rug() + 
  theme_minimal() + 
  theme(axis.title.y = element_blank()) +
  labs(x = "Total sample size")

library(patchwork)

sample_dist_plot <- SS1 / SS2 / SS3
sample_dist_plot


```

# Empirical distribution of effect size estimates (SUPPLEMENTARY MATERIAL)

```{r}
qrtls <- quantile(GBD_effect$gt, c(.25, .75), na.rm = TRUE)
fences <-  qrtls + 3 * diff(qrtls) * c(-1, 1)
fence_dat <- data.frame(qrtl = qrtls, fence = fences)

es_dist_plot <- 
  ggplot(GBD_effect, aes(gt)) + 
  geom_density(fill = "cornflowerblue") + 
  geom_vline(data = fence_dat, aes(xintercept = qrtl), linetype = "solid") + 
  geom_vline(data = fence_dat, aes(xintercept = fence), linetype = "dashed") + 
  geom_rug(alpha = 0.25) + 
  theme_minimal() + 
  theme(axis.title.y = element_blank()) +
  labs(x = "Effect size estimate")
```

```{r}
# Making data for plotting outcomes

# Without mental health outcomes and only reintergration-outcomes
GB_outcome_reintergration <- GBD_effect |> 
  filter(!str_detect(analysis_plan, "mental|used|hospi")) |>
  group_by(analysis_plan) |> 
  reframe(
    qrtl = quantile(gt,  c(.25, .75)),
    fence = qrtl + 3 * diff(qrtl) * c(-1,1),
    
    .groups = "drop"
  )


# Therefore All mental health outcomes, Unused outcome and hospitalization are excluded
reintegration_outcome_plot <- GBD_effect |> 
 filter(!str_detect(analysis_plan, "mental|used|hospi")) |>
  ggplot(aes(x = gt, fill = analysis_plan)) + 
  geom_density(alpha = 0.7) +
  geom_vline(data = GB_outcome_reintergration, aes(xintercept = qrtl), linetype = "solid")+
  geom_vline(data = GB_outcome_reintergration, aes(xintercept = fence), linetype = "dashed")+
  geom_rug(alpha = 0.25) +
  facet_wrap(~analysis_plan, scales = "free", ncol = 4) +
  theme_minimal() +
  theme(legend.position = "none", axis.title.y = element_blank()) +
  labs(x = "Effect size estimate")


# Plot with all mental health outcomes 

# Total mental health:
GB_outcome_mental_health <- GBD_effect |> 
  filter(str_detect(analysis_plan, "mental")) |> 
  filter(!str_detect(analysis_plan, "Unused")) |>
  reframe(
    qrtl = quantile(gt,  c(.25, .75)),
    fence = qrtl + 3 * diff(qrtl) * c(-1,1),
    
    .groups = "drop"
  )

mental_health_outcome_plot <- GBD_effect |> 
 filter(str_detect(analysis_plan, "mental")) |>
  ggplot(aes(x = gt)) + 
  geom_density(alpha = 0.7, fill = "cornflowerblue") +
  geom_vline(data = GB_outcome_mental_health, aes(xintercept = qrtl), linetype = "solid")+
  geom_vline(data = GB_outcome_mental_health, aes(xintercept = fence), linetype = "dashed")+
  geom_rug(alpha = 0.25) +
  theme_minimal() +
  theme(legend.position = "none", axis.title.y = element_blank()) +
  labs(x = "Effect size estimate")

# Seperated mental health outcomes
GB_outcomes_mental_health <- GBD_effect |> 
  mutate(analysis_plan = case_when(
  str_detect(analysis_plan, "All mental health outcomes/Symptoms of psychosis|All mental health outcomes/Negative symptoms") ~ "All mental health outcomes/Symptoms of psychosis",
   TRUE ~ analysis_plan)) |> 
   filter(str_detect(analysis_plan, "mental")) |>
  filter(!str_detect(analysis_plan, "Unused")) |>
  group_by(analysis_plan) |> 
  reframe(
    qrtl = quantile(gt,  c(.25, .75)),
    fence = qrtl + 3 * diff(qrtl) * c(-1,1),
    
    .groups = "drop"
  )


mental_health_outcomes_plot <- GBD_effect |> mutate(analysis_plan = case_when(
  # Gathering negative symptoms and symptoms of psychosis as negative symptoms refers to same symptoms
  str_detect(analysis_plan, "All mental health outcomes/Symptoms of psychosis|All mental health outcomes/Negative symptoms") ~ "All mental health outcomes/Symptoms of psychosis", 
   TRUE ~ analysis_plan)) |> 
  filter(str_detect(analysis_plan, "mental")) |> 
  filter(!str_detect(analysis_plan, "Unused")) |>
  ggplot(aes(x = gt, fill = analysis_plan)) + 
  geom_density(alpha = 0.7) +
  geom_vline(data = GB_outcomes_mental_health, aes(xintercept = qrtl), linetype = "solid")+
  geom_vline(data = GB_outcomes_mental_health, aes(xintercept = fence), linetype = "dashed")+
  geom_rug(alpha = 0.25) +
  facet_wrap(~analysis_plan, scales = "free") +
  theme_minimal() +
  theme(legend.position = "none", axis.title.y = element_blank()) +
  labs(x = "Effect size estimate")
```

# Funnel-plot

```{r}
# Funnel plot for overall effectsizes ----

# data prep
GBD_effect <- GBD_effect |> 
  mutate(timing = case_when(
    timing == "Followup" ~ "3m",
    timing == "Posttest" ~ "Post",
    timing == "12" ~ "12m",
    timing == "24" ~ "24m",
    timing == "post" ~ "Post",
    timing == "3 months" ~ "3m",
    timing == "6 months" ~ "6m",
    timing == "6w" ~ "Post",
    TRUE ~ timing))

unique_values <- unique(GBD_effect$timing)

GB_dat <- 
  GBD_effect |> 
  select(studyid, gt, vgt, timing, analysis_plan, outcome) |> 
  mutate(
    seg = sqrt(vgt),
    timing = if_else(is.na(timing), "Post", timing),
    timing = factor(
      timing, 
      levels = c("Post", "3m", "6m", "9m", "12m", "18m", "24m")
    ),
    es_ID = 1:n()
  ) |> 
  arrange(timing)

# Who are those with big seg
GB_high_seg <- GB_dat |> 
  filter(seg > 0.75) |> 
  left_join(GBD_effect, by = c("studyid", "outcome"))
  

# Discarded in this data frame
GB_dat <- GB_dat |> 
  filter(!seg > 0.75)


#es_exp <- as.numeric(mean_es_GB$b)
y_lim_exp1 <- max(sqrt(GB_dat$vgt)) + 0.02 



funnel_exp1 <-  tribble(
  ~ x90, ~ x95, ~ x99, ~ y,
  0,     0,     0,     0,
  qnorm(0.05) * y_lim_exp1, qnorm(0.025) * y_lim_exp1, qnorm(0.005) * y_lim_exp1, y_lim_exp1,
  qnorm(0.95) * y_lim_exp1, qnorm(0.975) * y_lim_exp1, qnorm(0.995) * y_lim_exp1, y_lim_exp1,
  0,     0,     0,     0
) 


GB_plot_all <-
  GB_dat |> 
  ggplot() + 
  geom_polygon(data = funnel_exp1, aes(x = y, y = x99), fill = "grey", alpha = 0.5) + 
  geom_polygon(data = funnel_exp1, aes(x = y, y = x95), fill = "grey10", alpha = 0.5) + 
  geom_polygon(data = funnel_exp1, aes(x = y, y = x90), fill = "lightcyan", alpha = 0.7) + 
  geom_point(aes(seg, gt), alpha = 1, size = 1.2) +
  scale_color_brewer(type = "qual", palette = 2) + 
  coord_flip() + 
  scale_x_reverse(limits = c(y_lim_exp1, 0.0), expand = c(0,0)) + 
  scale_y_continuous(breaks = seq(-3, 3, 1)) + 
  theme_bw() + 
  labs(x = "Standard error (adjusted)", 
       y = "Standardized mean difference (Hedges' g)", 
       color = "", shape = "") +
  theme(legend.position = "bottom")


# Funnelplot reintegration outcomes - Subgroup analysis ----
GB_dat_reintergration <- 
  GBD_effect |> 
  filter(!str_detect(analysis_plan, "mental|used|hospi|Employment|Physical")) |> 
  select(studyid, gt, vgt, timing, analysis_plan) |> 
  mutate(
    seg = sqrt(vgt),
    timing = if_else(is.na(timing), "Post", timing),
    timing = factor(
      timing, 
      levels = c("Post", "3m", "6m", "9m", "12m", "18m", "24m")
    ),
    es_ID = 1:n()
  ) |> 
  filter(!seg > 0.75) |> 
  arrange(timing)



#sub_GB_dat_reintergration <- 
#  GB_dat_reintergration |> 
#  summarise(
#    across(where(is.numeric), mean),
#    .by = analysis_plan
#  ) |> 
#  mutate(
#    Study_ID = 1, 
   # es_exp = as.numeric(mean_es_FP_subgrp$b),
#    slope_upper = qnorm(0.975),
#    slope_lower = qnorm(0.025)
#  )


y_lim_exp2 <- max(sqrt(GB_dat_reintergration$vgt)) + 0.02 

funnel_exp2 <-  tribble(
  ~ x90, ~ x95, ~ x99, ~ y,
  0,     0,     0,     0,
  qnorm(0.05) * y_lim_exp2, qnorm(0.025) * y_lim_exp2, qnorm(0.005) * y_lim_exp2, y_lim_exp2,
  qnorm(0.95) * y_lim_exp2, qnorm(0.975) * y_lim_exp2, qnorm(0.995) * y_lim_exp2, y_lim_exp2,
  0,     0,     0,     0
) 



# Overall effect-size for reintegration outcome
FP_plot_reintegration_overall <-
  GB_dat_reintergration |> 
  ggplot() + 
  geom_polygon(data = funnel_exp2, aes(x = y, y = x99), fill = "grey", alpha = 0.5) + 
  geom_polygon(data = funnel_exp2, aes(x = y, y = x95), fill = "grey10", alpha = 0.5) + 
  geom_polygon(data = funnel_exp2, aes(x = y, y = x90), fill = "lightcyan", alpha = 0.7) + 
  geom_point(aes(seg, gt), alpha = 1, size = 1.2) +
  scale_color_brewer(type = "qual", palette = 2) + 
  coord_flip() + 
  scale_x_reverse(limits = c(y_lim_exp2, 0.0), expand = c(0,0)) + 
  scale_y_continuous(breaks = seq(-3, 3, 1)) + 
  theme_bw() + 
  labs(x = "Standard error (adjusted)", 
       y = "Standardized mean difference (Hedges' g)", 
       color = "", shape = "") +
  theme(legend.position = "none")


# Effect-sizes for separated reintegration outcome
FP_plot_reintergration_subgrp <-
  GB_dat_reintergration |> 
  ggplot() + 
  geom_polygon(data = funnel_exp2, aes(x = y, y = x99), fill = "grey", alpha = 0.5) + 
  geom_polygon(data = funnel_exp2, aes(x = y, y = x95), fill = "grey10", alpha = 0.5) + 
  geom_polygon(data = funnel_exp2, aes(x = y, y = x90), fill = "lightcyan", alpha = 0.7) + 
  geom_point(aes(seg, gt), alpha = 1, size = 1.2) +
  scale_color_brewer(type = "qual", palette = 2) + 
  coord_flip() + 
  facet_wrap(~analysis_plan, scales = "free") +
  scale_x_reverse(limits = c(y_lim_exp2, 0.0), expand = c(0,0)) + 
  scale_y_continuous(breaks = seq(-3, 3, 1)) + 
  theme_bw() + 
  labs(x = "Standard error (adjusted)", 
       y = "Standardized mean difference (Hedges' g)", 
       color = "", shape = "") +
  theme(legend.position = "none")

# Funnel-plot health outcomes - Subgroup analysis ----
GB_dat_mental_health <- 
  GBD_effect |> 
  mutate(analysis_plan = case_when(
  str_detect(analysis_plan, "All mental health outcomes/Symptoms of psychosis|All mental health outcomes/Negative symptoms") ~ "All mental health outcomes/Symptoms of psychosis",
   TRUE ~ analysis_plan)) |> 
  filter(str_detect(analysis_plan, "mental")) |>
  filter(!str_detect(analysis_plan, "Unused")) |>
  select(studyid, gt, vgt, timing, analysis_plan) |> 
  mutate(
    seg = sqrt(vgt),
    timing = if_else(is.na(timing), "Post", timing),
    timing = factor(
      timing, 
      levels = c("Post", "3m", "6m", "9m", "12m", "18m", "24m")
    ),
    es_ID = 1:n()
  ) |> 
  arrange(timing)


y_lim_exp3 <- max(sqrt(GB_dat_mental_health$vgt)) + 0.02 

funnel_exp3 <-  tribble(
  ~ x90, ~ x95, ~ x99, ~ y,
  0,     0,     0,     0,
  qnorm(0.05) * y_lim_exp3, qnorm(0.025) * y_lim_exp3, qnorm(0.005) * y_lim_exp3, y_lim_exp3,
  qnorm(0.95) * y_lim_exp3, qnorm(0.975) * y_lim_exp3, qnorm(0.995) * y_lim_exp3, y_lim_exp3,
  0,     0,     0,     0
) 


# Overall effect size for mental health outcome
FP_plot_overall_mental <-
  GB_dat_mental_health |> 
  ggplot() + 
  geom_polygon(data = funnel_exp3, aes(x = y, y = x99), fill = "grey", alpha = 0.5) + 
  geom_polygon(data = funnel_exp3, aes(x = y, y = x95), fill = "grey10", alpha = 0.5) + 
  geom_polygon(data = funnel_exp3, aes(x = y, y = x90), fill = "lightcyan", alpha = 0.7) + 
  geom_point(aes(seg, gt), alpha = 1, size = 1.2) +
  scale_color_brewer(type = "qual", palette = 2) + 
  coord_flip() + 
  scale_x_reverse(limits = c(y_lim_exp3, 0.0), expand = c(0,0)) + 
  scale_y_continuous(breaks = seq(-3, 3, 1)) + 
  theme_bw() + 
  labs(x = "Standard error (adjusted)", 
       y = "Standardized mean difference (Hedges' g)", 
       color = "", shape = "") +
  theme(legend.position = "none")

# Subgroup effect size for mental health outcome
FP_plot_subgrp_mental <-
  GB_dat_mental_health |> 
  filter(!(analysis_plan == "All mental health outcomes")) |>
  ggplot() + 
  geom_polygon(data = funnel_exp3, aes(x = y, y = x99), fill = "grey", alpha = 0.5) + 
  geom_polygon(data = funnel_exp3, aes(x = y, y = x95), fill = "grey10", alpha = 0.5) + 
  geom_polygon(data = funnel_exp3, aes(x = y, y = x90), fill = "lightcyan", alpha = 0.7) + 
  geom_point(aes(seg, gt), alpha = 1, size = 1.2) +
  scale_color_brewer(type = "qual", palette = 2) + 
  coord_flip() + 
  facet_wrap(~analysis_plan, scales = "free") +
  scale_x_reverse(limits = c(y_lim_exp3, 0.0), expand = c(0,0)) + 
  scale_y_continuous(breaks = seq(-3, 3, 1)) + 
  theme_bw() + 
  labs(x = "Standard error (adjusted)", 
       y = "Standardized mean difference (Hedges' g)", 
       color = "", shape = "") +
  theme(legend.position = "none")

```

# Descriptive Tables

```{r}
# Study context
# Percent studies by countries
study_context <- GBD_effect |> 
  group_by(studyid, cnt) |> 
  summarise(
    es_n = n(),
    
    .groups = "drop"
  ) |> 
  group_by(cnt) |>
  summarise(
    study_char = paste0("% ", unique(cnt)), 
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
   # SD = NA,
    
    range = "0-1",
    
    .groups = "drop"
  ) |> 
  select(-cnt); study_context

# Average number of participants per effect size 

participants <- GBD_effect |> 
  group_by(studyid) |> 
  summarise(
    study_avg_sample = mean(N_total),
    es_n = n(), 
    .groups = "drop"
  ) |> 
  summarise(
    study_char = "Number of particiapnts",
    
    Study = n_distinct(studyid), # Studies
    Effect_size = sum(es_n), # Effect size
    
    Mean = round(mean(study_avg_sample)),
  #  SD = round(sd(study_avg_sample)),
    
    range = paste0(min(study_avg_sample), "-", max(study_avg_sample))
    
  ); participants

# Effective sample size (removed) 
#ESS <- GBD_effect |> 
#  group_by(studyid) |> 
#  summarise(
#    study_avg_ESS = mean(ESS),
    
#    es_n = n(),
    
#    .groups = "drop"
#  ) |> 
#  summarise(
#    variable = "Effective sample size",
#    study_char = "Sample size",
    
#    I = n_distinct(studyid),
#    K = sum(es_n),
    
#    Mean = round(mean(study_avg_ESS)),
#    SD = round(sd(study_avg_ESS)),
    
#    range = paste0(min(study_avg_ESS), "-", round(max(study_avg_ESS)))
    
#  ); ESS

# Average size of the groups
group_size <- GBD_effect |> 
  group_by(studyid) |> 
  summarise(
    treat_SampS = mean(N_t),
    cont_SampS = mean(N_c),
    
    es_n = n(),
    
    .groups = "drop"
  ) |> 
  summarise(
    study_char = c("Intervention group", "Control group"),
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = c(mean(treat_SampS), mean(cont_SampS)),
   # SD = c(sd(treat_SampS), sd(cont_SampS)),
    
    range = c(
      paste0(min(treat_SampS), "-", round(max(treat_SampS))),
      paste0(min(cont_SampS), "-", round(max(cont_SampS)))
    )
    
  ); group_size

# Number of samples per study 
samples_per_study <- GBD_effect |> 
  group_by(studyid) |> 
  summarise(
    samples = n_distinct(sample_id), 
    es_n = n(),
    
    .groups = "drop"
  ) |>
  summarise(
    study_char = "Samples per study",
    
    Study = sum(samples),  
    Effect_size = sum(es_n),  
    
    Mean = mean(samples), 
   # SD = sd(samples),  
    
    range = paste0(min(samples), "-", max(samples)),
    
    .groups = "drop"
  ); samples_per_study


# Number of distinct studies in review

n_distinct(GBD_effect$studyid)

study_context <- 
  bind_rows(
    country_all,
    participants,
 #   ESS,
    group_size,
    samples_per_study
    
); study_context


```

## Descriptive of studies design

```{r}

# Proportion cluster randomized or RCT studies

study_design <- GBD_effect |>  
  group_by(studyid) |> 
  summarise(
    design = unique(design),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(design) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", design),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
  #  SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |>  
  select(-c(design)); study_design

# Dont no if relevant to show details about study outlet and publishment as
# Every indcluded study is a journal article and published. 

# Randomization
study_randomization <- GBD_effect |>  
  group_by(studyid) |>  
  summarise(
    randomization = unique(randomization),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(randomization) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", randomization),
    
    Mean = Study/sum(Study),
    #SD = NA,
    range = "0-1",
   ) |> 
  relocate(study_char) |>  
  select(-c(randomization)); study_randomization

# Handling of clustering
clustering <- GBD_effect |>  
  group_by(studyid) |> 
  summarise(
    clustering = unique(cluster_treatment[!is.na(cluster_treatment)]),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(clustering) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", clustering),
    
    Mean = Study/sum(Study),
   # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(clustering)); clustering

# Analysis strategy 
analysis_strategy <- GBD_effect |>  
  group_by(studyid) |> 
  summarise(
    analysis_strat = unique(analysis_strategy),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  filter(!is.na(analysis_strat)) |> 
  group_by(analysis_strat) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |>
  mutate(
    
    study_char = paste("%", analysis_strat),
    
    Mean = Study / sum(Study),
   # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |>  
  select(-c(analysis_strat)); analysis_strategy

design <- 
  bind_rows(
    study_design,
    study_randomization,
    clustering,
    analysis_strategy
); design


```

## Participants characteristics

```{r}
# % Males in treatment and control group

male_per <- 
  GBD_effect |> 
  group_by(studyid) |>  
  summarise(
    
    t_male = mean(as.numeric(male_pct_t), na.rm = TRUE),
    c_male = mean(as.numeric(male_pct_c), na.rm = TRUE),
    
     es_n = sum(!is.na(male_pct_t)),
    
    .groups = "drop"
    
  ) |> 
  filter(es_n != 0) |> 
   summarise(
    study_char = c("Intervention group", "Control group"), 
    Study = n_distinct(studyid),  
    Effect_size = sum(es_n, na.rm = TRUE),
    
    Mean = c(mean(t_male, na.rm = TRUE), mean(c_male, na.rm = TRUE)), 
  #  SD = c(sd(t_male, na.rm = TRUE), sd(c_male, na.rm = TRUE)), 
    range = c(paste(min(t_male, na.rm = TRUE), "-", max(t_male, na.rm = TRUE)),  
              paste(min(c_male, na.rm = TRUE), "-", max(c_male, na.rm = TRUE)))
  ); male_per

# Mean age
age_mean <- 
  GBD_effect |> 
  group_by(studyid) |> 
  summarise(
    
    t_age = mean(as.numeric(age_mean_t), na.rm = TRUE),
    c_age = mean(as.numeric(age_mean_c), na.rm = TRUE),
    
     es_n = sum(!is.na(age_mean_c)),
    
    .groups = "drop"
    
  ) |>  
  filter(es_n != 0) |> 
   summarise(
    study_char = c("Intervention group", "Control group"),  # Kategorier for hver gruppe
    Study = n_distinct(studyid),  
    Effect_size = sum(es_n, na.rm = TRUE),
    
    Mean = c(mean(t_age, na.rm = TRUE), mean(c_age, na.rm = TRUE)),  # Gennemsnit for hver gruppe
    #SD = c(sd(t_age, na.rm = TRUE), sd(c_age, na.rm = TRUE)),  # Standardafvigelse for hver gruppe
    range = c(paste(min(t_age, na.rm = TRUE), "-", max(t_age, na.rm = TRUE)),  # Range for hver gruppe
              paste(min(c_age, na.rm = TRUE), "-", max(c_age, na.rm = TRUE)))
  ); age_mean

# Disorder type
disorder_type <- GBD_effect |>  
  group_by(studyid) |> 
  summarise(
    disorder = unique(disorder_type),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(disorder) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", disorder),
    
    Mean = Study/sum(Study),
   # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(disorder)); disorder_type


assesment <- GBD_effect |>  
  group_by(studyid) |>  
  summarise(
    assessment = unique(assessment),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(assessment) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", assessment),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
    #SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(assessment)); assesment

# Sample composition
sample_composition <- GBD_effect |>  
  group_by(studyid) |> 
  summarise(
    composition = unique(sample_comp),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(composition) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", composition),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
  #  SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(composition)); sample_composition

# Sample factors
sample_factors <- GBD_effect |>  
  group_by(studyid) |> 
  summarise(
    sample_factors = unique(sample_factors),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(sample_factors) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", sample_factors),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
   # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(sample_factors)); sample_factors


study_participants <- 
  bind_rows(
    male_per, age_mean, 
   # disorder_type, 
    assesment,
    sample_composition,
    sample_factors
); study_participants


```

## Intervention characteristics

```{r}
# Duration of intervention
duration <- 
  GBD_effect |> 
  group_by(studyid) |>  
  summarise(
    
    m_duration = mean(duration_weeks, na.rm = TRUE),
  
    es_n = n(),
    
    miss_dur = sum(is.na(duration_weeks)),
    
    dur_report = if_else(miss_dur == 0, "Reported", "Not reported"),
    
    .groups = "drop"
     
  ) |>  
  filter(dur_report != "Not reported") |>  
  summarise(
    study_char = "Duration in weeks",
    
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = mean(m_duration, na.rm = TRUE),
 #   SD = sd(m_duration, na.rm = TRUE),
    
    range = paste0(min(m_duration, na.rm = TRUE), "-",
                   max(m_duration, na.rm = TRUE)),
  
    
  ); duration

# Mean number of sessions per week

sessions_per_week <- 
  GBD_effect|> 
  mutate(sessions_per_week = as.numeric(sessions_per_week)) |> 
  group_by(studyid)  |>  
  summarise(
    
    m_intensity = mean(sessions_per_week, na.rm = TRUE),
  
    es_n = n(),
    
    miss_int = sum(is.na(sessions_per_week)),
    
    int_report = if_else(miss_int == 0, "Reported", "Not reported"),
    
    .groups = "drop"
     
  ) |> 
  filter(int_report != "Not reported") |>  
  summarise(
    study_char = "Number of sessions per week",
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = mean(m_intensity, na.rm = TRUE),
 #   SD = sd(m_intensity, na.rm = TRUE),
    
    range = paste0(min(m_intensity, na.rm = TRUE), "-",
                   max(m_intensity, na.rm = TRUE))
    
  ); sessions_per_week

# Average group size in the treatment intervention
avg_intevention_group_size <- 
  GBD_effect|> 
  mutate(avg_group_size = as.numeric(avg_group_size)) |> 
  group_by(studyid)  |>  
  summarise(
    
    m_intensity = mean(avg_group_size, na.rm = TRUE),
  
    es_n = n(),
    
    miss_int = sum(is.na(avg_group_size)),
    
    int_report = if_else(miss_int == 0, "Reported", "Not reported"),
    
    .groups = "drop"
     
  ) |> 
  filter(int_report != "Not reported") |>  
  summarise(
    study_char = "Average group size",
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = mean(m_intensity, na.rm = TRUE),
    #SD = sd(m_intensity, na.rm = TRUE),
    
    range = paste0(min(m_intensity, na.rm = TRUE), "-",
                   max(m_intensity, na.rm = TRUE))
    
  ); avg_intevention_group_size

# Number of interventions of each study
interventions <- GBD_effect|> 
 mutate(N_treatments = as.numeric(N_treatments)) |> 
  group_by(studyid)  |>  
  summarise(
    
    m_intensity = mean(N_treatments, na.rm = TRUE),
  
    es_n = n(),
    
    miss_int = sum(is.na(N_treatments)),
    
    int_report = if_else(miss_int == 0, "Reported", "Not reported"),
    
    .groups = "drop"
     
  ) |> 
  filter(int_report != "Not reported") |>  
  summarise(
    study_char = "Treatments",
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = mean(m_intensity, na.rm = TRUE),
  #  SD = sd(m_intensity, na.rm = TRUE),
    
    range = paste0(min(m_intensity, na.rm = TRUE), "-",
                   max(m_intensity, na.rm = TRUE))
    
  ); interventions

# Treatment types 
treatment_types <- GBD_effect |>  
  group_by(studyid) |> 
  summarise(
    treatment_type = unique(trt_type),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(treatment_type) |> 
  summarise(

    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    study_char = paste("%", treatment_type),
    
    Mean = Study/sum(Study),
   # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(treatment_type)); treatment_types



# Implementation types 
implementation <- GBD_effect |>  
  group_by(studyid) |> 
  summarise(
    implementation = unique(implementation),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(implementation) |> 
  summarise(
    Study = n_distinct(studyid),
    effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", implementation),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
  #  SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(implementation)); implementation


intervention_characteristics <- bind_rows(
  duration, sessions_per_week, 
  avg_intevention_group_size, 
  interventions, 
  treatment_types
)


```

## Control group

```{r}
# Control types 
control <- GBD_effect |>  
  group_by(studyid) |>  
  summarise(
    control = unique(control),
    es_n = n(),
    
    .groups = "drop"
    
  ) |>  
  group_by(control) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", control),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
    # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |>  
  select(-c(control)); control
```

## Methodological features

```{r}
# Average number of effect size per study
avg_es_study <- 
  GBD_effect |> 
  group_by(studyid) |> 
  summarise(
    
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  summarise(
    study_char = "Average n of es",
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = mean(es_n),
  #  SD = sd(es_n),
    
    range = paste0(min(es_n), "-", max(es_n))
    
  ); avg_es_study
```

## Outcome and measurement characteristics

```{r}
# Overall constructs
construct <- GBD_effect |>  
  group_by(studyid) |>  
  summarise(
    overall_construct = unique(analysis_plan),
    es_n = n(),
    
    .groups = "drop"
    
  ) |>  
  group_by(overall_construct) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", overall_construct),
    
    Mean = Study/sum(Study),
   # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(overall_construct)); construct


# Type of test 
test <- GBD_effect |>  
  group_by(studyid) |>  
  summarise(
    test_type = unique(test_type),
    es_n = n(),
    
    .groups = "drop"
    
  ) |>  
  group_by(test_type) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", test_type),
    
    Mean = Study/sum(Study),
  #  SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(test_type)); test

# Type of measurement
measure_type <- GBD_effect |>  
  group_by(studyid) |>  
  summarise(
    measure_type = unique(measure_type),
    es_n = n(),
    
    .groups = "drop"
    
  ) |>  
  group_by(measure_type) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    study_char = paste("%", measure_type),
    
    Mean = Study/sum(Study),
  #  SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(measure_type)); measure_type

outcome_measurement <- bind_rows(
  construct, test, measure_type
  
)

```

## Table 1 and 2

```{r}
table1 <- bind_rows(
  study_context, design, 
  study_participants, 
  intervention_characteristics, 
  control, 
  avg_es_study, 
  outcome_measurement
)



table1_percent <- 
  table1 |> 
  filter(str_detect(study_char, "%")) |> 
  select(-c(range)) |> 
  mutate(
    Mean = round(Mean, 3),
    
  ); table1_percent


table2_rest_desc <- 
  table1 |> 
  filter(!str_detect(study_char, "%")) |> 
  mutate(
    
    across(Mean, ~ round(.x, 3))
    
  ); table2_rest_desc


report_table(table = table1_percent[1:2,], file_name = "Table1", format = "word_document")


```
## Risk of Bias details
```{r}
# Distribution of RoB2 evaluations
RoB2_dat <- GBD_effect |> 
  select(rob_tool:Overall, studyid, Author) |> 
  filter(rob_tool == "RoB2") |> 
  select(-c(rob_tool,D6:D7))

p_rob2 <- rob_summary(data = RoB2_dat, tool = "ROB2", overall = TRUE)

# Distribution of ROBINS-I evaluations
ROBINS1_dat <- GBD_effect |> 
  select(rob_tool:Overall, studyid, Author) |> 
  filter(rob_tool == "ROBINS-I") |> 
  select(-c(rob_tool))

p_robins <- rob_summary(data = ROBINS1_dat, tool = "ROBINS-I", overall = TRUE)

```

# Descrptive tables: Wellbeing and Quality of life
```{r}
wellbeing_QoL <- GBD_effect |> 
  filter(analysis_plan == "Wellbeing and Quality of Life")


# Study context
# Percent studies by countries
study_context_WQoL <- wellbeing_QoL |> 
  group_by(studyid, cnt) |> 
  summarise(
    es_n = n(),
    
    .groups = "drop"
  ) |> 
  group_by(cnt) |>
  summarise(
    study_char = paste0("% ", unique(cnt)), 
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
   # SD = NA,
    
    range = "0-1",
    
    .groups = "drop"
  ) |> 
  select(-cnt); study_context_WQoL

# Average number of participants per effect size 

participants_WQoL <- wellbeing_QoL |> 
  group_by(studyid) |> 
  summarise(
    study_avg_sample = mean(N_total),
    es_n = n(), 
    .groups = "drop"
  ) |> 
  summarise(
    study_char = "Number of particiapnts",
    
    Study = n_distinct(studyid), # Studies
    Effect_size = sum(es_n), # Effect size
    
    Mean = round(mean(study_avg_sample)),
  #  SD = round(sd(study_avg_sample)),
    
    range = paste0(min(study_avg_sample), "-", max(study_avg_sample))
    
  ); participants_WQoL



# Average size of the groups
group_size_WQoL <- wellbeing_QoL |> 
  group_by(studyid) |> 
  summarise(
    treat_SampS = mean(N_t),
    cont_SampS = mean(N_c),
    
    es_n = n(),
    
    .groups = "drop"
  ) |> 
  summarise(
    study_char = c("Intervention group", "Control group"),
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = c(mean(treat_SampS), mean(cont_SampS)),
   # SD = c(sd(treat_SampS), sd(cont_SampS)),
    
    range = c(
      paste0(min(treat_SampS), "-", round(max(treat_SampS))),
      paste0(min(cont_SampS), "-", round(max(cont_SampS)))
    )
    
  ); group_size_WQoL

# Number of samples per study 
samples_per_study_WQoL <- wellbeing_QoL |> 
  group_by(studyid) |> 
  summarise(
    samples = n_distinct(sample_id), 
    es_n = n(),
    
    .groups = "drop"
  ) |>
  summarise(
    study_char = "Samples per study",
    
    Study = sum(samples),  
    Effect_size = sum(es_n),  
    
    Mean = mean(samples), 
   # SD = sd(samples),  
    
    range = paste0(min(samples), "-", max(samples)),
    
    .groups = "drop"
  ); samples_per_study_WQoL


# Number of distinct studies in review

n_distinct(GBD_effect$studyid)

study_context_WQoL <- 
  bind_rows(
    study_context_WQoL,
    participants_WQoL,
 #   ESS,
    group_size_WQoL,
    samples_per_study_WQoL
    
); study_context_WQoL

# Study Design
# Proportion cluster randomized or RCT studies
study_design_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |> 
  summarise(
    design = unique(design),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(design) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", design),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
  #  SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |>  
  select(-c(design)); study_design_WQoL


# Randomization
study_randomization_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |>  
  summarise(
    randomization = unique(randomization),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(randomization) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", randomization),
    
    Mean = Study/sum(Study),
    #SD = NA,
    range = "0-1",
   ) |> 
  relocate(study_char) |>  
  select(-c(randomization)); study_randomization_WQoL

# Handling of clustering
clustering_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |> 
  summarise(
    clustering = unique(cluster_treatment[!is.na(cluster_treatment)]),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(clustering) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", clustering),
    
    Mean = Study/sum(Study),
   # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(clustering)); clustering_WQoL

# Analysis strategy 
analysis_strategy_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |> 
  summarise(
    analysis_strat = unique(analysis_strategy),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  filter(!is.na(analysis_strat)) |> 
  group_by(analysis_strat) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |>
  mutate(
    
    study_char = paste("%", analysis_strat),
    
    Mean = Study / sum(Study),
   # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |>  
  select(-c(analysis_strat)); analysis_strategy_WQoL

design_WQoL <- 
  bind_rows(
    study_design_WQoL,
    study_randomization_WQoL,
    clustering_WQoL,
    analysis_strategy_WQoL
); design_WQoL


# Study participants
# % Males in treatment and control group

male_per_WQoL <- 
  wellbeing_QoL |> 
  group_by(studyid) |>  
  summarise(
    
    t_male = mean(as.numeric(male_pct_t), na.rm = TRUE),
    c_male = mean(as.numeric(male_pct_c), na.rm = TRUE),
    
     es_n = sum(!is.na(male_pct_t)),
    
    .groups = "drop"
    
  ) |> 
  filter(es_n != 0) |> 
   summarise(
    study_char = c("Intervention group", "Control group"), 
    Study = n_distinct(studyid),  
    Effect_size = sum(es_n, na.rm = TRUE),
    
    Mean = c(mean(t_male, na.rm = TRUE), mean(c_male, na.rm = TRUE)), 
  #  SD = c(sd(t_male, na.rm = TRUE), sd(c_male, na.rm = TRUE)), 
    range = c(paste(min(t_male, na.rm = TRUE), "-", max(t_male, na.rm = TRUE)),  
              paste(min(c_male, na.rm = TRUE), "-", max(c_male, na.rm = TRUE)))
  ); male_per_WQoL

# Mean age
age_mean_WQoL <- 
  wellbeing_QoL |> 
  group_by(studyid) |> 
  summarise(
    
    t_age = mean(as.numeric(age_mean_t), na.rm = TRUE),
    c_age = mean(as.numeric(age_mean_c), na.rm = TRUE),
    
     es_n = sum(!is.na(age_mean_c)),
    
    .groups = "drop"
    
  ) |>  
  filter(es_n != 0) |> 
   summarise(
    study_char = c("Intervention group", "Control group"),  # Kategorier for hver gruppe
    Study = n_distinct(studyid),  
    Effect_size = sum(es_n, na.rm = TRUE),
    
    Mean = c(mean(t_age, na.rm = TRUE), mean(c_age, na.rm = TRUE)),  # Gennemsnit for hver gruppe
    #SD = c(sd(t_age, na.rm = TRUE), sd(c_age, na.rm = TRUE)),  # Standardafvigelse for hver gruppe
    range = c(paste(min(t_age, na.rm = TRUE), "-", max(t_age, na.rm = TRUE)),  # Range for hver gruppe
              paste(min(c_age, na.rm = TRUE), "-", max(c_age, na.rm = TRUE)))
  ); age_mean_WQoL

# Disorder type
disorder_type_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |> 
  summarise(
    disorder = unique(disorder_type),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(disorder) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", disorder),
    
    Mean = Study/sum(Study),
   # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(disorder)); disorder_type_WQoL


assesment_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |>  
  summarise(
    assessment = unique(assessment),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(assessment) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", assessment),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
    #SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(assessment)); assesment_WQoL

# Sample composition
sample_composition_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |> 
  summarise(
    composition = unique(sample_comp),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(composition) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", composition),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
  #  SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(composition)); sample_composition_WQoL

# Sample factors
sample_factors_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |> 
  summarise(
    sample_factors = unique(sample_factors),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(sample_factors) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", sample_factors),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
   # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(sample_factors)); sample_factors_WQoL


study_participants_WQoL <- 
  bind_rows(
    male_per_WQoL, age_mean_WQoL, 
   # disorder_type, 
    assesment_WQoL,
    sample_composition_WQoL,
    sample_factors_WQoL
); study_participants_WQoL


# Intervention characteristics 

# Duration of intervention
duration_WQoL <- 
  wellbeing_QoL |> 
  group_by(studyid) |>  
  summarise(
    
    m_duration = mean(duration_weeks, na.rm = TRUE),
  
    es_n = n(),
    
    miss_dur = sum(is.na(duration_weeks)),
    
    dur_report = if_else(miss_dur == 0, "Reported", "Not reported"),
    
    .groups = "drop"
     
  ) |>  
  filter(dur_report != "Not reported") |>  
  summarise(
    study_char = "Duration in weeks",
    
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = mean(m_duration, na.rm = TRUE),
 #   SD = sd(m_duration, na.rm = TRUE),
    
    range = paste0(min(m_duration, na.rm = TRUE), "-",
                   max(m_duration, na.rm = TRUE)),
  
    
  ); duration_WQoL

# Mean number of sessions per week

sessions_per_week_WQoL <- 
  wellbeing_QoL|> 
  mutate(sessions_per_week = as.numeric(sessions_per_week)) |> 
  group_by(studyid)  |>  
  summarise(
    
    m_intensity = mean(sessions_per_week, na.rm = TRUE),
  
    es_n = n(),
    
    miss_int = sum(is.na(sessions_per_week)),
    
    int_report = if_else(miss_int == 0, "Reported", "Not reported"),
    
    .groups = "drop"
     
  ) |> 
  filter(int_report != "Not reported") |>  
  summarise(
    study_char = "Number of sessions per week",
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = mean(m_intensity, na.rm = TRUE),
 #   SD = sd(m_intensity, na.rm = TRUE),
    
    range = paste0(min(m_intensity, na.rm = TRUE), "-",
                   max(m_intensity, na.rm = TRUE))
    
  ); sessions_per_week_WQoL

# Average group size in the treatment intervention
avg_intevention_group_size_WQoL <- 
  wellbeing_QoL|> 
  mutate(avg_group_size = as.numeric(avg_group_size)) |> 
  group_by(studyid)  |>  
  summarise(
    
    m_intensity = mean(avg_group_size, na.rm = TRUE),
  
    es_n = n(),
    
    miss_int = sum(is.na(avg_group_size)),
    
    int_report = if_else(miss_int == 0, "Reported", "Not reported"),
    
    .groups = "drop"
     
  ) |> 
  filter(int_report != "Not reported") |>  
  summarise(
    study_char = "Average group size",
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = mean(m_intensity, na.rm = TRUE),
    #SD = sd(m_intensity, na.rm = TRUE),
    
    range = paste0(min(m_intensity, na.rm = TRUE), "-",
                   max(m_intensity, na.rm = TRUE))
    
  ); avg_intevention_group_size_WQoL

# Number of interventions of each study
interventions_WQoL <- wellbeing_QoL|> 
 mutate(N_treatments = as.numeric(N_treatments)) |> 
  group_by(studyid)  |>  
  summarise(
    
    m_intensity = mean(N_treatments, na.rm = TRUE),
  
    es_n = n(),
    
    miss_int = sum(is.na(N_treatments)),
    
    int_report = if_else(miss_int == 0, "Reported", "Not reported"),
    
    .groups = "drop"
     
  ) |> 
  filter(int_report != "Not reported") |>  
  summarise(
    study_char = "Treatments",
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = mean(m_intensity, na.rm = TRUE),
  #  SD = sd(m_intensity, na.rm = TRUE),
    
    range = paste0(min(m_intensity, na.rm = TRUE), "-",
                   max(m_intensity, na.rm = TRUE))
    
  ); interventions_WQoL

# Treatment types 
treatment_types_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |> 
  summarise(
    treatment_type = unique(trt_type),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(treatment_type) |> 
  summarise(

    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    study_char = paste("%", treatment_type),
    
    Mean = Study/sum(Study),
   # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(treatment_type)); treatment_types_WQoL



# Implementation types 
implementation_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |> 
  summarise(
    implementation = unique(implementation),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(implementation) |> 
  summarise(
    Study = n_distinct(studyid),
    effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", implementation),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
  #  SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(implementation)); implementation_WQoL


intervention_characteristics_WQoL <- bind_rows(
  duration_WQoL, sessions_per_week_WQoL, 
  avg_intevention_group_size_WQoL, 
  interventions_WQoL, 
  treatment_types_WQoL
)

# Control group 
# Control types 
control_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |>  
  summarise(
    control = unique(control),
    es_n = n(),
    
    .groups = "drop"
    
  ) |>  
  group_by(control) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", control),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
    # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |>  
  select(-c(control)); control_WQoL

# Methodological features
# Average number of effect size per study
avg_es_study_WQoL <- 
  wellbeing_QoL |> 
  group_by(studyid) |> 
  summarise(
    
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  summarise(
    study_char = "Average n of es",
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = mean(es_n),
  #  SD = sd(es_n),
    
    range = paste0(min(es_n), "-", max(es_n))
    
  ); avg_es_study_WQoL



# Outcome and measurement characteristics
# Type of test 
test_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |>  
  summarise(
    test_type = unique(test_type),
    es_n = n(),
    
    .groups = "drop"
    
  ) |>  
  group_by(test_type) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", test_type),
    
    Mean = Study/sum(Study),
  #  SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(test_type)); test_WQoL

# Type of measurement
measure_type_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |>  
  summarise(
    measure_type = unique(measure_type),
    es_n = n(),
    
    .groups = "drop"
    
  ) |>  
  group_by(measure_type) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    study_char = paste("%", measure_type),
    
    Mean = Study/sum(Study),
  #  SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(measure_type)); measure_type_WQoL

outcome_measurement_WQoL <- bind_rows(
  test_WQoL, measure_type_WQoL
); outcome_measurement_WQoL
```

## Tables for Wellbeing and Quality of Life
```{r}
table_WQoL <- bind_rows(
  study_context_WQoL, design_WQoL, 
  study_participants_WQoL, 
  intervention_characteristics_WQoL, 
  control_WQoL, 
  avg_es_study_WQoL, 
  outcome_measurement_WQoL
)



table_WQoL_percent <- 
  table_WQoL |> 
  filter(str_detect(study_char, "%")) |> 
  select(-c(range)) |> 
  mutate(
    Mean = round(Mean, 3),
    
  ); table_WQoL_percent


table_WQoL_rest_desc <- 
  table_WQoL |> 
  filter(!str_detect(study_char, "%")) |> 
  mutate(
    
    across(Mean, ~ round(.x, 3))
    
  ); table_WQoL_rest_desc
```


# Descrptive tables: Social functioning (degree of impairment)
```{r}
social_functioning <- GBD_effect |> 
  filter(analysis_plan == "Social functioning (degree of impairment)")


# Study context
# Percent studies by countries
study_context_functioning <- social_functioning |> 
  group_by(studyid, cnt) |> 
  summarise(
    es_n = n(),
    
    .groups = "drop"
  ) |> 
  group_by(cnt) |>
  summarise(
    study_char = paste0("% ", unique(cnt)), 
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
   # SD = NA,
    
    range = "0-1",
    
    .groups = "drop"
  ) |> 
  select(-cnt); study_context_functioning

# Average number of participants per effect size 

participants_WQoL <- wellbeing_QoL |> 
  group_by(studyid) |> 
  summarise(
    study_avg_sample = mean(N_total),
    es_n = n(), 
    .groups = "drop"
  ) |> 
  summarise(
    study_char = "Number of particiapnts",
    
    Study = n_distinct(studyid), # Studies
    Effect_size = sum(es_n), # Effect size
    
    Mean = round(mean(study_avg_sample)),
  #  SD = round(sd(study_avg_sample)),
    
    range = paste0(min(study_avg_sample), "-", max(study_avg_sample))
    
  ); participants_WQoL



# Average size of the groups
group_size_WQoL <- wellbeing_QoL |> 
  group_by(studyid) |> 
  summarise(
    treat_SampS = mean(N_t),
    cont_SampS = mean(N_c),
    
    es_n = n(),
    
    .groups = "drop"
  ) |> 
  summarise(
    study_char = c("Intervention group", "Control group"),
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = c(mean(treat_SampS), mean(cont_SampS)),
   # SD = c(sd(treat_SampS), sd(cont_SampS)),
    
    range = c(
      paste0(min(treat_SampS), "-", round(max(treat_SampS))),
      paste0(min(cont_SampS), "-", round(max(cont_SampS)))
    )
    
  ); group_size_WQoL

# Number of samples per study 
samples_per_study_WQoL <- wellbeing_QoL |> 
  group_by(studyid) |> 
  summarise(
    samples = n_distinct(sample_id), 
    es_n = n(),
    
    .groups = "drop"
  ) |>
  summarise(
    study_char = "Samples per study",
    
    Study = sum(samples),  
    Effect_size = sum(es_n),  
    
    Mean = mean(samples), 
   # SD = sd(samples),  
    
    range = paste0(min(samples), "-", max(samples)),
    
    .groups = "drop"
  ); samples_per_study_WQoL


# Number of distinct studies in review

n_distinct(GBD_effect$studyid)

study_context_WQoL <- 
  bind_rows(
    study_context_WQoL,
    participants_WQoL,
 #   ESS,
    group_size_WQoL,
    samples_per_study_WQoL
    
); study_context_WQoL

# Study Design
# Proportion cluster randomized or RCT studies
study_design_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |> 
  summarise(
    design = unique(design),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(design) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", design),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
  #  SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |>  
  select(-c(design)); study_design_WQoL


# Randomization
study_randomization_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |>  
  summarise(
    randomization = unique(randomization),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(randomization) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", randomization),
    
    Mean = Study/sum(Study),
    #SD = NA,
    range = "0-1",
   ) |> 
  relocate(study_char) |>  
  select(-c(randomization)); study_randomization_WQoL

# Handling of clustering
clustering_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |> 
  summarise(
    clustering = unique(cluster_treatment[!is.na(cluster_treatment)]),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(clustering) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", clustering),
    
    Mean = Study/sum(Study),
   # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(clustering)); clustering_WQoL

# Analysis strategy 
analysis_strategy_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |> 
  summarise(
    analysis_strat = unique(analysis_strategy),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  filter(!is.na(analysis_strat)) |> 
  group_by(analysis_strat) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |>
  mutate(
    
    study_char = paste("%", analysis_strat),
    
    Mean = Study / sum(Study),
   # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |>  
  select(-c(analysis_strat)); analysis_strategy_WQoL

design_WQoL <- 
  bind_rows(
    study_design_WQoL,
    study_randomization_WQoL,
    clustering_WQoL,
    analysis_strategy_WQoL
); design_WQoL


# Study participants
# % Males in treatment and control group

male_per_WQoL <- 
  wellbeing_QoL |> 
  group_by(studyid) |>  
  summarise(
    
    t_male = mean(as.numeric(male_pct_t), na.rm = TRUE),
    c_male = mean(as.numeric(male_pct_c), na.rm = TRUE),
    
     es_n = sum(!is.na(male_pct_t)),
    
    .groups = "drop"
    
  ) |> 
  filter(es_n != 0) |> 
   summarise(
    study_char = c("Intervention group", "Control group"), 
    Study = n_distinct(studyid),  
    Effect_size = sum(es_n, na.rm = TRUE),
    
    Mean = c(mean(t_male, na.rm = TRUE), mean(c_male, na.rm = TRUE)), 
  #  SD = c(sd(t_male, na.rm = TRUE), sd(c_male, na.rm = TRUE)), 
    range = c(paste(min(t_male, na.rm = TRUE), "-", max(t_male, na.rm = TRUE)),  
              paste(min(c_male, na.rm = TRUE), "-", max(c_male, na.rm = TRUE)))
  ); male_per_WQoL

# Mean age
age_mean_WQoL <- 
  wellbeing_QoL |> 
  group_by(studyid) |> 
  summarise(
    
    t_age = mean(as.numeric(age_mean_t), na.rm = TRUE),
    c_age = mean(as.numeric(age_mean_c), na.rm = TRUE),
    
     es_n = sum(!is.na(age_mean_c)),
    
    .groups = "drop"
    
  ) |>  
  filter(es_n != 0) |> 
   summarise(
    study_char = c("Intervention group", "Control group"),  # Kategorier for hver gruppe
    Study = n_distinct(studyid),  
    Effect_size = sum(es_n, na.rm = TRUE),
    
    Mean = c(mean(t_age, na.rm = TRUE), mean(c_age, na.rm = TRUE)),  # Gennemsnit for hver gruppe
    #SD = c(sd(t_age, na.rm = TRUE), sd(c_age, na.rm = TRUE)),  # Standardafvigelse for hver gruppe
    range = c(paste(min(t_age, na.rm = TRUE), "-", max(t_age, na.rm = TRUE)),  # Range for hver gruppe
              paste(min(c_age, na.rm = TRUE), "-", max(c_age, na.rm = TRUE)))
  ); age_mean_WQoL

# Disorder type
disorder_type_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |> 
  summarise(
    disorder = unique(disorder_type),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(disorder) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", disorder),
    
    Mean = Study/sum(Study),
   # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(disorder)); disorder_type_WQoL


assesment_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |>  
  summarise(
    assessment = unique(assessment),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(assessment) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", assessment),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
    #SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(assessment)); assesment_WQoL

# Sample composition
sample_composition_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |> 
  summarise(
    composition = unique(sample_comp),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(composition) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", composition),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
  #  SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(composition)); sample_composition_WQoL

# Sample factors
sample_factors_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |> 
  summarise(
    sample_factors = unique(sample_factors),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(sample_factors) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", sample_factors),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
   # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(sample_factors)); sample_factors_WQoL


study_participants_WQoL <- 
  bind_rows(
    male_per_WQoL, age_mean_WQoL, 
   # disorder_type, 
    assesment_WQoL,
    sample_composition_WQoL,
    sample_factors_WQoL
); study_participants_WQoL


# Intervention characteristics 

# Duration of intervention
duration_WQoL <- 
  wellbeing_QoL |> 
  group_by(studyid) |>  
  summarise(
    
    m_duration = mean(duration_weeks, na.rm = TRUE),
  
    es_n = n(),
    
    miss_dur = sum(is.na(duration_weeks)),
    
    dur_report = if_else(miss_dur == 0, "Reported", "Not reported"),
    
    .groups = "drop"
     
  ) |>  
  filter(dur_report != "Not reported") |>  
  summarise(
    study_char = "Duration in weeks",
    
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = mean(m_duration, na.rm = TRUE),
 #   SD = sd(m_duration, na.rm = TRUE),
    
    range = paste0(min(m_duration, na.rm = TRUE), "-",
                   max(m_duration, na.rm = TRUE)),
  
    
  ); duration_WQoL

# Mean number of sessions per week

sessions_per_week_WQoL <- 
  wellbeing_QoL|> 
  mutate(sessions_per_week = as.numeric(sessions_per_week)) |> 
  group_by(studyid)  |>  
  summarise(
    
    m_intensity = mean(sessions_per_week, na.rm = TRUE),
  
    es_n = n(),
    
    miss_int = sum(is.na(sessions_per_week)),
    
    int_report = if_else(miss_int == 0, "Reported", "Not reported"),
    
    .groups = "drop"
     
  ) |> 
  filter(int_report != "Not reported") |>  
  summarise(
    study_char = "Number of sessions per week",
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = mean(m_intensity, na.rm = TRUE),
 #   SD = sd(m_intensity, na.rm = TRUE),
    
    range = paste0(min(m_intensity, na.rm = TRUE), "-",
                   max(m_intensity, na.rm = TRUE))
    
  ); sessions_per_week_WQoL

# Average group size in the treatment intervention
avg_intevention_group_size_WQoL <- 
  wellbeing_QoL|> 
  mutate(avg_group_size = as.numeric(avg_group_size)) |> 
  group_by(studyid)  |>  
  summarise(
    
    m_intensity = mean(avg_group_size, na.rm = TRUE),
  
    es_n = n(),
    
    miss_int = sum(is.na(avg_group_size)),
    
    int_report = if_else(miss_int == 0, "Reported", "Not reported"),
    
    .groups = "drop"
     
  ) |> 
  filter(int_report != "Not reported") |>  
  summarise(
    study_char = "Average group size",
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = mean(m_intensity, na.rm = TRUE),
    #SD = sd(m_intensity, na.rm = TRUE),
    
    range = paste0(min(m_intensity, na.rm = TRUE), "-",
                   max(m_intensity, na.rm = TRUE))
    
  ); avg_intevention_group_size_WQoL

# Number of interventions of each study
interventions_WQoL <- wellbeing_QoL|> 
 mutate(N_treatments = as.numeric(N_treatments)) |> 
  group_by(studyid)  |>  
  summarise(
    
    m_intensity = mean(N_treatments, na.rm = TRUE),
  
    es_n = n(),
    
    miss_int = sum(is.na(N_treatments)),
    
    int_report = if_else(miss_int == 0, "Reported", "Not reported"),
    
    .groups = "drop"
     
  ) |> 
  filter(int_report != "Not reported") |>  
  summarise(
    study_char = "Treatments",
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = mean(m_intensity, na.rm = TRUE),
  #  SD = sd(m_intensity, na.rm = TRUE),
    
    range = paste0(min(m_intensity, na.rm = TRUE), "-",
                   max(m_intensity, na.rm = TRUE))
    
  ); interventions_WQoL

# Treatment types 
treatment_types_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |> 
  summarise(
    treatment_type = unique(trt_type),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(treatment_type) |> 
  summarise(

    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    study_char = paste("%", treatment_type),
    
    Mean = Study/sum(Study),
   # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(treatment_type)); treatment_types_WQoL



# Implementation types 
implementation_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |> 
  summarise(
    implementation = unique(implementation),
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  group_by(implementation) |> 
  summarise(
    Study = n_distinct(studyid),
    effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", implementation),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
  #  SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(implementation)); implementation_WQoL


intervention_characteristics_WQoL <- bind_rows(
  duration_WQoL, sessions_per_week_WQoL, 
  avg_intevention_group_size_WQoL, 
  interventions_WQoL, 
  treatment_types_WQoL
)

# Control group 
# Control types 
control_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |>  
  summarise(
    control = unique(control),
    es_n = n(),
    
    .groups = "drop"
    
  ) |>  
  group_by(control) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", control),
    
    Mean = Study/n_distinct(GBD_effect$studyid),
    # SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |>  
  select(-c(control)); control_WQoL

# Methodological features
# Average number of effect size per study
avg_es_study_WQoL <- 
  wellbeing_QoL |> 
  group_by(studyid) |> 
  summarise(
    
    es_n = n(),
    
    .groups = "drop"
    
  ) |> 
  summarise(
    study_char = "Average n of es",
    
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
    Mean = mean(es_n),
  #  SD = sd(es_n),
    
    range = paste0(min(es_n), "-", max(es_n))
    
  ); avg_es_study_WQoL



# Outcome and measurement characteristics
# Type of test 
test_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |>  
  summarise(
    test_type = unique(test_type),
    es_n = n(),
    
    .groups = "drop"
    
  ) |>  
  group_by(test_type) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    
    study_char = paste("%", test_type),
    
    Mean = Study/sum(Study),
  #  SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(test_type)); test_WQoL

# Type of measurement
measure_type_WQoL <- wellbeing_QoL |>  
  group_by(studyid) |>  
  summarise(
    measure_type = unique(measure_type),
    es_n = n(),
    
    .groups = "drop"
    
  ) |>  
  group_by(measure_type) |> 
  summarise(
    Study = n_distinct(studyid),
    Effect_size = sum(es_n),
    
  ) |> 
  mutate(
    study_char = paste("%", measure_type),
    
    Mean = Study/sum(Study),
  #  SD = NA,
    range = "0-1",
    
   ) |> 
  relocate(study_char) |> 
  select(-c(measure_type)); measure_type_WQoL

outcome_measurement_WQoL <- bind_rows(
  test_WQoL, measure_type_WQoL
); outcome_measurement_WQoL
```

## Tables for Wellbeing and Quality of Life
```{r}
table_WQoL <- bind_rows(
  study_context_WQoL, design_WQoL, 
  study_participants_WQoL, 
  intervention_characteristics_WQoL, 
  control_WQoL, 
  avg_es_study_WQoL, 
  outcome_measurement_WQoL
)



table_WQoL_percent <- 
  table_WQoL |> 
  filter(str_detect(study_char, "%")) |> 
  select(-c(range)) |> 
  mutate(
    Mean = round(Mean, 3),
    
  ); table_WQoL_percent


table_WQoL_rest_desc <- 
  table_WQoL |> 
  filter(!str_detect(study_char, "%")) |> 
  mutate(
    
    across(Mean, ~ round(.x, 3))
    
  ); table_WQoL_rest_desc


## Print Table

```{r}

# Report table function --------------------------------------------------------------
report_table <- 
  function(table, file_name, format = "html_document", ...){
    
    if (!require(gt)){
      install.packages(gt)
    }  
    
    if (!is.data.frame(table)) stop("This function only takes object of class 'data.frame'") 
    
    if (missing(file_name)) stop("Please provide a name to the word file you want to generate. Use file_name")
    
    # Make if command with .Rmd     
    name <- paste0(file_name, ".Rmd")  
    
    if (length(unique(names(table))) !=  length(names(table))){
      
     output <- suppressMessages(tibble::tibble(table, .name_repair = "universal"))
      
    } else {
      
      output <- table
      
    }
    
    
    
    cat("---
title: \"Table output\"
output: html_document
---
           
\`\`\`{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gt)
\`\`\`


\`\`\`{r, echo=FALSE, results='asis', include=TRUE}

output |> gt()

\`\`\`", 
        file = name
    )
    #message(paste0("Saving to", getwd(), "/", "StudyReport.Rmd")) 
    message(paste("Rendering", name))  
    file_out <-  rmarkdown::render(name, output_format = format, quiet = TRUE, ...) 
    
    message(paste("Opening", name))  
    shell.exec(file_out)
    
    invisible(file_out)
    invisible(file.remove(name))
    
  }


```

```{r}

# Group data and calculate the distribution of reintergrational outcomes for each interventionstype
distribution_summary <- GBD_effect |> 
  filter(!str_detect(analysis_plan, "mental|used|hospi|Employment|Physical")) |> 
  group_by(trt_type, analysis_plan) |> 
  summarise(
    count = n(), 
    .groups = "drop"
  ) |> 
  group_by(trt_type) |> 
  mutate(
    total_outcomes = sum(count),  
    proportion = count / total_outcomes  
  ) |> 
  ungroup()


ggplot(distribution_summary, aes(x = trt_type, y = proportion, fill = analysis_plan)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(
    title = "Outcome Distribution by type of Intervention",
    x = "Intervention Type",
    y = "Proportion",
    fill = "Outcome Construct"
  ) +
  coord_flip()


ggplot(distribution_summary, aes(x = trt_type, y = proportion, fill = analysis_plan)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(
     title = "Outcome Distribution by type of Intervention",
    x = "Intervention Type",
    y = "Proportion",
    fill = "Outcome Construct"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```
