---
title: Effect size calculation for 'Group-based community interventions to support
  the social reintegration of marginalised adults with mental illness'
date: "Last updated `r format(Sys.time(), '%Y.%m.%d')`"
output: 
  html_document:
    toc: true
    code_folding: show
    code_download: true
bibliography: Group-based interventions.bib
link-citations: yes
fontsize: 11pt
spacing: single
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

options(pillar.sigfig = 4) # ensure tibble include 4 digits
options(tibble.width = Inf)
options(dplyr.print_min = 310)
options(scipen = 10)
options(dplyr.summarise.inform = FALSE) # Avoids summarize info from tidyverse

```

### Introduction 
This document contains effect size calculation for the Campbell systematic review 'Group-based community interventions to support the social reintegration of marginalised adults with mental illness' [@Dalgaard2022a]. 

### R package used for effect size calculation

```{r}
#devtools::install_github("MikkelVembye/VIVECampbell")

library(tidyverse)
#library(dplyr)
library(readxl)
library(writexl)
library(purrr)
library(VIVECampbell)

```

### ICC values used for cluster adjustment

```{r}
ICC_005 <- 0.05
ICC_01 <- 0.1
ICC_02 <- 0.2

ppcor_imp <- 0.5
R2_imp <- 0

```


## **Studies in meta-analysis**

### **Acarturk et al. [-@Acarturk2022]**
#### (Multi-level analysis and reported raw means, at baseline, post, and followup times)

To calculate pretest-adjusted effect sizes, we first estimate pre-post and pre-followup correlations from 
the reported results in "Treatment effect" section (p. 7)

```{r Acarturk_ppcor}

# _fu = followup

Acarturk_text_res <- 
  tibble(
    
    outcome = rep(c("HSCL-25", "PCL-5", "PSYCHLOPS"), each = 2),
    
    timing = rep(c("Posttest", "Followup"), 3),
    
    N = rep(c(41, 44, 19), c(2, 2, 2)), # Obtained from df(t)/2
    
    m_pre = rep(c(2.34, 1.77, 4.06), each = 2),
    sd_pre = rep(c(0.60, 0.86, 0.76), each = 2),
    
    m_post = c(
      2.15, 2.11, # HSCL-25
      1.43, 1.19, # PCL-5
      3.82, 3.45  # PSYCHLOPS
      
      ),
    
    sd_post = c(
      0.60, 0.59,
      0.79, 0.78,
      0.86, 1.32
      ),
    
    
    paired_t = c(
      2.43, 2.83,
      2.61, 4.45,
      1.01, 2.57
      )
    
  ) |> 
  mutate(
    
    ppcor = ((sd_pre^2*paired_t^2 + sd_post^2*paired_t^2) - (m_post - m_pre)^2 * N)/
      (2*sd_pre*sd_post*paired_t^2),
    
    .by = c(outcome, timing)
    
  ); Acarturk_text_res

```

Entering data from Table 2 (p. 7)

```{r Acarturk_data}

Acarturk2022 <- 
  tibble(
    
    outcome = rep(c("HSCL-25", "PCL-5", "PSYCHLOPS"), each = 4),
    
    timing = rep(c("Posttest", "Followup"), each = 2, n_distinct(outcome)),
    
    group = rep(c("gPM+", "Control"), n_distinct(outcome)*2),
    
    N = rep(c(24, 22), n_distinct(outcome)*2),
    
    m_pre = c(
        rep(c(2.37, 2.31), 2), # HSCL-25
        rep(c(1.84, 1.70), 2), # PCL-5
        rep(c(4.20, 3.92), 2)  # PSYCHLOPS
        
      ),
    
    sd_pre = c(
        
        rep(c(0.58, 0.64), 2),
        rep(c(0.88, 0.86), 2),
        rep(c(0.68, 0.84), 2)
      
      ),
    
    m_post = c(
      
      2.01, 2.28, 2.07, 2.14, 
      1.27, 1.59, 1.12, 1.26,
      3.82, 3.82, 3.67, 3.23
      
    ),
    
    sd_post = c(
      
      0.59, 0.58, 0.52, 0.43,
      0.70, 0.86, 0.85, 0.70,
      1.00, 0.63, 1.32, 1.63
      
    ),
    
    es_paper = rep(c(
      
      0.48, 0.12,
      0.40, 0.18,
      0, -0.30
      
      ),
      each = 2
    ),
    
    pval_paper = rep(c(
      
      0.109, 0.698,
      0.185, 0.553,
      0.996, 0.319
      
      ),
      each = 2
    )
    
    
    
  ); Acarturk2022


wide_format_Acarturk2022 <- 
  function(data, filter_value, trt_name, ctr_name){
  
  filter_func <- 
    function(data, filter_value, trt_name, ctr_name){
      
        
    dat <- data |> dplyr::filter(timing == filter_value)
    
    dat |> 
    dplyr::mutate(group = case_match(group, trt_name ~ "t", ctr_name ~ "c")) |> 
    tidyr::pivot_wider(
      names_from = group,
      names_glue = "{.value}_{group}",
      values_from = N:last_col()
    )
    
    
  }
  
  purrr::pmap_dfr(
    list(filter_value), ~ 
    filter_func(data = data, filter_value = .x,
                trt_name = trt_name, ctr_name = ctr_name)) |> 
    arrange(outcome)
  
  
}

Acarturk2022_wide <- 
  wide_format_Acarturk2022(
    data = Acarturk2022, 
    filter_value = c("Posttest", "Followup"),
    trt_name = "gPM+",
    ctr_name = "Control"
  ) |> 
  mutate(
    es_paper = es_paper_t,
    pval_paper = pval_paper_t
  ) |> 
  select(-c(es_paper_t:pval_paper_c))


```

Effect size calculation and cluster bias adjustment

```{r}

eta_acarturk_sqrt <- VIVECampbell::eta_1armcluster(
  N_total = 46, Nc = 22, avg_grp_size = 10, ICC = ICC_01,
  sqrt = TRUE
)

Acarturk2022_es <- 
  Acarturk2022 |>
  mutate(
    ppcor = rep(Acarturk_text_res$ppcor, each = 2)
  ) |> 
  summarise(
    
    effect_size = "SMD",
    sd_used = "Pooled posttest SD",
    
    study = "Acarturk et al. 2022",
    es_calc_method = "Raw diff-in-diffs",
    
    ppcor = ppcor[1],  
    ppcor_calc_method = "Calculated from study",
    
    R2 = NA,
    R2_calc_method = "Not relevant",
    
    N_t = N[1],
    N_c = N[2],
    
    N_tot = N_t + N_c, 
    
    df_ind = N_tot,
    
    n_covariates = 1,
    
    d_paper = es_paper[1],
    pval_paper = pval_paper[1],
    tval_paper = qnorm(pval_paper/2, lower.tail = FALSE),
    se_d_paper = d_paper/tval_paper,
    se_d_paper = if_else(se_d_paper == 0, sqrt(sum(1/N)) * eta_acarturk_sqrt, se_d_paper),
    vd_paper = se_d_paper^2,
    
    sd_pool = sqrt( sum((N-1)*sd_post^2)/ (N_tot-2) ),
    m_diff_post = (m_post[1] - m_post[2]) * -1,
    
    # Difference in differences measures
    diff_t = (m_post[1] - m_pre[1]) * -1,  
    diff_c = (m_post[2] - m_pre[2]) * -1,
    
    DD = diff_t - diff_c,
    
    d_posttest = m_diff_post/sd_pool, 
    vd_posttest = sum(1/N) + d_posttest^2/(2*df_ind),
    Wd_posttest = sum(1/N),
    
    d = DD/sd_pool,
    vd = 2*(1-ppcor) * sum(1/N) + d^2/(2*df_ind),
    Wd = 2*(1-ppcor) * sum(1/N),
    
    d_alt = d_paper,
    vd_alt = vd_paper,
    Wd_alt = vd_paper,
    
    J = 1 - 3/(4*df_ind-1),
    
    g_posttest = J * d_posttest,
    vg_posttest = sum(1/N) + g_posttest^2/(2*df_ind),
    Wg_posttest = Wd_posttest,
    
    g = J * d, 
    vg = 2*(1-ppcor) * sum(1/N) + g^2/(2*df_ind), 
    Wg = Wd,
    
    g_alt = J * d_alt,
    vg_alt = vd_alt,
    Wg_alt = vd_alt,
    
    .by = c(outcome, timing) 
    
  ) |> 
  rowwise() |> 
  mutate(
    
    # Average cluster size in treatment group
    # " eight to ten participants per group" (p. 1)
    avg_cl_size = 10, 
    avg_cl_type = "From study (p. 1)",
    
    # Imputed icc value
    icc = ICC_01,
    icc_type = "Imputed",
    
    # Find info about the function via ?VIVECampbell::gamma_1armcluster
    gamma_sqrt = VIVECampbell::gamma_1armcluster(
      N_total = N_tot, Nc = N_c, avg_grp_size = avg_cl_size, ICC = icc
      ),
    gamma_sqrt_icc005 = gamma_1armcluster(
      N_total = N_tot, Nc = N_c, avg_grp_size = avg_cl_size, ICC = ICC_005
      ),
    gamma_sqrt_icc02 = gamma_1armcluster(
      N_total = N_tot, Nc = N_c, avg_grp_size = avg_cl_size, ICC = ICC_02
      ),
    
    gt = g * gamma_sqrt,
    VIVECampbell::vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = icc, 
      g = gt, 
      model = "DiD",
      cluster_adj = FALSE,
      prepost_cor = ppcor,
      q = n_covariates
      ),
    
    gt_icc005 = g * gamma_sqrt_icc005,
    vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = ICC_005, 
      g = gt_icc005, 
      model = "DiD",
      cluster_adj = FALSE,
      prepost_cor = ppcor,
      q = n_covariates,
      add_name_to_vars = "_icc005",
      vars = vgt_icc005:Wgt_icc005
      ),
    
    gt_icc02 = g * gamma_sqrt_icc02,
    vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = ICC_02, 
      g = gt_icc02, 
      model = "DiD",
      cluster_adj = FALSE,
      prepost_cor = ppcor,
      q = n_covariates,
      add_name_to_vars = "_icc02",
      vars = vgt_icc02:Wgt_icc02
      ),
    
    gt_alt = g_alt * gamma_sqrt,
    vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = icc, 
      g = gt_alt, 
      model = "posttest",
      cluster_adj = TRUE,
      q = n_covariates,
      add_name_to_vars = "_alt",
      vars = vgt_alt:Wgt_alt
      ), 
    
    gt_alt_type = "Posttest reported in paper",

    gt_posttest = g_posttest * gamma_sqrt,
    VIVECampbell::vgt_smd_1armcluster(
      N_cl_grp = N_t,
      N_ind_grp = N_c,
      avg_grp_size = avg_cl_size,
      ICC = icc, 
      g = gt_posttest, 
      model = "posttest",
      cluster_adj = FALSE,
      add_name_to_vars = "_posttest",
      vars = vgt_posttest:Wgt_posttest
    )
    
) |> 
ungroup()

Acarturk2022_est <- 
  left_join(Acarturk2022_wide, Acarturk2022_es) |> 
  relocate(study) |> 
  mutate(
    vary_id = paste0(outcome, "/", timing)
  )

Acarturk2022_est

```


### **Barbic et al.[-@Acarturk2022]**
#### (Randomized trial reporting raw means at baseline and after treatment. Uses repeated ANOVA and does not account for clusting in treament)

Entering data from Table 3 (p. 495).

```{r}
Barbic2009 <- tibble(
  outcome = rep(c("Hope Index", "Empowerment Scale", "Quality of Life", "Recovery Assessment"), each = 2),
  group = rep(c("Recovery Workbook", "Control"), dplyr::n_distinct(outcome)),
  N = rep(c(16, 17), dplyr::n_distinct(outcome)),
  
  m_pre = c(
    37.13, 36.00, 
    55.93, 63.88, 
    20.34, 20.70, 
    163.75, 156.41),
  
   sd_pre = c(
    6.53, 5.36, 
    6.91, 6.91, 
    5.01, 4.13, 
    22.60, 14.22),
  
  m_post = c(
    38.93, 35.06, 
    14.93, 61.96, 
    21.60, 22.27, 
    168.81, 149.11),
  
  
  sd_post = c(
    5.34, 6.21, 
    10.43, 7.33, 
    3.35, 4.91, 
    20.11, 22.09)
)

Barbic2009

Barbic2009_wide <- 
  Barbic2009 |> 
    mutate(group = case_match(group, "Recovery Workbook" ~ "t", "Control" ~ "c")) |> 
    tidyr::pivot_wider(
      names_from = group,
      names_glue = "{.value}_{group}",
      values_from = N:last_col()
    ) |> 
  mutate(
# Based on the degrees of freedom value reported in Barbic et al. (2009),
# we cannot replicate the report F_values. Therefore, we do not use any F_values for 
# for the effect size correlation

  p_val_f = c(.05, .21, .96, .02), 
  df1 = 1, 
  df2 = 32,
  F_val = qf(p_val_f, df1 = df1, df2 = df2, lower.tail = FALSE)
  )
```

Effect size calculating, including cluster-bias correction
```{r}
Barbic2009_est <- 
  Barbic2009_wide |>
  mutate(
    analysis_plan = rep(
      c("Hope, Empowerment & Self-efficacy", "Wellbeing and Quality of Life", 
        "Hope, Empowerment & Self-efficacy/uses all"), 
      c(2, 1, 1))
  ) |> 
  rowwise() |> 
  mutate(
    
    F_val = if_else(outcome == "Empowerment Scale", 14.93, F_val), # Retrieved from (p. 495)
    
    effect_size = "SMD",
    sd_used = "Pooled posttest SD",
    
    study = "Barbic et al. 2009",
    main_es_calc_method = "Raw diff-in-diffs",
    
    ppcor = ppcor_imp,  
    ppcor_calc_method = "Imputed",
    
    R2 = NA_real_,
    R2_calc_method = "Not relevant",
    
    N_total = N_t + N_c,
    df_ind = N_total,
    
    # Calculate d post
    m_post = if_else(outcome != "Empowerment Scale", m_post_t - m_post_c, (m_post_t - m_post_c) * -1),
    sd_pool = sqrt(((N_t-1)*sd_post_t^2 + (N_c-1)*sd_post_c^2)/(N_t + N_c - 2)),  
    
    d_post = m_post/sd_pool, 
    vd_post = (1/N_t + 1/N_c) + d_post^2/df_ind,
    Wd_post = (1/N_t + 1/N_c),
    
    J = 1 - 3/(4*df_ind-1),
    
    g_post = J * d_post,
    vg_post = (1/N_t + 1/N_c) + g_post^2/df_ind,
    Wg_post = Wd_post,
    
    # Account for the fact that some outcomes are on different scales
    m_diff_t = if_else(outcome != "Empowerment Scale", m_post_t - m_pre_t, (m_post_t - m_pre_t) * -1),
    m_diff_c = if_else(outcome != "Empowerment Scale", m_post_c - m_pre_c, (m_post_c - m_pre_c) * -1),
    
    d_DD = (m_diff_t - m_diff_c)/sd_pool,
    vd_DD = 2*(1-ppcor) * (1/N_t + 1/N_c) + d_DD^2/df_ind,
    Wd_DD = 2*(1-ppcor) * (1/N_t + 1/N_c),
    
    g_DD = J * d_DD, 
    vg_DD = 2*(1-ppcor) * (1/N_t + 1/N_c) + g_DD^2/df_ind,
    Wg_DD = 2*(1-ppcor) * (1/N_t + 1/N_c),
    
    # Average cluster size in treatment group
    # "12 weekly two-hour group sessions with seven to nine participants." (p. 493)
    avg_cl_size = 8, 
    avg_cl_type = "From study (p. 493)",
    
    # Imputed icc value
    icc = ICC_01,
    icc_type = "Imputed",
    
    # Find info about the function via ?VIVECampbell::gamma_1armcluster
    gamma_sqrt = VIVECampbell::gamma_1armcluster(
      N_total = N_total, Nc = N_c, avg_grp_size = avg_cl_size, ICC = icc
      ),
    gamma_sqrt_icc005 = gamma_1armcluster(
      N_total = N_total, Nc = N_c, avg_grp_size = avg_cl_size, ICC = ICC_005
      ),
    gamma_sqrt_icc02 = gamma_1armcluster(
      N_total = N_total, Nc = N_c, avg_grp_size = avg_cl_size, ICC = ICC_02
      ),
    
    n_covariates = 1,
    
    # Cluster-adjusting g_post
    gt_post = g_post * gamma_sqrt,
    VIVECampbell::vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = icc, 
      g = gt_post, 
      model = "posttest",
      cluster_adj = FALSE,
      add_name_to_vars = "_post",
      vars = vgt_post:Wgt_post
      ),
    
    gt_DD = g_DD * gamma_sqrt,
    VIVECampbell::vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = icc, 
      g = gt_DD, 
      model = "DiD",
      cluster_adj = FALSE,
      prepost_cor = ppcor,
      q = n_covariates,
      add_name_to_vars = "_DD"
      ),
    
    gt_DD_icc005 = g_DD * gamma_sqrt_icc005,
    vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = ICC_005, 
      g = gt_DD_icc005, 
      model = "DiD",
      cluster_adj = FALSE,
      prepost_cor = ppcor,
      q = n_covariates,
      add_name_to_vars = "_DD_icc005",
      vars = vgt_DD_icc005:Wgt_DD_icc005
      ),
    
    gt_DD_icc02 = g_DD * gamma_sqrt_icc02,
    vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = ICC_02, 
      g = gt_DD_icc02, 
      model = "DiD",
      cluster_adj = FALSE,
      prepost_cor = ppcor,
      q = n_covariates,
      add_name_to_vars = "_DD_icc02",
      vars = vgt_DD_icc02:Wgt_DD_icc02
      ),
    
    vary_id = outcome
    

  ) |> 
  ungroup() |> 
  relocate(N_total, .after = N_c); Barbic2009_est


```


### **Bond et al. [-@Bond2015]**
#### (RCT - no treatment of clustering)

Entering data from Table 3 and 4 (p. 1032). Recovery Assessnebt Scale Scores are retrieved from the text on page 1032. 
In out analysis, we do not distinguish between different types of work as done in the paper. We, threrefore, amalgamate all work category. 
We code the control group as the our treatment group because the control is the group-based treatment, we are main concerned about
```{r}
# _t = Work choice

Bond2015_continious <- 
  tibble(
    outcome = c("Recovery Assessment Scale", "Days hospitalized"),
    N_t = 43,
    N_c = c(42, 41),
    m_post_t = c(4.14, 4.93),
    sd_post_t = c(0.49, 7.59),
    m_post_c = c(4.14, 10.44), 
    sd_post_c = c(0.57, 23.07),
    
    analysis_plan = c("Hope, Empowerment & Self-efficacy/uses all", "Psychiatric hospitalization"),
    
    main_effect_size = "SMD",
    sd_used = "Pooled posttest SD",
    
    study = "Bond et al. 2015",
    main_es_calc_method = "Posttest means",
    
    ppcor_calc_method = "Not relevant",
    R2_calc_method = "Not relevant",
    
    N_total = N_t + N_c,
    df_ind = N_total,
    
    # Calculate d post
    m_post = if_else(outcome != "Days hospitalized", m_post_t - m_post_c, (m_post_t - m_post_c) * -1),
    sd_pool = sqrt(((N_t-1)*sd_post_t^2 + (N_c-1)*sd_post_c^2)/(N_t + N_c - 2)),
    
    d_post = m_post/sd_pool, 
    vd_post = (1/N_t + 1/N_c) + d_post^2/df_ind,
    Wd_post = (1/N_t + 1/N_c),
    
    J = 1 - 3/(4*df_ind-1),
    
    g_post = J * d_post,
    vg_post = (1/N_t + 1/N_c) + g_post^2/df_ind,
    Wg_post = Wd_post,
    
    # Cluster bias correction
    # Average cluster size in treatment group
    # "Classes were scheduled weekly at two conveniently located sites" (p. 1029)
    # Assuming two class in the Work Choice group is 44/2 = 22
    avg_cl_size = 22, 
    avg_cl_type = "Guessed from study",
    
    # Imputed icc value
    icc = ICC_01,
    icc_type = "Imputed",
    
    # Find info about the function via ?VIVECampbell::gamma_1armcluster
    gamma_sqrt = VIVECampbell::gamma_1armcluster(
      N_total = N_total, Nc = N_c, avg_grp_size = avg_cl_size, ICC = icc
      ),
    
    gamma_sqrt_icc005 = gamma_1armcluster(
      N_total = N_total, Nc = N_c, avg_grp_size = avg_cl_size, ICC = ICC_005
      ),
    gamma_sqrt_icc02 = gamma_1armcluster(
      N_total = N_total, Nc = N_c, avg_grp_size = avg_cl_size, ICC = ICC_02
      ),
    
    gt_post = g_post * gamma_sqrt,
    VIVECampbell::vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = icc, 
      g = gt_post, 
      model = "posttest",
      cluster_adj = FALSE,
      add_name_to_vars = "_post",
      vars = vgt_post:adj_value_post
      ),
    
    gt_post_icc005 = g_post * gamma_sqrt_icc005,
    vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = ICC_005, 
      g = gt_post_icc005, 
      model = "posttest",
      cluster_adj = FALSE,
      add_name_to_vars = "_post_icc005",
      vars = vgt_post_icc005:Wgt_post_icc005
      ),
    
    gt_post_icc02 = g_post * gamma_sqrt_icc02,
    vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = ICC_02, 
      g = gt_post_icc02, 
      model = "posttest",
      cluster_adj = FALSE,
      add_name_to_vars = "_post_icc02",
      vars = vgt_post_icc02:Wgt_post_icc02
      ),
    
    vary_id = outcome
    
  )

Bond2015_binary <- 
  tibble(
    outcome = c("Employment", "Risk of Psychiatric Hospitalization"),
    N_t = c(43, 42), # See note a in Table for sample size of Table 4 (i.e., 42, 40, respectively)
    N_c = c(42, 40),
    A = c(13, 12), 
    B = c(30, 31),  
    C = c(20, 11),
    D = c(22, 30),
    
    analysis_plan = c("Employment", "Psychiatric hospitalization"),
    
    main_effect_size = "OR",
    sd_used = "Not relevant",
    
    study = "Bond et al. 2015",
    main_es_calc_method = "Raw events",
    
    ppcor_calc_method = "Not relevant",
    R2_calc_method = "Not relevant",
    
    N_total = N_t + N_c,
    
    p_t = A/N_t,
    p_c = C/N_c,
    
    RD = p_t - p_c,
    vRD = (A*B)/N_t^3 + (C*D)/N_c^3,
    
    # Average cluster size in treatment group
    # "Classes were scheduled weekly at two conveniently located sites" (p. 1029)
    # Assuming two class in the Work Choice group is 44/2 = 22
    avg_cl_size = 22, 
    avg_cl_type = "Guessed from study",
    
    # Imputed icc value
    icc = ICC_01,
    icc_type = "Imputed",
    
    # OR calculation and cluster bias adjustment
    VIVECampbell::OR_calc(
      A = A, B = B, C = C, D = D, 
      ICC = icc, avg_cl_size = avg_cl_size, n_cluster_arms = 1
    ),
    
    # Calculating the sampling variance of the odds ratio based on ICC = 0.05
    OR_calc(
      A = A, B = B, C = C, D = D, 
      ICC = ICC_005, avg_cl_size = avg_cl_size, n_cluster_arms = 1,
      add_name_to_vars = "_icc005", vars = DE_icc005:vln_OR_C_icc005
    ),
    
    # Calculating the sampling variance of the odds ratio based on ICC = 0.2
    OR_calc(
      A = A, B = B, C = C, D = D, 
      ICC = ICC_02, avg_cl_size = avg_cl_size, n_cluster_arms = 1,
      add_name_to_vars = "_icc02", vars = DE_icc02:vln_OR_C_icc02
    ),
    
    vary_id = outcome
    
)

Bond2015_est <- bind_rows(Bond2015_continious, Bond2015_binary)
Bond2015_est
```


### **Cano-Vindel et al. [-@Cano-Vindel2022]**

```{r}
#Insert Jakobs codes
```

### **Craigie & Nathan [-@Craigie2009]**
#### (No randmoized studie, with a pre-posttest design with adjusting for clustering in treatment)

Entering data from Table 2 and Treatment Format $\times$ Time interaction estimate from text results reported on pages 307-08

```{r}
Craigie2009 <- tibble(
  analysis = rep(c(
    "ITT",
    "Completers"), each = 6),
  
  outcome = rep(c(
  "BDI_II", 
  "BAI",
  "Q_LES_Q"), each = 2,2),
  
  group = rep(c(
    "Individual",
    "Group"), each = 1, 6), 
  
  N = c(rep(c(116, 240), each = 1,3),
        rep(c(77, 157), each = 1,3)
        
  ),
  
  # pre-treatment means 
  m_pre = c( 
    # Intention to treat
    30.0, 31.3, # BDI-II
    21.1, 20.2, # BAI 
    43.2, 42.3, # Q-LES-Q
    # Completers (treatment-on-treated)
    30.8, 30.7,
    20.7, 19.6,
    46.4, 42.9
  ), 
  
  # pre-treatment standard deviation 
  sd_pre = c(
    # Intention to treat
    10.4, 11.2,
    12.2, 11.3,
    14.7, 14.1,
    # Completers (treatment-on-treated)
    10.3, 11.1,
    12.0, 11.0,
    13.5, 13.8
  ),
  
  # post-treatment means
  m_post = c(
    # Intention to treat
    16.3, 20.9,
    12.9, 15.6,
    52.3, 50.8,
    # Completers (treatment-on-treated)
    11.7, 17.7,
    9.2, 13.7,
    62.7, 55.3
  ),
  
  # post-treatment means 
  sd_post = c(
    # Intention to treat
    12.2, 13.6,
    11.2, 11.4,
    19.9, 17.9,
    # Completers (treatment-on-treated)
    9.9, 12.4,
    8.3, 10.7,
    14.7, 15.8
  ),
  
  F_within = c(
    129.79, 187.21,
    64.96, 56.00,
    42.27, 79.70,
    
    192.23, 200.75, 
    86.27, 61.57,
    62.45, 101.19
  ),
  
  # From Wilson (2016)
  r = ((sd_pre^2*F_within + sd_post^2*F_within) - 
        (m_post-m_pre)^2 * N)/ (2 * sd_pre*sd_post*F_within),
    
  # For pooling of correlation coefficients 
  z = 0.5 * log( (1+r)/(1-r) ),
  v = 1/(N-3)
  
) 
```

Effect size calculation
```{r}
# Calculating preposttest-correlations across groups
ppcors_Craigie2009 <- 
  Craigie2009 |> 
  summarise(
    M = sum(v*z)/sum(v),
    ppcor = (exp(2*M)-1)/(exp(2*M)+1),
    ppcor_calc_method = "From study (t^2 = F)",
    .by = c(analysis, outcome)
  )

ppcors_Craigie2009  

Craigie2009_est <- 
  Craigie2009 |> 
  mutate(group = case_match(group, "Group" ~ "t", "Individual" ~ "c")) |> 
    tidyr::pivot_wider(
      names_from = group,
      names_glue = "{.value}_{group}",
      values_from = N:last_col()
    ) |> 
  left_join(ppcors_Craigie2009) |> 
  mutate(
    F_val = c(
      5.96, 9.84, 0.17, # (p. 307 left side bottom)
      13.86, 16.96, 2.74 # (p. 308 right side top)
    ),
    
  R2 = NA_real_,
  R2_calc_method = "Not relevant",
  
  N_total = N_t + N_c,
  df_ind = N_total,
  
  # Calculate d post
  m_post = if_else(outcome == "Q_LES_Q", m_post_t - m_post_c, (m_post_t - m_post_c) * -1),
  sd_pool = sqrt(((N_t-1)*sd_post_t^2 + (N_c-1)*sd_post_c^2)/(N_t + N_c - 2)),  
  
  d_post = m_post/sd_pool, 
  vd_post = (1/N_t + 1/N_c) + d_post^2/df_ind,
  Wd_post = (1/N_t + 1/N_c), 
  
  J = 1 - 3/(4*df_ind-1),
    
  g_post = J * d_post,
  vg_post = (1/N_t + 1/N_c) + g_post^2/df_ind,
  Wg_post = Wd_post,
  
  # Account for the fact that some outcomes are on different scales
  m_diff_t = if_else(outcome == "Q_LES_Q", m_post_t - m_pre_t, (m_post_t - m_pre_t) * -1),
  m_diff_c = if_else(outcome == "Q_LES_Q", m_post_c - m_pre_c, (m_post_c - m_pre_c) * -1),
    
  d_DD = (m_diff_t - m_diff_c)/sd_pool,
  vd_DD = d_DD^2/F_val + d_DD^2/df_ind,
  Wd_DD = d_DD^2/F_val,
  
  g_DD = J * d_DD, 
  vg_DD = g_DD^2/F_val + g_DD^2/df_ind,
  Wg_DD = g_DD^2/F_val
    
  ) |> 
  rowwise() |> 
  mutate(
    
    # Average cluster size in treatment group
    # "groups consisted of between 5 to 12 patients" p. 306
    avg_cl_size = 8.5, 
    avg_cl_type = "From study (p. 305)",
    
    # Imputed icc value
    icc = ICC_01,
    icc_type = "Imputed",
    
    # Find info about the function via ?VIVECampbell::gamma_1armcluster
    gamma_sqrt = VIVECampbell::gamma_1armcluster(
      N_total = N_total, Nc = N_c, avg_grp_size = avg_cl_size, ICC = icc
      ),
    gamma_sqrt_icc005 = gamma_1armcluster(
      N_total = N_total, Nc = N_c, avg_grp_size = avg_cl_size, ICC = ICC_005
      ),
    gamma_sqrt_icc02 = gamma_1armcluster(
      N_total = N_total, Nc = N_c, avg_grp_size = avg_cl_size, ICC = ICC_02
      ),
    
    n_covariates = 1,
    
    # Cluster-adjusting g_post
    gt_post = g_post * gamma_sqrt,
    VIVECampbell::vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = icc, 
      g = gt_post, 
      model = "posttest",
      cluster_adj = FALSE,
      add_name_to_vars = "_post",
      vars = vgt_post:Wgt_post
      ),
    
    gt_DD = g_DD * gamma_sqrt,
    VIVECampbell::vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = icc, 
      g = gt_DD, 
      model = "DiD",
      cluster_adj = FALSE,
      F_val = F_val,
      q = n_covariates,
      add_name_to_vars = "_DD"
      ),
    
    gt_DD_icc005 = g_DD * gamma_sqrt_icc005,
    vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = ICC_005, 
      g = gt_DD_icc005, 
      model = "DiD",
      cluster_adj = FALSE,
      F_val = F_val,
      q = n_covariates,
      add_name_to_vars = "_DD_icc005",
      vars = vgt_DD_icc005:Wgt_DD_icc005
      ),
    
    gt_DD_icc02 = g_DD * gamma_sqrt_icc02,
    vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = ICC_02, 
      g = gt_DD_icc02, 
      model = "DiD",
      cluster_adj = FALSE,
      F_val = F_val,
      q = n_covariates,
      add_name_to_vars = "_DD_icc02",
      vars = vgt_DD_icc02:Wgt_DD_icc02
      ),
    
    vary_id = paste0(analysis, "/", outcome)
    
  ) |> 
  ungroup(); Craigie2009_est


```


### **Gestel-Timmermans et al. [-@VanGestel-Timmermans2012]**
#### (Multi-level analysis to handle clustering)

Missing data analysis to support the  RoB 2 D4 assessment 

```{r}
# Testing missing 

Timmermans_sample_size_dat <-
  tibble(
    
    outcome = rep(c("Empoverment", "Hope", "Quality", "Self-e", "Loneliness"), each = 4),
    timing = rep(c("3 months", "6 months"), each = 2, n_distinct(outcome)),
    #measure = rep(c("post", "followup"), each = 2, n_distinct(outcome)),
    group = rep(c("Treatment", "Control"), 10),
    
    N_start = rep(rep(c(168, 165), 10)),
    
    N_actual = c(
      136, 117, 121, 99,
      132, 118, 120, 97,
      124, 114, 111, 97,
      134, 116, 121, 100,
      138, 122, 125, 102
    )
    
); Timmermans_sample_size_dat
```

Missingness analysis

```{r}
Timmermans_missingness <- 
  Timmermans_sample_size_dat |> 
  summarise(
    N_start_total = sum(N_start),
    N_actual_total = sum(N_actual),
    
    #percent_missing_total = round(mean(percent_missing)),
    
    percent_missing_total = round((1 - (N_actual_total/N_start_total)) * 100),
    
    RoB_D3_assess = case_when(
      percent_missing_total >= 25 ~ "High",
      percent_missing_total < 25 ~ "Some concerns",
      TRUE ~ NA_character_
    ),
    
    .by = c(outcome, timing)
  )

Timmermans_missingness 
```

Data is retrieved from Tables 2 & 3 (p. 58) 

```{r}

Timmermans2012 <- 
  Timmermans_sample_size_dat |> 
  rename(N =  N_actual) |> 
  mutate(
    
    #From Table 2 (p. 58)
    
    m_pre = c(
      rep(c(3.40, 3.37), 2), # Empowerment
      rep(c(2.78, 2.76), 2), # Hope
      rep(c(4.32, 4.23), 2), # Quality of life
      rep(c(4.38, 4.33), 2), # Self-efficacy beliefs
      rep(c(6.40, 6.87), 2)  # Loneliness
    ),
    
    sd_pre = c(
      rep(c(0.49, 0.51), 2), # Empowerment
      rep(c(0.47, 0.48), 2), # Hope
      rep(c(0.88, 1), 2),    # Quality of life
      rep(c(0.82, 0.89), 2), # Self-efficacy beliefs
      rep(c(3.56, 3.40), 2)  # Loneliness
    ),
    
    m_post = c(
      
      3.55, 3.38, 3.59, 3.40, # Empowerment
      2.91, 2.79, 2.97, 2.73, # Hope
      4.49, 4.36, 4.63, 4.39, # Quality of life
      4.65, 4.35, 4.71, 4.4,  # Self-efficacy beliefs
      5.89, 6.27, 3.87, 3.68  # Loneliness
      
    ),
    
    sd_post = c(
      
      0.48, 0.53, 0.50, 0.56,
      0.47, 0.53, 0.46, 0.48,
      0.96, 1.07, 0.97, 1.05,
      0.81, 0.97, 0.93, 0.88,
      3.61, 3.55, 3.87, 3.68
      
    ),
    
    es_paper = rep(
      c(
        0.27, 0.36, 
        0.25, 0.48,
        0.03, 0.15,
        0.27, 0.23, 
        -0.04, 0.15
      ),
      each = 2
    ),
    
    # From Table 3 (p. 58)
    
    b_adj = c(
      .12, .021, .13, .046,   #Empowerment
      .10, .038, .17, .004,   #Hope
      .064, .11, .11, .15,    #Quality of life
      .23, .064, .21, .14,    #Self-efficacy beliefs
      .066, -.65, -.34, -.49  #Loneliness
      
    ),
    
    pval_b_adj = c(
      .016, .55, .012, .24,  #Empowerment
      .039, .28, .001, .91,  #Hope
      .471, .09, .24, .025,  #Quality of life
      .010, .31, .026, .042, #Self-efficacy beliefs
      .85, .008, .35, .07    #Loneliness
      
      ),
    
    ci_l_b_adj = c(
      .022, -.05, .026, -.025,
      NA, -.030, .026, -.025,
      -.11, -.016, -.071, 0.020,
      .059, -.062, .027, .006,
      -.60, -1.14, -1.05, -1.02
    ),
    
    ci_u_b_adj = c(
      .22, .092, .23, .12,
      NA, .11, .23, .12, 
      .23, .24, .29, .28,
      .40, .19, .39, .27,
      .74, -.16, .37, .042
    ),
    
    tval_b_adj = qt(pval_b_adj/2, df = N-2, lower.tail = FALSE),
    se_b_adj = b_adj/tval_b_adj
    
  ); Timmermans2012 


wide_format_Timmermans2012 <- function(data, filter){
  
  filter_func <- function(data, filter){
    
    dat <- data |> dplyr::filter(timing != filter)
    
    dat |> 
    dplyr::mutate(group = case_match(group, "Treatment" ~ "t", "Control" ~ "c")) |> 
    tidyr::pivot_wider(
      names_from = group,
      names_glue = "{.value}_{group}",
      values_from = N_start:dplyr::last_col()
    )
    
    
  }
  
  purrr::pmap_dfr(list(filter), ~ filter_func(data = data, filter = .x )) |> 
    arrange(outcome)
  
  
}

# Continue from here

Timmermans2012_wide <- 
wide_format_Timmermans2012(data = Timmermans2012, filter = c("6 months", "3 months"))

rm(wide_format_Timmermans2012)

```

Effect sizes calculation

```{r}

Timmermans2012_es <- 
  Timmermans2012 |>
  summarise(
    
    effect_size = "SMD",
    sd_used = "Pooled posttest SD",
    
    study = "Timmermans et al. 2012",
    es_calc_method = "Pretest adj. means",
    
    ppcor = .76,  
    ppcor_calc_method = "From study (p. 57)",
    
    R2 = NA,
    R2_calc_method = "Not relevant - calculated from SE(b)",
    
    N_t = N[1],
    N_c = N[2],
    
    N_tot = N_t + N_c, 
    
    df_ind = N_tot,
    
    n_covariates = 1,
    
    sd_pool = sqrt( sum((N-1)*sd_post^2)/ (N_tot-2) ),
    m_diff_post = m_post[1] - m_post[2],
    
    # Pretest adjusted means
    b_adj = b_adj[1] - b_adj[2],
    
    # Difference in differences measures
    diff_t = m_post[1] - m_pre[1],  
    diff_c = m_post[2] - m_pre[2],
    
    DD = diff_t - diff_c,
    
    d_paper = es_paper[1],
    
    # Converting Loneliness measure since "Possible scores range from 0 to 11, 
    # with higher scores indicating more loneliness." (p. 58)
    d_posttest = if_else(unique(outcome) == "Loneliness", m_diff_post/sd_pool * -1, m_diff_post/sd_pool),
    vd_posttest = sum(1/N) + d_posttest^2/(2*df_ind),
    Wd_posttest = sum(1/N),
    
    d = if_else(unique(outcome) == "Loneliness", b_adj/sd_pool * -1, b_adj/sd_pool),
    vd = sum((se_b_adj/sd_pool)^2) + d^2/(2*df_ind),
    #vd_test = sum(1/N) + d^2/(2*df_ind),
    Wd = sum((se_b_adj/sd_pool)^2),
    #Wd_test = sum(1/N),
    
    d_alt = if_else(unique(outcome) == "Loneliness", DD/sd_pool * -1, DD/sd_pool),
    vd_alt = 2*(1-ppcor) * sum(1/N) + d_alt^2/(2*df_ind),
    Wd_alt = 2*(1-ppcor) * sum(1/N),
    
    J = 1 - 3/(4*df_ind-1),
    
    g_posttest = J * d_posttest,
    vg_posttest = sum(1/N) + g_posttest^2/(2*df_ind),
    Wg_posttest = Wd_posttest,
    
    g = J * d, 
    vg = sum((se_b_adj/sd_pool)^2) + g^2/(2*df_ind), 
    Wg = Wd,
    
    g_alt = J * d_alt,
    vg_alt = 2*(1-ppcor) * sum(1/N) + g_alt^2/(2*df_ind),
    Wg_alt = Wd_alt,
    
    
    .by = c(outcome, timing) 
    
    
  ) |> 
  rowwise() |> 
  mutate(
    
    # Average cluster size in treatment group
    # "was 7.0±2.1 (range of three to 12)" (p. 57)
    avg_cl_size = 7, 
    avg_cl_type = "From study (p. 57)",
    
    # Imputed icc value
    icc = 0.06,
    icc_type = "From study (p. 56)",
    
    # Find info about the function via ?VIVECampbell::gamma_1armcluster
    gamma_sqrt = VIVECampbell::gamma_1armcluster(
      N_total = N_tot, Nc = N_c, avg_grp_size = avg_cl_size, ICC = icc
      ),
    
    gt = g * gamma_sqrt,
    VIVECampbell::vgt_smd_1armcluster(
      N_cl_grp = N_t,
      N_ind_grp = N_c,
      avg_grp_size = avg_cl_size,
      ICC = icc, 
      g = gt, 
      model = "std_reg_coef",
      cluster_adj = TRUE,
      SE_std = sqrt(Wg)
    ),
    
    gt_alt = g_alt * gamma_sqrt,
    VIVECampbell::vgt_smd_1armcluster(
      N_cl_grp = N_t,
      N_ind_grp = N_c,
      avg_grp_size = avg_cl_size,
      ICC = icc, 
      g = gt_alt, 
      model = "DiD",
      cluster_adj = FALSE,
      prepost_cor = ppcor,
      add_name_to_vars = "_alt",
      vars = vgt_alt:Wgt_alt
    ),
    
    gt_alt_type = "DiD from raw means",
    
    gt_posttest = g_posttest * gamma_sqrt,
    VIVECampbell::vgt_smd_1armcluster(
      N_cl_grp = N_t,
      N_ind_grp = N_c,
      avg_grp_size = avg_cl_size,
      ICC = icc, 
      g = gt_posttest, 
      model = "posttest",
      cluster_adj = FALSE,
      add_name_to_vars = "_posttest",
      vars = vgt_posttest:Wgt_posttest
    )

    
    
  ) |> 
  ungroup()

# Timmermans2012_es

Timmermans2012_est <- 
  left_join(Timmermans2012_wide, Timmermans2012_es) |> 
  select(-c(es_paper_c, es_paper_t)) |> 
  mutate(vary_id = paste0(outcome, "/", timing))


#clubSandwich::impute_covariance_matrix(
#  vi = Timmermans2012_est$vgt,
#  cluster = Timmermans2012_est$study,
#  r = Timmermans2012_est$ppcor,
#  smooth_vi = FALSE
#)

```


### **Wuthrich & Rapee [-@Wuthrich2013] and Smith et al. [-@Smith2021]**
#### (Accounts for clustering via the use of mixed-effects models/multi-level models)


Entering data from Table 2 (p. 445). Sample size information is retrieved from Table 1 (p. 442). 

```{r Wuthrich20132021dat}
# Calculate paired t-test statistics to obtain pre-posttest score correlation estimates

#-----------------------------------------------------------------
# OUTCOME ANCRONYMS AND FULL NAMES
#-----------------------------------------------------------------
# GDS = Geriatric Depression Scale
# CES-D = The Centre for Epidemiological Studies Depression Scale (loneliness only item used)
# GAI = Geriatric Anxiety Inventory
# PSWQ = The Penn State Worry Questionnaire
# SF12 = The Short Form 12 version 1 Mental Health Subscale
#-----------------------------------------------------------------


# F-stats from the interaction between time and group for mean
# It was uncertain whether we could use these estimates. Therefore, we didn't use
# the reported F-statistics. 
F_stat_Wuthrich <- 
  tibble(
    
    year = c(13, 21, 21, 13, 21, 13, 13, 13),
    
    outcome = c(
      "Primary problem", 
      "Anxiety", 
      "Depression", 
      "GDS", 
      "Loneliness (CES-D 14)", 
      "GAI", 
      "PSWQ", 
      "SF12"),
    
    df1 = 1,
    df2 = c(
      
      47.95,  # Primary problem severity (2013, p. 783)
      49.603, # Anxiety disorder severity (2021, p. 444)
      45.451, # Depressive disorder severity [Mood] (2021, p. 444)
      50.88,  # GDS (2013, p. 783)
      40.609, # Loneliness (2021, p. 444)
      55.65,  # GAI (2013, p. 783)
      54.95,  # PSWQ (2013, p. 783)
      51.39   # SF15 (2013, p. 783)
      
      ),
    F_val = c(
      
      17.36, 
      17.858,
      30.884,
      8.86,
      7.070,
      7.4,
      0.57,
      qf(.988, df1 = 1, df2 = df2[8], lower.tail = FALSE)
      
    ),
    
    pval_reported = c(
      
      pf(F_val[1], df1 = 1, df2 = df2[1], lower.tail = FALSE),
      pf(F_val[2], df1 = 1, df2 = df2[2], lower.tail = FALSE),
      pf(F_val[3], df1 = 1, df2 = df2[3], lower.tail = FALSE),
      .004,
      .011,
      .009,
      .452,
      .988
      
    )
  
)

F_stat_Wuthrich

## emm = estimated marginal means

Wuthrich2013_2021_smd <- 
  tibble(
    
    outcome = rep(
      c("Primary problem", 
        "Anxiety", 
        "Depression", 
        "GDS", 
        "Loneliness (CES-D 14)",
        "GAI",
        "PSWQ",
        "SF12"
        ), 
      each = 2),
    
    group = rep(c("CBT", "Waitlist"), n_distinct(outcome)),
    
    N_start = rep(c(27, 35), n_distinct(outcome)), # From Table 2, 2013, p. 783
    
    N = rep(c(27, 35), n_distinct(outcome)), # From Table 2, 2013, p. 783
    
    emm_pre = c(
      
      6.33, 5.81,    # ADIS primary disorder severity (from Table 3, 2013, p. 784)
      5.2, 4.58,     # ADIS mean anxiety disorder severity (from Table 2, 2021, p. 445)
      5.48, 4.98,    # ADIS depressive disorder severity (from Table 2, 2021, p. 445)
      18.14, 16.35,  # Geriatric Depression Scale (from Table 3, 2013, p. 784)
      1.59, 1.36,    # Loneliness (CES-D item 14) (from Table 2, 2021, p. 445)
      11.59, 9.48,   # Geriatric Anxiety Inventory (from Table 3, 2013, p. 784)
      53.62, 49.27,  # Penn State Worry Questionnaire (from Table 3, 2013, p. 784) 
      37.09, 38.45   # Short Form-12 (Mental) (from Table 3, 2013, p. 784)
      
    ),
    
    emm_post = c(
      
      3.46, 5.15,   # ADIS primary disorder severity (from Table 3, 2013, p. 784)
      2.68, 4.01,   # ADIS mean anxiety disorder severity (from Table 2, 2021, p. 445)
      2.02, 4.25,   # ADIS depressive disorder severity (from Table 2, 2021, p. 445)
      9.21, 14.38,  # Geriatric Depression Scale (from Table 3, 2013, p. 784)
      .593, 1.24,   # Loneliness (CES-D item 14) (from Table 2, 2021, p. 445)
      5.84, 8.33,   # Geriatric Anxiety Inventory (from Table 3, 2013, p. 784)
      46.54, 47.24, # Penn State Worry Questionnaire (from Table 3, 2013, p. 784)
      47.79, 43.56  # Short Form-12 (Mental) (from Table 3, 2013, p. 784)
      
    ),
    
    sd_pre = c(
      
      0.653, 1.16,  # ADIS primary disorder severity (from Table 2, 2013, p. 783)
      0.74, 1.07,   # ADIS mean anxiety disorder severity (from Table 1, 2021, p. 442)
      1.05, 1.27,   # ADIS depressive disorder severity (from Table 1, 2021, p. 442)
      6.18, 5.99,   # Geriatric Depression Scale (from Table 2, 2013, p. 783)
      0.82, 0.97,   # Loneliness (CES-D item 14)  (from Table 1, 2021, p. 442)
      4.72, 5.43,   # Geriatric Anxiety Inventory (from Table 2, 2013, p. 783)
      12.39, 13.06, # Penn State Worry Questionnaire (from Table 2, 2013, p. 783)
      9.22, 6.69    # Short Form-12 (Mental) (from Table 2, 2013, p. 783)
      
    ),
    
    # Number of controlled covariates
    q = rep(c(2, 4, 4, 2, 4, rep(2, 3)), each = 2)
    
  )

Wuthrich2013_2021_smd

Wuthrich2013_2021_wide <- 
  Wuthrich2013_2021_smd |>
  select(-q) |> 
  mutate(group = case_match(group, "CBT" ~ "t", "Waitlist" ~ "c")) |> 
  pivot_wider(
    names_from = group,
    values_from = N_start:sd_pre
  )

#Wuthrich2013_2021_wide
```

Calculating effect sizes and conducting a small number of clusters correction, as suggested by WWC [-@WWC_clusterbias].

```{r Wuthrich20132021SMDcalc}

Wuthrich2013_2021_es_smd <- 
  Wuthrich2013_2021_smd |> 
  summarise(
    
    effect_size = "SMD",
    sd_used = "Pooled pretest SD",
    
    study = "Wuthrich et al.",
    es_calc_method = "DiD emmeans",
    
    ppcor = NA,  
    ppcor_calc_method = "Not relevant",
    
    R2 = R2_imp,
    R2_calc_method = "Imputed",
    
    N_t = N[1],
    N_c = N[2],
    N_tot = sum(N),
    
    df_ind = N_tot,
    
    n_covariates = q[1],
    
    b_adj_emm = emm_post[1] - emm_post[2],
    
    # Reverting outcomes so all outcomes has the same direction
    b_adj_emm = if_else(unique(outcome) != "SF12", b_adj_emm * -1, b_adj_emm),
    
    dif_t_emm = emm_post[1] - emm_pre[1],
    dif_c_emm = emm_post[2] - emm_pre[2],
    
    
    DD_emm = dif_t_emm - dif_c_emm,
    # Reverting outcomes so all outcomes has the same direction
    DD_emm = if_else(unique(outcome) != "SF12", DD_emm * -1, DD_emm),
    sd_pool = sqrt(sum((N - 1) * sd_pre^2) / (N_tot-2)),
    
    d = DD_emm/sd_pool,
    vd = sum(1/N) + d^2/(2*df_ind),
    Wd = sum(1/N),
    
    d_alt = b_adj_emm/sd_pool,
    vd_alt = sum(1/N) + d_alt^2/(2*df_ind),
    Wd_alt = sum(1/N),
    
    J = 1 - 3/(4*df_ind-1),
    
    g = J * d,
    vg = sum(1/N) + g^2/(2*df_ind),
    Wg = Wd,
    
    g_alt = J * d_alt,
    vg_alt = sum(1/N) + g_alt^2/(2*df_ind),
    Wg_alt = sum(1/N),
    
    .by = outcome
    
  ) |> 
  mutate(
    
    # Average cluster size in treatment group
    # "in blocks of 8 participants." (2013, p. 781)
    avg_cl_size = 8, 
    avg_cl_type = "From study (2013, p. 781)",
    
    # Imputed icc value
    icc = ICC_01,
    icc_type = "Imputed",
    
    # Find info about the function via ?VIVECampbell::gamma_1armcluster
    gamma_sqrt = VIVECampbell::gamma_1armcluster(
      N_total = N_tot, Nc = N_c, avg_grp_size = avg_cl_size, ICC = icc
      ),
    gamma_sqrt_icc005 = gamma_1armcluster(
      N_total = N_tot, Nc = N_c, avg_grp_size = avg_cl_size, ICC = ICC_005
      ),
    gamma_sqrt_icc02 = gamma_1armcluster(
      N_total = N_tot, Nc = N_c, avg_grp_size = avg_cl_size, ICC = ICC_02
      ),
    
    gt = g * gamma_sqrt,
    VIVECampbell::vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = icc, 
      g = gt, 
      model = "emmeans",
      cluster_adj = TRUE,
      R2 = R2,
      q = n_covariates
      ),
    
    gt_icc005 = g * gamma_sqrt_icc005,
    vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = ICC_005, 
      g = gt_icc005, 
      model = "emmeans",
      cluster_adj = TRUE,
      R2 = R2,
      q = n_covariates,
      add_name_to_vars = "_icc005",
      vars = vgt_icc005:Wgt_icc005
      ),
    
    gt_icc02 = g * gamma_sqrt_icc02,
    vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = ICC_02, 
      g = gt_icc02, 
      model = "emmeans",
      cluster_adj = TRUE,
      R2 = R2,
      q = n_covariates,
      add_name_to_vars = "_icc02",
      vars = vgt_icc02:Wgt_icc02
      ),
    
    gt_alt = g_alt * gamma_sqrt,
    vgt_smd_1armcluster(
      N_cl_grp = N_t, 
      N_ind_grp = N_c, 
      avg_grp_size = avg_cl_size, 
      ICC = icc, 
      g = gt_alt, 
      model = "emmeans",
      cluster_adj = TRUE,
      R2 = R2,
      q = n_covariates,
      add_name_to_vars = "_alt",
      vars = vgt_alt:Wgt_alt
      ), 
    
    gt_alt_type = "Posttest emmeans",
    
    .by = outcome
    
  )

# Wuthrich2013_2021_es_smd

Wuthrich2013_2021_smd_est <- 
  left_join(Wuthrich2013_2021_wide, Wuthrich2013_2021_es_smd) |> 
  relocate(study, .before = outcome)

Wuthrich2013_2021_smd_est

#rm(Wuthrich2013_2021_wide, Wuthrich2013_2021_es_smd)

```

Calculating odds ratio effect sizes from Recovery rates reported in @Wuthrich2013[p.784]

```{r Wuthrich20132021ORcalc}

# Odd ratio based on recovery rates reported in Wuthrich 2013 (p. 784)

Wuthrich2013_OR_dat <- 
  tibble(
    study = "Wuthrich et al.",
    outcome = "Recovery rates",
    effect_size = "OR",
    es_calc_method = "Proportions",
    
    N_start_t = 27,
    N_start_c = 35,
    
    N_t = 20,
    N_c = 26,
    p_t = 0.53, 
    p_c = 0.11,
    
    # Average cluster size in treatment group
    # "in blocks of 8 participants." (2013, p. 781)
    avg_cl_size = 8, 
    avg_cl_type = "From study (2013, p. 781)",
    
    # Imputed icc value
    icc = ICC_01,
    icc_type = "Imputed",
    
    # OR calculation and cluster bias adjustment
    VIVECampbell::OR_calc(
      p1 = p_t, p2 = p_c, n1 = N_t, n2 = N_c, 
      ICC = icc, avg_cl_size = avg_cl_size, n_cluster_arms = 1
    ),
    
    # Calculating the sampling variance of the odds ratio based on ICC = 0.05
    OR_calc(
      p1 = p_t, p2 = p_c, n1 = N_t, n2 = N_c, 
      ICC = ICC_005, avg_cl_size = avg_cl_size, n_cluster_arms = 1,
      add_name_to_vars = "_icc005", vars = DE_icc005:vln_OR_C_icc005
    ),
    
    # Calculating the sampling variance of the odds ratio based on ICC = 0.2
    OR_calc(
      p1 = p_t, p2 = p_c, n1 = N_t, n2 = N_c, 
      ICC = ICC_02, avg_cl_size = avg_cl_size, n_cluster_arms = 1,
      add_name_to_vars = "_icc02", vars = DE_icc02:vln_OR_C_icc02
    )
    
    
  )

Wuthrich2013_OR_dat


# Amalgamating the SMD and OR results
Wuthrich2013_2021_est <- 
  bind_rows(Wuthrich2013_2021_smd_est, Wuthrich2013_OR_dat) |> 
  mutate(
    vary_id = outcome
  )

Wuthrich2013_2021_est

#rm(Wuthrich2013_2021_smd_est, Wuthrich2013_OR_dat)


```


## Amalgamation of data

Amalgamating effect size data

```{r, include=FALSE, eval=FALSE}

#select_across_df <- function(dataframes = list(), list_labels){
#  
#  map_dfr(dataframes, ~ select(., !!!list_labels))
#  
#}
#
## Extend variables
#var_label <- c(
#  "study", "es_method", "ppcor", "ppcor_type", "Nt", "Nc", "N_tot",
#  "df_ind", "d",  "vd", "Wd", "g", "vg", "Wg", # Continue here more variables are needed
#  "vary_id"
#)
#
#es_dat <- 
#  select_across_df(
#    list(
#      Timmermans2012_est
#    ),
#    
#    var_label
#
#); es_dat



```

Amalgating covariates and effect size data
```{r dataamalgamation, eval=FALSE}
#Remember to see working directory to "Group-based-interventions/ES calc"

covariates <- read_xlsx(
  "Descriptive coding scheme for group-based interventions (data).xlsx",
  na = c(".", "")
)


group_based_dat_es <- 
  bind_rows(
    Timmermans2012_est,
    Wuthrich2013_2021_est,
    Acarturk2022_est
  ) |> 
  relocate(sd_pool, .after = sd_used) |> 
  relocate(emm_pre_t:DD_emm, .after = se_b_adj_c)

group_based_dat <- 
  bind_cols(
    covariates,
    group_based_dat_es

)

write_xlsx(group_based_dat, "Group-based interventions data.xlsx")
save(group_based_dat, file = "Group-based interventions data.RData")

#clubSandwich::impute_covariance_matrix(
#  vi = group_based_dat$vgt,
#  cluster = group_based_dat$studyid,
#  r = c(.7, 0.1),
#  smooth_vi = TRUE
#)

```

```{r, eval=FALSE, include=FALSE}

test_dat <- covariates |> 
  filter(str_detect(authors, "Craigie")) |> 
  bind_cols(Craigie2009_est)

select(test_dat, varifier, vary_id)

```


## **Reference**




























