---
title: "Publication bias testing in Dalgaard et al. (2025)"
date: "Last updated `r format(Sys.time(), '%Y.%m.%d')`"
format:
  html:
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
#knitr::opts_chunk$set(eval = FALSE)

options(pillar.sigfig = 4) # ensure tibble include 4 digits
options(tibble.width = Inf)
options(dplyr.print_min = 310)
options(scipen = 10)
options(dplyr.summarise.inform = FALSE) # Avoids summarize info from tidyverse

library(DT)
library(kableExtra)

```

```{r, echo=FALSE}

library(tidyverse)
library(robvis)
library(purrr)
library(metafor)
library(patchwork)
library(clubSandwich)
library(wildmeta)
library(gt)
library(metaselection)

library(puniform)
library(tidyverse) # for tidying
library(janitor)   # for tidying variable names
library(boot)      # for bootstrapping
library(tictoc) 

# Loading in helper function used to calculate effect size and conduct the analysis
source_path <- if (isTRUE(getOption('knitr.in.progress'))) "Helpers.R" else "ES calc/Helpers.R"
source_path2 <- if (isTRUE(getOption('knitr.in.progress'))) "pub-bias-test-helpers.R" else "ES calc/pub-bias-test-helpers.R"

source(source_path)
source(source_path2)
```

```{r, warning = FALSE, message = FALSE, echo = FALSE}
# Loading data set
reint_dat <- 
  if (isTRUE(getOption('knitr.in.progress'))) {
    readRDS("reintergation_dat.rds")
  } else {
    readRDS("ES calc/reintergation_dat.rds")
  }
```
# Data
```{r, eval=FALSE}
reint_dat <- readRDS("ES calc/reintergation_dat.rds") 
reint_dat
```

## Select relevant variables

```{r}
reintergation_dat <- 
  reint_dat |> 
  mutate(esid = 1:n()) |> 
  select(
    study, eppi_id, esid, N_t, N_c, N_total, inv_sample_size, gt, vgt, Wgt, Wse, 
    prereg_chr, conventional, analysis_plan, Overall, D5, D7, timing
  )
```



```{r warning = FALSE, message = FALSE, echo = FALSE}
reintergation_dat |> 
  mutate(
    p_val = 2 * ( 1 - pnorm( abs(gt) / sqrt(Wgt) ) )
  ) |> 
  select(
    `Authors (year)` = study, N_t, N_c, `1/N_t + 1/N_c` = inv_sample_size,
    `Outcome construct` = analysis_plan, gt, vgt, Wgt, Wse, p_val, 
    `No protocol` = conventional, `Overall RoB` = Overall
  ) |> 
  kable(digits=3)  |> 
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    font_size = 10
  ) |> 
  scroll_box(width = "100%", height = "300px", fixed_thead = TRUE)
```

# Number of preregistered studies

```{r}
reintergation_dat |> 
  summarise(
    prereg_chr = unique(prereg_chr),
    n_es = n(),
    .by = study
  ) |> 
  summarise(
    N_studies = n_distinct(study),
    N_es = sum(n_es),
    .by = prereg_chr
  )
```


# Main Analyses

::: {.panel-tabset}

## Overall average effect
```{r}
reintegration_che_res <- .CHE_RVE(reintergation_dat) 

reintegration_che_res |> 
select(studies:UL, tau:sd_total, I2) |>
gt() |> 
fmt_number(columns = 3:9, decimals = 3) |> 
tab_header(
  title = "Overall average effect size",
  subtitle = "Across all reintegrational outcomes"
) 
```


## Subgroup effects (across type of outcome)
```{r}
reintegration_sce_res <- 
  .SCEp(mod = analysis_plan, data = reintergation_dat) 

reintegration_sce_res |> 
select(Moderator:pval) |> 
gt()|> 
fmt_number(columns = 4:10, decimals = 3) |> 
tab_header(
  title = "Overall average effect sizes",
  subtitle = "Across reintegrational subgroups"
) 
```

:::

# Funnel Plots

::: {.panel-tabset}

## Overall

```{r}

rho <- 0.8
# CHE pub bias
V_mat <- vcalc(Wgt, cluster = study, obs = esid, data = reintergation_dat, rho = rho)

W <- solve(V_mat)

optimizers <- c("nlminb","nloptr","Rvmmin","BFGS")
mod <- "Non-converged"
i <- 1L

while (!inherits(mod, "rma.mv") & i <= 4L) {
    mod <- tryCatch(
      rma.mv(
        yi = gt,
        V = V_mat,
        W = W,
        mods = ~ Wse,
        random = ~ 1 | study / esid,
        data = reintergation_dat,
        sparse = TRUE,
        control = list(optimizer=optimizers[i])
      ),
      error = function(e) "Non-converged"
    )
    i <- i + 1L
}

RE <- rma(yi = gt, vi = Wgt, data = reintergation_dat)

egg_res <- regtest(RE)
egg_res

mod_robu <- robust(mod, cluster = study, clubSandwich = TRUE) 
#mod_robu


overall_mean <- reintegration_che_res$avg_effect

y_lim_exp1 <- max(reintergation_dat$Wse) + 0.02 

funnel_exp1 <-  tribble(
  ~ x90, ~ x95, ~ x99, ~ y,
  0,     0,     0,     0,
  qnorm(0.05) * y_lim_exp1, qnorm(0.025) * y_lim_exp1, qnorm(0.005) * y_lim_exp1, y_lim_exp1,
  qnorm(0.95) * y_lim_exp1, qnorm(0.975) * y_lim_exp1, qnorm(0.995) * y_lim_exp1, y_lim_exp1,
  0,     0,     0,     0
) 

line1 <- "dashed"
alpha_line <- 0.5

#png("Funnel plot overall.png", height = 4.5, width = 7, unit = "in", res = 600)

.fp_plot(outcome_name = "Reintegrational")

#dev.off()
```

## Across outcome subgroups

```{r, eval = FALSE}

reintergation_dat |> 
ggplot() + 
geom_polygon(data = funnel_exp1, aes(x = y, y = x99), fill = "grey", alpha = 0.5) + 
geom_polygon(data = funnel_exp1, aes(x = y, y = x95), fill = "grey10", alpha = 0.5) + 
geom_polygon(data = funnel_exp1, aes(x = y, y = x90), fill = "lightcyan", alpha = 0.7) + 
geom_point(aes(Wse, gt, color = prereg_chr), alpha = 1, size = 1.2) +
scale_color_brewer(type = "qual", palette = 2) + 
coord_flip() + 
facet_wrap(~analysis_plan, scales = "free") +
scale_x_reverse(limits = c(y_lim_exp1, 0.0), expand = c(0,0)) + 
scale_y_continuous(breaks = seq(-3, 3, 1)) + 
theme_bw() + 
labs(x = "Standard error (adjusted)", 
     y = "Standardized mean difference (Hedges' g)", 
     color = "", shape = "") +
theme(legend.position = "bottom")

```


:::

# Preregistered vs. not-preregistered

::: {.panel-tabset}

## Alcohol and drug abuse/misuse

2

## Hope, Empowerment & Self-efficacy

3

## Social functioning (degree of impairment)

4

## Wellbeing and quality of life

5

::: 



 
# References
Dalgaard, N. T., Flensborg Jensen, M. C., Bengtsen, E., Krassel, K. F., & Vembye, M. H. (2025) Group‐based community interventions to support the social reintegration of marginalised adults with mental illness. A Systematic Review and meta-analysus. *Campbell Systematic Reviews*, 18(3), e1254. https://doi.org/10.1002/cl2.1254

::: {.callout-note icon=false appearance="simple" title="Session Information" collapse=true}

## Session Information

```{r}
#| code-fold: false
sessioninfo::session_info()
```

:::