---
title: "Publication bias testing in Dalgaard et al. (2025)"
date: "Last updated `r format(Sys.time(), '%Y.%m.%d')`"
format:
  html:
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
#knitr::opts_chunk$set(eval = FALSE)

options(pillar.sigfig = 4) # ensure tibble include 4 digits
options(tibble.width = Inf)
options(dplyr.print_min = 310)
options(scipen = 10)
options(dplyr.summarise.inform = FALSE) # Avoids summarize info from tidyverse

library(DT)
library(kableExtra)

```

```{r, echo=FALSE}

library(tidyverse)
library(robvis)
library(purrr)
library(metafor)
library(patchwork)
library(clubSandwich)
library(wildmeta)
library(gt)
library(metaselection)

library(puniform)
library(tidyverse) # for tidying
library(janitor)   # for tidying variable names
library(boot)      # for bootstrapping
library(tictoc) 

# Loading in helper function used to calculate effect size and conduct the analysis
source_path <- if (isTRUE(getOption('knitr.in.progress'))) "Helpers.R" else "ES calc/Helpers.R"
source_path2 <- if (isTRUE(getOption('knitr.in.progress'))) "pub-bias-test-helpers.R" else "ES calc/pub-bias-test-helpers.R"

source(source_path)
source(source_path2)
```

```{r, warning = FALSE, message = FALSE, echo = FALSE}
# Loading data set
reintergation_dat <- 
  if (isTRUE(getOption('knitr.in.progress'))) {
    readRDS("reintergation_dat.rds")
  } else {
    readRDS("ES calc/reintergation_dat.rds")
  }
```
# Data
```{r, eval=FALSE}
reintergation_dat <- readRDS("ES calc/reintergation_dat.rds") 
reintergation_dat
```

```{r warning = FALSE, message = FALSE, echo = FALSE}
reintergation_dat |> 
  mutate(
    p_val = 2 * ( 1 - pnorm( abs(gt) / sqrt(Wgt) ) )
  ) |> 
  select(
    `Authors (year)` = author_year, N_t, N_c, `1/N_t + 1/N_c` = inv_sample_size,
    `Outcome construct` = analysis_plan, gt, vgt, Wgt, Wse, p_val, 
    `No protocol` = conventional, `Overall RoB` = Overall
  ) |> 
  kable(digits=3)  |> 
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    font_size = 10
  ) |> 
  scroll_box(width = "100%", height = "300px", fixed_thead = TRUE)
```

# Number of preregistered studies

```{r}
reintergation_dat |> 
  summarise(
    prereg_text = unique(prereg_text),
    n_es = n(),
    .by = author_year
  ) |> 
  summarise(
    N_studies = n_distinct(author_year),
    N_es = sum(n_es),
    .by = prereg_text
  )
```


# Main Analyses

::: {.panel-tabset}

## Overall average effect
```{r}
reintegration_che_res <- .CHE_RVE(reintergation_dat) 

reintegration_che_res |> 
select(studies:UL, tau:sd_total, I2) |>
gt() |> 
fmt_number(columns = 3:9, decimals = 3) |> 
tab_header(
  title = "Overall average effect size",
  subtitle = "Across all reintegrational outcomes"
) 
```


## Subgroup effects (across type of outcome)
```{r}
reintegration_sce_res <- 
  .SCEp(mod = analysis_plan, data = reintergation_dat) 

reintegration_sce_res |> 
select(Moderator:pval) |> 
gt()|> 
fmt_number(columns = 4:10, decimals = 3) |> 
tab_header(
  title = "Overall average effect sizes",
  subtitle = "Across reintegrational subgroups"
) 
```

:::

# Funnel Plots

::: {.panel-tabset}

## Overall

```{r}

rho <- 0.7
# CHE pub bias
V_mat <- vcalc(Wgt, cluster = author_year, obs = esid, data = reintergation_dat, rho = rho)

W <- solve(V_mat)

optimizers <- c("nlminb","nloptr","Rvmmin","BFGS")
mod <- "Non-converged"
i <- 1L

while (!inherits(mod, "rma.mv") & i <= 4L) {
    mod <- tryCatch(
      rma.mv(
        yi = gt,
        V = V_mat,
        W = W,
        mods = ~ Wse,
        random = ~ 1 | author_year / esid,
        data = reintergation_dat,
        sparse = TRUE,
        control = list(optimizer=optimizers[i])
      ),
      error = function(e) "Non-converged"
    )
    i <- i + 1L
}

RE <- rma(yi = gt, vi = Wgt, data = reintergation_dat)

egg_res <- regtest(RE)
egg_res

mod_robu <- robust(mod, cluster = author_year, clubSandwich = TRUE) 
#mod_robu


overall_mean <- reintegration_che_res$avg_effect

y_lim_exp1 <- max(reintergation_dat$Wse) + 0.02 

funnel_exp1 <-  tribble(
  ~ x90, ~ x95, ~ x99, ~ y,
  0,     0,     0,     0,
  qnorm(0.05) * y_lim_exp1, qnorm(0.025) * y_lim_exp1, qnorm(0.005) * y_lim_exp1, y_lim_exp1,
  qnorm(0.95) * y_lim_exp1, qnorm(0.975) * y_lim_exp1, qnorm(0.995) * y_lim_exp1, y_lim_exp1,
  0,     0,     0,     0
) 

line1 <- "dashed"
alpha_line <- 0.5

#png("Funnel plot overall.png", height = 4.5, width = 7, unit = "in", res = 600)

.fp_plot(outcome_name = "Reintegrational")

#dev.off()
```

## Across outcome subgroups

```{r, eval = FALSE}

reintergation_dat |> 
ggplot() + 
geom_polygon(data = funnel_exp1, aes(x = y, y = x99), fill = "grey", alpha = 0.5) + 
geom_polygon(data = funnel_exp1, aes(x = y, y = x95), fill = "grey10", alpha = 0.5) + 
geom_polygon(data = funnel_exp1, aes(x = y, y = x90), fill = "lightcyan", alpha = 0.7) + 
geom_point(aes(Wse, gt, color = factor(conventional)), alpha = 1, size = 1.2) +
scale_color_brewer(type = "qual", palette = 2) + 
coord_flip() + 
facet_wrap(~analysis_plan, scales = "free") +
scale_x_reverse(limits = c(y_lim_exp1, 0.0), expand = c(0,0)) + 
scale_y_continuous(breaks = seq(-3, 3, 1)) + 
theme_bw() + 
labs(x = "Standard error (adjusted)", 
     y = "Standardized mean difference (Hedges' g)", 
     color = "", shape = "") +
theme(legend.position = "bottom")

```


:::

# Preregistered vs. not-preregistered

::: {.panel-tabset}

## Alcohol and drug abuse/misuse

2

## Hope, Empowerment & Self-efficacy

3

## Social functioning (degree of impairment)

4

## Wellbeing and quality of life

5

::: 

# Play 

## Overall average effect
```{r}
# CHE-ISCW
V_mat <- metafor::vcalc(vi = Wgt, cluster = author_year, obs = es_id, data = reintergation_dat, rho = 0.7)

W <- solve(V_mat)

# CHE
che <- 
  rma.mv(
    yi = gt,
    V = V_mat,
    random = ~ 1 | author_year / es_id,
    data = reintergation_dat,
    sparse = TRUE
) |> 
  robust(cluster = author_year, clubSandwich = TRUE)

# ISCW


# CHE-ISCW-RVE
che_iscw <- rma.mv(
  yi = gt,
  V = V_mat,
  W = W,
  mods = ~ Wse,
  random = ~ 1 | author_year / es_id,
  data = reintergation_dat,
  sparse = TRUE
) |> 
  robust(cluster = author_year, clubSandwich = TRUE)
```

## Preregistered vs. not preregistered 
```{r}

prereg_dat <-  
  reintergation_dat |> 
  filter(conventional == 0)

V_mat_prereg <- metafor::vcalc(vi = Wgt, cluster = author_year, obs = es_id, data = prereg_dat, rho = 0.7)

W_prereg <- solve(V_mat_prereg)

egg_prereg <-
  rma.mv(
  yi = gt,
  V = V_mat_prereg,
  W = W_prereg,
  mods = ~ Wse,
  random = ~ 1 | author_year / es_id,
  data = prereg_dat,
  sparse = TRUE
) |> 
  robust(cluster = author_year, clubSandwich = TRUE)

egg_prereg_res <- 
  tibble(
    subgroup = "Preregistered",
    egg_intercept = as.numeric(egg_prereg$b[1]),
    egg_slope = as.numeric(egg_prereg$b[2])
  )

notprereg_dat <-  
  reintergation_dat |> 
  filter(conventional == 1)


V_mat_notprereg <- metafor::vcalc(vi = Wgt, cluster = author_year, obs = es_id, data = notprereg_dat, rho = 0.7)

W_notprereg <- solve(V_mat_notprereg)

egg_notprereg <-
  rma.mv(
  yi = gt,
  V = V_mat_notprereg,
  W = W_notprereg,
  mods = ~ Wse,
  random = ~ 1 | author_year / es_id,
  data = notprereg_dat,
  sparse = TRUE
) |> 
  robust(cluster = author_year, clubSandwich = TRUE)


egg_notprereg_res <- 
  tibble(
    subgroup = "Not preregistered",
    egg_intercept = as.numeric(egg_notprereg$b[1]),
    egg_slope = as.numeric(egg_notprereg$b[2])
  )

egg_res_subgrouped <- bind_rows(egg_prereg_res, egg_notprereg_res)
egg_res_subgrouped

# SCEp+ 
subgroup_means <- .SCEp(mod = prereg_text, data = reintergation_dat)

subgroup_dat <- 
  reintergation_dat |> 
  summarise(
    gt = mean(gt),
    Wse = mean(Wse),
    analysis_plan = analysis_plan[1],
    .by = prereg_text
  ) |> 
  bind_cols(subgroup_means[2:3,], egg_res_subgrouped) |> 
  mutate(slope_low = qnorm(0.025), slope_high = qnorm(0.975), level = "Effect size level") 
  


y_lim_exp1 <- max(reintergation_dat$Wse) + 0.02 
y_lim_exp1  

funnel_exp1 <-  tribble(
  ~ x90, ~ x95, ~ x99, ~ y,
  0,     0,     0,     0,
  qnorm(0.05) * y_lim_exp1, qnorm(0.025) * y_lim_exp1, qnorm(0.005) * y_lim_exp1, y_lim_exp1,
  qnorm(0.95) * y_lim_exp1, qnorm(0.975) * y_lim_exp1, qnorm(0.995) * y_lim_exp1, y_lim_exp1,
  0,     0,     0,     0
) 


  
alpha_line <- 0.5
polygon_fill <- c("grey", "grey10", "lightcyan")
mean_line <- "dashed"
reg_test <- TRUE
reg_line <- "longdash"
reg_color <- "blue"
breaks_y <- seq(-3, 3, 0.5)


es_level_fp <- 
  reintergation_dat |> 
  mutate(level = "Effect size level") |> 
  ggplot() + 
  geom_polygon(data = funnel_exp1, aes(x = y, y = x99), fill = polygon_fill[1], alpha = 0.5) + 
  geom_polygon(data = funnel_exp1, aes(x = y, y = x95), fill = polygon_fill[2], alpha = 0.5) + 
  geom_polygon(data = funnel_exp1, aes(x = y, y = x90), fill = polygon_fill[3], alpha = 0.7) + 
  geom_abline(data = subgroup_dat, aes(slope = slope_high, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_hline(data = subgroup_dat, aes(yintercept = avg_effect), linetype = mean_line, alpha = alpha_line) +  
  geom_abline(data = subgroup_dat, aes(slope = slope_low, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_abline(data = subgroup_dat, aes(slope = -egg_slope, intercept = egg_intercept), linetype = reg_line, color = reg_color) +
  geom_point(aes(Wse, gt, col = analysis_plan), alpha = 1, size = 1.2) +
  scale_color_brewer(type = "qual", palette = 2) + 
  coord_flip() +
  facet_grid(level~prereg_text) +
  scale_x_reverse(limits = c(y_lim_exp1, 0.0), expand = c(0,0)) + 
  scale_y_continuous(breaks = breaks_y) + 
  theme_bw() + 
  labs(x = "Standard error (modified)", 
       y = "Standardized mean difference (Hedges' g)", 
       color = "", shape = "") +
  theme(
    legend.position = "bottom",
    strip.text.x = element_blank()
    ) +
  labs(color = "Outcome") +
  guides(col = guide_legend(nrow = 2))

# Make aggregate plot

reintergation_dat_agg <- 
  reintergation_dat |> 
  escalc(measure = "SMD", yi = gt, vi = Wgt, data = _) |> 
  aggregate.escalc(cluster = author_year, rho = 0.7) |> 
  mutate(
    Wse = sqrt(vi)
  )

prereg_dat_agg <-  
  reintergation_dat_agg |> 
  as_tibble() |> 
  dplyr::filter(conventional == 0)

egg_prereg_agg <- 
  rma(yi = yi, vi = vi, data = prereg_dat_agg) |> 
  regtest()

egg_prereg_agg_res <- 
  tibble(
    subgroup = "Preregistered",
    egg_intercept = as.numeric(egg_prereg_agg$fit$b[1]),
    egg_slope = as.numeric(egg_prereg_agg$fit$b[2])
  )

notprereg_dat_agg <-  
  reintergation_dat_agg |> 
  as_tibble() |> 
  dplyr::filter(conventional == 1)

egg_notprereg_agg <- 
  rma(yi = yi, vi = vi, data = notprereg_dat_agg) |> 
  regtest()

egg_notprereg_agg_res <- 
  tibble(
    subgroup = "Not preregistered",
    egg_intercept = as.numeric(egg_notprereg_agg$fit$b[1]),
    egg_slope = as.numeric(egg_notprereg_agg$fit$b[2])
  )

egg_res_agg_subgrouped <- bind_rows(egg_notprereg_agg_res, egg_prereg_agg_res)
egg_res_agg_subgrouped

means_agg <- 
  rma(yi, vi, mods = ~ -1 +prereg_text, data = reintergation_dat_agg) |> 
  robust(cluster = author_year, clubSandwich = TRUE)

subgroup_means_agg <- 
  tibble(
    Moderator = c("Not preregistered", "Preregistered"),
    avg_effect = as.numeric(means_agg$b), 
    LL = as.numeric(means_agg$ci.lb), 
    UL = as.numeric(means_agg$ci.ub)
  )

subgroup_dat_agg <- 
  reintergation_dat_agg |> 
  summarise(
    gt = mean(gt),
    Wse = mean(Wse),
    analysis_plan = analysis_plan[1],
    .by = prereg_text
  ) |> 
  arrange(prereg_text) |> 
  bind_cols(subgroup_means_agg, egg_res_agg_subgrouped) |> 
  mutate(slope_low = qnorm(0.025), slope_high = qnorm(0.975), level = "Study level") 


#subgroup_dat <- 
#  reintergation_dat |> 
#  summarise(
#    gt = mean(gt),
#    Wse = mean(Wse),
#    analysis_plan = analysis_plan[1],
#    .by = prereg_text
#  ) |> 
#  bind_cols(subgroup_means[2:3,], egg_res_subgrouped) |> 
#  mutate(slope_low = qnorm(0.025), slope_high = qnorm(0.975), level = "Effect size level") 
  


y_lim_exp2 <- max(reintergation_dat_agg$Wse) + 0.02 
y_lim_exp2  

funnel_exp2 <-  tribble(
  ~ x90, ~ x95, ~ x99, ~ y,
  0,     0,     0,     0,
  qnorm(0.05) * y_lim_exp2, qnorm(0.025) * y_lim_exp2, qnorm(0.005) * y_lim_exp2, y_lim_exp2,
  qnorm(0.95) * y_lim_exp2, qnorm(0.975) * y_lim_exp2, qnorm(0.995) * y_lim_exp2, y_lim_exp2,
  0,     0,     0,     0
) 

study_level_fp <- 
  reintergation_dat_agg |> 
  mutate(level = "Study level") |> 
  ggplot() + 
  geom_polygon(data = funnel_exp2, aes(x = y, y = x99), fill = polygon_fill[1], alpha = 0.5) + 
  geom_polygon(data = funnel_exp2, aes(x = y, y = x95), fill = polygon_fill[2], alpha = 0.5) + 
  geom_polygon(data = funnel_exp2, aes(x = y, y = x90), fill = polygon_fill[3], alpha = 0.7) + 
  geom_abline(data = subgroup_dat_agg, aes(slope = slope_high, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_hline(data = subgroup_dat_agg, aes(yintercept = avg_effect), linetype = mean_line, alpha = alpha_line) +  
  geom_abline(data = subgroup_dat_agg, aes(slope = slope_low, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_abline(data = subgroup_dat_agg, aes(slope = -egg_slope, intercept = egg_intercept), linetype = reg_line, color = reg_color) +
  geom_point(aes(Wse, gt), alpha = 1, size = 1.2) +
  scale_color_brewer(type = "qual", palette = 2) + 
  coord_flip() +
  facet_grid(level~prereg_text) +
  scale_x_reverse(limits = c(y_lim_exp2, 0.0), expand = c(0,0)) + 
  scale_y_continuous(breaks = breaks_y) + 
  theme_bw() +
  theme(
    axis.title = element_blank()
  )

ylab <- es_level_fp$labels$x

study_level_fp$labels$x <- es_level_fp$labels$x <- "" 

#png("plots/funnel plots (overall effect) across prereg.png", width = 8, height = 5.5, res = 300, unit = "in")
study_level_fp / es_level_fp
grid::grid.draw(grid::textGrob(ylab, y = 0.6, x = 0.02, rot = 90))
#dev.off()
```

### Investigating the impact of Cano-Vindel et al.

```{r}
prereg_dat_cano <-  
  reintergation_dat |> 
  filter(conventional == 0) |>
  mutate(
    cano_vindel = if_else(str_detect(author_year, "Cano"), 1, 0),
    cano_vindel = factor(cano_vindel)
  )

V_mat_prereg_cano <- metafor::vcalc(vi = Wgt, cluster = author_year, obs = es_id, data = prereg_dat_cano, rho = 0.7)

W_prereg_cano <- solve(V_mat_prereg_cano)

egg_prereg_cano <-
  rma.mv(
  yi = gt,
  V = V_mat_prereg_cano,
  W = W_prereg_cano,
  mods = ~ Wse + cano_vindel,
  random = ~ 1 | author_year / es_id,
  data = prereg_dat_cano,
  sparse = TRUE
) |> 
  robust(cluster = author_year, clubSandwich = TRUE)

egg_prereg_res_cano <- 
  tibble(
    subgroup = "Preregistered",
    egg_intercept = as.numeric(egg_prereg_cano $b[1]),
    egg_slope = as.numeric(egg_prereg_cano$b[2])
  )

subgroup_means <- .SCEp(mod = prereg_text, data = reintergation_dat)

subgroup_dat_cano <- 
  prereg_dat_cano |> 
  summarise(
    gt = mean(gt),
    Wse = mean(Wse),
    analysis_plan = analysis_plan[1],
    .by = prereg_text
  ) |> 
  bind_cols(subgroup_means[3,], egg_prereg_res_cano) |> 
  mutate(slope_low = qnorm(0.025), slope_high = qnorm(0.975)) 
  


y_lim_exp_cano <- max(prereg_dat_cano$Wse) + 0.02 
y_lim_exp_cano  

funnel_exp_cano <-  tribble(
  ~ x90, ~ x95, ~ x99, ~ y,
  0,     0,     0,     0,
  qnorm(0.05) * y_lim_exp_cano, qnorm(0.025) * y_lim_exp_cano, qnorm(0.005) * y_lim_exp_cano, y_lim_exp_cano,
  qnorm(0.95) * y_lim_exp_cano, qnorm(0.975) * y_lim_exp_cano, qnorm(0.995) * y_lim_exp_cano, y_lim_exp_cano,
  0,     0,     0,     0
) 


  
alpha_line <- 0.5
polygon_fill <- c("grey", "grey10", "lightcyan")
mean_line <- "dashed"
reg_test <- TRUE
reg_line <- "longdash"
reg_color <- "blue"
breaks_y <- seq(-3, 3, 0.5)


cano_fp <- 
  prereg_dat_cano |> 
  mutate(alpha_val = if_else(cano_vindel == 1, 0.9, 1)) |>
  ggplot() + 
  geom_polygon(data = funnel_exp_cano, aes(x = y, y = x99), fill = polygon_fill[1], alpha = 0.5) + 
  geom_polygon(data = funnel_exp_cano, aes(x = y, y = x95), fill = polygon_fill[2], alpha = 0.5) + 
  geom_polygon(data = funnel_exp_cano, aes(x = y, y = x90), fill = polygon_fill[3], alpha = 0.7) + 
  geom_abline(data = subgroup_dat_cano, aes(slope = slope_high, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_hline(data = subgroup_dat_cano, aes(yintercept = avg_effect), linetype = mean_line, alpha = alpha_line) +  
  geom_abline(data = subgroup_dat_cano, aes(slope = slope_low, intercept = avg_effect), linetype = mean_line, alpha = alpha_line) + 
  geom_abline(data = subgroup_dat_cano, aes(slope = -egg_slope, intercept = egg_intercept), linetype = reg_line, color = reg_color) +
  geom_point(aes(Wse, gt, col = cano_vindel, alpha = alpha_val), size = 1.5) +
  scale_color_brewer(type = "qual", palette = 2) + 
  coord_flip() +
  facet_grid(~prereg_text) +
  scale_x_reverse(limits = c(y_lim_exp_cano, 0.0), expand = c(0,0)) + 
  scale_y_continuous(breaks = breaks_y) + 
  theme_bw() + 
  labs(x = "Standard error (modified)", 
       y = "Standardized mean difference (Hedges' g)", 
       color = "", shape = "") +
  theme(
    legend.position = "bottom"
    ) +
  labs(color = "Cano-vindel") +
  guides(col = "none", alpha = "none")

png("plots/funnel plots (overall effect) without Cano-Vindel.png", width = 8, height = 5.5, res = 300, unit = "in")
cano_fp
dev.off()
```

# van Aert methods
See van Aert [(2025)](https://psycnet.apa.org/fulltext/2025-81751-001.html)
## Overall effect correcting for publication bias in not-preregistered studies only

```{r}

```


## Subgroup effects correcting for publication bias in not-preregistered studies only


# Checking variance estimate vs. sample size
```{r}
 
reintergation_dat |> 
mutate(
  gt_above_05 = if_else(gt > 0.5, "g > 0.5", "g < 0.5"),
  gt_above_05 = factor(gt_above_05, levels = c("g > 0.5", "g < 0.5"))
  ) |> 
ggplot(aes(Wgt, vgt, color = gt_above_05)) + 
geom_point() +
geom_abline(intercept = 0, slope = 1) +
theme_bw() +
theme(
  plot.caption=element_text(hjust = 0, size = 10),
  legend.position= "bottom",
  legend.title = element_blank(),
  panel.spacing.x = unit(5, "mm"), 
  panel.spacing.y = unit(5, "mm"),
  #panel.grid.major = element_blank(),
  #panel.grid.minor = element_blank()
 ) +
scale_x_continuous(expand=c(0,0), breaks = seq(0L, 1L, 0.1)) + 
scale_y_continuous(expand=c(0,0), breaks = seq(0L, 1L, 0.1)) + 
expand_limits(x = c(0L, 0.5), y = c(0L, 0.5))


reintergation_dat |> 
ggplot(aes(N_total, Wse)) + 
geom_point() + 
theme_bw()

```


 
# References
Dalgaard, N. T., Flensborg Jensen, M. C., Bengtsen, E., Krassel, K. F., & Vembye, M. H. (2025) Group‐based community interventions to support the social reintegration of marginalised adults with mental illness. A Systematic Review and meta-analysus. *Campbell Systematic Reviews*, 18(3), e1254. https://doi.org/10.1002/cl2.1254

::: {.callout-note icon=false appearance="simple" title="Session Information" collapse=true}

## Session Information

```{r}
#| code-fold: false
sessioninfo::session_info()
```

:::